### 2024-02-09 paper.tex
Download sample files and set up development environment

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc.\ does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

\subsubsection{Acknowledgements} Please place your acknowledgments at
the end of the paper, preceded by an unnumbered run-in heading (i.e.
3rd-level heading).

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2024-02-09 enter_container.sh

@@ -1,0 +1,6 @@
+#!/usr/bin/bash
+
+docker compose up -d
+xhost +local:
+docker compose exec latex bash
+xhost -local:

### 2024-02-09 paper.tex
Add submodule MyRef and work on paper

@@
 %
-\title{Contribution Title\thanks{Supported by organization x.}}
+\title{R-LIME: Rectangular Constraints and Optimization for Local Interpretable
+Model-agnostic Explanation Methods\thanks{Supported by organization x.}}
 %
@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+\author{Genji Ohara\inst{1}\orcidID{0000-1111-2222-3333} \and
+Keigo Kimura\inst{2,3}\orcidID{1111-2222-3333-4444} \and
+Mineichi Kudo\inst{3}\orcidID{2222--3333-4444-5555}}
 %
-\authorrunning{F. Author et al.}
+\authorrunning{G. Ohara et al.}
 % First names are abbreviated in the running head.
@@
 %
+% The abstract should briefly summarize the contents of the paper in
+% 150--250 words.
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+    In recent years, complex machine learning models such as deep neural network or random forests are used in many situations because of their high accuracy.
+    However, complexity of the models leads to difficulty for introducing them in sensitive context because users cannot understand the reason why the models output the specific results.
+    We propose a new method to generate explanations about the complex classifier and its particular output, that is called R-LIME.
+    R-LIME approximizes a complex decision boundary by a linear classifier locally and maximizes the approximation region as long as the accuracy of the linear model is higher than given threshold.
+% 102 words
+\keywords{Interpretable machine learning \and Local surrogate model}
+\end{abstract}
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
-\end{abstract}
-%
-%
-%
-\section{First Section}
+\section{Introduction}
+In recent years, complex machine learning models such as deep neural network or random forests are used in many situations because of their high accuracy.
+However, complexity of the models leads to difficulty for introducing them in sensitive context because users cannot understand the reason why the models output the specific results.
+To solve this problem, many explanation methods have been proposed.
+
+In this paper, we focus on local and model-agnostic explanation methods.
+LIME (Local Interpretable Model-agnostic Explanation) \cite{ribeiro2016why} is one of the most popular explanation methods.
+LIME approximizes a complex decision boundary by a linear classifier locally.
+But users cannot evaluate generality of LIME explanations because it does not provide the approximation region.
+To solve this problem, we propose a new method, R-LIME.
+R-LIME approximizes a complex decision boundary by a linear classifier locally and maximizes the approximation region as long as the accuracy of the linear model is higher than given threshold.
+Moreover, R-LIME provides the approximation region as conjunction of predicates, that is called anchor \cite{ribeiro2018anchors}.
+\section{Related Works}
+\subsection{LIME}
+\subsection{Anchor}
+\subsection{BELLA}
+\section{Proposed Method}
+\subsection{Overview}
+\subsection{Algorithm}
+\section{Experiments}
+\subsection{Qualitative Evaluation}
+\subsection{Quantitative Evaluation}
+\section{Future Works}
+\section{Conclusion}
 \subsection{A Subsection Sample}
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
+\bibliographystyle{splncs04}
+\bibliography{MyRef/ref}
 %

### 2024-02-13 paper.tex
Work on paper

--- 2024-02-09 paper.tex
@@
 %
+
+% We import package amsmath before the documentclass to avoid the warning.
+% Command '\usepackage{amsmath}' results in the following warning:
+% Package amsmath Warning: Unable to redefine math accent \vec.
+\RequirePackage{amsmath} % for environments such as align
+
 \documentclass[runningheads]{llncs}
@@
 %
+
+\usepackage{amssymb} % for \mathbb
+\usepackage{cleveref} % for \cref
+\usepackage{bbm} % for \mathbbm
+\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
+\usepackage{pgffor} % for \foreach
+\usepackage{csvsimple} % for \csvreader
+\usepackage{array} % for m column type
+
+% Fig. 1a -> Fig. 1(a)
+\usepackage[labelformat=simple]{subcaption}
+\graphicspath{{./data/}{./python/data/}}
+\renewcommand\thesubfigure{(\alph{subfigure})}
+\makeatletter
+\def\caption@documentclass{elsarticle}%
+\makeatother
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+
+\input{macro}
+
 \begin{document}
 %
-\title{Contribution Title\thanks{Supported by organization x.}}
+\title{%
+  R-LIME: Rectangular Constraints and Optimization for Local Interpretable
+  Model-agnostic Explanation Methods}
 %
-%\titlerunning{Abbreviated paper title}
+\titlerunning{%
+  R-LIME: Rectangular Constraints and Optimization for LIME Methods
+}
 % If the paper title is too long for the running head, you can set
@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+\author{Genji Ohara\inst{1}\orcidID{0009-0000-5854-2820} \and
+  Keigo Kimura\inst{1}\orcidID{0000-0002-3614-6568} \and
+  Mineichi Kudo\inst{1}\orcidID{0000-0003-1013-3870}
+}
 %
-\authorrunning{F. Author et al.}
+\authorrunning{G. Ohara et al.}
 % First names are abbreviated in the running head.
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
-%
+\institute{Division of Computer Science and Information Technology\\
+  Graduate School of Information Sci.\ and Tech.,
+  Hokkaido University\\
+  Sapporo 060-0814, JAPAN,\\
+  \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}
+
 \maketitle              % typeset the header of the contribution
 %
+% The abstract should briefly summarize the contents of the paper in
+% 150--250 words.
+
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+  In recent years, complex machine learning models such as deep neural networks
+  have been used in various industrial fields due to their high accuracy.
+  However, its complexity has been a major obstacle to implementation
+  in decision-making situations where transparency of the decision process is required.
+  In order to solve this problem,
+  various post-hoc explanation methods have been proposed,
+  but they have not been able to achieve interpretability of
+  both the explanation and its scope.
+  We propose a new method that interprets complex models in an interpretable
+  approximation region.
+  R-LIME locally approximizes a complex decision boundary with a linear classifier
+  and maximizes the approximation region as long as the accuracy of the linear
+  model is higher than a specified threshold.
+  We demonstrate the effectiveness of the proposed method through a qualitative
+  and quantitative evaluation using a real-world dataset.
+  Finally, we discuss limitations and future work of the proposed method.
+  % 148 words
+  \keywords{Interpretable machine learning \and Local surrogate model}
+\end{abstract}
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
-\end{abstract}
+\section{Introduction}
+Machine learning models, such as deep learning and random forests,
+have been widely employed in various industrial applications
+due to their significant improvement in accuracy in recent years.
+However,
+the increasing complexity and black-box nature of these models pose challenges,
+particularly in critical decision-making scenarios like healthcare and finance,
+where the opacity of decision rationale becomes a major obstacle to 
+implementation.
+Consequently,
+there has been extensive research in the field of post hoc explanation
+for machine learning models \cite{%
+  ribeiro2016why,ribeiro2018anchors,radulovic2023bella,guidotti2018local}.
+
+Existing studies on post hoc explanations categorize into model-dependent and
+model-agnostic methods,
+depending on their dependence on the model's structure.
+Model-dependent methods primarily focus on deep neural networks and
+explain the model's behavior using internal parameters.
+While they allow a direct approach to the model, 
+applying the same method to models with different structures is often challenging.
+On the other hand, model-agnostic methods do not rely on internal parameters and utilize only the model's output.
+Although they provide high generality, their information is constrained, making them more versatile.
+Model-agnostic methods further classify into global and local methods based on their treatment of input space.
+Global methods aim to explain the model's behavior across the entire input space, seeking explanations valid for any input.
+However, providing global explanations becomes challenging as the model's complexity increases.
+Local methods, in contrast, explain the model's output for a specific input (focus point) in the vicinity of that input.
+While local methods offer simple and accurate explanations compared to global methods, their applicability is limited.
+
+This paper specifically focuses on model-agnostic and local methods.
+For instance, Local Interpretable Model-agnostic Explanations (LIME) \cite{ribeiro2016why} approximates the complex model's decision boundary locally using a simpler model.
+Although LIME enables users to interpret the local behavior of complex models, it has been criticized for not optimizing the approximation region \cite{radulovic2023bella} and not presenting the approximation region in an interpretable form \cite{ribeiro2018anchors}.
+
+To address the limitations of LIME,
+we propose an algorithm that interprets complex models
+in an interpretable approximation region,
+taking inspiration from another explanation method called Anchor
+\cite{ribeiro2018anchors}.
+Our proposed method maximizes the accuracy of the learned approximation model
+within a rectangular approximation region under lower-bound constraints.
+The resulting rectangular region is expressed as a conjunction of predicates
+related to features, enhancing interpretability for the user.
+
+\section{Related Work}
+The figures presented visually compare three methods: LIME, Anchor, and BELLA.
+
+\begin{figure}[t]
+  \vspace{0.5cm}
+  \begin{subfigure}[t]{\textwidth}
+    \centering
+    \includegraphics[width=0.55\textwidth]{lime_vs_anchor_exp_a.png}
+    \caption{Instance around the focal point.}\label{fig:lime_vs_anchor_exp_a}
+    \vspace{0.5cm}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\textwidth}
+    \centering
+    \includegraphics[width=0.4\textwidth]{lime_vs_anchor_exp_b.png}
+    \caption{Explanation by LIME.}\label{fig:lime_vs_anchor_exp_b}
+    \vspace{0.5cm}
+  \end{subfigure}
+  \begin{subfigure}[t]{\textwidth}
+    \centering
+    \includegraphics[width=0.55\textwidth]{lime_vs_anchor_exp_c.png}
+    \caption{Explanation by Anchor.}\label{fig:lime_vs_anchor_exp_c}
+  \end{subfigure}
+  \caption[Examples of output results by LIME and Anchor]{Examples of output results by LIME and Anchor \cite{ribeiro2018anchors}.}\label{fig:lime_vs_anchor_exp}
+\end{figure}
+In this chapter, we provide an overview of existing research on model-agnostic and local post hoc explanations, particularly focusing on studies closely related to the proposed method.
+
+\subsection{LIME (Local Interpretable Model-agnostic Explanations) \cite{ribeiro2016why}}
+LIME is a method for locally approximating a trained black-box classifier $f: \mathbb{R}^d \to \{0,1\}$ around a focal point $x \in \mathbb{R}^d$ using a linear model $g: \mathbb{R}^d \to \{0,1\}$ (\cref{fig:lime}).
+The process involves:
+\begin{enumerate}
+  \item Obtaining a set of perturbed samples $\mathcal{Z}_p$ around $x$ and the set of pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
+  \item Learning an interpretable model $g$ using $\mathcal{Z}_p$ and $f(\mathcal{Z}_p)$ by minimizing the following loss function:
+        \begin{equation}
+          \label{eq:lime_loss}
+          \mathcal{L}(f,g,\pi_x)=\sum_{z\in\mathcal{Z}_p}
+          \pi_x(z){\left(f(z)-g(z)\right)}^2,
+        \end{equation}
+        where $\pi_x(z)$ is a weight function designed to be larger for samples closer to $x$, typically implemented using an exponential kernel.
+\end{enumerate}
+
+LIME provides valuable insights into the local behavior of the model by showing the contribution of each feature to the output $f(x)$.
+However, due to not explicitly indicating the perturbation region, users cannot assess the effective scope of the explanation \cite{ribeiro2018anchors}.
+An example explanation for an LSTM sentiment prediction model using LIME is illustrated in \cref{fig:lime_vs_anchor_exp_b}.
+The left explanation suggests that the word "not" contributes to the model's positive prediction, which does not apply to the instance on the right.
+However, without the explicit perturbation region, users might mistakenly apply the left explanation to the right instance, potentially leading to a misunderstanding of the black-box model's behavior \cite{ribeiro2018anchors}.
+
+\subsection{Anchor \cite{ribeiro2018anchors}}\label{sec:anchor}
+Anchor represents a rectangular region, expressed as a conjunction of predicates (rules) related to features, that maximizes the probability of the black-box classifier $f$ outputting $f(x)$ within the region.
+It aims to highlight important features contributing significantly to the output (\cref{fig:anchor}).
+
+For a discrete $m$-dimensional input space $\ispace$ with a trained black-box classifier $f: \ispace \to \{0,1\}$, an instance $x \in \ispace$, and a distribution $\mathcal{D}$ over the input space, a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
+The predicates $a_i(z)$ evaluate to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
+The precision $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
+\begin{align}
+  \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
+  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor_def_prec} \\
+  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)].
+\end{align}
+
+Here, $\mathcal{D}(z|A)$ is the conditional distribution in the region where the rule $A$ is true.
+% When sampling the perturbation vector $z$ according to the distribution $\mathcal{D}$,
+$\Prec(A)$ represents the probability that the output of $f$ matches between the perturbation $z$ and the focal point $x$ in the region $A$, and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
+
+An Anchor maximizes coverage within the given threshold $\tau$ while maintaining precision.
+However, direct computation of \cref{eq:anchor_def_prec} is not feasible, and it is evaluated using PAC (Probably Approximately Correct) through sampling.
+Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$, the precision constraint is relaxed as follows:
+\begin{equation}
+  \label{eq:const_prec}
+  P(\Prec(A)\ge\tau)\ge1-\delta.
+\end{equation}
+Thus, the following optimization problem is solved:
+\begin{equation}
+  \label{eq:main_problem}
+  A^*=\underset{A \text{ s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
+  {\arg\max}\Cov(A).
+\end{equation}
+
+While Anchor provides a clear presentation of the effective scope of the explanation, the information it includes is less than LIME, limiting its utility \cite{ribeiro2018anchors}.
+An example explanation for an LSTM sentiment prediction model using Anchor is depicted in \cref{fig:lime_vs_anchor_exp_c}.
+The left explanation suggests that changing words other than "not" and "bad" has little impact on the classifier's output.
+While it clearly does not apply to the right instance, the explanation does not provide details about the influence of words like "not" or "bad," resulting in less user insight into the model's behavior compared to LIME (\cref{fig:lime_vs_anchor_exp_b}).
+
+\subsection{BELLA (Black box model Explanations by Local Linear Approximations) \cite{radulovic2023bella}}
+BELLA addresses the non-optimization of the approximation region, a drawback of LIME, by learning a local linear approximation model $g$ using a subset $Z'$ of the dataset $Z$ instead of perturbed samples (\cref{fig:bella}).
+The process involves:
+\begin{enumerate}
+  \item Computing the distance $d_x(z)$ for all instances $z$ in $Z$ with respect to the focal point $x$.
+  \item Selecting the $k$ instances with the smallest $d_x(z)$, forming a subset $Z_s(k) \subseteq Z$.
+  \item Learning the local linear approximation model $g$ using $Z_s(k)$ and calculating the similarity measure $\mathcal{R}(k)$ between $f$ and $g$.
+  \item Obtaining the optimal $k^*$ by maximizing $\mathcal{R}(k)$.
+\end{enumerate}
+
+BELLA aims to enhance the reliability of explanations by optimizing the approximation region for high-accuracy linear approximations.
+However, it assumes direct access to the dataset $Z$ used for training the classifier, making it inapplicable in scenarios where direct access to the dataset is restricted for privacy reasons.
+Additionally, as BELLA presents the approximation region as a subset of the dataset, its interpretability is lower compared to Anchor.
+
+\section{Proposed Method}
+\begin{figure}[tb]
+  \centering
+  \begin{subfigure}[t]{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{lime}
+    \caption{%
+      LIME: Locally approximates decision boundaries around the focal point.}\label{fig:lime}
+  \end{subfigure}%
+  \hfill
+  \begin{subfigure}[t]{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{anchor}
+    \caption{Anchor: Maximizes coverage of a rectangular region containing the focal point under precision constraints.}\label{fig:anchor}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{0.45\textwidth}
+    \centering
+    \includegraphics[width=0.85\textwidth]{bella}
+    \caption{%
+      BELLA: Explores a subset of the dataset, maximizing similarity between the local linear approximation model and the black-box classifier.}\label{fig:bella}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{rlime3}
+    \caption{%
+      R-LIME: Maximizes coverage of a rectangular region containing the focal point under lower constraints on the accuracy of the approximation model.}\label{fig:rlime}
+  \end{subfigure}
+  \caption{%
+    Visual comparison of LIME, Anchor, BELLA and R-LIME (our proposed method).
+    The solid line represents the rectangular region containing the focal
+    point, and the dashed line represents the learned approximation model.
+  }
+\end{figure}
+
+\subsection{Overview}
+The proposed method aims to overcome the limitations of LIME \cite{ribeiro2016why} and its improvement methods such as Anchor \cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
+Similar to LIME, the proposed method locally approximates the given black-box classifier $f$ around the focal point $x$ using a linear model $g$.
+However, by adopting a rectangular perturbation region similar to Anchor, it represents predicates (rules) concerning features.
+The accuracy of explanations is defined as the "accuracy" of rules, and the "coverage" of rules defines the generality of explanations.
+The proposed method maximizes coverage under lower constraints on accuracy (\cref{fig:rlime}).
+
+Anchor maximizes the coverage of region $A$ within which the output of the black-box classifier $f$ matches $f(x)$ with respect to the probability under lower constraints.
+The proposed method, on the other hand, learns an approximation model $g$ within the rectangular region $A$ and maximizes the coverage of $A$ under lower constraints on the accuracy of $g$.
+We modify the definition of accuracy using \cref{eq:anchor_def_prec} as follows:
+\begin{equation}
+  \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
+  [\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
+\end{equation}
+Here, $G$ represents the set of possible linear approximation models.
+By solving the optimization problem in \cref{eq:main_problem} under this modified accuracy definition, we can select rules that learn high-accuracy approximation models, among which the coverage is maximized.
+The proposed method's algorithm, shown in \cref{sec:alg}, is largely based on the algorithms used in Anchor.
+
+In this paper, we refer to the proposed method as "R-LIME" (Ruled LIME). The characteristics of R-LIME are listed below:
+\begin{itemize}
+  \item The perturbation vector's generation region is optimized and presented in a user-interpretable format.
+  \item Interpretation is conducted without direct access to the dataset, utilizing only the distribution.
+  \item The number of samples is dynamically determined based on the estimated accuracy without the need for a predefined amount.
+\end{itemize}
+% This enables model interpretation without direct access to the data, even in scenarios with significant privacy constraints.
+The optimized and presented explanation's applicable range allows users to evaluate the reliability and generality of the generated explanations.
+
+\subsection{Algorithm}\label{sec:alg}
+{%
+  \begin{figure}[t]
+    \centering
+    \includegraphics[width=0.32\textwidth]{rlime1}
+    \includegraphics[width=0.32\textwidth]{rlime2}
+    \includegraphics[width=0.32\textwidth]{rlime3}
+    \caption[Overview of the R-LIME Algorithm]{%
+      Overview of the R-LIME algorithm.
+The progression of the algorithm from left to right is illustrated.
+The solid red line represents the rectangular region $A$, and the red dashed line represents the linear approximation model $g$ learned within $A$.
+The initial value of $A$ is an empty rule (entire input space), and predicates are added to $A$, reducing coverage.
+The process continues until $\Prec(A)\ge\tau$, at which point the rule with the maximum coverage is output.
+    }
+  \end{figure}
+  \begin{algorithm}[p]
+    \input{alg1}
+  \end{algorithm}
+  \begin{algorithm}[p]
+    \input{alg2}
+  \end{algorithm}
+  \def\myidt{\hspace{\algorithmicindent}}
+  \begin{algorithm}[p]
+    \input{alg3}
+  \end{algorithm}
+  \begin{algorithm}[p]
+    \input{alg4}
+  \end{algorithm}
+}
+For non-convex optimization problems like \cref{eq:main_problem}, greedy methods are often employed.
+However, greedy methods tend to converge to local optima, and to address this, the proposed method utilizes beam search, which selects multiple candidates at each iteration.
+The pseudocode is shown in \cref{alg:greedy_search}.
+
+\subsubsection{Candidate Rule Generation}
+To generate new candidate rules, one additional predicate is added to each of the $B$ candidate rules obtained in the previous iteration.
+The pseudocode is shown in \cref{alg:generate_cands}.
+Here, $T(x)$ represents the set of attribute-value pairs (predicates) that $x$ possesses, and $T(x)\setminus A$ represents the conjunction of predicates in $T(x)$ not included in rule $A$.
+
+\subsubsection{Selection of Candidate Rule with Maximum Accuracy}
+Given the set of generated candidate rules $\cands$, the algorithm selects the top $B$ candidates with the highest accuracy.
+This is treated as an optimal arm identification problem in the multi-armed bandit framework.
+Each candidate rule $A_i\in\cands$ is considered an arm, and their accuracy $\Prec(A_i)$ is treated as the distribution of rewards.
+By sampling $z\sim\mathcal{D}(\cdot|A_i)$ and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial, the algorithm updates $g_i$ using the sampled perturbation vector $z$ and the pseudo-label $f(z)$ immediately after each trial.
+To efficiently select the rule (arm) with the highest accuracy, the KL-LUCB algorithm \cite{kaufmann2013information} is employed.
+The pseudocode is shown in \cref{alg:best_cands}.
+The KL-LUCB algorithm assumes that the reward distribution for each arm remains unchanged, while the proposed method updates the approximation model $g_i$ with each sampling, which may not satisfy this assumption.
+This issue is discussed further in \cref{sec:reward}.
+
+\subsubsection{Selection of Rule with Maximum Coverage Meeting Constraints}
+To meet the constraint in \cref{eq:const_prec}, rule $A$ must satisfy the lower constraint
+\begin{equation}
+  \label{eq:stop_condition}
+  \Prec_{l}(A,\delta)>\tau
+\end{equation}
+where $\Prec_{l}(A,\delta)$ is the lower bound on accuracy and $\delta$ is a small positive value.
+To check this condition, the algorithm performs a binary search on $\delta$ to find the smallest $\delta$ that satisfies \cref{eq:stop_condition}.
+The pseudocode is shown in \cref{alg:largest_valid_cand}.
+\newline
+
+The algorithmic procedure outlined above approximates the solution to the optimization problem in \cref{eq:main_problem} under the definition of accuracy in \cref{eq:def_prec}.
+It iteratively selects a rectangular region (rule) with the learned approximation model's accuracy exceeding a given threshold while maximizing coverage.
+The selected rule, with the maximum coverage meeting accuracy constraints, is output after each iteration.
+
+\section{Experiments}
+To verify the effectiveness of the proposed method, LIME and R-LIME were compared using a single dataset.
+
+\subsection{Qualitative Evaluation}
+\subsubsection{Experimental Setup}\label{sec:exp_setting}
+{%
+  \renewcommand{\arraystretch}{1.05}
+  \begin{table}[tbp]
+    \centering
+    \caption[Attributes and overview of the recidivism dataset used in the experiments]{%
+      Attributes and overview of the recidivism dataset used in the experiments. Continuous features are discretized, and only binary and ordinal features are considered.
+    }\label{tab:rcdv}
+    \begin{tabular}{llc}
+      \toprule
+      Attribute              & Overview                              & \# of Possible Values \\
+      \midrule
+      Race                   & Race (Black or White)                 & 2                     \\
+      Alcohol                & Presence of serious alcohol issues    & 2                     \\
+      Junky                  & Drug usage                            & 2                     \\
+      Supervised Release     & Supervised release                    & 2                     \\
+      Married                & Marital status                        & 2                     \\
+      Felony                 & Felony or not                         & 2                     \\
+      WorkRelease            & Participation in work release program & 2                     \\
+      Crime against Property & Crime against property or not         & 2                     \\
+      Crime against Person   & Crime against a person or not         & 2                     \\
+      Gender                 & Gender (Female or Male)               & 2                     \\
+      Priors                 & Number of prior offenses              & 4                     \\
+      YearsSchool            & Years of formal education completed   & 4                     \\
+      PrisonViolations       & Number of prison rule violations      & 3                     \\
+      Age                    & Age                                   & 4                     \\
+      MonthsServed           & Months served in prison               & 4                     \\
+      \midrule
+      Recidivism             & Recidivism or not                     & 2                     \\
+      \bottomrule
+    \end{tabular}
+  \end{table}
+}
+
+The experiments utilized the recidivism dataset \cite{schmidt1988predicting}.
+This dataset contains information on 9,549 prisoners released from North Carolina prisons between July 1, 1979, and June 30, 1980.
+The dataset includes 19 items such as race, gender, presence of alcohol dependence, number of prior offenses, and recidivism.
+For this experiment, we treated the binary classification problem of predicting the presence or absence of recidivism (Recidivism) as the target label.
+Preprocessing included discretization of continuous features, resulting in 15 features.
+This problem setting simulates a case where a machine learning model is introduced to decide parole for prisoners.
+Since such decisions can have a significant impact on a person's life, it is crucial for users to interpret the outputs of black-box models appropriately.
+
+The dataset, after removing missing values, was split into training data (7,639 instances) and test data (955 instances).
+A random forest model with 50 trees was trained using the training data.
+Subsequently, LIME and R-LIME explanations were generated for two instances extracted from the test data (\cref{fig:instance}).
+In R-LIME, logistic regression was used as the linear approximation model, and the distribution $\mathcal{D}$ was estimated using a multivariate normal distribution based on the training data.
+
+The beam width was set to $B=10$, the confidence coefficient to $1-\delta=0.95$, and the tolerance of the KL-LUCB algorithm to $\epsilon=0.05$.
+Accuracy thresholds $\tau$ were set to $\tau=0.70,0.80,0.90$.
+
+  {%
+    \def\vval{0pt}
+    \def\dir{python/exp1}
+    \def\Asample{0012}
+    \def\Bsample{0011}
+    \def\AB#1{\ifnum#1=0 A\else B\fi}
+
+    % \def\rcdvIdx#1{\ifnum#1=0 0253\else 0599\fi}
+    \def\index#1{\ifnum#1=0 \Asample \else \Bsample \fi}
+
+    \def\dataset#1{\ifnum#1=0 recidivism\else adult\fi}
+    \def\taulist{60, 70, 80}
+    % Tables
+    % \foreach\d in {0,1}{\foreach\a in {0,1}{\instancetab{\d}{\a}}}
+    {%
+      \renewcommand{\arraystretch}{1.02}
+      \begin{figure}[tbp]
+        \foreach\a in {0,1}{%
+            \centering
+            \begin{subfigure}{\textwidth}
+              \centering
+              \begin{tabular}{p{14em}m{16em}}
+                \toprule
+                \csvreader[no head, late after line= \\]{%
+                  \dir/\index{\a}.csv
+                }{}{%
+                \ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii
+                }
+                \bottomrule
+              \end{tabular}
+              \caption{Instance~\AB{\a}}\label{fig:\AB{\a}-instance}
+              \vspace{15pt}
+            \end{subfigure}
+          }
+        \vspace{-15pt}
+        \caption{Two instances sampled from recidivism dataset.}\label{fig:instance}
+      \end{figure}
+    }
+    \begin{figure}[p]
+      \def\scale{0.3}
+      \def\imgwidth{0.49\textwidth}
+      \begin{subfigure}[t]{\imgwidth}
+        \includegraphics[scale=\scale]{\dir/lime-\Asample}
+        \caption{LIME}\label{fig:A-lime}
+      \end{subfigure}
+      \begin{subfigure}[t]{\imgwidth}
+        \hspace{1.3em}
+        \includegraphics[scale=\scale]{\dir/newlime-\Asample-70}
+        \caption{R-LIME ($\tau=0.70$)}\label{fig:A-rlime-70}
+      \end{subfigure}
+      \begin{subfigure}[t]{\imgwidth}
+        \includegraphics[scale=\scale]{\dir/newlime-\Asample-80}
+        \caption{R-LIME ($\tau=0.80$)}\label{fig:A-rlime-80}
+      \end{subfigure}
+      \begin{subfigure}[t]{\imgwidth}
+        \includegraphics[scale=\scale]{\dir/newlime-\Asample-90}
+        \caption{R-LIME ($\tau=0.90$)}\label{fig:A-rlime-90}
+      \end{subfigure}
+      \caption{Explanation for Instance A by LIME and R-LIME.}\label{fig:A}
+    \end{figure}
+    \begin{figure}[p]
+      \def\scale{0.3}
+      \def\imgwidth{0.5\textwidth}
+      \begin{subfigure}[t]{\imgwidth}
+        \includegraphics[scale=\scale]{\dir/lime-\Bsample}
+        \caption{LIME}\label{fig:B-lime}
+      \end{subfigure}
+      \begin{subfigure}[t]{\imgwidth}
+        \includegraphics[scale=\scale]{\dir/newlime-\Bsample-70}
+        \caption{R-LIME ($\tau=0.70$)}\label{fig:B-rlime-70}
+      \end{subfigure}
+      \begin{subfigure}[t]{\imgwidth}
+        \includegraphics[scale=\scale]{\dir/newlime-\Bsample-80}
+        \caption{R-LIME ($\tau=0.80$)}\label{fig:B-rlime-80}
+      \end{subfigure}
+      \begin{subfigure}[t]{\imgwidth}
+        \includegraphics[scale=\scale]{\dir/newlime-\Bsample-90}
+        \caption{R-LIME ($\tau=0.90$)}\label{fig:B-rlime-90}
+      \end{subfigure}
+      \caption{Explanation for Instance B by LIME and R-LIME}\label{fig:B}
+    \end{figure}
+  }
+\subsubsection{Experimental Results}
+The results of the experiment are shown in \cref{fig:A,fig:B}.
+The values assigned to each attribute name represent the contribution (weights of the learned linear approximation model) to the output of the black-box classifier, normalized such that the absolute sum is 1.
+The figures also highlight the five attributes with the highest absolute contribution.
+
+Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) indicate that attributes such as having a significant prior record (Prior) or committing a crime against property (Crime against Property) primarily contribute positively to the prediction (predicting that the inmate will be re-incarcerated).
+On the other hand, attributes like older age (Age), being married (Married), and being of white race (Race) contribute negatively to the prediction (predicting that the inmate will not be re-incarcerated).
+While these LIME explanations provide valuable insights into the behavior of the black-box model, they do not explicitly indicate the range of application, leaving users unable to determine to which inmates the explanations are applicable.
+
+In contrast, R-LIME expresses the application range of explanations
+as a conjunction of predicates.
+For example, the explanation for instance A
+under $\tau=0.70$ (\cref{fig:A-rlime-70}) indicates that it is applicable
+only to married males (Married$=$Yes, Gender$=$Male).
+Furthermore, the generated explanations include the accuracy and coverage of
+the approximation region, allowing users to evaluate how reliable the
+explanations are.
+For example, the coverage of the explanation for instance B under $\tau=0.90$
+(\cref{fig:B-rlime-90}) is 0.002,
+indicating that the decision boundaries around instance B are complex,
+making it challenging to obtain a high-precision linear approximation.
+This allows users to discern that the application scope of this explanation is
+very narrow, limiting its utility.
+
+\subsection{Quantitative Evaluation}\label{sec:exp2}
+\subsubsection{Experimental Setup}
+To demonstrate that R-LIME adapts a highly accurate linear approximation model
+to the optimized approximation region,
+we conducted a comparison of the local accuracy of explanations
+between LIME and R-LIME.
+Using the same settings as in \cref{sec:exp_setting},
+we randomly sampled 100 instances from the test data of the recidivism dataset
+and generated explanations (with $\tau=0.70,0.80,0.90$) using LIME and R-LIME.
+We then sampled 10,000 instances within the rectangular region obtained by R-LIME and calculated the local accuracy of both methods.
+\subsubsection{Experimental Results}
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=0.55\textwidth]{python/exp2/box_plot}
+  \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
+    Comparison of local accuracy between LIME and R-LIME.
+    We generated explanations for 100 instances using each method
+    and calculated the accuracy for each method within the 10,000 instances
+    sampled inside the rectangular region obtained by R-LIME.
+  }\label{fig:box_plot}
+\end{figure}
+The results are presented in \cref{fig:box_plot}, showcasing the distribution of the accuracy of the linear approximation models obtained by LIME and R-LIME.
+R-LIME exhibits higher accuracy compared to LIME for all values of $\tau$.
+This suggests that the linear approximation models learned by LIME and R-LIME differ significantly, and R-LIME learns a high-precision linear approximation model adapted to the rectangular region.
+Additionally, as $\tau$ increases, the variability in the accuracy of LIME widens.
+This indicates that the linear models learned by LIME may not function effectively as approximation models depending on how the region is selected.
+
+\section{Challenges and Future Perspectives}
+
+ {%
+  \def\imgwidth{0.49\textwidth}
+  \begin{figure}[t]
+    \centering
+    \begin{subfigure}[t]{\imgwidth}
+      \centering
+      \includegraphics[width=0.78\textwidth]{newlime}
+      \caption{R-LIME for balanced data.}\label{fig:balanced}
+    \end{subfigure}
+    \begin{subfigure}[t]{\imgwidth}
+      \centering
+      \includegraphics[width=0.8\textwidth]{newlime_for_imbalanced_data}
+      \caption{R-LIME for imbalanced data.
+      }\label{fig:imbalanced}
+    \end{subfigure}
+    \caption{%
+      Behavior of R-LIME for balanced and imbalanced data.
+      In case of imbalanced label distribution, 
+      the approximation region covers the entire input space and the
+      linear approximation model always outputs the majority label.
+    }
+    \vspace{10pt}
+  \end{figure}
+ }
+
+\subsection{Behavior Regarding Imbalanced Label Distribution}
+R-LIME may generate less useful explanations when there is bias in the distribution of black-box model outputs.
+When the distribution of black-box model outputs is significantly biased for a given accuracy threshold $\tau$ (the ratio of the majority label is less than $\tau$), the approximation region generated by R-LIME covers the entire input space, and the learned linear approximation model always outputs the majority label (\cref{fig:imbalanced}).
+
+As a first solution to this problem, changing the loss function is considered.
+Using weighted logistic loss or Focal Loss \cite{lin2020focal} as the loss function might lead to the generation of more useful explanations in the case of imbalanced label distribution.
+Another solution involves adding constraints to limit the label distribution bias within the approximation region.
+In addition to \cref{eq:const_prec}, adding a constraint like
+\begin{equation}
+  {\left(\mathbb{E}_{z\sim\mathcal{D}(z\mid A)}[\mathbbm{1}_{f(z)=1}]-\frac{1}{2}\right)}^2<\mu
+\end{equation}
+could suppress the excessive expansion of the approximation region.
+
+\subsection{Changes in Reward Distribution in Optimal Arm Identification}\label{sec:reward}
+{%
+  \renewcommand{\arraystretch}{1.1}
+  \begin{table}[tbp]
+    \centering
+    \caption{%
+      Deviation between the estimated accuracy and the true accuracy.
+    }\label{tab:reward}
+    \input{tab_exp_adv}
+  \end{table}
+}
+In R-LIME, the problem of selecting the rule with the highest accuracy is formulated as the optimal arm identification problem in multi-armed bandit theory, solved using the KL-LUCB algorithm \cite{kaufmann2013information}.
+However, this algorithm assumes that the reward distribution remains constant, while in R-LIME, the reward distribution (accuracy of the linear approximation model) changes with every update of the approximation model after sampling.
+Therefore, rewards obtained at an early stage when the accuracy is still low might influence the estimated value and deviate from the true value.
+
+An experiment was conducted to evaluate the deviation between the estimated accuracy and the true accuracy.
+Explanations were generated for 3,200 data instances sampled from the dataset, and the estimated accuracy was compared with the true accuracy.
+The true accuracy was calculated based on 1,000 instances sampled within the approximation region, considering cases where the outputs of the black-box model and the linear approximation model matched.
+The results in \cref{tab:reward} show a mean deviation of 0.012 with a standard deviation of 0.017.
+While the deviation is relatively small, improvements to the selection algorithm need to consider the changing accuracy.
+
+\subsection{Evaluation through User Studies}
+Given the nature of the field of "interpretable machine learning,"
+where the goal is to "interpret" machine learning models,
+it is challenging to quantitatively compare various methods.
+While quantitative experiments were conducted in \cref{sec:exp2},
+they mainly demonstrated that the proposed method generates
+locally accurate explanations compared to LIME.
+The results do not directly prove the high interpretability of the proposed method.
+
+One potential method to quantitatively evaluate "interpretability" is through user studies.
+For example, \cite{ribeiro2018anchors} conducted user studies, assuming that if users could predict the output of a black-box model with high accuracy based on provided explanations, those explanations contained valuable information about the model's behavior.
+Similarly, conducting user studies in this research would be desirable to evaluate the interpretability of the proposed method.
+
+\section{Conclusion}
+We identified challenges in existing methods for local model-agnostic post-hoc
+explanations of black-box classifiers and proposed R-LIME to address them.
+We represented the rectangular region for local linear approximation as a
+conjunction of predicates of features and proposed an algorithm to
+maximize coverage under the constraint of minimum approximation accuracy.
+Comparing the outputs of LIME and R-LIME on real-world datasets,
+we demonstrated that explanations provided by R-LIME have clearer application
+scopes and can be evaluated by users for reliability and generality.
+However, we discussed the instability of behavior concerning imbalanced label
+distributions and raised questions about the theoretical validity of using
+the KL-LUCB algorithm.
+
+% \subsection{A Subsection Sample}
+% Please note that the first paragraph of a section or subsection is
+% not indented. The first paragraph that follows a table, figure,
+% equation etc.\ does not need an indent, either.
+%
+% Subsequent paragraphs, however, are indented.
+%
+% \subsubsection{Sample Heading (Third Level)} Only two levels of
+% headings should be numbered. Lower level headings remain unnumbered;
+% they are formatted as run-in headings.
+%
+% \paragraph{Sample Heading (Fourth Level)}
+% The contribution should contain no more than four levels of
+% headings. Table~\ref{tab1} gives a summary of all heading levels.
+%
+% \begin{table}
+% \caption{Table captions should be placed above the
+% tables.}\label{tab1}
+% \begin{tabular}{|l|l|l|}
+% \hline
+% Heading level &  Example & Font size and style\\
+% \hline
+% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
+% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
+% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
+% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
+% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
+% \hline
+% \end{tabular}
+% \end{table}
 %
 %
+% \noindent Displayed equations are centered and set on a separate
+% line.
+% \begin{equation}
+% x + y = z
+% \end{equation}
+% Please try to avoid rasterized images for line-art diagrams and
+% schemas. Whenever possible, use vector graphics instead (see
+% Fig.~\ref{fig1}).
 %
-\section{First Section}
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc.\ does not need an indent, either.
+% \begin{figure}
+% \includegraphics[width=\textwidth]{fig1.eps}
+% \caption{A figure caption is always placed below the illustration.
+% Please note that short captions are centered, while long ones are
+% justified by the macro package automatically.} \label{fig1}
+% \end{figure}
+%
+% \begin{theorem}
+% This is a sample theorem. The run-in heading is set in bold, while
+% the following text appears in italics. Definitions, lemmas,
+% propositions, and corollaries are styled the same way.
+% \end{theorem}
+% %
+% % the environments 'definition', 'lemma', 'proposition', 'corollary',
+% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
+% %
+% \begin{proof}
+% Proofs, examples, and remarks have the initial word in italics,
+% while the following text appears in normal font.
+% \end{proof}
+% For citations of references, we prefer the use of square brackets
+% and consecutive numbers. Citations using labels or the author/year
+% convention are also acceptable. The following bibliography provides
+% a sample reference list with entries for journal
+% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
+% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
+% and a homepage~\cite{ref_url1}. Multiple citations are grouped
+% \cite{ref_article1,ref_lncs1,ref_book1},
+% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
 
-Subsequent paragraphs, however, are indented.
-
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
-
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
-
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
-
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-
-\subsubsection{Acknowledgements} Please place your acknowledgments at
-the end of the paper, preceded by an unnumbered run-in heading (i.e.
-3rd-level heading).
+\subsubsection{Acknowledgements}
+% Please place your acknowledgments at
+% the end of the paper, preceded by an unnumbered run-in heading (i.e.
+% 3rd-level heading).
+I would like to express my gratitude to Associate Professor Keigo Kimura from the Department of Mathematical Science, Division of Information Recognition, Graduate School of Information Science and Technology, Hokkaido University.
+He provided invaluable guidance, from setting the research theme to outlining the strategy and content of this study.
+Additionally, I appreciate the diverse insights shared by Professor Mineichi Kudo in the same laboratory.
+Finally, I am deeply thankful to all the members of the laboratory for their helpful advice and collaboration throughout the research process.
 
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
+\bibliographystyle{splncs04}
+\bibliography{MyRef/ref}
 %
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
 \end{document}

### 2024-02-13 python/exp2/box_plot.py

@@ -1,0 +1,59 @@
+"""Module providing a function creating a box plot of the data in a file."""
+
+import csv
+
+import matplotlib.pyplot as plt
+
+
+def main() -> None:
+    """Main function of the module."""
+
+    plt.figure()
+
+    accs = []
+    for tau_percent in [70, 80, 90]:
+        file_name = f"{tau_percent}.csv"
+        lime_acc, rlime_acc = read_data(file_name)
+        accs.append(lime_acc)
+        accs.append(rlime_acc)
+
+    bp = plt.boxplot(
+        accs,
+        labels=["LIME", "R-LIME"] * 3,
+        widths=0.7,
+        positions=[1, 2, 3.5, 4.5, 6, 7],
+        showfliers=False,
+        patch_artist=True,
+    )
+    colors = ["#377eb8", "#4daf4a"] * 3
+    for patch, med, color in zip(bp["boxes"], bp["medians"], colors):
+        patch.set_facecolor(color)
+        med.set_color("black")
+
+    for i, tau_percent in enumerate([70, 80, 90]):
+        plt.text(1.0 + 2.5 * i, 0.36, r"$\tau=$" + f"0.{tau_percent}")
+
+    plt.hlines(
+        [0.7, 0.8, 0.9],
+        [0, 2.5, 5],
+        [3.0, 5.5, 8],
+        colors="black",
+        linestyles="dashed",
+    )
+    # plt.title("Accuracy of LIME and R-LIME")
+    plt.ylabel("Accuracy")
+    plt.savefig("box_plot.png")
+
+
+def read_data(filename: str) -> tuple[list[float], list[float]]:
+    """Reads data from a file and returns it as a list of lists."""
+    data = []
+    with open(filename, newline="", encoding="utf-8") as file:
+        reader = csv.reader(file, delimiter=",")
+        for row in reader:
+            data.append([float(x) for x in row])
+    return data[0], data[1]
+
+
+if __name__ == "__main__":
+    main()

### 2024-02-13 python/exp2/lime_vs_rlime.py

@@ -1,0 +1,144 @@
+"""Compare LIME and R-LIME on the recidivism dataset."""
+
+import csv
+import multiprocessing
+import sys
+from functools import partial
+
+import numpy as np
+import pandas as pd
+from sklearn.ensemble import RandomForestClassifier
+
+sys.path.append("../NewLIME")
+# pylint: disable=import-error,wrong-import-position
+import newlime_base  # pyright: ignore[reportMissingImports] # noqa: E402
+import newlime_tabular  # pyright: ignore[reportMissingImports] # noqa: E402
+import newlime_utils  # pyright: ignore[reportMissingImports] # noqa: E402
+
+
+def main() -> None:
+    """Main function."""
+
+    # Load the dataset.
+    dataset = newlime_utils.load_dataset(
+        "recidivism", "../NewLIME/anchor-experiments/datasets/", balance=True
+    )
+
+    # Learn the black box model.
+    black_box = RandomForestClassifier(n_estimators=100, n_jobs=1)
+    black_box.fit(dataset.train, dataset.labels_train)
+
+    # Get the target instances.
+    sample_num = 100
+    result_list = multiprocessing.Manager().list()
+
+    tau = 0.70
+
+    func = partial(
+        compare_lime_and_newlime,
+        dataset=dataset,
+        black_box=black_box,
+        tau=tau,
+        result_list=result_list,
+    )
+
+    with multiprocessing.Pool() as pool:
+        pool.map(func, range(sample_num))
+
+    lime_acc, rlime_acc = zip(*result_list)
+    print("LIME")
+    print(f"  Mean: {np.mean(lime_acc):.4f}")
+    print(f"  Std : {np.std(lime_acc):.4f}")
+    print("R-LIME")
+    print(f"  Mean: {np.mean(rlime_acc):.4f}")
+    print(f"  Std : {np.std(rlime_acc):.4f}")
+
+    # Save the results to a CSV file.
+    with open(f"{int(tau*100)}.csv", "w", encoding="utf-8") as f:
+        writer = csv.writer(f)
+        writer.writerow(lime_acc)
+        writer.writerow(rlime_acc)
+
+
+def compare_lime_and_newlime(
+    idx: int,
+    dataset: newlime_utils.Dataset,
+    black_box: RandomForestClassifier,
+    tau: float,
+    result_list: list[tuple[float, float]],
+) -> None:
+    """Compare LIME and R-LIME.
+
+    Parameters
+    ----------
+    idx: int
+        The index of the target instance.
[…]

### 2024-02-13 python/exp_adv/imbalanced.py

@@ -1,0 +1,142 @@
+"""This module generates the experiment data for the paper."""
+
+import random
+import sys
+
+import numpy as np
+import pandas as pd
+from river import compose
+from sklearn.ensemble import RandomForestClassifier
+from tqdm import tqdm
+
+from prelearning import get_covered_samples, surrogate_precision
+
+sys.path.append("NewLIME")
+# pylint: disable=import-error,wrong-import-position
+import newlime_tabular  # pyright: ignore[reportMissingImports] # noqa: E402
+import newlime_utils  # pyright: ignore[reportMissingImports] # noqa: E402
+
+
+def main() -> None:
+    """Main function."""
+
+    # Load the dataset.
+    balanced = newlime_utils.load_dataset(
+        "recidivism", "NewLIME/anchor-experiments/datasets/", balance=True
+    )
+    imbalanced = newlime_utils.get_imbalanced_dataset(balanced, 0.10)
+
+    # Set the hyper-parameters for NewLIME.
+    hyper_param = newlime_tabular.HyperParam(
+        delta=0.05,
+        epsilon=0.05,
+        epsilon_stop=0.05,
+        beam_size=10,
+        batch_size=1000,
+        desired_confidence=0.70,
+        coverage_samples_num=10000,
+        max_rule_length=None,
+    )
+
+    for dataset in [imbalanced, balanced]:
+        # Learn the black box model.
+        black_box = RandomForestClassifier(n_estimators=100, n_jobs=5)
+        black_box.fit(dataset.train, dataset.labels_train)
+
+        # Print the number of labels in the dataset.
+        print_labels_count(dataset, black_box)
+
+        # Print the precision, recall, and coverage of the surrogate model
+        # returned by NewLIME under the rule.
+        idx_list = random.sample(range(len(dataset.test)), 10)
+        trgs = dataset.test[idx_list]
+        explainer = newlime_tabular.NewLimeTabularExplainer(
+            dataset.class_names,
+            dataset.feature_names,
+            dataset.train,
+            dataset.categorical_names,
+        )
+        sum_vals = [0.0, 0.0, 0.0]
+        names = ["Precision", "Recall", "Coverage"]
+        for trg in tqdm(trgs):
+            vals = get_prec_and_recall(
+                explainer, hyper_param, black_box, dataset, trg
+            )
+            sum_vals = [sum_val + val for sum_val, val in zip(sum_vals, vals)]
+
[…]

### 2024-02-13 python/exp_adv/prelearning.py

@@ -1,0 +1,210 @@
+"""This module generates the experiment data for the paper. The data is used to
+measure the gap between the precision returned by NewLIME and the true
+precision under the rule. The gap is calculated by the following formula:
+
+        gap = returned_precision - true_precision
+
+The gap is calculated for each target sample. The mean and the standard
+deviation of the gaps are calculated for all the target samples. The mean and
+the standard deviation are used to evaluate the performance of NewLIME. The
+smaller the mean and the standard deviation are, the better the performance of
+NewLIME is.
+"""
+
+import multiprocessing
+import sys
+from typing import Any
+
+import numpy as np
+import pandas as pd
+from river import compose
+from sklearn.ensemble import RandomForestClassifier
+from tqdm import tqdm
+
+sys.path.append("../NewLIME")
+
+
+# pylint: disable=import-error,wrong-import-position
+import newlime_tabular  # pyright: ignore[reportMissingImports] # noqa: E402
+import newlime_utils  # pyright: ignore[reportMissingImports] # noqa: E402
+
+
+def main() -> None:
+    """Main function."""
+
+    # Set the hyperparameters.
+    hyper_param = newlime_tabular.HyperParam(
+        tau=0.80,
+        delta=0.05,
+        epsilon=0.05,
+        epsilon_stop=0.05,
+        beam_size=10,
+        batch_size=1000,
+        init_sample_num=0,
+        coverage_samples_num=1000,
+        max_rule_length=None,
+    )
+
+    # Set the number of processes.
+    process_num = 16
+
+    # Set the number of target samples for each process.
+    samples_num = 200
+
+    # Load the dataset.
+    dataset = newlime_utils.load_dataset(
+        "recidivism", "../NewLIME/anchor-experiments/datasets/", balance=True
+    )
+
+    # Learn the black box model.
+    black_box = RandomForestClassifier(n_estimators=100, n_jobs=5)
+    black_box.fit(dataset.train, dataset.labels_train)
+
+    processes = []
+    result_list = multiprocessing.Manager().list()
+
+    # Measure the gap between the precision returned by NewLIME and the true
+    # precision. Caluculating the gap is time-consuming, so we use multiple
+    # processes to accelerate the calculation.
+    for i in range(process_num):
+        np.random.seed(i)
+        process = multiprocessing.Process(
+            target=measure_gap,
+            args=(samples_num, dataset, black_box, hyper_param, result_list),
+        )
+        process.start()
[…]

### 2024-02-13 paper.tex
Remove errors by linter

@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.21 of 2022/01/12
-%
-
 % We import package amsmath before the documentclass to avoid the warning.
@@
 \documentclass[runningheads]{llncs}
-%
-\usepackage[T1]{fontenc}
-% T1 fonts will be used to generate the final print and online PDFs,
-% so please use T1 fonts in your manuscript whenever possible.
-% Other font encondings may result in incorrect characters.
-%
-\usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
+
+% If possible, figure files should be included in EPS format.
+
 % If you use the hyperref package, please uncomment the following two lines
@@
 %\renewcommand\UrlFont{\color{blue}\rmfamily}
-%
 
-\usepackage{amssymb} % for \mathbb
-\usepackage{cleveref} % for \cref
-\usepackage{bbm} % for \mathbbm
-\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
-\usepackage{pgffor} % for \foreach
-\usepackage{csvsimple} % for \csvreader
-\usepackage{array} % for m column type
-
-% Fig. 1a -> Fig. 1(a)
-\usepackage[labelformat=simple]{subcaption}
-\graphicspath{{./data/}{./python/data/}}
-\renewcommand\thesubfigure{(\alph{subfigure})}
+% The following code is used to remove the warning with subcaption package:
+% ------------------------------
+% Package caption Warning: Unknown document class (or package),
+% standard defaults will be used.
+% ------------------------------
+% cf. https://teratail.com/questions/q2vuwf6skm5hph
 \makeatletter
-\def\caption@documentclass{elsarticle}%
+\def\caption@documentclass{elsarticle}
 \makeatother
@@
 \usepackage{algpseudocode}
+\usepackage{amssymb} % for \mathbb
+\usepackage{array} % for m column type
+\usepackage{bbm} % for \mathbbm
+\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
+\usepackage{cleveref} % for \cref
+\usepackage{csvsimple} % for \csvreader
+\usepackage[T1]{fontenc} % for T1 font encoding
+\usepackage{graphicx} % for \includegraphics
+\usepackage{pgffor} % for \foreach
+\usepackage[labelformat=simple]{subcaption} % for subfigure environment
 
+% The following code is used to remove the warning with bibliography:
+% ------------------------------
+% Underfull \hbox (badness 2653) in paragraph at lines 28--34
+% ------------------------------
+% cf. https://tex.stackexchange.com/questions/10924/underfull-hbox-in-bibliography
+\apptocmd{\sloppy}{\hbadness 10000\relax}{}{}
+
+% set the path for figures
+\graphicspath{{./data/}{./python/data/}}
+
+% set the label format for subcaption
+\renewcommand\thesubfigure{(\alph{subfigure})}
+
+% settings for cleveref
+\crefname{figure}{Fig.}{Figs.}
+\crefname{table}{Tab.}{Tabs.}
+
+% import the TeX file containing macro definitions
 \input{macro}
@@
 \begin{document}
-%
+
+% Authentic title
 \title{%
@@
   Model-agnostic Explanation Methods}
-%
+
+% Abbreviated title for the running head
 \titlerunning{%
@@
 }
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
+
+% Author names and ORCID IDs
 \author{Genji Ohara\inst{1}\orcidID{0009-0000-5854-2820} \and
@@
 }
-%
+
+% Abbreviated author list for the running head (First names are abbreviated)
+% If there are more than two authors, 'et al.' is used.
 \authorrunning{G. Ohara et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
+
+% The authors' affiliations
 \institute{Division of Computer Science and Information Technology\\
@@
 
-\maketitle              % typeset the header of the contribution
-%
+% typeset the header of the contribution
+\maketitle              %
+
 % The abstract should briefly summarize the contents of the paper in
 % 150--250 words.
-
 \begin{abstract}
@@
   in decision-making situations where transparency of the decision process is required.
-  In order to solve this problem,
+  In order to address this problem,
   various post-hoc explanation methods have been proposed,
@@
   both the explanation and its scope.
-  We propose a new method that interprets complex models in an interpretable
-  approximation region.
-  R-LIME locally approximizes a complex decision boundary with a linear classifier
-  and maximizes the approximation region as long as the accuracy of the linear
-  model is higher than a specified threshold.
-  We demonstrate the effectiveness of the proposed method through a qualitative
-  and quantitative evaluation using a real-world dataset.
+  We propose a new method, R-LIME,
+  which interprets complex classifiers in an interpretable scope.
+  R-LIME locally approximizes a complex decision boundary linearly
+  in a rectangular region
+  and maximizes the region as long as the accuracy of the linear
+  classifier is higher than a specified threshold.
+  The resulting rectangular region is interpretable for users because it is
+  expressed as a conjunction of feature predicates.
+  We demonstrate the effectiveness of the proposed method through qualitative
+  and quantitative experiments using a real-world dataset.
   Finally, we discuss limitations and future work of the proposed method.
@@
 
-Existing studies on post hoc explanations categorize into model-dependent and
+Existing methods on post hoc explanations categorize into model-dependent and
 model-agnostic methods,
-depending on their dependence on the model's structure.
+based on their dependence on the model's structure.
 Model-dependent methods primarily focus on deep neural networks and
-explain the model's behavior using internal parameters.
+explain the models' behavior using their parameters.
 While they allow a direct approach to the model,
 applying the same method to models with different structures is often challenging.
-On the other hand, model-agnostic methods do not rely on internal parameters and utilize only the model's output.
-Although they provide high generality, their information is constrained, making them more versatile.
-Model-agnostic methods further classify into global and local methods based on their treatment of input space.
-Global methods aim to explain the model's behavior across the entire input space, seeking explanations valid for any input.
+On the other hand,
+model-agnostic methods do not rely on the models' parameters and utilize only their output.
+Although they are applicable to any model, available information is limited.
+Model-agnostic methods further classify into global and local methods
+based on their treatment of input space.
+Global methods aim to explain the model's behavior across the entire input space,
+seeking explanations valid for any input.
 However, providing global explanations becomes challenging as the model's complexity increases.
-Local methods, in contrast, explain the model's output for a specific input (focus point) in the vicinity of that input.
-While local methods offer simple and accurate explanations compared to global methods, their applicability is limited.
+Local methods, in contrast, explain the model's output for a specific input
+(focus point) in the vicinity of that input.
+While local methods offer more simple and accurate explanations than global methods,
+the scope of the explanation is limited to the vicinity of the focus point.
 
@@
 within a rectangular approximation region under lower-bound constraints.
-The resulting rectangular region is expressed as a conjunction of predicates
-related to features, enhancing interpretability for the user.
+The resulting rectangular region is expressed as a conjunction of feature predicates,
+enhancing interpretability for the user.
 
@@
 \subsection{Anchor \cite{ribeiro2018anchors}}\label{sec:anchor}
-Anchor represents a rectangular region, expressed as a conjunction of predicates (rules) related to features, that maximizes the probability of the black-box classifier $f$ outputting $f(x)$ within the region.
+Anchor represents a rectangular region,
+expressed as a conjunction of feature predicates (rules),
+that maximizes the probability of the black-box classifier $f$ outputting $f(x)$ within the region.
 It aims to highlight important features contributing significantly to the output (\cref{fig:anchor}).
@@
 The predicates $a_i(z)$ evaluate to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
-The precision $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
+The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
 \begin{align}
@@
 
-Here, $\mathcal{D}(z|A)$ is the conditional distribution in the region where the rule $A$ is true.
+where $\mathcal{D}(z|A)$ is the conditional distribution in the region where the rule $A$ is true.
 % When sampling the perturbation vector $z$ according to the distribution $\mathcal{D}$,
@@
 
-An Anchor maximizes coverage within the given threshold $\tau$ while maintaining precision.
+An Anchor maximizes coverage within the given threshold $\tau$ while maintaining accuracy.
 However, direct computation of \cref{eq:anchor_def_prec} is not feasible, and it is evaluated using PAC (Probably Approximately Correct) through sampling.
-Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$, the precision constraint is relaxed as follows:
+Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$, the accuracy constraint is relaxed as follows:
 \begin{equation}
@@
   \label{eq:main_problem}
-  A^*=\underset{A \text{ s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
+  A^*=\underset{A \text{~s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
   {\arg\max}\Cov(A).
@@
     \caption{%
-      LIME: Locally approximates decision boundaries around the focal point.}\label{fig:lime}
+      LIME: Locally approximates the decision boundary around the focal point.}\label{fig:lime}
   \end{subfigure}%
@@
     \includegraphics[width=\textwidth]{anchor}
-    \caption{Anchor: Maximizes coverage of a rectangular region containing the focal point under precision constraints.}\label{fig:anchor}
+    \caption{Anchor: Maximizes coverage of a rectangular region containing the focal point under accuracy constraints.}\label{fig:anchor}
   \end{subfigure}
@@
 \subsection{Overview}
-The proposed method aims to overcome the limitations of LIME \cite{ribeiro2016why} and its improvement methods such as Anchor \cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
-Similar to LIME, the proposed method locally approximates the given black-box classifier $f$ around the focal point $x$ using a linear model $g$.
-However, by adopting a rectangular perturbation region similar to Anchor, it represents predicates (rules) concerning features.
-The accuracy of explanations is defined as the "accuracy" of rules, and the "coverage" of rules defines the generality of explanations.
-The proposed method maximizes coverage under lower constraints on accuracy (\cref{fig:rlime}).
+We propose R-LIME,
+a method that aims to address the limitations of LIME \cite{ribeiro2016why}
+and its improvement methods such as
+Anchor \cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
+Similar to LIME,
+the proposed method locally approximates the given black-box classifier $f$
+around the focal point $x$ by a linear model $g$.
+However,
+by adopting a rectangular perturbation region similar to Anchor,
+it represents feature predicates (rules).
+The accuracy of explanations is defined as the "accuracy" of rules,
+and the "coverage" of rules defines the generality of explanations.
+The proposed method maximizes coverage under lower constraints on accuracy
+(\cref{fig:rlime}).
 
@@
 \end{equation}
-Here, $G$ represents the set of possible linear approximation models.
+where $G$ represents the set of possible linear approximation models.
 By solving the optimization problem in \cref{eq:main_problem} under this modified accuracy definition, we can select rules that learn high-accuracy approximation models, among which the coverage is maximized.
@@
     \includegraphics[width=0.32\textwidth]{rlime3}
-    \caption[Overview of the R-LIME Algorithm]{%
+    \caption{%
       Overview of the R-LIME algorithm.
       The progression of the algorithm from left to right is illustrated.
-The solid red line represents the rectangular region $A$, and the red dashed line represents the linear approximation model $g$ learned within $A$.
-The initial value of $A$ is an empty rule (entire input space), and predicates are added to $A$, reducing coverage.
-The process continues until $\Prec(A)\ge\tau$, at which point the rule with the maximum coverage is output.
+      The solid line represents the rectangular region $A$,
+      and the dashed line represents the linear approximation model $g$
+      learned within $A$.
+      The initial value of $A$ is an empty rule (entire input space),
+      and predicates are added to $A$, reducing coverage.
+      The process continues until $\Prec(A)\ge\tau$,
+      at which point the rule with the maximum coverage is output.
     }
@@
 The pseudocode is shown in \cref{alg:generate_cands}.
-Here, $T(x)$ represents the set of attribute-value pairs (predicates) that $x$ possesses, and $T(x)\setminus A$ represents the conjunction of predicates in $T(x)$ not included in rule $A$.
+$T(x)$ represents the set of attribute-value pairs (predicates) that $x$ possesses, and $T(x)\setminus A$ represents the conjunction of predicates in $T(x)$ not included in rule $A$.
 
@@
 
-\subsubsection{Selection of Rule with Maximum Coverage Meeting Constraints}
-To meet the constraint in \cref{eq:const_prec}, rule $A$ must satisfy the lower constraint
+\subsubsection{Selection of the Rule with Maximum Coverage Meeting the Constraint}
+To satisfy the constraint imposed by \cref{eq:const_prec}, rule $A$ needs to fulfill the lower bound constraint:
 \begin{equation}
+  \Prec_{l}(A,\delta)>\tau
   \label{eq:stop_condition}
-  \Prec_{l}(A,\delta)>\tau
 \end{equation}
-where $\Prec_{l}(A,\delta)$ is the lower bound on accuracy and $\delta$ is a small positive value.
-To check this condition, the algorithm performs a binary search on $\delta$ to find the smallest $\delta$ that satisfies \cref{eq:stop_condition}.
-The pseudocode is shown in \cref{alg:largest_valid_cand}.
-\newline
+where $\Prec_{l}(A,\delta)$ represents the lower limit of the $100(1-\delta)$\% confidence interval for $\Prec(A)$.
+If the received set of candidate rules, $\mathcal{A}$, includes a rule satisfying \cref{eq:stop_condition},
+the one with the maximum coverage among them is selected, and the iteration is concluded.
+If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop_condition}, it returns \textbf{null},
+and proceeds to the next iteration.
+The pseudocode is presented in \cref{alg:largest_valid_cand}.
 
@@
     \centering
-    \caption[Attributes and overview of the recidivism dataset used in the experiments]{%
-      Attributes and overview of the recidivism dataset used in the experiments. Continuous features are discretized, and only binary and ordinal features are considered.
+    \caption{%
+      Attributes of the recidivism dataset used in the experiments.
+      Continuous features are all discretized
+      and only binary and ordinal features are considered.
     }\label{tab:rcdv}
@@
   {%
-    \def\vval{0pt}
+
     \def\dir{python/exp1}
@@
     \def\Bsample{0011}
-    \def\AB#1{\ifnum#1=0 A\else B\fi}
-
-    % \def\rcdvIdx#1{\ifnum#1=0 0253\else 0599\fi}
     \def\index#1{\ifnum#1=0 \Asample \else \Bsample \fi}
 
-    \def\dataset#1{\ifnum#1=0 recidivism\else adult\fi}
-    \def\taulist{60, 70, 80}
-    % Tables
-    % \foreach\d in {0,1}{\foreach\a in {0,1}{\instancetab{\d}{\a}}}
     {%
+      \def\AB#1{\ifnum#1=0 A\else B\fi}
+      \def\mylabel#1{\ifnum#1=0 \label{fig:A-instance}\else \label{fig:B-instance}\fi}
       \renewcommand{\arraystretch}{1.02}
@@
               \end{tabular}
-              \caption{Instance~\AB{\a}}\label{fig:\AB{\a}-instance}
+              \caption{Instance~\AB{\a}}\mylabel{\a}
               \vspace{15pt}
@@
     }
+    {%
+      \def\scale{0.315}
+      \def\imgwidth{0.495\textwidth}
+      \def\hspacebase{\hspace{-1.5em}}
+      \def\vspacebase{\vspace{0.5em}}
+      \def\vspacebeforecaption{\vspace{-0.4em}}
       \begin{figure}[p]
-      \def\scale{0.3}
-      \def\imgwidth{0.49\textwidth}
+        \centering
         \begin{subfigure}[t]{\imgwidth}
+          \hspacebase
           \includegraphics[scale=\scale]{\dir/lime-\Asample}
+          \vspacebeforecaption
           \caption{LIME}\label{fig:A-lime}
+          \vspacebase
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
-        \hspace{1.3em}
+          \hspacebase
+          \hspace{1.0em}
           \includegraphics[scale=\scale]{\dir/newlime-\Asample-70}
+          \vspacebeforecaption
           \caption{R-LIME ($\tau=0.70$)}\label{fig:A-rlime-70}
+          \vspacebase
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
+          \hspacebase
           \includegraphics[scale=\scale]{\dir/newlime-\Asample-80}
+          \vspacebeforecaption
           \caption{R-LIME ($\tau=0.80$)}\label{fig:A-rlime-80}
@@
         \begin{subfigure}[t]{\imgwidth}
+          \hspacebase
           \includegraphics[scale=\scale]{\dir/newlime-\Asample-90}
+          \vspacebeforecaption
           \caption{R-LIME ($\tau=0.90$)}\label{fig:A-rlime-90}
@@
       \begin{figure}[p]
-      \def\scale{0.3}
-      \def\imgwidth{0.5\textwidth}
+        \centering
         \begin{subfigure}[t]{\imgwidth}
+          \hspacebase
           \includegraphics[scale=\scale]{\dir/lime-\Bsample}
+          \vspacebeforecaption
           \caption{LIME}\label{fig:B-lime}
+          \vspacebase
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
+          \hspacebase
           \includegraphics[scale=\scale]{\dir/newlime-\Bsample-70}
+          \vspacebeforecaption
           \caption{R-LIME ($\tau=0.70$)}\label{fig:B-rlime-70}
+          \vspacebase
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
+          \hspacebase
           \includegraphics[scale=\scale]{\dir/newlime-\Bsample-80}
+          \vspacebeforecaption
           \caption{R-LIME ($\tau=0.80$)}\label{fig:B-rlime-80}
@@
         \begin{subfigure}[t]{\imgwidth}
+          \hspacebase
+          \hspace{0em}
           \includegraphics[scale=\scale]{\dir/newlime-\Bsample-90}
+          \vspacebeforecaption
           \caption{R-LIME ($\tau=0.90$)}\label{fig:B-rlime-90}
@@
       \end{figure}
+    }
   }
@@
 indicating that the decision boundaries around instance B are complex,
-making it challenging to obtain a high-precision linear approximation.
+making it challenging to obtain a high-accuracy linear approximation.
 This allows users to discern that the application scope of this explanation is
@@
 R-LIME exhibits higher accuracy compared to LIME for all values of $\tau$.
-This suggests that the linear approximation models learned by LIME and R-LIME differ significantly, and R-LIME learns a high-precision linear approximation model adapted to the rectangular region.
+This suggests that the linear approximation models learned by LIME and R-LIME differ significantly, and R-LIME learns a high-accuracy linear approximation model adapted to the rectangular region.
 Additionally, as $\tau$ increases, the variability in the accuracy of LIME widens.
@@
 We represented the rectangular region for local linear approximation as a
-conjunction of predicates of features and proposed an algorithm to
+conjunction of feature predicates and proposed an algorithm to
 maximize coverage under the constraint of minimum approximation accuracy.

### 2024-02-14 paper.tex
Complete 1st version

@@
 \crefname{figure}{Fig.}{Figs.}
-\crefname{table}{Tab.}{Tabs.}
+\crefname{table}{Table.}{Tables.}
 
@@
 Consequently,
-there has been extensive research in the field of post hoc explanation
+there has been extensive research in the field of post hoc explanations
 for machine learning models \cite{%
@@
 
-Existing methods on post hoc explanations categorize into model-dependent and
-model-agnostic methods,
+Existing methods on post hoc explanations categorize into
+\emph{model-dependent} and \emph{model-agnostic} methods,
 based on their dependence on the model's structure.
@@
 Although they are applicable to any model, available information is limited.
-Model-agnostic methods further classify into global and local methods
-based on their treatment of input space.
+Model-agnostic methods further classify into
+\emph{global} and \emph{local} methods based on their locality in input space.
 Global methods aim to explain the model's behavior across the entire input space,
@@
 Local methods, in contrast, explain the model's output for a specific input
-(focus point) in the vicinity of that input.
+(focal point) in the vicinity of that input.
 While local methods offer more simple and accurate explanations than global methods,
@@
 
-This paper specifically focuses on model-agnostic and local methods.
-For instance, Local Interpretable Model-agnostic Explanations (LIME) \cite{ribeiro2016why} approximates the complex model's decision boundary locally using a simpler model.
-Although LIME enables users to interpret the local behavior of complex models, it has been criticized for not optimizing the approximation region \cite{radulovic2023bella} and not presenting the approximation region in an interpretable form \cite{ribeiro2018anchors}.
+This paper specifically focuses on \emph{local} \emph{model-agnostic} methods.
+For instance, LIME (Local Interpretable Model-agnostic Explanations)
+\cite{ribeiro2016why} approximates the complex model's decision boundary
+locally using a simpler model.
+Although LIME enables users to interpret the local behavior of complex models,
+it does not optimize the approximation region \cite{radulovic2023bella} and
+the effective scope of the explanation is not explicitly presented
+\cite{ribeiro2018anchors}.
 
 To address the limitations of LIME,
-we propose an algorithm that interprets complex models
-in an interpretable approximation region,
-taking inspiration from another explanation method called Anchor
-\cite{ribeiro2018anchors}.
-Our proposed method maximizes the accuracy of the learned approximation model
-within a rectangular approximation region under lower-bound constraints.
-The resulting rectangular region is expressed as a conjunction of feature predicates,
-enhancing interpretability for the user.
+we propose a new method called R-LIME (Ruled LIME),
+which interprets complex classifiers in an interpretable region.
+R-LIME locally approximates a complex decision boundary linearly
+in a rectangular region and maximizes the region as long as the accuracy of the linear
+classifier is higher than a specified threshold.
+The resulting rectangular region is interpretable for users because it is
+expressed as a conjunction of feature predicates.
 
 \section{Related Work}
-The figures presented visually compare three methods: LIME, Anchor, and BELLA.
-
 \begin{figure}[t]
+  \centering
   \vspace{0.5cm}
-  \begin{subfigure}[t]{\textwidth}
+  \begin{subfigure}[t]{0.55\textwidth}
     \centering
-    \includegraphics[width=0.55\textwidth]{lime_vs_anchor_exp_a.png}
-    \caption{Instance around the focal point.}\label{fig:lime_vs_anchor_exp_a}
+    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_a.png}
+    \caption{Instances around the focal point.}\label{fig:lime_vs_anchor_exp_a}
     \vspace{0.5cm}
   \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\textwidth}
+  \begin{subfigure}[t]{0.45\textwidth}
     \centering
-    \includegraphics[width=0.4\textwidth]{lime_vs_anchor_exp_b.png}
-    \caption{Explanation by LIME.}\label{fig:lime_vs_anchor_exp_b}
+    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_b.png}
+    \caption{%
+      Explanations by LIME.
+      They provide contributions of each feature to the output,
+      but do not explicitly indicate its scope.
+    }\label{fig:lime_vs_anchor_exp_b}
     \vspace{0.5cm}
   \end{subfigure}
-  \begin{subfigure}[t]{\textwidth}
+  \begin{subfigure}[t]{0.55\textwidth}
     \centering
-    \includegraphics[width=0.55\textwidth]{lime_vs_anchor_exp_c.png}
-    \caption{Explanation by Anchor.}\label{fig:lime_vs_anchor_exp_c}
+    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_c.png}
+    \caption{%
+      Explanations by Anchor.
+      They provide the effective scope of the explanation,
+      but do not provide details about the influence of each feature.
+    }\label{fig:lime_vs_anchor_exp_c}
   \end{subfigure}
-  \caption[Examples of output results by LIME and Anchor]{Examples of output results by LIME and Anchor \cite{ribeiro2018anchors}.}\label{fig:lime_vs_anchor_exp}
+  \caption{%
+    Explanations by LIME and Anchor
+    for an LSTM sentiment prediction model \cite{ribeiro2018anchors}.
+  }\label{fig:lime_vs_anchor_exp}
 \end{figure}
-In this chapter, we provide an overview of existing research on model-agnostic and local post hoc explanations, particularly focusing on studies closely related to the proposed method.
+In this chapter,
+we provide an overview of existing research on local model-agnostic explanations,
+particularly focusing on studies closely related to our proposed method.
 
 \subsection{LIME (Local Interpretable Model-agnostic Explanations) \cite{ribeiro2016why}}
-LIME is a method for locally approximating a trained black-box classifier $f: \mathbb{R}^d \to \{0,1\}$ around a focal point $x \in \mathbb{R}^d$ using a linear model $g: \mathbb{R}^d \to \{0,1\}$ (\cref{fig:lime}).
+LIME locally
+approximates a trained black-box classifier $f: \mathbb{R}^d \to \{0,1\}$
+around a focal point $x \in \mathbb{R}^d$
+by a linear classifier $g: \mathbb{R}^d \to \{0,1\}$
+(\cref{fig:lime}).
 The process involves:
 \begin{enumerate}
-  \item Obtaining a set of perturbed samples $\mathcal{Z}_p$ around $x$ and the set of pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
-  \item Learning an interpretable model $g$ using $\mathcal{Z}_p$ and $f(\mathcal{Z}_p)$ by minimizing the following loss function:
+  \item Obtaining a set of perturbed samples $\mathcal{Z}_p$ around $x$
+        and the set of pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
+  \item Learning a linear classifier $g$
+        using $\mathcal{Z}_p$ and $f(\mathcal{Z}_p)$
+        by minimizing the following loss function:
         \begin{equation}
@@
         \end{equation}
-        where $\pi_x(z)$ is a weight function designed to be larger for samples closer to $x$, typically implemented using an exponential kernel.
+        where $\pi_x(z)$ is a weight function designed to be larger for samples
+        closer to $x$, typically implemented using an exponential kernel.
 \end{enumerate}
 
-LIME provides valuable insights into the local behavior of the model by showing the contribution of each feature to the output $f(x)$.
-However, due to not explicitly indicating the perturbation region, users cannot assess the effective scope of the explanation \cite{ribeiro2018anchors}.
-An example explanation for an LSTM sentiment prediction model using LIME is illustrated in \cref{fig:lime_vs_anchor_exp_b}.
-The left explanation suggests that the word "not" contributes to the model's positive prediction, which does not apply to the instance on the right.
-However, without the explicit perturbation region, users might mistakenly apply the left explanation to the right instance, potentially leading to a misunderstanding of the black-box model's behavior \cite{ribeiro2018anchors}.
+LIME provides valuable insights into the local behavior of the model
+by showing the contribution of each feature to the output $f(x)$.
+However, due to not explicitly indicating the perturbation region,
+users cannot assess the effective scope of the explanation
+\cite{ribeiro2018anchors}.
+An example of explanation by LIME for an LSTM sentiment prediction model
+is illustrated in \cref{fig:lime_vs_anchor_exp_b}.
+The left explanation suggests that
+the word "not" contributes to the model's positive prediction,
+which does not apply to the instance on the right.
+However, without the explicit perturbation region,
+users might mistakenly apply the left explanation to the right instance,
+potentially leading to a misunderstanding of the black-box model's behavior
+\cite{ribeiro2018anchors}.
 
 \subsection{Anchor \cite{ribeiro2018anchors}}\label{sec:anchor}
-Anchor represents a rectangular region,
-expressed as a conjunction of feature predicates (rules),
-that maximizes the probability of the black-box classifier $f$ outputting $f(x)$ within the region.
-It aims to highlight important features contributing significantly to the output (\cref{fig:anchor}).
+Anchor represents a rectangular region containing the focal point $x$,
+expressed as a conjunction of feature predicates (a rule),
+that maximizes the probability of the black-box classifier $f$
+outputting $f(x)$ within the region.
+It aims to highlight important features
+contributing significantly to the output (\cref{fig:anchor}).
 
-For a discrete $m$-dimensional input space $\ispace$ with a trained black-box classifier $f: \ispace \to \{0,1\}$, an instance $x \in \ispace$, and a distribution $\mathcal{D}$ over the input space, a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
+For a discrete $m$-dimensional input space $\ispace$
+with a trained black-box classifier $f: \ispace \to \{0,1\}$,
+an instance $x \in \ispace$, 
+and a distribution $\mathcal{D}$ over the input space,
+a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
 The predicates $a_i(z)$ evaluate to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
@@
 
-where $\mathcal{D}(z|A)$ is the conditional distribution in the region where the rule $A$ is true.
-% When sampling the perturbation vector $z$ according to the distribution $\mathcal{D}$,
-$\Prec(A)$ represents the probability that the output of $f$ matches between the perturbation $z$ and the focal point $x$ in the region $A$, and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
+where $\mathcal{D}(z|A)$ is the conditional distribution in the region
+where the rule $A$ returns true.
+$\Prec(A)$ represents the probability that the output of $f$ matches
+between the perturbation $z\sim\mathcal{D}(z|A)$ and the focal point $x$,
+and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
 
-An Anchor maximizes coverage within the given threshold $\tau$ while maintaining accuracy.
-However, direct computation of \cref{eq:anchor_def_prec} is not feasible, and it is evaluated using PAC (Probably Approximately Correct) through sampling.
-Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$, the accuracy constraint is relaxed as follows:
+Anchor maximizes coverage under the constraint that
+the accuracy of the rule $A$ exceeds a given threshold $\tau$.
+However, \cref{eq:anchor_def_prec} is not directly computable.
+Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$,
+the accuracy constraint is relaxed as follows:
 \begin{equation}
@@
 
-While Anchor provides a clear presentation of the effective scope of the explanation, the information it includes is less than LIME, limiting its utility \cite{ribeiro2018anchors}.
-An example explanation for an LSTM sentiment prediction model using Anchor is depicted in \cref{fig:lime_vs_anchor_exp_c}.
-The left explanation suggests that changing words other than "not" and "bad" has little impact on the classifier's output.
-While it clearly does not apply to the right instance, the explanation does not provide details about the influence of words like "not" or "bad," resulting in less user insight into the model's behavior compared to LIME (\cref{fig:lime_vs_anchor_exp_b}).
+While Anchor provides an effective scope of the explanation,
+the information it includes is less than LIME,
+limiting its utility \cite{ribeiro2018anchors}.
+An example of Anchor explanation for an LSTM sentiment prediction model
+is depicted in \cref{fig:lime_vs_anchor_exp_c}.
+The left explanation suggests that changing words other than "not" and "bad"
+has little impact on the classifier's output.
+While it clearly does not apply to the right instance,
+the explanation does not provide details about the influence of each word,
+resulting in less user insight into the model's behavior compared to LIME
+(\cref{fig:lime_vs_anchor_exp_b}).
 
-\subsection{BELLA (Black box model Explanations by Local Linear Approximations) \cite{radulovic2023bella}}
-BELLA addresses the non-optimization of the approximation region, a drawback of LIME, by learning a local linear approximation model $g$ using a subset $Z'$ of the dataset $Z$ instead of perturbed samples (\cref{fig:bella}).
+\subsection{%
+  BELLA (Black box model Explanations by Local Linear Approximations)
+  \cite{radulovic2023bella}
+}
+BELLA addresses the non-optimization of the approximation region,
+a drawback of LIME,
+by learning a local linear classifier $g$
+using a subset $Z'$ of the dataset $Z$
+instead of perturbed samples (\cref{fig:bella}).
 The process involves:
 \begin{enumerate}
-  \item Computing the distance $d_x(z)$ for all instances $z$ in $Z$ with respect to the focal point $x$.
-  \item Selecting the $k$ instances with the smallest $d_x(z)$, forming a subset $Z_s(k) \subseteq Z$.
-  \item Learning the local linear approximation model $g$ using $Z_s(k)$ and calculating the similarity measure $\mathcal{R}(k)$ between $f$ and $g$.
+  \item Computing the distance $d_x(z)$ for all instances $z$ in $Z$
+        with respect to the focal point $x$.
+  \item Selecting the $k$ instances with the smallest $d_x(z)$,
+        forming a subset $Z_s(k) \subseteq Z$.
+  \item Learning the local linear classifier $g$ using $Z_s(k)$
+        and calculating the similarity measure $\mathcal{R}(k)$ between $f$ and $g$
+        over $k=1,2,\dots,|Z|$.
   \item Obtaining the optimal $k^*$ by maximizing $\mathcal{R}(k)$.
@@
 
-BELLA aims to enhance the reliability of explanations by optimizing the approximation region for high-accuracy linear approximations.
-However, it assumes direct access to the dataset $Z$ used for training the classifier, making it inapplicable in scenarios where direct access to the dataset is restricted for privacy reasons.
-Additionally, as BELLA presents the approximation region as a subset of the dataset, its interpretability is lower compared to Anchor.
+BELLA aims to enhance the reliability of explanations
+by optimizing the approximation region for high-accuracy linear approximations.
+However, it assumes direct access to the dataset $Z$ used for training the classifier,
+making it inapplicable in scenarios where direct access to the dataset is restricted.
+Additionally,
+as BELLA presents the approximation region as a subset of the dataset,
+its interpretability is lower compared to Anchor.
 
@@
     \caption{%
-      LIME: Locally approximates the decision boundary around the focal point.}\label{fig:lime}
+      LIME: Locally approximates the decision boundary around the focal point.
+    }\label{fig:lime}
   \end{subfigure}%
@@
     \includegraphics[width=\textwidth]{anchor}
-    \caption{Anchor: Maximizes coverage of a rectangular region containing the focal point under accuracy constraints.}\label{fig:anchor}
+    \caption{%
+      Anchor: Maximizes coverage of a rectangular region
+      containing the focal point under accuracy constraints.
+    }\label{fig:anchor}
   \end{subfigure}
@@
     \caption{%
-      BELLA: Explores a subset of the dataset, maximizing similarity between the local linear approximation model and the black-box classifier.}\label{fig:bella}
+      BELLA: Explores a subset of the dataset,
+      maximizing similarity between the local linear classifier
+      and the black-box classifier.
+    }\label{fig:bella}
   \end{subfigure}
@@
     \caption{%
-      R-LIME: Maximizes coverage of a rectangular region containing the focal point under lower constraints on the accuracy of the approximation model.}\label{fig:rlime}
+      R-LIME:
+      Maximizes coverage of a rectangular region containing the focal point
+      under lower constraints on the accuracy of the linear classifier.
+    }\label{fig:rlime}
   \end{subfigure}
@@
 We propose R-LIME,
-a method that aims to address the limitations of LIME \cite{ribeiro2016why}
-and its improvement methods such as
+a method that aims to address the limitations of LIME \cite{ribeiro2016why},
 Anchor \cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
-Similar to LIME,
-the proposed method locally approximates the given black-box classifier $f$
-around the focal point $x$ by a linear model $g$.
-However,
-by adopting a rectangular perturbation region similar to Anchor,
-it represents feature predicates (rules).
-The accuracy of explanations is defined as the "accuracy" of rules,
-and the "coverage" of rules defines the generality of explanations.
-The proposed method maximizes coverage under lower constraints on accuracy
+Our method locally approximates the given black-box classifier $f$
+around the focal point $x$ by a linear classifier $g$ similar to LIME and BELLA,
+but samples parturbation from a rectangular region similar to Anchor
 (\cref{fig:rlime}).
+The accuracy of $g$ is defined as the "accuracy" of the rule,
+and the generality of explanations is defined as the "coverage" of the rule.
 
-Anchor maximizes the coverage of region $A$ within which the output of the black-box classifier $f$ matches $f(x)$ with respect to the probability under lower constraints.
-The proposed method, on the other hand, learns an approximation model $g$ within the rectangular region $A$ and maximizes the coverage of $A$ under lower constraints on the accuracy of $g$.
-We modify the definition of accuracy using \cref{eq:anchor_def_prec} as follows:
+Anchor maximizes the coverage of region $A$
+as long as the probability of the output of the black-box classifier $f$ matching $f(x)$
+within $A$ exceeds a given threshold $\tau$.
+The proposed method, on the other hand, learns an linear classifier $g$
+within the rectangular region $A$ and maximizes the coverage of $A$
+under lower constraints on the accuracy of $g$. 
+We modify the Anchor's definition of accuracy in \cref{eq:anchor_def_prec}
+as follows:
 \begin{equation}
@@
 \end{equation}
-where $G$ represents the set of possible linear approximation models.
-By solving the optimization problem in \cref{eq:main_problem} under this modified accuracy definition, we can select rules that learn high-accuracy approximation models, among which the coverage is maximized.
-The proposed method's algorithm, shown in \cref{sec:alg}, is largely based on the algorithms used in Anchor.
-
-In this paper, we refer to the proposed method as "R-LIME" (Ruled LIME). The characteristics of R-LIME are listed below:
+where $G$ is the set of possible linear classifiers.
+By solving the optimization problem in \cref{eq:main_problem}
+under the modified accuracy definition in \cref{eq:def_prec},
+we can select the rule that enables explanation with high accuracy and generality.
+The characteristics of R-LIME are listed below:
 \begin{itemize}
-  \item The perturbation vector's generation region is optimized and presented in a user-interpretable format.
-  \item Interpretation is conducted without direct access to the dataset, utilizing only the distribution.
-  \item The number of samples is dynamically determined based on the estimated accuracy without the need for a predefined amount.
+  \item The approximation region is optimal and interpretable.
+  \item The dataset is not directly accessed, and only the distribution is utilized.
+  \item The number of samples is dynamically determined
+        based on the estimated accuracy without the need for predefining it.
 \end{itemize}
-% This enables model interpretation without direct access to the data, even in scenarios with significant privacy constraints.
-The optimized and presented explanation's applicable range allows users to evaluate the reliability and generality of the generated explanations.
 
@@
       Overview of the R-LIME algorithm.
-      The progression of the algorithm from left to right is illustrated.
+      The progression of the algorithm is illustrated from left to right.
       The solid line represents the rectangular region $A$,
@@
 }
-For non-convex optimization problems like \cref{eq:main_problem}, greedy methods are often employed.
-However, greedy methods tend to converge to local optima, and to address this, the proposed method utilizes beam search, which selects multiple candidates at each iteration.
+
+Our method's algorithm is mainly based on that used in Anchor.
+For non-convex optimization problems like \cref{eq:main_problem},
+greedy search are often used.
+However,
+greedy methods tend to converge to local optima, and to address this,
+R-LIME utilizes beam search,
+which selects multiple candidates at each iteration.
 The pseudocode is shown in \cref{alg:greedy_search}.
 
-\subsubsection{Candidate Rule Generation}
-To generate new candidate rules, one additional predicate is added to each of the $B$ candidate rules obtained in the previous iteration.
+\subsubsection{Generation of New Candidate Rules}
+To generate new candidate rules,
+one additional predicate is added to each of the $B$ candidate rules
+selected in the previous iteration.
 The pseudocode is shown in \cref{alg:generate_cands}.
-$T(x)$ represents the set of attribute-value pairs (predicates) that $x$ possesses, and $T(x)\setminus A$ represents the conjunction of predicates in $T(x)$ not included in rule $A$.
+$T(x)$ is the set of attribute-value pairs (predicates) that are true for $x$,
+and $T(x)\setminus A$ is the set of predicates in $T(x)$ not included in rule $A$.
 
-\subsubsection{Selection of Candidate Rule with Maximum Accuracy}
-Given the set of generated candidate rules $\cands$, the algorithm selects the top $B$ candidates with the highest accuracy.
+\subsubsection{Selection of Candidate Rules with Maximum Accuracy}
+Given the set of generated candidate rules $\cands$,
+the algorithm selects the top $B$ candidates with the highest accuracy.
 This is treated as an optimal arm identification problem in the multi-armed bandit framework.
-Each candidate rule $A_i\in\cands$ is considered an arm, and their accuracy $\Prec(A_i)$ is treated as the distribution of rewards.
-By sampling $z\sim\mathcal{D}(\cdot|A_i)$ and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial, the algorithm updates $g_i$ using the sampled perturbation vector $z$ and the pseudo-label $f(z)$ immediately after each trial.
-To efficiently select the rule (arm) with the highest accuracy, the KL-LUCB algorithm \cite{kaufmann2013information} is employed.
+Each candidate rule $A_i\in\cands$ is considered an arm,
+and their accuracy $\Prec(A_i)$ is treated as the distribution of rewards.
+By sampling $z\sim\mathcal{D}(\cdot|A_i)$
+and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial,
+the algorithm updates $g_i$ using the sampled perturbation vector $z$
+and the pseudo-label $f(z)$ after each trial.
+To efficiently select the rule (arm) with the highest accuracy,
+we employ the KL-LUCB algorithm \cite{kaufmann2013information}.
 The pseudocode is shown in \cref{alg:best_cands}.
-The KL-LUCB algorithm assumes that the reward distribution for each arm remains unchanged, while the proposed method updates the approximation model $g_i$ with each sampling, which may not satisfy this assumption.
+For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
+\begin{equation}
+  P(\underset{A\in\cands}{\min}\Prec(A)\ge
+  \underset{A'\in\mathcal{A}}{\min}\Prec(A')-\epsilon)\ge1-\delta.
+\end{equation}
+However, 
+the KL-LUCB algorithm assumes that the reward distribution for each arm
+remains unchanged, 
+while our method updates the classifier $g_i$ with each sampling,
+which may not satisfy this assumption.
 This issue is discussed further in \cref{sec:reward}.
@@
 \end{equation}
-where $\Prec_{l}(A,\delta)$ represents the lower limit of the $100(1-\delta)$\% confidence interval for $\Prec(A)$.
-If the received set of candidate rules, $\mathcal{A}$, includes a rule satisfying \cref{eq:stop_condition},
-the one with the maximum coverage among them is selected, and the iteration is concluded.
-If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop_condition}, it returns \textbf{null},
+where $\Prec_{l}(A,\delta)$ is the lower limit of
+the $100(1-\delta)$\% confidence interval for $\Prec(A)$.
+If the received set of candidate rules, $\mathcal{A}$,
+includes a rule satisfying \cref{eq:stop_condition},
+the one with the maximum coverage among them is selected,
+and the iteration is terminated.
+If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop_condition},
+it returns \textbf{null},
 and proceeds to the next iteration.
@@
 
-The algorithmic procedure outlined above approximates the solution to the optimization problem in \cref{eq:main_problem} under the definition of accuracy in \cref{eq:def_prec}.
-It iteratively selects a rectangular region (rule) with the learned approximation model's accuracy exceeding a given threshold while maximizing coverage.
-The selected rule, with the maximum coverage meeting accuracy constraints, is output after each iteration.
+% The algorithmic procedure outlined above approximates
+% the solution to the optimization problem in \cref{eq:main_problem}
+% under the definition of accuracy in \cref{eq:def_prec}.
 
 \section{Experiments}
-To verify the effectiveness of the proposed method, LIME and R-LIME were compared using a single dataset.
+To verify the effectiveness of the proposed method,
+We compare LIME and R-LIME using a real-world dataset.
 
@@
 The experiments utilized the recidivism dataset \cite{schmidt1988predicting}.
-This dataset contains information on 9,549 prisoners released from North Carolina prisons between July 1, 1979, and June 30, 1980.
-The dataset includes 19 items such as race, gender, presence of alcohol dependence, number of prior offenses, and recidivism.
-For this experiment, we treated the binary classification problem of predicting the presence or absence of recidivism (Recidivism) as the target label.
-Preprocessing included discretization of continuous features, resulting in 15 features.
-This problem setting simulates a case where a machine learning model is introduced to decide parole for prisoners.
-Since such decisions can have a significant impact on a person's life, it is crucial for users to interpret the outputs of black-box models appropriately.
+This dataset contains information on 9,549 prisoners released from
+North Carolina prisons between July 1, 1979, and June 30, 1980.
+The dataset includes 19 items such as race, gender,
+presence of alcohol dependence, number of prior offenses, and recidivism.
+For this experiment, 
+we treated the binary classification problem of predicting
+the presence or absence of recidivism (Recidivism) as the target label. 
+We discretized continuous features and removed missing values,
+resulting in 15 features. 
+This problem setting can be considered as a case
+where a machine learning model is introduced to decide parole for prisoners.
+Since such decisions can have a significant impact on a person's life,
+it is crucial for users to interpret the outputs of black-box models appropriately.
 
-The dataset, after removing missing values, was split into training data (7,639 instances) and test data (955 instances).
+The dataset, after removing missing values,
+was split into training data (7,639 instances) and test data (955 instances).
 A random forest model with 50 trees was trained using the training data.
-Subsequently, LIME and R-LIME explanations were generated for two instances extracted from the test data (\cref{fig:instance}).
-In R-LIME, logistic regression was used as the linear approximation model, and the distribution $\mathcal{D}$ was estimated using a multivariate normal distribution based on the training data.
-
-The beam width was set to $B=10$, the confidence coefficient to $1-\delta=0.95$, and the tolerance of the KL-LUCB algorithm to $\epsilon=0.05$.
+Subsequently, LIME and R-LIME explanations were generated
+for two instances extracted from the test data (\cref{fig:instance}).
+In R-LIME, logistic regression was used as the linear approximation model, 
+and the distribution $\mathcal{D}$ was a multivariate normal distribution
+estimated from the training data.
+The beam width was set to $B=10$,
+the confidence coefficient to $1-\delta=0.95$,
+and the tolerance of the KL-LUCB algorithm to $\epsilon=0.05$.
 Accuracy thresholds $\tau$ were set to $\tau=0.70,0.80,0.90$.
@@
 The results of the experiment are shown in \cref{fig:A,fig:B}.
-The values assigned to each attribute name represent the contribution (weights of the learned linear approximation model) to the output of the black-box classifier, normalized such that the absolute sum is 1.
-The figures also highlight the five attributes with the highest absolute contribution.
+The values assigned to each attribute name represent the contribution
+(weights of the learned linear classifier)
+to the output of the black-box classifier,
+normalized such that the absolute sum is 1.
+The figures also display the 5 attributes with the highest absolute contribution.
 
-Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) indicate that attributes such as having a significant prior record (Prior) or committing a crime against property (Crime against Property) primarily contribute positively to the prediction (predicting that the inmate will be re-incarcerated).
-On the other hand, attributes like older age (Age), being married (Married), and being of white race (Race) contribute negatively to the prediction (predicting that the inmate will not be re-incarcerated).
-While these LIME explanations provide valuable insights into the behavior of the black-box model, they do not explicitly indicate the range of application, leaving users unable to determine to which inmates the explanations are applicable.
+Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) indicate that
+attributes such as having a significant prior record (Prior) or committing a
+crime against property (Crime against Property) primarily contribute positively
+to the prediction (predicting that the prisoner will be re-arrested).
+On the other hand,
+attributes like older age (Age), being married (Married),
+and being of white race (Race) contribute negatively to the prediction
+(predicting that the prisoner will not be re-arrested).
+While these LIME explanations provide valuable insights into the behavior of
+the black-box model,
+they do not explicitly indicate the application scope of the explanations, 
+leaving users unable to determine to which inmates the explanations are applicable.
 
-In contrast, R-LIME expresses the application range of explanations
+In contrast, R-LIME expresses the application scope of explanations
 as a conjunction of predicates.
@@
 under $\tau=0.70$ (\cref{fig:A-rlime-70}) indicates that it is applicable
-only to married males (Married$=$Yes, Gender$=$Male).
+only to married prisoner (Married$=$Yes).
 Furthermore, the generated explanations include the accuracy and coverage of
@@
 \subsubsection{Experimental Setup}
-To demonstrate that R-LIME adapts a highly accurate linear approximation model
-to the optimized approximation region,
+To demonstrate that R-LIME learns a highly accurate linear approximation model
+in the optimized approximation region,
 we conducted a comparison of the local accuracy of explanations
@@
 and generated explanations (with $\tau=0.70,0.80,0.90$) using LIME and R-LIME.
-We then sampled 10,000 instances within the rectangular region obtained by R-LIME and calculated the local accuracy of both methods.
+We then sampled 10,000 instances within the rectangular region
+obtained by R-LIME and calculated the local accuracy of both methods.
 \subsubsection{Experimental Results}
@@
     Comparison of local accuracy between LIME and R-LIME.
-    We generated explanations for 100 instances using each method
-    and calculated the accuracy for each method within the 10,000 instances
-    sampled inside the rectangular region obtained by R-LIME.
+    R-LIME achieved higher and less variable accuracy compared to LIME
+    for all values of $\tau$.
   }\label{fig:box_plot}
 \end{figure}
-The results are presented in \cref{fig:box_plot}, showcasing the distribution of the accuracy of the linear approximation models obtained by LIME and R-LIME.
+The results are presented in \cref{fig:box_plot},
+showcasing the distribution of the accuracy of the linear approximation models
+learned by LIME and R-LIME.
 R-LIME exhibits higher accuracy compared to LIME for all values of $\tau$.
-This suggests that the linear approximation models learned by LIME and R-LIME differ significantly, and R-LIME learns a high-accuracy linear approximation model adapted to the rectangular region.
-Additionally, as $\tau$ increases, the variability in the accuracy of LIME widens.
-This indicates that the linear models learned by LIME may not function effectively as approximation models depending on how the region is selected.
+This suggests that the linear classifiers learned by LIME and R-LIME
+differ significantly,
+and R-LIME learns a high-accuracy linear classifier adapted to the rectangular region.
+Additionally, as $\tau$ increases,
+the variability in the accuracy of LIME widens.
+This indicates that the linear classifiers learned by LIME may not function
+effectively as approximation models depending on how the region is selected.
 
 \section{Challenges and Future Perspectives}
-
  {%
@@
 \subsection{Behavior Regarding Imbalanced Label Distribution}
-R-LIME may generate less useful explanations when there is bias in the distribution of black-box model outputs.
-When the distribution of black-box model outputs is significantly biased for a given accuracy threshold $\tau$ (the ratio of the majority label is less than $\tau$), the approximation region generated by R-LIME covers the entire input space, and the learned linear approximation model always outputs the majority label (\cref{fig:imbalanced}).
+R-LIME may generate less useful explanations
+when there is bias in the distribution of black-box model outputs.
+When the distribution of black-box model outputs is significantly biased
+for a given accuracy threshold $\tau$
+(when the ratio of the minority label is less than $1-\tau$),
+the approximation region generated by R-LIME covers the entire input space,
+and the learned linear classifier always outputs the majority label
+(\cref{fig:imbalanced}).
 
-As a first solution to this problem, changing the loss function is considered.
-Using weighted logistic loss or Focal Loss \cite{lin2020focal} as the loss function might lead to the generation of more useful explanations in the case of imbalanced label distribution.
-Another solution involves adding constraints to limit the label distribution bias within the approximation region.
+A first possible solution to this problem is modifying the loss function.
+Using weighted logistic loss or Focal Loss \cite{lin2020focal}
+as the loss function might lead to the generation of more useful explanations
+in the case of imbalanced label distribution.
+Another solution involves adding constraints
+to limit the label distribution bias within the approximation region.
 In addition to \cref{eq:const_prec}, adding a constraint like
@@
       Deviation between the estimated accuracy and the true accuracy.
+      Deviation was relatively small considering confidence level $1-\delta=0.95$.
     }\label{tab:reward}
@@
 }
-In R-LIME, the problem of selecting the rule with the highest accuracy is formulated as the optimal arm identification problem in multi-armed bandit theory, solved using the KL-LUCB algorithm \cite{kaufmann2013information}.
-However, this algorithm assumes that the reward distribution remains constant, while in R-LIME, the reward distribution (accuracy of the linear approximation model) changes with every update of the approximation model after sampling.
-Therefore, rewards obtained at an early stage when the accuracy is still low might influence the estimated value and deviate from the true value.
+In R-LIME,
+the problem of selecting the rule with the highest accuracy is formulated
+as the optimal arm identification problem in multi-armed bandit theory,
+solved using the KL-LUCB algorithm \cite{kaufmann2013information}.
+However, this algorithm assumes that the reward distribution remains constant,
+while in R-LIME,
+the reward distribution (accuracy of the linear approximation)
+changes with every update of the approximation model after sampling.
+Therefore, rewards obtained at an early stage
+might influence the estimated value and deviate from the true value.
 
-An experiment was conducted to evaluate the deviation between the estimated accuracy and the true accuracy.
-Explanations were generated for 3,200 data instances sampled from the dataset, and the estimated accuracy was compared with the true accuracy.
-The true accuracy was calculated based on 1,000 instances sampled within the approximation region, considering cases where the outputs of the black-box model and the linear approximation model matched.
-The results in \cref{tab:reward} show a mean deviation of 0.012 with a standard deviation of 0.017.
-While the deviation is relatively small, improvements to the selection algorithm need to consider the changing accuracy.
+We conducted an experiment to evaluate the deviation
+between the estimated accuracy and the true accuracy.
+We generated explanations for 3,200 data instances sampled from the dataset,
+and compared the estimated accuracy with the true accuracy.
+The true accuracy was calculated based on 1,000 instances sampled
+within the approximation region.
+The results in \cref{tab:reward} show a mean deviation of 0.012
+with a standard deviation of 0.017.
+While the deviation was relatively small considering confidence level $1-\delta=0.95$,
+we should modify the selection algorithm to consider the varying accuracy.
 
@@
 
-One potential method to quantitatively evaluate "interpretability" is through user studies.
-For example, \cite{ribeiro2018anchors} conducted user studies, assuming that if users could predict the output of a black-box model with high accuracy based on provided explanations, those explanations contained valuable information about the model's behavior.
-Similarly, conducting user studies in this research would be desirable to evaluate the interpretability of the proposed method.
+One potential method to quantitatively evaluate "interpretability" is
+through user studies.
+For example, \cite{ribeiro2018anchors} conducted user studies,
+assuming that if users could predict the output of a black-box model
+with high accuracy based on provided explanations,
+those explanations contained valuable information about the model's behavior.
+Similarly,
+conducting user studies in this research would be desirable
+to evaluate the interpretability of the proposed method.
 
@@
 
-% \subsection{A Subsection Sample}
-% Please note that the first paragraph of a section or subsection is
-% not indented. The first paragraph that follows a table, figure,
-% equation etc.\ does not need an indent, either.
-%
-% Subsequent paragraphs, however, are indented.
-%
-% \subsubsection{Sample Heading (Third Level)} Only two levels of
-% headings should be numbered. Lower level headings remain unnumbered;
-% they are formatted as run-in headings.
-%
-% \paragraph{Sample Heading (Fourth Level)}
-% The contribution should contain no more than four levels of
-% headings. Table~\ref{tab1} gives a summary of all heading levels.
-%
-% \begin{table}
-% \caption{Table captions should be placed above the
-% tables.}\label{tab1}
-% \begin{tabular}{|l|l|l|}
-% \hline
-% Heading level &  Example & Font size and style\\
-% \hline
-% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-% \hline
-% \end{tabular}
-% \end{table}
-%
-%
-% \noindent Displayed equations are centered and set on a separate
-% line.
-% \begin{equation}
-% x + y = z
-% \end{equation}
-% Please try to avoid rasterized images for line-art diagrams and
-% schemas. Whenever possible, use vector graphics instead (see
-% Fig.~\ref{fig1}).
-%
-% \begin{figure}
-% \includegraphics[width=\textwidth]{fig1.eps}
-% \caption{A figure caption is always placed below the illustration.
-% Please note that short captions are centered, while long ones are
-% justified by the macro package automatically.} \label{fig1}
-% \end{figure}
-%
-% \begin{theorem}
-% This is a sample theorem. The run-in heading is set in bold, while
-% the following text appears in italics. Definitions, lemmas,
-% propositions, and corollaries are styled the same way.
-% \end{theorem}
-% %
-% % the environments 'definition', 'lemma', 'proposition', 'corollary',
-% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
-% %
-% \begin{proof}
-% Proofs, examples, and remarks have the initial word in italics,
-% while the following text appears in normal font.
-% \end{proof}
-% For citations of references, we prefer the use of square brackets
-% and consecutive numbers. Citations using labels or the author/year
-% convention are also acceptable. The following bibliography provides
-% a sample reference list with entries for journal
-% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-% and a homepage~\cite{ref_url1}. Multiple citations are grouped
-% \cite{ref_article1,ref_lncs1,ref_book1},
-% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-
 \subsubsection{Acknowledgements}
@@
 % 3rd-level heading).
-I would like to express my gratitude to Associate Professor Keigo Kimura from the Department of Mathematical Science, Division of Information Recognition, Graduate School of Information Science and Technology, Hokkaido University.
-He provided invaluable guidance, from setting the research theme to outlining the strategy and content of this study.
-Additionally, I appreciate the diverse insights shared by Professor Mineichi Kudo in the same laboratory.
-Finally, I am deeply thankful to all the members of the laboratory for their helpful advice and collaboration throughout the research process.
+I would like to express my gratitude to Associate Professor Keigo Kimura
+from the Department of Mathematical Science,
+Division of Information Recognition,
+Graduate School of Information Science and Technology, Hokkaido University.
+He provided invaluable guidance,
+from setting the research theme to outlining the strategy and content of this study.
+Additionally,
+I appreciate the diverse insights shared by Professor Mineichi Kudo in the same laboratory.
+Finally, I am deeply thankful to all the members of the laboratory
+for their helpful advice and collaboration throughout the research process.
 

### 2024-02-14 python/exp2/lime_vs_rlime.py

@@ -2,18 +2,16 @@
 
 import csv
 import multiprocessing
-import sys
 from functools import partial
 
 import numpy as np
 import pandas as pd
 from sklearn.ensemble import RandomForestClassifier
 
-sys.path.append("../NewLIME")
-# pylint: disable=import-error,wrong-import-position
-import newlime_base  # pyright: ignore[reportMissingImports] # noqa: E402
-import newlime_tabular  # pyright: ignore[reportMissingImports] # noqa: E402
-import newlime_utils  # pyright: ignore[reportMissingImports] # noqa: E402
+from NewLIME import mylime, newlime_base, newlime_tabular, newlime_utils
+from NewLIME.newlime_base import Arm
+from NewLIME.newlime_types import IntArray
+from NewLIME.sampler import Sampler
 
 
 def main() -> None:
@@ -21,7 +19,7 @@ def main() -> None:
 
     # Load the dataset.
     dataset = newlime_utils.load_dataset(
-        "recidivism", "../NewLIME/anchor-experiments/datasets/", balance=True
+        "recidivism", "NewLIME/datasets/", balance=True
     )
 
     # Learn the black box model.
@@ -30,39 +28,75 @@ def main() -> None:
 
     # Get the target instances.
     sample_num = 100
-    result_list = multiprocessing.Manager().list()
 
-    tau = 0.70
+    for tau in [0.80, 0.90]:
 
-    func = partial(
-        compare_lime_and_newlime,
-        dataset=dataset,
-        black_box=black_box,
-        tau=tau,
-        result_list=result_list,
-    )
+        print(f"tau = {tau:.2f}")
 
-    with multiprocessing.Pool() as pool:
-        pool.map(func, range(sample_num))
+        result_list = multiprocessing.Manager().list()
 
-    lime_acc, rlime_acc = zip(*result_list)
-    print("LIME")
-    print(f"  Mean: {np.mean(lime_acc):.4f}")
-    print(f"  Std : {np.std(lime_acc):.4f}")
-    print("R-LIME")
-    print(f"  Mean: {np.mean(rlime_acc):.4f}")
-    print(f"  Std : {np.std(rlime_acc):.4f}")
+        func = partial(
+            compare_lime_and_newlime,
+            dataset=dataset,
+            black_box=black_box,
+            tau=tau,
+            result_list=result_list,
+        )
 
-    # Save the results to a CSV file.
[…]

### 2024-02-16 paper.tex
Modify line feed code in paper.tex

@@
 \cite{ribeiro2016why} approximates the complex model's decision boundary
-locally using a simpler model.
+locally using a simpler model around the given focal point.
 Although LIME enables users to interpret the local behavior of complex models,
-it does not optimize the approximation region \cite{radulovic2023bella} and
-the effective scope of the explanation is not explicitly presented
+it does not explicitly provide the effective scope of the explanation
 \cite{ribeiro2018anchors}.
+This limitation can lead users to overgeneralize the knowledge derived from the explanation.
+Without a clear indication of the scope of the explanation,
+users might mistakenly apply the derived knowledge to instances outside this scope,
+potentially leading to a misunderstanding of the black-box model's behavior.
 
-To address the limitations of LIME,
+To address this limitation of LIME,
 we propose a new method called R-LIME (Ruled LIME),
@@
     \caption{%
-      Explanations by LIME.
+      Explanations by LIME\@.
       They provide contributions of each feature to the output,
@@
 we conducted a comparison of the local accuracy of explanations
-between LIME and R-LIME.
+between LIME and R-LIME\@.
 Using the same settings as in \cref{sec:exp_setting},
 we randomly sampled 100 instances from the test data of the recidivism dataset
-and generated explanations (with $\tau=0.70,0.80,0.90$) using LIME and R-LIME.
+and generated explanations (with $\tau=0.70,0.80,0.90$) using LIME and R-LIME\@.
 We then sampled 10,000 instances within the rectangular region
@@
   \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
-    Comparison of local accuracy between LIME and R-LIME.
+    Comparison of local accuracy between LIME and R-LIME\@.
     R-LIME achieved higher and less variable accuracy compared to LIME
@@
 showcasing the distribution of the accuracy of the linear approximation models
-learned by LIME and R-LIME.
+learned by LIME and R-LIME\@.
 R-LIME exhibits higher accuracy compared to LIME for all values of $\tau$.
@@
  }
+
+\subsection{Computational Complexity}
+Most post-hoc explanation methods, including LIME, Anchor, BELLA and R-LIME,
+need to query the black-box model multiple times
+to get labels for perturbed samples, which can be computationally expensive.
+The number of queries required for LIME is $|\mathcal{Z}_p|$,
+where $|\mathcal{Z}_p|$ is the number of perturbed samples.
 
@@
 
-\subsection{Evaluation through User Studies}
-Given the nature of the field of "interpretable machine learning,"
-where the goal is to "interpret" machine learning models,
-it is challenging to quantitatively compare various methods.
-While quantitative experiments were conducted in \cref{sec:exp2},
-they mainly demonstrated that the proposed method generates
-locally accurate explanations compared to LIME.
-The results do not directly prove the high interpretability of the proposed method.
-
-One potential method to quantitatively evaluate "interpretability" is
-through user studies.
-For example, \cite{ribeiro2018anchors} conducted user studies,
-assuming that if users could predict the output of a black-box model
-with high accuracy based on provided explanations,
-those explanations contained valuable information about the model's behavior.
-Similarly,
-conducting user studies in this research would be desirable
-to evaluate the interpretability of the proposed method.
+% \subsection{Evaluation through User Studies}
+% Given the nature of the field of "interpretable machine learning,"
+% where the goal is to "interpret" machine learning models,
+% it is challenging to quantitatively compare various methods.
+% While quantitative experiments were conducted in \cref{sec:exp2},
+% they mainly demonstrated that the proposed method generates
+% locally accurate explanations compared to LIME.
+% The results do not directly prove the high interpretability of the proposed method.
+% 
+% One potential method to quantitatively evaluate "interpretability" is
+% through user studies.
+% For example, \cite{ribeiro2018anchors} conducted user studies,
+% assuming that if users could predict the output of a black-box model
+% with high accuracy based on provided explanations,
+% those explanations contained valuable information about the model's behavior.
+% Similarly,
+% conducting user studies in this research would be desirable
+% to evaluate the interpretability of the proposed method.
 
@@
 
-\subsubsection{Acknowledgements}
+% \subsubsection{Acknowledgements}
 % Please place your acknowledgments at
@@
 % 3rd-level heading).
-I would like to express my gratitude to Associate Professor Keigo Kimura
-from the Department of Mathematical Science,
-Division of Information Recognition,
-Graduate School of Information Science and Technology, Hokkaido University.
-He provided invaluable guidance,
-from setting the research theme to outlining the strategy and content of this study.
-Additionally,
-I appreciate the diverse insights shared by Professor Mineichi Kudo in the same laboratory.
-Finally, I am deeply thankful to all the members of the laboratory
-for their helpful advice and collaboration throughout the research process.
 

### 2024-02-23 paper/paper.tex
Refine directory structure
Create EPS images and remove redundant images

--- 2024-02-16 paper.tex
@@
 % set the path for figures
-\graphicspath{{./data/}{./python/data/}}
+\graphicspath{{./data/}{../python/data/}}
 
@@
 % Author names and ORCID IDs
-\author{Genji Ohara\inst{1}\orcidID{0009-0000-5854-2820} \and
-  Keigo Kimura\inst{1}\orcidID{0000-0002-3614-6568} \and
-  Mineichi Kudo\inst{1}\orcidID{0000-0003-1013-3870}
+\author{Genji Ohara\orcidID{0009-0000-5854-2820} \and
+	Keigo Kimura\orcidID{0000-0002-3614-6568} \and
+	Mineichi Kudo\orcidID{0000-0003-1013-3870}
 }
@@
 \begin{abstract}
-  In recent years, complex machine learning models such as deep neural networks
+	In recent years,
+	complex machine learning models such as deep neural networks
 	have been used in various industrial fields due to their high accuracy.
-  However, its complexity has been a major obstacle to implementation
-  in decision-making situations where transparency of the decision process is required.
+	However,
+	its complexity has been a major obstacle to implementation
+	in decision-making situations where transparency of the decision process
+	is required.
 	In order to address this problem,
@@
 Consequently,
-there has been extensive research in the field of post hoc explanations
+there has been extensive research in the field of post-hoc explanations
 for machine learning models \cite{%
@@
 
-Existing methods on post hoc explanations categorize into
-\emph{model-dependent} and \emph{model-agnostic} methods,
+Existing post-hoc explanation methods are categorized
+into \emph{model-dependent} and \emph{model-agnostic} methods,
 based on their dependence on the model's structure.
@@
 explain the models' behavior using their parameters.
-While they allow a direct approach to the model,
-applying the same method to models with different structures is often challenging.
+While these methods can provide detailed explanations
+(e.g., layer-wise explanations for neural networks)
+using the models' internal parameters,
+it is often challenging
+to apply the same method to models with different structures.
 On the other hand,
-model-agnostic methods do not rely on the models' parameters and utilize only their output.
-Although they are applicable to any model, available information is limited.
-Model-agnostic methods further classify into
+model-agnostic methods
+do not rely on the models' parameters and utilize only their output.
+Although they are applicable to any model,
+they cannot explain reasoning process inside the model.
+Model-agnostic methods are classified into
 \emph{global} and \emph{local} methods based on their locality in input space.
-Global methods aim to explain the model's behavior across the entire input space,
+Global methods
+aim to explain the model's behavior across the entire input space,
 seeking explanations valid for any input.
-However, providing global explanations becomes challenging as the model's complexity increases.
-Local methods, in contrast, explain the model's output for a specific input
+However, providing global explanations becomes challenging
+as the model's complexity increases.
+Local methods, in contrast, explain output of the model for a specific input
 (focal point) in the vicinity of that input.
-While local methods offer more simple and accurate explanations than global methods,
+While local methods offer more simple and accurate explanations
+than global methods,
 the scope of the explanation is limited to the vicinity of the focus point.
@@
 \cite{ribeiro2018anchors}.
-This limitation can lead users to overgeneralize the knowledge derived from the explanation.
+This limitation can lead
+users to overgeneralize the knowledge derived from the explanation.
 Without a clear indication of the scope of the explanation,
-users might mistakenly apply the derived knowledge to instances outside this scope,
+users might mistakenly apply
+the derived knowledge to instances outside this scope,
 potentially leading to a misunderstanding of the black-box model's behavior.
@@
 R-LIME locally approximates a complex decision boundary linearly
-in a rectangular region and maximizes the region as long as the accuracy of the linear
-classifier is higher than a specified threshold.
+in a rectangular region and maximizes the region
+as long as the accuracy of the linear classifier is
+higher than a specified threshold.
 The resulting rectangular region is interpretable for users because it is
-expressed as a conjunction of feature predicates.
+expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).
 
 \section{Related Work}
+% I want to arrange figures in the following order:
+% (a) Instances around the focal point.
+% (b) Explanations by LIME.
+% (c) Explanations by Anchor.
+% (d) Explanations by R-LIME.
+% but I want to put both (b) and (c) vertically in left column
+% and (d) in right column.
+
 \begin{figure}[t]
@@
 		\centering
-    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_a.png}
-    \caption{Instances around the focal point.}\label{fig:lime_vs_anchor_exp_a}
-    \vspace{0.5cm}
+		\includegraphics[scale=0.35]{example-instance}
+		\caption{Focal point.}\label{fig:example-instance}
 	\end{subfigure}
+	\hfill
+	\begin{subfigure}[t]{0.45\textwidth}
+		\begin{subfigure}[t]{\textwidth}
+			\centering
+			\includegraphics[scale=0.35]{example-lime}
+			\caption{%
+				Explanation by LIME\@.
+				It provides contributions of each feature to the output,
+				but does not explicitly indicate its scope.
+			}\label{fig:example-lime}
+			\vspace{0.4cm}
+		\end{subfigure}
+		\begin{subfigure}[t]{\textwidth}
+			\centering
+			\includegraphics[scale=0.35]{example-anchor}
+			\caption{%
+				Explanation by Anchor.
+				It provides the effective scope of the explanation,
+				but does not show the influence of each feature.
+			}\label{fig:example-anchor}
+		\end{subfigure}
+	\end{subfigure}
+	\hspace{0.3cm}
 	\begin{subfigure}[t]{0.45\textwidth}
 		\centering
-    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_b.png}
+		\vspace{-2.05cm}
+		\includegraphics[scale=0.35]{example-rlime}
 		\caption{%
-      Explanations by LIME\@.
-      They provide contributions of each feature to the output,
-      but do not explicitly indicate its scope.
-    }\label{fig:lime_vs_anchor_exp_b}
-    \vspace{0.5cm}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.55\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_c.png}
-    \caption{%
-      Explanations by Anchor.
-      They provide the effective scope of the explanation,
-      but do not provide details about the influence of each feature.
-    }\label{fig:lime_vs_anchor_exp_c}
+			Explanation by R-LIME\@.
+			It provides both contributions of each feature and
+			its effective scope.
+		}\label{fig:example-rlime}
 	\end{subfigure}
 	\caption{%
-    Explanations by LIME and Anchor
-    for an LSTM sentiment prediction model \cite{ribeiro2018anchors}.
-  }\label{fig:lime_vs_anchor_exp}
+		Example of explanations by LIME, Anchor and R-LIME
+		for a sentiment prediction model.
+	}\label{fig:example}
 \end{figure}
 In this chapter,
-we provide an overview of existing research on local model-agnostic explanations,
+we briefly review existing research on local model-agnostic explanations,
 particularly focusing on studies closely related to our proposed method.
@@
 \cite{ribeiro2018anchors}.
-An example of explanation by LIME for an LSTM sentiment prediction model
-is illustrated in \cref{fig:lime_vs_anchor_exp_b}.
-The left explanation suggests that
-the word "not" contributes to the model's positive prediction,
-which does not apply to the instance on the right.
-However, without the explicit perturbation region,
-users might mistakenly apply the left explanation to the right instance,
-potentially leading to a misunderstanding of the black-box model's behavior
+An example of explanation by LIME for a sentiment prediction model
+is illustrated in \cref{fig:example-lime}.
+The explanation provides valuable insights that
+the word "not" mainly contributes to the model's positive prediction,
+but does not explicitly indicate the effective scope of that insight.
+Without the effective scope,
+users might mistakenly apply the explanation to other instances
+(e.g., ``This book is not good''),
+potentially leading to misunderstanding of the black-box model's behavior
 \cite{ribeiro2018anchors}.
@@
 limiting its utility \cite{ribeiro2018anchors}.
-An example of Anchor explanation for an LSTM sentiment prediction model
-is depicted in \cref{fig:lime_vs_anchor_exp_c}.
-The left explanation suggests that changing words other than "not" and "bad"
+An example of Anchor explanation for a sentiment prediction model
+is illustrated in \cref{fig:example-anchor}.
+The explanation suggests that changing words other than ``not'' and ``bad''
 has little impact on the classifier's output.
-While it clearly does not apply to the right instance,
+While it clearly does not apply to the sentence ``This book is not good''
+because of not including the word ``bad'',
 the explanation does not provide details about the influence of each word,
 resulting in less user insight into the model's behavior compared to LIME
-(\cref{fig:lime_vs_anchor_exp_b}).
+(\cref{fig:example-lime}).
 
@@
 but samples parturbation from a rectangular region similar to Anchor
+so that the generality of approximation is explicitly provided
 (\cref{fig:rlime}).
@@
 
-Our method's algorithm is mainly based on that used in Anchor.
+The algorithm of our method
+is mainly based on that used in Anchor\cite{ribeiro2018anchors}.
 For non-convex optimization problems like \cref{eq:main_problem},
@@
 which selects multiple candidates at each iteration.
-The pseudocode is shown in \cref{alg:greedy_search}.
+The pseudo code is shown in \cref{alg:greedy_search}.
 
@@
 selected in the previous iteration.
-The pseudocode is shown in \cref{alg:generate_cands}.
+The pseudo code is shown in \cref{alg:generate_cands}.
 $T(x)$ is the set of attribute-value pairs (predicates) that are true for $x$,
@@
 we employ the KL-LUCB algorithm \cite{kaufmann2013information}.
-The pseudocode is shown in \cref{alg:best_cands}.
+The pseudo code is shown in \cref{alg:best_cands}.
 For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
@@
 and proceeds to the next iteration.
-The pseudocode is presented in \cref{alg:largest_valid_cand}.
+The pseudo code is presented in \cref{alg:largest_valid_cand}.
 
@@
 
-    \def\dir{python/exp1}
+		\def\dir{experiments/exp1}
 		\def\Asample{0012}
@@
 	\centering
-  \includegraphics[width=0.55\textwidth]{python/exp2/box_plot}
+	\includegraphics[width=0.55\textwidth]{experiments/exp2/box_plot}
 	\caption[Comparison of Local Accuracy between R-LIME and LIME]{%

### 2024-02-23 experiments/exp2/box_plot.py
Compare original and my lime then they differ

@@ -42,7 +42,7 @@ def main() -> None:
     )
     # plt.title("Accuracy of LIME and R-LIME")
     plt.ylabel("Accuracy")
-    plt.savefig("box_plot.png")
+    plt.savefig("box_plot.eps")
 
 
 def read_data(filename: str) -> tuple[list[float], list[float]]:

### 2024-02-23 experiments/exp2/lime_vs_rlime.py

@@ -5,13 +5,14 @@ import multiprocessing
 from functools import partial
 
 import numpy as np
-import pandas as pd
-from sklearn.ensemble import RandomForestClassifier
+import pandas as pd  # type: ignore
+from lime import lime_tabular  # type: ignore
+from sklearn.ensemble import RandomForestClassifier  # type: ignore
 
-from NewLIME import mylime, newlime_base, newlime_tabular, newlime_utils
-from NewLIME.newlime_base import Arm
-from NewLIME.newlime_types import IntArray
-from NewLIME.sampler import Sampler
+from RLIME import mylime, newlime_base, newlime_tabular, newlime_utils
+from RLIME.newlime_base import Arm
+from RLIME.newlime_types import IntArray
+from RLIME.sampler import Sampler
 
 
 def main() -> None:
@@ -19,7 +20,7 @@ def main() -> None:
 
     # Load the dataset.
     dataset = newlime_utils.load_dataset(
-        "recidivism", "NewLIME/datasets/", balance=True
+        "recidivism", "RLIME/datasets/", balance=True
     )
 
     # Learn the black box model.
@@ -29,7 +30,7 @@ def main() -> None:
     # Get the target instances.
     sample_num = 100
 
-    for tau in [0.80, 0.90]:
+    for tau in [0.70, 0.80, 0.90]:
 
         print(f"tau = {tau:.2f}")
 
@@ -94,6 +95,29 @@ def calc_accuracy(
     return lime_acc, rlime_acc
 
 
+def original_lime(
+    dataset: newlime_tabular.Dataset,
+    trg: IntArray,
+    model: RandomForestClassifier,
+    pred_label: int,
+) -> list[float]:
+    """Calculate the weights of LIME."""
+
+    lime_explainer = lime_tabular.LimeTabularExplainer(
+        dataset.train,
+        feature_names=dataset.feature_names,
+        class_names=dataset.class_names,
+        discretize_continuous=False,
+    )
+    lime_exp = lime_explainer.explain_instance(
+        trg, model.predict_proba, num_features=5, top_labels=1
+    )
+    weights = [0.0] * len(dataset.feature_names)
+    for t in lime_exp.local_exp[pred_label]:
+        weights[t[0]] = t[1] * (pred_label * 2 - 1)
+    return weights
+
+
 def compare_lime_and_newlime(
     idx: int,
     dataset: newlime_tabular.Dataset,
[…]

### 2024-02-23 experiments/exp2/lime_vs_rlime.py
Modify a little

@@ -110,7 +110,7 @@ def original_lime(
         discretize_continuous=False,
     )
     lime_exp = lime_explainer.explain_instance(
-        trg, model.predict_proba, num_features=5, top_labels=1
+        trg, model.predict_proba, num_features=15, top_labels=1
     )
     weights = [0.0] * len(dataset.feature_names)
     for t in lime_exp.local_exp[pred_label]:

### 2024-02-24 paper/paper.tex
Modify structure of paper and recreate visualization images in EPS

@@
 particularly in critical decision-making scenarios like healthcare and finance,
-where the opacity of decision rationale becomes a major obstacle to
+where the opacity of decision process becomes a major obstacle to
 implementation.
@@
 there has been extensive research in the field of post-hoc explanations
-for machine learning models \cite{%
-	ribeiro2016why,ribeiro2018anchors,radulovic2023bella,guidotti2018local}.
+for machine learning models~\cite{%
+	guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.
 
@@
 based on their dependence on the model's structure.
-Model-dependent methods primarily focus on deep neural networks and
-explain the models' behavior using their parameters.
-While these methods can provide detailed explanations
-(e.g., layer-wise explanations for neural networks)
-using the models' internal parameters,
-it is often challenging
-to apply the same method to models with different structures.
-On the other hand,
-model-agnostic methods
-do not rely on the models' parameters and utilize only their output.
-Although they are applicable to any model,
-they cannot explain reasoning process inside the model.
-Model-agnostic methods are classified into
+Furthermore, model-agnostic methods are classified into
 \emph{global} and \emph{local} methods based on their locality in input space.
-Global methods
-aim to explain the model's behavior across the entire input space,
-seeking explanations valid for any input.
-However, providing global explanations becomes challenging
-as the model's complexity increases.
 Local methods, in contrast, explain output of the model for a specific input
@@
 
-This paper specifically focuses on \emph{local} \emph{model-agnostic} methods.
+This paper specifically focuses on \emph{local} \emph{model-agnostic} methods,
+which do not rely on the models' structure
+and explain the models' behavior in the vicinity of a specific input.
 For instance, LIME (Local Interpretable Model-agnostic Explanations)
@@
 the derived knowledge to instances outside this scope,
-potentially leading to a misunderstanding of the black-box model's behavior.
+potentially leading to misunderstanding of the black-box model's behavior.
 
@@
 \section{Related Work}
-% I want to arrange figures in the following order:
-% (a) Instances around the focal point.
-% (b) Explanations by LIME.
-% (c) Explanations by Anchor.
-% (d) Explanations by R-LIME.
-% but I want to put both (b) and (c) vertically in left column
-% and (d) in right column.
-
 \begin{figure}[t]
@@
 		\centering
-		\vspace{-2.05cm}
+		\vspace{-1.96cm}
 		\includegraphics[scale=0.35]{example-rlime}
@@
 In this chapter,
+we overview existing research on post-hoc explanations,
+which explain the behavior of complex models already trained.
+They are categorized
+into \emph{model-dependent} and \emph{model-agnostic} methods
+based on their dependence on the model's structure.
+
+Model-dependent methods primarily focus on deep neural networks and
+explain the models' behavior using their parameters~\cite{samek2021explaining}.
+Layer-wise relevance propagation (LRP)~\cite{bach2015pixel} and
+deep Taylor decomposition (DTD)~\cite{montavon2017explaining}
+are representative model-dependent methods.
+While these methods can provide detailed explanations
+(e.g., layer-wise explanations for neural networks)
+using the models' internal parameters,
+it is often challenging
+to apply the same method to models with different structures.
+
+On the other hand,
+model-agnostic methods
+do not rely on the models' parameters and utilize only their output.
+Although these methods are applicable to any model,
+they cannot explain the reasoning process inside the model.
+Furthermore, model-agnostic methods are classified into
+\emph{global} and \emph{local} methods based on their locality in input space.
+Global methods
+aim to explain the model's behavior across the entire input space,
+seeking explanations valid for any input.
+Partial dependence plots (PDP)~\cite{friedman2001greedy} and
+accumulated local effects (ALE)~\cite{apley2020visualizing}
+are representative global methods.
+However, providing global explanations becomes challenging
+as the model's complexity increases.
+Local methods, in contrast, explain output of the model for a specific input
+(focal point) in the vicinity of that input.
+While local methods offer more simple and accurate explanations
+than global methods,
+the scope of the explanation is limited to the vicinity of the focus point.
+
+Model-dependent methods aim to explain the behavior of complex models
+using their internal parameters.
+
+% BELLA\cite{radulovic2023bella} addresses the non-optimization of the approximation region,
+% a drawback of LIME,
+% by learning a local linear classifier $g$
+% using a subset $Z'$ of the dataset $Z$
+% instead of perturbed samples.
+% The process involves:
+% \begin{enumerate}
+% 	\item Computing the distance $d_x(z)$ for all instances $z$ in $Z$
+% 	      with respect to the focal point $x$.
+% 	\item Selecting the $k$ instances with the smallest $d_x(z)$,
+% 	      forming a subset $Z_s(k) \subseteq Z$.
+% 	\item Learning the local linear classifier $g$ using $Z_s(k)$
+% 	      and calculating the similarity measure $\mathcal{R}(k)$ between $f$ and $g$
+% 	      over $k=1,2,\dots,|Z|$.
+% 	\item Obtaining the optimal $k^*$ by maximizing $\mathcal{R}(k)$.
+% \end{enumerate}
+% 
+% BELLA aims to enhance the reliability of explanations
+% by optimizing the approximation region for high-accuracy linear approximations.
+% However, it assumes direct access to the dataset $Z$ used for training the classifier,
+% making it inapplicable in scenarios where direct access to the dataset is restricted.
+% Additionally,
+% as BELLA presents the approximation region as a subset of the dataset,
+% its interpretability is lower compared to Anchor.
+
+\section{Proposed Method}
+\begin{figure}[tbp]
+	\centering
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{visual-lime}
+		\caption{%
+			LIME: Locally approximates the decision boundary around the focal point.
+		}\label{fig:lime}
+	\end{subfigure}%
+	\hspace{0.03\textwidth}
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{visual-anchor}
+		\caption{%
+			Anchor: Maximizes coverage of a rectangular region
+			containing the focal point under accuracy constraints.
+		}\label{fig:anchor}
+	\end{subfigure}
+	\hspace{0.03\textwidth}
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{visual-rlime}
+		\caption{%
+			R-LIME:
+			Maximizes coverage of a rectangular region containing the focal point
+			under lower constraints on the accuracy of the linear classifier.
+		}\label{fig:rlime}
+	\end{subfigure}
+	\caption{%
+		Visual comparison of LIME, Anchor and R-LIME (our proposed method).
+		The solid line represents the rectangular region containing the focal
+		point, and the dashed line represents the learned approximation model.
+	}
+\end{figure}
+\subsection{Previous Work}
+We specifically focuses on \emph{local} and \emph{model-agnostic} methods.
+In this section,
 we briefly review existing research on local model-agnostic explanations,
 particularly focusing on studies closely related to our proposed method.
-
-\subsection{LIME (Local Interpretable Model-agnostic Explanations) \cite{ribeiro2016why}}
+\subsubsection{%
+	LIME (Local Interpretable Model-agnostic Explanations)
+	\cite{ribeiro2016why}
+}
 LIME locally
@@
 is illustrated in \cref{fig:example-lime}.
-The explanation provides valuable insights that
-the word "not" mainly contributes to the model's positive prediction,
-but does not explicitly indicate the effective scope of that insight.
-Without the effective scope,
-users might mistakenly apply the explanation to other instances
-(e.g., ``This book is not good''),
+The explanation provides suggests that
+the word ``not'' mainly contributes to the positive prediction,
+but does not explicitly indicate the effective scope.
+Without the scope,
+users might mistakenly apply the knowledge derived from the explanation
+to other instances far from the focal point,
 potentially leading to misunderstanding of the black-box model's behavior
 \cite{ribeiro2018anchors}.
+For example,
+user may apply the insights derived from the explanation
+(\cref{fig:example-lime})
+to the sentence ``This book is not good.''
+and mistakenly conclude that the word ``not''
+mainly contributes to the positive prediction for this sentence as well,
+which is incorrect obviously.
 
-\subsection{Anchor \cite{ribeiro2018anchors}}\label{sec:anchor}
+\subsubsection{Anchor~\cite{ribeiro2018anchors}}\label{sec:anchor}
 Anchor represents a rectangular region containing the focal point $x$,
@@
 the information it includes is less than LIME,
-limiting its utility \cite{ribeiro2018anchors}.
+limiting its utility~\cite{ribeiro2018anchors}.
 An example of Anchor explanation for a sentiment prediction model
@@
 has little impact on the classifier's output.
-While it clearly does not apply to the sentence ``This book is not good''
+While it clearly cannot be applied to the sentence ``This book is not good''
 because of not including the word ``bad'',
@@
 
-\subsection{%
-	BELLA (Black box model Explanations by Local Linear Approximations)
-	\cite{radulovic2023bella}
-}
-BELLA addresses the non-optimization of the approximation region,
-a drawback of LIME,
-by learning a local linear classifier $g$
-using a subset $Z'$ of the dataset $Z$
-instead of perturbed samples (\cref{fig:bella}).
-The process involves:
-\begin{enumerate}
-	\item Computing the distance $d_x(z)$ for all instances $z$ in $Z$
-	      with respect to the focal point $x$.
-	\item Selecting the $k$ instances with the smallest $d_x(z)$,
-	      forming a subset $Z_s(k) \subseteq Z$.
-	\item Learning the local linear classifier $g$ using $Z_s(k)$
-	      and calculating the similarity measure $\mathcal{R}(k)$ between $f$ and $g$
-	      over $k=1,2,\dots,|Z|$.
-	\item Obtaining the optimal $k^*$ by maximizing $\mathcal{R}(k)$.
-\end{enumerate}
-
-BELLA aims to enhance the reliability of explanations
-by optimizing the approximation region for high-accuracy linear approximations.
-However, it assumes direct access to the dataset $Z$ used for training the classifier,
-making it inapplicable in scenarios where direct access to the dataset is restricted.
-Additionally,
-as BELLA presents the approximation region as a subset of the dataset,
-its interpretability is lower compared to Anchor.
-
-\section{Proposed Method}
-\begin{figure}[tb]
-	\centering
-	\begin{subfigure}[t]{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{lime}
-		\caption{%
-			LIME: Locally approximates the decision boundary around the focal point.
-		}\label{fig:lime}
-	\end{subfigure}%
-	\hfill
-	\begin{subfigure}[t]{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{anchor}
-		\caption{%
-			Anchor: Maximizes coverage of a rectangular region
-			containing the focal point under accuracy constraints.
-		}\label{fig:anchor}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[t]{0.45\textwidth}
-		\centering
-		\includegraphics[width=0.85\textwidth]{bella}
-		\caption{%
-			BELLA: Explores a subset of the dataset,
-			maximizing similarity between the local linear classifier
-			and the black-box classifier.
-		}\label{fig:bella}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[t]{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{rlime3}
-		\caption{%
-			R-LIME:
-			Maximizes coverage of a rectangular region containing the focal point
-			under lower constraints on the accuracy of the linear classifier.
-		}\label{fig:rlime}
-	\end{subfigure}
-	\caption{%
-		Visual comparison of LIME, Anchor, BELLA and R-LIME (our proposed method).
-		The solid line represents the rectangular region containing the focal
-		point, and the dashed line represents the learned approximation model.
-	}
-\end{figure}
-
 \subsection{Overview}
 We propose R-LIME,
-a method that aims to address the limitations of LIME \cite{ribeiro2016why},
-Anchor \cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
+a method that aims to address the limitations of LIME~\cite{ribeiro2016why},
+Anchor~\cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
 Our method locally approximates the given black-box classifier $f$
@@
 %
+\newpage
 \bibliographystyle{splncs04}

### 2024-02-24 experiments/exp2/box_plot.py

@@ -31,7 +31,7 @@ def main() -> None:
         med.set_color("black")
 
     for i, tau_percent in enumerate([70, 80, 90]):
-        plt.text(1.0 + 2.5 * i, 0.36, r"$\tau=$" + f"0.{tau_percent}")
+        plt.text(1.0 + 2.5 * i, 0.3, r"$\tau=$" + f"0.{tau_percent}")
 
     plt.hlines(
         [0.7, 0.8, 0.9],

### 2024-02-24 experiments/exp2/lime_vs_rlime.py

@@ -2,6 +2,7 @@
 
 import csv
 import multiprocessing
+import sys
 from functools import partial
 
 import numpy as np
@@ -9,10 +10,14 @@ import pandas as pd  # type: ignore
 from lime import lime_tabular  # type: ignore
 from sklearn.ensemble import RandomForestClassifier  # type: ignore
 
-from RLIME import mylime, newlime_base, newlime_tabular, newlime_utils
-from RLIME.newlime_base import Arm
-from RLIME.newlime_types import IntArray
-from RLIME.sampler import Sampler
+sys.path.append("RLIME")
+import mylime  # type: ignore
+import newlime_base  # type: ignore
+import newlime_tabular
+import newlime_utils
+from newlime_base import Arm
+from newlime_types import IntArray
+from sampler import Sampler
 
 
 def main() -> None:
@@ -63,7 +68,11 @@ def main() -> None:
 
 
 def calc_accuracy(
-    sample: IntArray, labels: IntArray, lime_weights: list[float], arm: Arm
+    sample: IntArray,
+    labels: IntArray,
+    lime_weights: list[float],
+    lime_scaler,
+    arm: Arm,
 ) -> tuple[float, float]:
     """Calculate the precision of LIME and R-LIME.
 
@@ -85,7 +94,7 @@ def calc_accuracy(
     """
 
     # Get predictions of LIME and R-LIME.
-    lime_pred = np.dot(sample, lime_weights) > 0
+    lime_pred = np.dot(lime_scaler.transform(sample), lime_weights) > 0
     rlime_pred = arm.surrogate_model.predict_many(pd.DataFrame(sample))
 
     # Calculate the precision of LIME and R-LIME.
@@ -149,10 +158,10 @@ def compare_lime_and_newlime(
         trg, dataset.train, black_box.predict, dataset.categorical_names
     )
 
-    # lime_weights = mylime.explain(trg, sampler, 5000)
-    lime_weights = original_lime(
-        dataset, trg, black_box, black_box.predict(trg.reshape(1, -1))[0]
-    )
+    lime_weights, scaler = mylime.explain(trg, sampler, 5000)
+    # lime_weights = original_lime(
+    #     dataset, trg, black_box, black_box.predict(trg.reshape(1, -1))[0]
+    # )
 
     hyper_param = newlime_base.HyperParam(
         tau=tau,
@@ -175,7 +184,9 @@ def compare_lime_and_newlime(
 
     # Sample from the rule.
[…]

### 2024-02-26 paper/paper.tex
Work on the paper

@@
 \crefname{figure}{Fig.}{Figs.}
-\crefname{table}{Table.}{Tables.}
+\crefname{table}{Table}{Tables}
+\crefname{algorithm}{Algorithm}{Algorithms}
 
@@
 	guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.
-
 Existing post-hoc explanation methods are categorized
-into \emph{model-dependent} and \emph{model-agnostic} methods,
+into \emph{model-dependent} and \emph{model-agnostic} methods
 based on their dependence on the model's structure.
@@
 \emph{global} and \emph{local} methods based on their locality in input space.
-Local methods, in contrast, explain output of the model for a specific input
-(focal point) in the vicinity of that input.
-While local methods offer more simple and accurate explanations
-than global methods,
-the scope of the explanation is limited to the vicinity of the focus point.
 
-This paper specifically focuses on \emph{local} \emph{model-agnostic} methods,
+This paper specifically focuses
+on \emph{model-agnostic} and \emph{local} methods,
 which do not rely on the models' structure
-and explain the models' behavior in the vicinity of a specific input.
-For instance, LIME (Local Interpretable Model-agnostic Explanations)
+and explain the models' behavior
+in the vicinity of a given input (focal point).
+For example, LIME (Local Interpretable Model-agnostic Explanations)
 \cite{ribeiro2016why} approximates the complex model's decision boundary
@@
 as long as the accuracy of the linear classifier is
-higher than a specified threshold.
+higher than a given threshold.
 The resulting rectangular region is interpretable for users because it is
@@
 \section{Related Work}
-\begin{figure}[t]
-	\centering
-	\vspace{0.5cm}
-	\begin{subfigure}[t]{0.55\textwidth}
-		\centering
-		\includegraphics[scale=0.35]{example-instance}
-		\caption{Focal point.}\label{fig:example-instance}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[t]{0.45\textwidth}
-		\begin{subfigure}[t]{\textwidth}
-			\centering
-			\includegraphics[scale=0.35]{example-lime}
-			\caption{%
-				Explanation by LIME\@.
-				It provides contributions of each feature to the output,
-				but does not explicitly indicate its scope.
-			}\label{fig:example-lime}
-			\vspace{0.4cm}
-		\end{subfigure}
-		\begin{subfigure}[t]{\textwidth}
-			\centering
-			\includegraphics[scale=0.35]{example-anchor}
-			\caption{%
-				Explanation by Anchor.
-				It provides the effective scope of the explanation,
-				but does not show the influence of each feature.
-			}\label{fig:example-anchor}
-		\end{subfigure}
-	\end{subfigure}
-	\hspace{0.3cm}
-	\begin{subfigure}[t]{0.45\textwidth}
-		\centering
-		\vspace{-1.96cm}
-		\includegraphics[scale=0.35]{example-rlime}
-		\caption{%
-			Explanation by R-LIME\@.
-			It provides both contributions of each feature and
-			its effective scope.
-		}\label{fig:example-rlime}
-	\end{subfigure}
-	\caption{%
-		Example of explanations by LIME, Anchor and R-LIME
-		for a sentiment prediction model.
-	}\label{fig:example}
-\end{figure}
 In this chapter,
@@
 
-Model-dependent methods primarily focus on deep neural networks and
+Model-dependent methods,
+such as DTD (Deep Taylor Decomposition)~\cite{montavon2017explaining}
+and LRP (Layer-wise Relevance Propagation)~\cite{bach2015pixel},
+primarily focus on deep neural networks and
 explain the models' behavior using their parameters~\cite{samek2021explaining}.
-Layer-wise relevance propagation (LRP)~\cite{bach2015pixel} and
-deep Taylor decomposition (DTD)~\cite{montavon2017explaining}
-are representative model-dependent methods.
 While these methods can provide detailed explanations
@@
 \emph{global} and \emph{local} methods based on their locality in input space.
-Global methods
+Global methods,
+such as PDP (Partial Dependence Plots)~\cite{friedman2001greedy}
+and ALE (Accumulated Local Effects)~\cite{apley2020visualizing},
 aim to explain the model's behavior across the entire input space,
 seeking explanations valid for any input.
-Partial dependence plots (PDP)~\cite{friedman2001greedy} and
-accumulated local effects (ALE)~\cite{apley2020visualizing}
-are representative global methods.
 However, providing global explanations becomes challenging
 as the model's complexity increases.
-Local methods, in contrast, explain output of the model for a specific input
+In contrast, local methods,
+such as LIME (Local Interpretable Model-agnostic Explanations)~\cite{ribeiro2016why}
+and Anchor~\cite{ribeiro2018anchors},
+% SHAP~\cite{lundberg2017unified},
+% EXPLAN~\cite{rasouli2020explan},
+% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
+% and BELLA (Black box model Explanations by Local Linear Approximations)
+% \cite{radulovic2023bella},
+explain output of the model for a specific input
 (focal point) in the vicinity of that input.
@@
 than global methods,
-the scope of the explanation is limited to the vicinity of the focus point.
+the scope of the explanation is limited to the vicinity of the focal point.
 
-Model-dependent methods aim to explain the behavior of complex models
-using their internal parameters.
+\begin{figure}[tbp]
+	\def\scale{0.38}
+	\centering
+	\vspace{0.5cm}
+	\begin{subfigure}[t]{0.55\textwidth}
+		\centering
+		\includegraphics[scale=\scale]{example-instance}
+		\caption{Focal point.}\label{fig:example-instance}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[t]{0.45\textwidth}
+		\begin{subfigure}[t]{\textwidth}
+			\centering
+			\includegraphics[scale=\scale]{example-lime}
+			\caption{%
+				Explanation by LIME\@.
+				It provides contributions of each feature to the output,
+				but does not explicitly indicate its scope.
+			}\label{fig:example-lime}
+			\vspace{0.4cm}
+		\end{subfigure}
+		\begin{subfigure}[t]{\textwidth}
+			\centering
+			\includegraphics[scale=\scale]{example-anchor}
+			\caption{%
+				Explanation by Anchor.
+				It provides the effective scope of the explanation,
+				but does not show the influence of each feature.
+			}\label{fig:example-anchor}
+		\end{subfigure}
+	\end{subfigure}
+	\hspace{0.3cm}
+	\begin{subfigure}[t]{0.45\textwidth}
+		\centering
+		\vspace{-2.24cm}
+		\includegraphics[scale=\scale]{example-rlime}
+		\caption{%
+			Explanation by R-LIME\@.
+			It provides both contributions of each feature and
+			its effective scope.
+		}\label{fig:example-rlime}
+	\end{subfigure}
+	\caption{%
+		Example of explanations by LIME~\cite{ribeiro2016why},
+		Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method).
+		for a sentiment prediction model.
+	}\label{fig:example}
+\end{figure}
+In this paper,
+we focus on local model-agnostic methods.
+An example of explanations by LIME and Anchor
+for a sentiment prediction model is illustrated in \cref{fig:example}.
+LIME~\cite{ribeiro2016why} approximates the complex decision boundary
+locally using a linear model around the given focal point,
+then provides the weights of the linear model as the contribution of each feature
+to the output.
+The explanation by LIME (\cref{fig:example-lime}) provides suggests that
+the word ``not'' mainly contributes to the positive prediction,
+but does not explicitly indicate the effective scope.
+Without the scope,
+users might mistakenly apply the knowledge derived from the explanation
+to other instances far from the focal point,
+potentially leading to misunderstanding of the black-box model's behavior
+\cite{ribeiro2018anchors}.
+For example,
+user may apply the insights derived from the explanation
+to the sentence ``This book is not good.''
+and mistakenly conclude that the word ``not''
+mainly contributes to the positive prediction for this sentence as well,
+which is incorrect obviously.
+Anchor~\cite{ribeiro2018anchors} represents a rectangular region
+containing the focal point,
+that maximizes the probability of the black-box classifier outputting
+the same label as the focal point.
+While Anchor provides an effective scope of the explanation,
+the information it includes is less than LIME,
+limiting its utility~\cite{ribeiro2018anchors}.
+The explanation by Anchor (\cref{fig:example-anchor})
+suggests that changing words other than ``not'' and ``bad''
+has little impact on the classifier's output.
+While it clearly cannot be applied to the sentence ``This book is not good''
+because of not including the word ``bad'',
+the explanation does not provide details about the influence of each word,
+resulting in less user insight into the model's behavior compared to LIME.
 
@@
 \cite{ribeiro2018anchors}.
-An example of explanation by LIME for a sentiment prediction model
-is illustrated in \cref{fig:example-lime}.
-The explanation provides suggests that
-the word ``not'' mainly contributes to the positive prediction,
-but does not explicitly indicate the effective scope.
-Without the scope,
-users might mistakenly apply the knowledge derived from the explanation
-to other instances far from the focal point,
-potentially leading to misunderstanding of the black-box model's behavior
-\cite{ribeiro2018anchors}.
-For example,
-user may apply the insights derived from the explanation
-(\cref{fig:example-lime})
-to the sentence ``This book is not good.''
-and mistakenly conclude that the word ``not''
-mainly contributes to the positive prediction for this sentence as well,
-which is incorrect obviously.
 
@@
 
-While Anchor provides an effective scope of the explanation,
-the information it includes is less than LIME,
-limiting its utility~\cite{ribeiro2018anchors}.
-An example of Anchor explanation for a sentiment prediction model
-is illustrated in \cref{fig:example-anchor}.
-The explanation suggests that changing words other than ``not'' and ``bad''
-has little impact on the classifier's output.
-While it clearly cannot be applied to the sentence ``This book is not good''
-because of not including the word ``bad'',
-the explanation does not provide details about the influence of each word,
-resulting in less user insight into the model's behavior compared to LIME
-(\cref{fig:example-lime}).
-
 \subsection{Overview}
@@
 a method that aims to address the limitations of LIME~\cite{ribeiro2016why},
-Anchor~\cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
+and Anchor~\cite{ribeiro2018anchors}.
 Our method locally approximates the given black-box classifier $f$
 around the focal point $x$ by a linear classifier $g$ similar to LIME and BELLA,
-but samples parturbation from a rectangular region similar to Anchor
+but samples perturbation from a rectangular region similar to Anchor
 so that the generality of approximation is explicitly provided
@@
 we can select the rule that enables explanation with high accuracy and generality.
-The characteristics of R-LIME are listed below:
-\begin{itemize}
-	\item The approximation region is optimal and interpretable.
-	\item The dataset is not directly accessed, and only the distribution is utilized.
-	\item The number of samples is dynamically determined
-	      based on the estimated accuracy without the need for predefining it.
-\end{itemize}
+% The characteristics of R-LIME are listed below:
+% \begin{itemize}
+% 	\item The approximation region is optimal and interpretable.
+% 	\item The dataset is not directly accessed, and only the distribution is utilized.
+% 	\item The number of samples is dynamically determined
+% 	      based on the estimated accuracy without the need for predefining it.
+% \end{itemize}
 
@@
 
+\subsection{Computational Complexity}
+Post-hoc explanation methods including LIME, Anchor, and R-LIME
+need to query the black-box model multiple times
+to get labels for perturbed samples, which is computationally expensive.
+The number of queries required for LIME is $|\mathcal{Z}_p|$,
+where $|\mathcal{Z}_p|$ is the number of perturbed samples.
+On the other hand, the number of queries required for Anchor and R-LIME
+is $|\mathcal{D}|$,
+
 \section{Experiments}
@@
 			Attributes of the recidivism dataset used in the experiments.
-			Continuous features are all discretized
+			Continuous features are all discretized,
 			and only binary and ordinal features are considered.
@@
 The dataset includes 19 items such as race, gender,
-presence of alcohol dependence, number of prior offenses, and recidivism.
+presence of alcohol dependence, number of prior offenses and recidivism.
 For this experiment,
@@
   \def\imgwidth{0.49\textwidth}
+  \def\scale{0.08}
   \begin{figure}[t]
@@
 		  \centering
-		  \includegraphics[width=0.78\textwidth]{newlime}
-		  \caption{R-LIME for balanced data.}\label{fig:balanced}
+		  \includegraphics[scale=\scale]{newlime}
+		  \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
 	  \end{subfigure}
@@
 		  \centering
-		  \includegraphics[width=0.8\textwidth]{newlime_for_imbalanced_data}
-		  \caption{R-LIME for imbalanced data.
+		  \includegraphics[scale=\scale]{newlime_for_imbalanced_data}
+		  \caption{R-LIME for imbalanced label distribution.
 		  }\label{fig:imbalanced}
@@
 	  \caption{%
-		  Behavior of R-LIME for balanced and imbalanced data.
+		  Behavior of R-LIME for balanced and imbalanced label distribution.
 		  In case of imbalanced label distribution,
@@
 	  }
-	  \vspace{10pt}
   \end{figure}
  }
-
-\subsection{Computational Complexity}
-Most post-hoc explanation methods, including LIME, Anchor, BELLA and R-LIME,
-need to query the black-box model multiple times
-to get labels for perturbed samples, which can be computationally expensive.
-The number of queries required for LIME is $|\mathcal{Z}_p|$,
-where $|\mathcal{Z}_p|$ is the number of perturbed samples.
 
@@
 %
-\newpage
 \bibliographystyle{splncs04}

### 2024-02-27 paper/paper.tex
Adapt paper.tex for graduation thesis

@@
 
+\def\mode{0} % 0: Graduation thesis, 1: ICPR paper
+
+\ifnum\mode=0
+	\documentclass{article}
+	\usepackage{prmlthesis}
+\else
 	\documentclass[runningheads]{llncs}
+\fi
 
@@
 
-% Authentic title
+\ifnum\mode=0
+	\title{%
+		R-LIME: Rectangular Constraints and Optimization for Local Interpretable
+		Model-agnostic Explanation Methods
+	}
+	\etitle{}
+	\author{Genji Ohara}
+	\institute{hogehoge}
+\else
 	\title{%
@@
 		Model-agnostic Explanation Methods}
-
 	% Abbreviated title for the running head
@@
 		\email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}
+\fi
 
@@
 \maketitle              %
+
+\ifnum\mode=0
+	\pagestyle{plain}
+	\pagenumbering{roman}
+	\tableofcontents
+	\newpage
+	\listoffigures\listoftables\clearpage
+	\AddToHook{cmd/section/before}{\clearpage}
+	\pagestyle{plain}
+	\pagenumbering{arabic}
+\else
 
@@
 	\end{abstract}
+\fi
 
@@
 	\end{subfigure}
-	\caption{%
+	\caption[Example of explanations by LIME, Anchor and R-LIME]{%
 		Example of explanations by LIME~\cite{ribeiro2016why},
@@
 	\end{subfigure}
-	\caption{%
+	\caption[Visual comparison of LIME, Anchor and R-LIME]{%
 		Visual comparison of LIME, Anchor and R-LIME (our proposed method).
@@
 particularly focusing on studies closely related to our proposed method.
-\subsubsection{%
+\subsubsection[LIME]{%
 	LIME (Local Interpretable Model-agnostic Explanations)
@@
 
-\subsubsection{Anchor~\cite{ribeiro2018anchors}}\label{sec:anchor}
+\subsubsection[Anchor]{%
+	Anchor~\cite{ribeiro2018anchors}
+}\label{sec:anchor}
 Anchor represents a rectangular region containing the focal point $x$,
@@
 (\cref{fig:rlime}).
-The accuracy of $g$ is defined as the "accuracy" of the rule,
-and the generality of explanations is defined as the "coverage" of the rule.
+The accuracy of $g$ is defined as the ``accuracy'' of the rule,
+and the generality of explanations is defined as the ``coverage'' of the rule.
 
@@
 		\includegraphics[width=0.32\textwidth]{rlime3}
-		\caption{%
+		\caption[Overview of the R-LIME algorithm]{%
 			Overview of the R-LIME algorithm.
@@
 	\end{figure}
-	\begin{algorithm}[p]
+	\def\myidt{\hspace{\algorithmicindent}}
+	\ifnum\mode=0
+		\begin{algorithm}[t]
+			\small
 			\input{alg1}
 		\end{algorithm}
+	\else
 		\begin{algorithm}[p]
-		\input{alg2}
+			\small
+			\input{alg1}
 		\end{algorithm}
-	\def\myidt{\hspace{\algorithmicindent}}
+	\fi
+
+	\foreach \alg in {2,3,4}{%
 			\begin{algorithm}[p]
-		\input{alg3}
+				\small
+				\input{alg\alg}
 			\end{algorithm}
-	\begin{algorithm}[p]
-		\input{alg4}
-	\end{algorithm}
+		}
 }
@@
 
+\ifnum\mode=1
 	\subsection{Computational Complexity}
@@
 	is $|\mathcal{D}|$,
+\fi
 
@@
 		\centering
-		\caption{%
+		\caption[Attributes of the recidivism dataset used in the experiments]{%
 			Attributes of the recidivism dataset used in the experiments.
@@
 		}\label{tab:rcdv}
+		\ifnum\mode=0
+			\small
+		\fi
 		\begin{tabular}{llc}
 			\toprule
-			Attribute              & Overview                              & \# of Possible Values \\
+			Attribute              & Overview                              & \# of \ifnum\mode=1 Possible \fi Values \\
 			\midrule
@@
 			\def\mylabel#1{\ifnum#1=0 \label{fig:A-instance}\else \label{fig:B-instance}\fi}
+			\ifnum\mode=0
+				\renewcommand{\arraystretch}{0.99}
+			\else
 				\renewcommand{\arraystretch}{1.02}
+			\fi
 			\begin{figure}[tbp]
@@
 						\begin{subfigure}{\textwidth}
+							\ifnum\mode=0
+								\small
+							\fi
 							\centering
@@
 				\vspace{-15pt}
-				\caption{Two instances sampled from recidivism dataset.}\label{fig:instance}
+				\caption[Two instances sampled from recidivism dataset]{%
+					Two instances sampled from recidivism dataset.
+				}\label{fig:instance}
 			\end{figure}
@@
 		{%
+			\ifnum\mode=0
+				\def\scale{0.3}
+				\def\imgwidth{0.45\textwidth}
+			\else
 				\def\scale{0.315}
 				\def\imgwidth{0.495\textwidth}
+			\fi
 			\def\hspacebase{\hspace{-1.5em}}
@@
 				\end{subfigure}
-				\caption{Explanation for Instance A by LIME and R-LIME.}\label{fig:A}
+				\caption[Explanation for Instance A by LIME and R-LIME]{%
+					Explanation for Instance A by LIME and R-LIME.
+				}\label{fig:A}
 			\end{figure}
@@
 				\end{subfigure}
-				\caption{Explanation for Instance B by LIME and R-LIME}\label{fig:B}
+				\caption[Explanation for Instance B by LIME and R-LIME]{%
+					Explanation for Instance B by LIME and R-LIME.
+				}\label{fig:B}
 			\end{figure}
@@
 	  \end{subfigure}
-	  \caption{%
+	  \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
 		  Behavior of R-LIME for balanced and imbalanced label distribution.
@@
 
-\subsection{Changes in Reward Distribution in Optimal Arm Identification}\label{sec:reward}
+\subsection{Changes in Reward Distribution in Best Arm Identification}\label{sec:reward}
 {%
@@
 		\centering
-		\caption{%
+		\caption[Deviation between the estimated accuracy and the true accuracy]{%
 			Deviation between the estimated accuracy and the true accuracy.
@@
 
-% \subsection{Evaluation through User Studies}
-% Given the nature of the field of "interpretable machine learning,"
-% where the goal is to "interpret" machine learning models,
-% it is challenging to quantitatively compare various methods.
-% While quantitative experiments were conducted in \cref{sec:exp2},
-% they mainly demonstrated that the proposed method generates
-% locally accurate explanations compared to LIME.
-% The results do not directly prove the high interpretability of the proposed method.
-% 
-% One potential method to quantitatively evaluate "interpretability" is
-% through user studies.
-% For example, \cite{ribeiro2018anchors} conducted user studies,
-% assuming that if users could predict the output of a black-box model
-% with high accuracy based on provided explanations,
-% those explanations contained valuable information about the model's behavior.
-% Similarly,
-% conducting user studies in this research would be desirable
-% to evaluate the interpretability of the proposed method.
-
 \section{Conclusion}
@@
 
+\ifnum\mode=0
+	\acknowledge
+	I would like to express my gratitude to Associate Professor Keigo Kimura
+	from the Department of Mathematical Science,
+	Division of Information Recognition,
+	Graduate School of Information Science and Technology, Hokkaido University.
+	He provided invaluable guidance,
+	from setting the research theme to outlining the strategy and content of this study.
+	Additionally,
+	I appreciate the diverse insights shared by Professor Mineichi Kudo in the same laboratory.
+	Finally, I am deeply thankful to all the members of the laboratory
+	for their helpful advice and collaboration throughout the research process.
+\fi
+
 % \subsubsection{Acknowledgements}
@@
 %
+\ifnum\mode=0
+	\bibliographystyle{prml}
+\else
 	\bibliographystyle{splncs04}
+\fi
 \bibliography{MyRef/ref}

### 2024-02-27 paper/paper.tex
Work on paper

@@
 \ifnum\mode=0
-	\documentclass{article}
+	\documentclass[11pt]{article}
 	\usepackage{prmlthesis}
+	\usepackage[a4paper]{geometry}
 \else
@@
 			\ifnum\mode=0
-				\renewcommand{\arraystretch}{0.99}
+				\renewcommand{\arraystretch}{0.97}
 			\else
@@
 				\def\imgwidth{0.45\textwidth}
+				\def\hspacebase{\hspace{-0.5em}}
 			\else
@@
 				\def\imgwidth{0.495\textwidth}
+				\def\hspacebase{\hspace{-1.5em}}
 			\fi
-			\def\hspacebase{\hspace{-1.5em}}
 			\def\vspacebase{\vspace{0.5em}}
@@
  {%
-  \def\imgwidth{0.49\textwidth}
-  \def\scale{0.08}
+  \def\imgwidth{0.45\textwidth}
   \begin{figure}[t]
@@
 		  \centering
-		  \includegraphics[scale=\scale]{newlime}
+		  \includegraphics[width=0.7\textwidth]{newlime}
 		  \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
@@
 		  \centering
-		  \includegraphics[scale=\scale]{newlime_for_imbalanced_data}
+		  \includegraphics[width=0.7\textwidth]{newlime_for_imbalanced_data}
 		  \caption{R-LIME for imbalanced label distribution.
@@
 	\acknowledge
-	I would like to express my gratitude to Associate Professor Keigo Kimura
-	from the Department of Mathematical Science,
-	Division of Information Recognition,
-	Graduate School of Information Science and Technology, Hokkaido University.
-	He provided invaluable guidance,
-	from setting the research theme to outlining the strategy and content of this study.
-	Additionally,
-	I appreciate the diverse insights shared by Professor Mineichi Kudo in the same laboratory.
-	Finally, I am deeply thankful to all the members of the laboratory
-	for their helpful advice and collaboration throughout the research process.
+	I would like to thank Associate Professor Keigo Kimura
+	of the Laboratory for Pattern Recognition and Machine Learning,
+	Division of Computer Science and Information Technology,
+	Graduate School of Information Sci.\ and Tech., Hokkaido University.
+	He provided valuable guidance
+	from setting the research theme to outlining the research method.
+	Furthermore,
+	I appreciate the various insights shared by Professor Mineichi Kudo
+	in the same laboratory.
+	Finally, I am deeply thankful to all the members of our laboratory
+	for their helpful advice and cooperation throughout the research process.
 \fi

### 2024-03-02 paper/paper.tex
Modify detail of images

@@
 LIME locally
-approximates a trained black-box classifier $f: \mathbb{R}^d \to \{0,1\}$
-around a focal point $x \in \mathbb{R}^d$
-by a linear classifier $g: \mathbb{R}^d \to \{0,1\}$
+approximates a trained black-box classifier $f: \mathbb{R}^m \to \{0,1\}$
+around a focal point $x \in \mathbb{R}^m$
+by a linear classifier $g: \mathbb{R}^m \to \{0,1\}$
 (\cref{fig:lime}).
@@
 
-\ifnum\mode=1
 \subsection{Computational Complexity}
@@
 where $|\mathcal{Z}_p|$ is the number of perturbed samples.
-	On the other hand, the number of queries required for Anchor and R-LIME
-	is $|\mathcal{D}|$,
-\fi
+On the other hand,
+the number of queries required for Anchor and R-LIME is
+$\mathcal{O}(B\cdot m^2+m^2\cdot\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]})$,
+where $B$ is the beam width, $m$ is the number of features, and
+$\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$ is the computational complexity of
+pure exploration
+of the multi-armed bandit algorithm with $B\cdot m$ arms and beam width $B$.
+$\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$ depends on hyperparameters
+such as threshold $\tau$, confidence level $1-\delta$ and tolerance $\epsilon$.
 
@@
 			\ifnum\mode=0
-				\def\scale{0.3}
+				\def\scale{0.32}
 				\def\imgwidth{0.45\textwidth}
@@
 					\hspacebase
+					\hspace{1.0em}
 					\includegraphics[scale=\scale]{\dir/lime-\Asample}
@@
 					\hspacebase
-					\hspace{1.0em}
+					\hspace{0.5em}
 					\includegraphics[scale=\scale]{\dir/newlime-\Asample-70}
@@
 					\hspacebase
+					\hspace{-0.5em}
 					\includegraphics[scale=\scale]{\dir/newlime-\Asample-90}
@@
 					\hspacebase
+					\hspace{-0.7em}
 					\includegraphics[scale=\scale]{\dir/lime-\Bsample}
@@
 					\hspacebase
+					\hspace{0.5em}
 					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-70}
@@
 					\hspacebase
+					\hspace{-0.8em}
 					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-80}
@@
 					\hspacebase
-					\hspace{0em}
+					\hspace{-0.8em}
 					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-90}

### 2024-03-02 paper/paper.tex
Work on paper

@@
 	\documentclass[11pt]{article}
+	\usepackage{luatexja}
 	\usepackage{prmlthesis}
@@
 	\title{%
+		R-LIME: LIME法における矩形制約と最適化
+	}
+	\etitle{%
 		R-LIME: Rectangular Constraints and Optimization for Local Interpretable
@@
 	}
-	\etitle{}
-	\author{Genji Ohara}
-	\institute{hogehoge}
+	\author{大原 玄嗣 (Genji Ohara)}
+	\institute{%
+		北海道大学 工学部 \\
+		情報エレクトロニクス学科 \\
+		情報理工学コース \\
+		情報認識学研究室
+	}
+	\date{2024年3月}
+	% \institute{%
+	% 	Laboratory for Pattern Recognition and Machine Learning,\\
+	% 	Division of Computer Science and Information Technology,\\
+	% 	Department of Electronics and Information Engineering,\\
+	% 	School of Engineering, Hokkaido University
+	% }
 \else
@@
 Model-dependent methods,
-such as DTD (Deep Taylor Decomposition)~\cite{montavon2017explaining}
-and LRP (Layer-wise Relevance Propagation)~\cite{bach2015pixel},
+such as Deep Taylor Decomposition (DTD)~\cite{montavon2017explaining}
+and Layer-wise Relevance Propagation (LRP)~\cite{bach2015pixel},
 primarily focus on deep neural networks and
@@
 Global methods,
-such as PDP (Partial Dependence Plots)~\cite{friedman2001greedy}
-and ALE (Accumulated Local Effects)~\cite{apley2020visualizing},
+such as Partial Dependence Plots (PDP)~\cite{friedman2001greedy}
+and Accumulated Local Effects (ALE)~\cite{apley2020visualizing},
 aim to explain the model's behavior across the entire input space,
@@
 		\centering
+		\ifnum\mode=0
+			\vspace{-1.79cm}
+		\else
 			\vspace{-2.24cm}
+		\fi
 		\includegraphics[scale=\scale]{example-rlime}
@@
 maximize coverage under the constraint of minimum approximation accuracy.
-Comparing the outputs of LIME and R-LIME on real-world datasets,
-we demonstrated that explanations provided by R-LIME have clearer application
-scopes and can be evaluated by users for reliability and generality.
+Comparing the outputs of LIME and R-LIME on the real-world dataset,
+we demonstrated that R-LIME provides a clear application scope of the
+explanation and can be evaluated by users for its reliability and generality.
 However, we discussed the instability of behavior concerning imbalanced label

### 2024-03-04 paper/paper.tex
Completed graduation thesis

@@
 % set the path for figures
-\graphicspath{{./data/}{../python/data/}}
+\graphicspath{{./src/}{../python/data/}{../experiments/}}
 
@@
 % settings for cleveref
-\crefname{figure}{Fig.}{Figs.}
+\crefname{figure}{Figure}{Figures}
 \crefname{table}{Table}{Tables}
@@
 		\centering
-		\includegraphics[width=\textwidth]{visual-rlime}
+		\includegraphics[width=\textwidth]{visual-rlime3}
 		\caption{%
 			R-LIME:
-			Maximizes coverage of a rectangular region containing the focal point
+			Maximizes coverage of a rectangular region
 			under lower constraints on the accuracy of the linear classifier.
@@
 		\centering
-		\includegraphics[width=0.32\textwidth]{rlime1}
-		\includegraphics[width=0.32\textwidth]{rlime2}
-		\includegraphics[width=0.32\textwidth]{rlime3}
+		\includegraphics[width=0.32\textwidth]{visual-rlime1}
+		\includegraphics[width=0.32\textwidth]{visual-rlime2}
+		\includegraphics[width=0.32\textwidth]{visual-rlime3}
 		\caption[Overview of the R-LIME algorithm]{%
@@
 	such as threshold $\tau$, confidence level $1-\delta$ and tolerance $\epsilon$.
+\fi
 
@@
 
-Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) indicate that
-attributes such as having a significant prior record (Prior) or committing a
-crime against property (Crime against Property) primarily contribute positively
-to the prediction (predicting that the prisoner will be re-arrested).
+Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) provide insights
+that attributes such as having a prior offenses (Priors),
+being served for a long time in prison (MonthsServed),
+and committing a crime against property (Crime against Property)
+primarily contribute to the positive prediction
+(prediction that the prisoner will be re-arrested).
 On the other hand,
 attributes like older age (Age), being married (Married),
-and being of white race (Race) contribute negatively to the prediction
-(predicting that the prisoner will not be re-arrested).
+and being of white race (Race) contribute to the negative prediction
+(prediction that the prisoner will not be re-arrested).
 While these LIME explanations provide valuable insights into the behavior of
@@
 For example, the coverage of the explanation for instance B under $\tau=0.90$
-(\cref{fig:B-rlime-90}) is 0.002,
+(\cref{fig:B-rlime-90}) is 0.01\%,
 indicating that the decision boundaries around instance B are complex,
@@
 		  \centering
-		  \includegraphics[width=0.7\textwidth]{newlime}
+		  \includegraphics[width=0.8\textwidth]{visual-rlime3}
 		  \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
@@
 		  \centering
-		  \includegraphics[width=0.7\textwidth]{newlime_for_imbalanced_data}
+		  \includegraphics[width=0.8\textwidth]{visual-rlime-imbalanced}
 		  \caption{R-LIME for imbalanced label distribution.

### 2024-03-04 experiments/exp_adv/complexity.py

@@ -1,0 +1,56 @@
+"""Calculate the complexity of queries for the black-box classifiers
+in R-LIME."""
+
+import sys
+from typing import Any
+
+from sklearn.ensemble import RandomForestClassifier
+
+sys.path.append("RLIME")
+
+from RLIME import newlime_base, newlime_tabular, newlime_utils
+from RLIME.newlime_types import IntArray
+
+
+class BlackBoxClassifier(RandomForestClassifier):  # type: ignore
+    """A black-box classifier for R-LIME."""
+
+    def __init__(self, *args: str, **kwargs: int) -> None:
+        """Initialize the black-box classifier."""
+
+        super().__init__(*args, **kwargs)
+        self.predict_count = 0
+
+    def predict(self, X: IntArray) -> Any:
+        """Predict the labels of the input instances."""
+
+        self.predict_count += X.shape[0]
+        print(f"Predict count: {self.predict_count}")
+        return super().predict(X)
+
+
+def main() -> None:
+    """Main function."""
+
+    # Load the dataset.
+    dataset = newlime_utils.load_dataset(
+        "recidivism", "datasets/", balance=True
+    )
+
+    # Learn the black box model.
+    black_box = BlackBoxClassifier(n_estimators=100, n_jobs=1)
+    black_box.fit(dataset.train, dataset.labels_train)
+
+    idx = 0
+    trg, _, _ = newlime_utils.get_trg_sample(idx, dataset)
+    hyper_param = newlime_base.HyperParam()
+    result = newlime_tabular.explain_instance(
+        trg, dataset, black_box, hyper_param
+    )
+
+    if result is None:
+        print("No explanation found.")
+        return
+    names, arm = result
+    print(f"Names: {names}")
+    print(f"ARM: {arm}")

### 2024-03-04 paper/paper.tex
ICPR 2nd version

@@
 \end{enumerate}
-
 LIME provides valuable insights into the local behavior of the model
@@
 contributing significantly to the output (\cref{fig:anchor}).
-
 For a discrete $m$-dimensional input space $\ispace$
@@
 \end{align}
-
 where $\mathcal{D}(z|A)$ is the conditional distribution in the region
@@
 and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
-
 Anchor maximizes coverage under the constraint that
@@
 	$\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$ is the computational complexity of
-	pure exploration
-	of the multi-armed bandit algorithm with $B\cdot m$ arms and beam width $B$.
+	pure exploration problem of finding the $B$ best arms among $B\cdot m$ arms.
 	$\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$ depends on hyperparameters
@@
 only to married prisoner (Married$=$Yes).
-Furthermore, the generated explanations include the accuracy and coverage of
-the approximation region, allowing users to evaluate how reliable the
-explanations are.
+Furthermore, the explanations include the accuracy and coverage,
+allowing users to evaluate its reliability.
 For example, the coverage of the explanation for instance B under $\tau=0.90$
@@
 	\centering
-	\includegraphics[width=0.55\textwidth]{experiments/exp2/box_plot}
+	\includegraphics[width=0.53\textwidth]{experiments/exp2/box_plot}
 	\caption[Comparison of Local Accuracy between R-LIME and LIME]{%
@@
 The results are presented in \cref{fig:box_plot},
-showcasing the distribution of the accuracy of the linear approximation models
+showing the distribution of the accuracy of the linear approximation models
 learned by LIME and R-LIME\@.
-R-LIME exhibits higher accuracy compared to LIME for all values of $\tau$.
+R-LIME achieved higher accuracy compared to LIME for all values of $\tau$.
 This suggests that the linear classifiers learned by LIME and R-LIME
@@
  {%
-  \def\imgwidth{0.45\textwidth}
+  \def\imgwidth{0.47\textwidth}
   \begin{figure}[t]
@@
 		  \centering
-		  \includegraphics[width=0.8\textwidth]{visual-rlime3}
+		  \includegraphics[width=0.75\textwidth]{visual-rlime3}
 		  \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
@@
 		  \centering
-		  \includegraphics[width=0.8\textwidth]{visual-rlime-imbalanced}
+		  \includegraphics[width=0.75\textwidth]{visual-rlime-imbalanced}
 		  \caption{R-LIME for imbalanced label distribution.

### 2024-03-04 paper/paper.tex
Sort out repository

@@
 
-\def\mode{0} % 0: Graduation thesis, 1: ICPR paper
+\def\mode{1} % 0: Graduation thesis, 1: ICPR paper
 
@@
   \usepackage{luatexja}
-	\usepackage{prmlthesis}
+  \usepackage{style/prmlthesis}
   \usepackage[a4paper]{geometry}
@@
 % import the TeX file containing macro definitions
-\input{macro}
+\input{tex/macro}
 
@@
   \centering
-	\vspace{0.5cm}
   \begin{subfigure}[t]{0.55\textwidth}
@@
     \caption{Focal point.}\label{fig:example-instance}
-	\end{subfigure}
-	\hfill
+    \vspace{0.5cm}
+  \end{subfigure}
   \begin{subfigure}[t]{0.45\textwidth}
@@
       \small
-			\input{alg1}
+      \input{tex/alg1}
     \end{algorithm}
@@
         \small
-				\input{alg\alg}
+        \input{tex/alg\alg}
       \end{algorithm}
@@
     }\label{tab:reward}
-		\input{tab_exp_adv}
+    \input{tex/tab_exp_adv}
   \end{table}
@@
 \ifnum\mode=0
-	\bibliographystyle{prml}
+  \bibliographystyle{style/prml}
 \else
-	\bibliographystyle{splncs04}
+  \bibliographystyle{style/splncs04}
 \fi

### 2024-03-15 paper/paper.tex
Work on the paper

@@
 % settings for cleveref
-\crefname{figure}{Figure}{Figures}
 \crefname{table}{Table}{Tables}
 \crefname{algorithm}{Algorithm}{Algorithms}
+\ifnum\mode=0
+  \crefname{figure}{Figure}{Figures}
+\else
+  \crefname{figure}{Fig.}{Figs.}
+\fi
 
@@
 \else
-
   % The abstract should briefly summarize the contents of the paper in
@@
 \emph{global} and \emph{local} methods based on their locality in input space.
-
-This paper specifically focuses
-on \emph{model-agnostic} and \emph{local} methods,
-which do not rely on the models' structure
-and explain the models' behavior
-in the vicinity of a given input (focal point).
-For example, LIME (Local Interpretable Model-agnostic Explanations)
-\cite{ribeiro2016why} approximates the complex model's decision boundary
-locally using a simpler model around the given focal point.
-Although LIME enables users to interpret the local behavior of complex models,
-it does not explicitly provide the effective scope of the explanation
-\cite{ribeiro2018anchors}.
-This limitation can lead
-users to overgeneralize the knowledge derived from the explanation.
-Without a clear indication of the scope of the explanation,
-users might mistakenly apply
-the derived knowledge to instances outside this scope,
-potentially leading to misunderstanding of the black-box model's behavior.
-
-To address this limitation of LIME,
-we propose a new method called R-LIME (Ruled LIME),
-which interprets complex classifiers in an interpretable region.
-R-LIME locally approximates a complex decision boundary linearly
-in a rectangular region and maximizes the region
-as long as the accuracy of the linear classifier is
-higher than a given threshold.
-The resulting rectangular region is interpretable for users because it is
-expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).
-
-\section{Related Work}
-In this chapter,
-we overview existing research on post-hoc explanations,
-which explain the behavior of complex models already trained.
-They are categorized
-into \emph{model-dependent} and \emph{model-agnostic} methods
-based on their dependence on the model's structure.
-
-Model-dependent methods,
-such as Deep Taylor Decomposition (DTD)~\cite{montavon2017explaining}
-and Layer-wise Relevance Propagation (LRP)~\cite{bach2015pixel},
-primarily focus on deep neural networks and
-explain the models' behavior using their parameters~\cite{samek2021explaining}.
-While these methods can provide detailed explanations
-(e.g., layer-wise explanations for neural networks)
-using the models' internal parameters,
-it is often challenging
-to apply the same method to models with different structures.
-
-On the other hand,
-model-agnostic methods
-do not rely on the models' parameters and utilize only their output.
-Although these methods are applicable to any model,
-they cannot explain the reasoning process inside the model.
-Furthermore, model-agnostic methods are classified into
-\emph{global} and \emph{local} methods based on their locality in input space.
-Global methods,
-such as Partial Dependence Plots (PDP)~\cite{friedman2001greedy}
-and Accumulated Local Effects (ALE)~\cite{apley2020visualizing},
-aim to explain the model's behavior across the entire input space,
-seeking explanations valid for any input.
-However, providing global explanations becomes challenging
-as the model's complexity increases.
-In contrast, local methods,
-such as LIME (Local Interpretable Model-agnostic Explanations)~\cite{ribeiro2016why}
-and Anchor~\cite{ribeiro2018anchors},
-% SHAP~\cite{lundberg2017unified},
-% EXPLAN~\cite{rasouli2020explan},
-% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
-% and BELLA (Black box model Explanations by Local Linear Approximations)
-% \cite{radulovic2023bella},
-explain output of the model for a specific input
-(focal point) in the vicinity of that input.
-While local methods offer more simple and accurate explanations
-than global methods,
-the scope of the explanation is limited to the vicinity of the focal point.
-
+% This paper specifically focuses
+% on \emph{model-agnostic} and \emph{local} methods,
+% which do not rely on the models' structure
+% and explain the models' behavior
+% in the vicinity of a given input (focal point).
+% For example, LIME (Local Interpretable Model-agnostic Explanations)
+% \cite{ribeiro2016why} approximates the complex model's decision boundary
+% locally using a simpler model around the given focal point.
+% Although LIME enables users to interpret the local behavior of complex models,
+% it does not explicitly provide the effective scope of the explanation
+% \cite{ribeiro2018anchors}.
+% This limitation can lead
+% users to overgeneralize the knowledge derived from the explanation.
+% Without a clear indication of the scope of the explanation,
+% users might mistakenly apply
+% the derived knowledge to instances outside this scope,
+% potentially leading to misunderstanding of the black-box model's behavior.
 \begin{figure}[tbp]
@@
 
-% BELLA\cite{radulovic2023bella} addresses the non-optimization of the approximation region,
-% a drawback of LIME,
-% by learning a local linear classifier $g$
-% using a subset $Z'$ of the dataset $Z$
-% instead of perturbed samples.
-% The process involves:
-% \begin{enumerate}
-% 	\item Computing the distance $d_x(z)$ for all instances $z$ in $Z$
-% 	      with respect to the focal point $x$.
-% 	\item Selecting the $k$ instances with the smallest $d_x(z)$,
-% 	      forming a subset $Z_s(k) \subseteq Z$.
-% 	\item Learning the local linear classifier $g$ using $Z_s(k)$
-% 	      and calculating the similarity measure $\mathcal{R}(k)$ between $f$ and $g$
-% 	      over $k=1,2,\dots,|Z|$.
-% 	\item Obtaining the optimal $k^*$ by maximizing $\mathcal{R}(k)$.
-% \end{enumerate}
-% 
-% BELLA aims to enhance the reliability of explanations
-% by optimizing the approximation region for high-accuracy linear approximations.
-% However, it assumes direct access to the dataset $Z$ used for training the classifier,
-% making it inapplicable in scenarios where direct access to the dataset is restricted.
-% Additionally,
-% as BELLA presents the approximation region as a subset of the dataset,
-% its interpretability is lower compared to Anchor.
+To address this limitation of LIME,
+we propose a new method called R-LIME (Ruled LIME),
+which interprets complex classifiers in an interpretable region.
+R-LIME locally approximates a complex decision boundary linearly
+in a rectangular region and maximizes the region
+as long as the accuracy of the linear classifier is
+higher than a given threshold.
+The resulting rectangular region is interpretable for users because it is
+expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).
+
+\section{Related Work}
+In this chapter,
+we overview existing research on post-hoc explanations,
+which explain the behavior of complex models already trained.
+They are categorized
+into \emph{model-dependent} and \emph{model-agnostic} methods
+based on their dependence on the model's structure.
+
+Model-dependent methods,
+such as Deep Taylor Decomposition (DTD)~\cite{montavon2017explaining}
+and Layer-wise Relevance Propagation (LRP)~\cite{bach2015pixel},
+primarily focus on deep neural networks and
+explain the models' behavior using their parameters~\cite{samek2021explaining}.
+While these methods can provide detailed explanations
+(e.g., layer-wise explanations for neural networks)
+using the models' internal parameters,
+it is often challenging
+to apply the same method to models with different structures.
+
+On the other hand,
+model-agnostic methods
+do not rely on the models' parameters and utilize only their output.
+Although these methods are applicable to any model,
+they cannot explain the reasoning process inside the model.
+Furthermore, model-agnostic methods are classified into
+\emph{global} and \emph{local} methods based on their locality in input space.
+Global methods,
+such as Partial Dependence Plots (PDP)~\cite{friedman2001greedy}
+and Accumulated Local Effects (ALE)~\cite{apley2020visualizing},
+aim to explain the model's behavior across the entire input space,
+seeking explanations valid for any input.
+However, providing global explanations becomes challenging
+as the model's complexity increases.
+In contrast, local methods,
+such as LIME (Local Interpretable Model-agnostic Explanations)~\cite{ribeiro2016why}
+and Anchor~\cite{ribeiro2018anchors},
+% SHAP~\cite{lundberg2017unified},
+% EXPLAN~\cite{rasouli2020explan},
+% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
+% and BELLA (Black box model Explanations by Local Linear Approximations)
+% \cite{radulovic2023bella},
+explain output of the model for a specific input
+(focal point) in the vicinity of that input.
+While local methods offer more simple and accurate explanations
+than global methods,
+the scope of the explanation is limited to the vicinity of the focal point.
 
@@
 \end{figure}
+
 \subsection{Previous Work}
@@
 particularly focusing on studies closely related to our proposed method.
+
 \subsubsection[LIME]{%
@@
 }
-
 The algorithm of our method
@@
   The number of queries required for LIME is $|\mathcal{Z}_p|$,
-  where $|\mathcal{Z}_p|$ is the number of perturbed samples.
+  where $|\mathcal{Z}_p|$ is the number of perturbed samples selected by the user.
   On the other hand,

### 2024-03-18 paper/paper.tex
Update submodule myref
ICPR 3rd version

--- 2024-03-04 paper/paper.tex
@@
 \usepackage[labelformat=simple]{subcaption} % for subfigure environment
+\usepackage{tikz}
+\usetikzlibrary{positioning}
 
@@
 \emph{global} and \emph{local} methods based on their locality in input space.
-
-This paper specifically focuses
-on \emph{model-agnostic} and \emph{local} methods,
-which do not rely on the models' structure
-and explain the models' behavior
-in the vicinity of a given input (focal point).
-For example, LIME (Local Interpretable Model-agnostic Explanations)
-\cite{ribeiro2016why} approximates the complex model's decision boundary
-locally using a simpler model around the given focal point.
-Although LIME enables users to interpret the local behavior of complex models,
-it does not explicitly provide the effective scope of the explanation
-\cite{ribeiro2018anchors}.
-This limitation can lead
-users to overgeneralize the knowledge derived from the explanation.
-Without a clear indication of the scope of the explanation,
-users might mistakenly apply
-the derived knowledge to instances outside this scope,
-potentially leading to misunderstanding of the black-box model's behavior.
-
-To address this limitation of LIME,
-we propose a new method called R-LIME (Ruled LIME),
-which interprets complex classifiers in an interpretable region.
-R-LIME locally approximates a complex decision boundary linearly
-in a rectangular region and maximizes the region
-as long as the accuracy of the linear classifier is
-higher than a given threshold.
-The resulting rectangular region is interpretable for users because it is
-expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).
-
-\section{Related Work}
-In this chapter,
-we overview existing research on post-hoc explanations,
-which explain the behavior of complex models already trained.
-They are categorized
-into \emph{model-dependent} and \emph{model-agnostic} methods
-based on their dependence on the model's structure.
-
-Model-dependent methods,
-such as Deep Taylor Decomposition (DTD)~\cite{montavon2017explaining}
-and Layer-wise Relevance Propagation (LRP)~\cite{bach2015pixel},
-primarily focus on deep neural networks and
-explain the models' behavior using their parameters~\cite{samek2021explaining}.
-While these methods can provide detailed explanations
-(e.g., layer-wise explanations for neural networks)
-using the models' internal parameters,
-it is often challenging
-to apply the same method to models with different structures.
-
-On the other hand,
-model-agnostic methods
-do not rely on the models' parameters and utilize only their output.
-Although these methods are applicable to any model,
-they cannot explain the reasoning process inside the model.
-Furthermore, model-agnostic methods are classified into
-\emph{global} and \emph{local} methods based on their locality in input space.
-Global methods,
-such as Partial Dependence Plots (PDP)~\cite{friedman2001greedy}
-and Accumulated Local Effects (ALE)~\cite{apley2020visualizing},
-aim to explain the model's behavior across the entire input space,
-seeking explanations valid for any input.
-However, providing global explanations becomes challenging
-as the model's complexity increases.
-In contrast, local methods,
-such as LIME (Local Interpretable Model-agnostic Explanations)~\cite{ribeiro2016why}
-and Anchor~\cite{ribeiro2018anchors},
-% SHAP~\cite{lundberg2017unified},
-% EXPLAN~\cite{rasouli2020explan},
-% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
-% and BELLA (Black box model Explanations by Local Linear Approximations)
-% \cite{radulovic2023bella},
-explain output of the model for a specific input
-(focal point) in the vicinity of that input.
-While local methods offer more simple and accurate explanations
-than global methods,
-the scope of the explanation is limited to the vicinity of the focal point.
-
 \begin{figure}[tbp]
@@
 \end{figure}
+
 In this paper,
 we focus on local model-agnostic methods.
-An example of explanations by LIME and Anchor
+An example of explanations by LIME~\cite{ribeiro2016why} and
+Anchor~\cite{ribeiro2018anchors}
 for a sentiment prediction model is illustrated in \cref{fig:example}.
-LIME~\cite{ribeiro2016why} approximates the complex decision boundary
-locally using a linear model around the given focal point,
+LIME approximates the complex decision boundary
+linearly around the given focal point,
 then provides the weights of the linear model as the contribution of each feature
@@
 \cite{ribeiro2018anchors}.
-For example,
-user may apply the insights derived from the explanation
+For this example,
+user may apply the derived insights
 to the sentence ``This book is not good.''
@@
 mainly contributes to the positive prediction for this sentence as well,
-which is incorrect obviously.
-Anchor~\cite{ribeiro2018anchors} represents a rectangular region
+which is obviously incorrect.
+Anchor represents a rectangular region
 containing the focal point,
@@
 
-% BELLA\cite{radulovic2023bella} addresses the non-optimization of the approximation region,
-% a drawback of LIME,
-% by learning a local linear classifier $g$
-% using a subset $Z'$ of the dataset $Z$
-% instead of perturbed samples.
-% The process involves:
-% \begin{enumerate}
-% 	\item Computing the distance $d_x(z)$ for all instances $z$ in $Z$
-% 	      with respect to the focal point $x$.
-% 	\item Selecting the $k$ instances with the smallest $d_x(z)$,
-% 	      forming a subset $Z_s(k) \subseteq Z$.
-% 	\item Learning the local linear classifier $g$ using $Z_s(k)$
-% 	      and calculating the similarity measure $\mathcal{R}(k)$ between $f$ and $g$
-% 	      over $k=1,2,\dots,|Z|$.
-% 	\item Obtaining the optimal $k^*$ by maximizing $\mathcal{R}(k)$.
-% \end{enumerate}
-% 
-% BELLA aims to enhance the reliability of explanations
-% by optimizing the approximation region for high-accuracy linear approximations.
-% However, it assumes direct access to the dataset $Z$ used for training the classifier,
-% making it inapplicable in scenarios where direct access to the dataset is restricted.
-% Additionally,
-% as BELLA presents the approximation region as a subset of the dataset,
-% its interpretability is lower compared to Anchor.
+To address this limitation of LIME,
+we propose a new method called R-LIME (Ruled LIME),
+which interprets complex classifiers in an interpretable region.
+R-LIME locally approximates a complex decision boundary linearly
+in a rectangular region and maximizes the region
+as long as the accuracy of the linear classifier is
+higher than a given threshold.
+The rectangular region is interpretable for users because it is
+expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).
+An example of the explanation by R-LIME for a sentiment prediction model
+is illustrated in \cref{fig:example-rlime}.
+It is clear that users can apply the insights derived from the explanation
+only to the sentences containing the word ``not''.
+
+\section{Related Work}
+\begin{figure}[tbp]
+  \centering
+  \def\w{2.2}
+  \def\ww{4.4}
+  \def\h{0.7}
+  \def\hh{1.4}
+  \def\hhh{2.1}
+  \def\hhhh{2.8}
+  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,node font=\normalsize\itshape,auto}]
+    \node[nodestyle] (post-hoc) at (0,0){post-hoc};
+    \node[nodestyle] (dependent) at (-\w,-\hh){model-dependent};
+    \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
+    \node[nodestyle] (global) at (0,-\hhhh){global};
+    \node[nodestyle] (local) at (\ww,-\hhhh){\textbf{local}};
+    \draw(post-hoc) -- (0,-\h);
+    \draw(dependent) -- (-\w,-\h) -- (\w,-\h) -- (agnostic);
+    \draw(agnostic) -- (\w,-\hhh);
+    \draw(global) -- (0,-\hhh)  -- (\ww,-\hhh) -- (local);
+  \end{tikzpicture}
+  \caption{%
+    Categorization of post-hoc explanation methods.
+    We focus on \emph{model-agnostic} and \emph{local} methods,
+    which explain model's local behavior using only its output.
+  }\label{fig:post-hoc}
+\end{figure}
+In this chapter,
+we overview existing research on post-hoc explanation methods,
+which explain the behavior of black-box models already trained.
+As shown in \cref{fig:post-hoc},
+post-hoc methods are classified into several categories.
+
+First, they are categorized into \emph{model-dependent} and \emph{model-agnostic} methods
+based on their dependence on the model's structure.
+Model-dependent methods,
+such as Deep Taylor Decomposition (DTD)~\cite{montavon2017explaining}
+and Layer-wise Relevance Propagation (LRP)~\cite{bach2015pixel},
+most of which focus on neural networks and
+explain the model's behavior using its parameters~\cite{samek2021explaining}.
+While these methods provide detailed explanations
+(e.g., layer-wise explanations for neural networks),
+it is often challenging
+to apply the same method to models with different structures.
+On the other hand,
+model-agnostic methods use only the output of the model.
+Although they are applicable to any model,
+they cannot explain the reasoning process inside the model.
+
+Then, model-agnostic methods are classified into
+\emph{global} and \emph{local} methods based on their locality in input space.
+Global methods,
+such as Partial Dependence Plots (PDP)~\cite{friedman2001greedy}
+and Accumulated Local Effects (ALE)~\cite{apley2020visualizing},
+aim to explain the model's behavior across the entire input space.
+% seeking explanations valid for any input.
+However, providing global explanations becomes challenging
+as the model's complexity increases.
+In contrast, local methods,
+such as Local Interpretable Model-agnostic Explanations (LIME)
+\cite{ribeiro2016why}
+and Anchor~\cite{ribeiro2018anchors},
+% SHAP~\cite{lundberg2017unified},
+% EXPLAN~\cite{rasouli2020explan},
+% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
+% and BELLA (Black box model Explanations by Local Linear Approximations)
+% \cite{radulovic2023bella},
+explain model's behavior in the vicinity of a specific input.
+While local methods offer explanations more simple and accurate
+than global methods,
+the scope of the explanation is limited locally.
 
@@
 LIME locally
-approximates a trained black-box classifier $f: \mathbb{R}^m \to \{0,1\}$
+approximates a black-box classifier $f: \mathbb{R}^m \to \{0,1\}$
 around a focal point $x \in \mathbb{R}^m$
@@
 (\cref{fig:lime}).
-The process involves:
+The approximation is performed by the following two steps:
 \begin{enumerate}
-  \item Obtaining a set of perturbed samples $\mathcal{Z}_p$ around $x$
+  \item Generating a set of perturbed samples $\mathcal{Z}_p$ around $x$
         and the set of pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
+        (i) $x$ is converted into a binary vector
+        $x'\in\{0,1\}^{m'}$,
+        (ii) perturbed samples are generated by drawing non-zero elements
+        from $x'$ uniformly at random,
+        and (iii) the perturbed samples are converted back to the original space.
   \item Learning a linear classifier $g$
@@
 }
-
-The algorithm of our method
+The algorithm of R-LIME
 is mainly based on that used in Anchor\cite{ribeiro2018anchors}.
@@
 \subsubsection{Selection of Candidate Rules with Maximum Accuracy}
-Given the set of generated candidate rules $\cands$,
+Given the set of candidate rules $\cands$,
 the algorithm selects the top $B$ candidates with the highest accuracy.
-This is treated as an optimal arm identification problem in the multi-armed bandit framework.
-Each candidate rule $A_i\in\cands$ is considered an arm,
-and their accuracy $\Prec(A_i)$ is treated as the distribution of rewards.
+This problem can be formulated
+as best arm identification in the multi-armed bandit framework.
+Each candidate rule $A_i\in\cands$ is considered as an arm,
+and its accuracy $\Prec(A_i)$ is considered as the distribution of rewards.
 By sampling $z\sim\mathcal{D}(\cdot|A_i)$
@@
   \subsection{Computational Complexity}
+  % \subsubsection{Number of Queries}
   Post-hoc explanation methods including LIME, Anchor, and R-LIME
@@
   $\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$ is the computational complexity of
-  pure exploration problem of finding the $B$ best arms among $B\cdot m$ arms.
+  best arm identification finding the $B$ best arms among $B\cdot m$ arms.
   $\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$ depends on hyperparameters
-  such as threshold $\tau$, confidence level $1-\delta$ and tolerance $\epsilon$.
+  such as beam width $B$, confidence level $1-\delta$ and tolerance $\epsilon$.
+  % \subsubsection{Updating the Linear Classifier}
+  % For Anchor, each trial is composed of sampling a perturbation vector $z$
+  % and getting output $f(z)$.
+  % But for R-LIME, a trial
+  % includes additionally updating the linear classifier $g$ by $z$ and $f(z)$.
+  % If we use support vector machine (SVM) as the linear classifier and
+  % update it by stochastic gradient descent (SGD)~\cite{robbins1951stochastic},
+  % the computational complexity of updating $g$ for each trial is $\mathcal{O}(m^2)$.
 \fi
@@
 for two instances extracted from the test data (\cref{fig:instance}).
-In R-LIME, logistic regression was used as the linear approximation model,
+For R-LIME, logistic regression was used as the linear approximation model,
 and the distribution $\mathcal{D}$ was a multivariate normal distribution
@@
 }
-In R-LIME,
+For R-LIME,
 the problem of selecting the rule with the highest accuracy is formulated
@@
 \fi
-\bibliography{MyRef/ref}
+\bibliography{myref/myref}
 %

### 2024-03-19 paper/paper.tex
ICPR 4th version

@@
     In recent years,
-    complex machine learning models such as deep neural networks
-    have been used in various industrial fields due to their high accuracy.
+    complex machine learning models have been introduced
+    in various industrial fields due to their high accuracy.
     However,
-    its complexity has been a major obstacle to implementation
-    in decision-making situations where transparency of the decision process
-    is required.
+    their complexity has been a major obstacle to implementation
+    in sensitive decision-making situations.
     In order to address this problem,
@@
     which interprets complex classifiers in an interpretable scope.
-    R-LIME locally approximizes a complex decision boundary linearly
+    R-LIME locally approximates a decision boundary of a black-box classifier
     in a rectangular region
     and maximizes the region as long as the accuracy of the linear
-    classifier is higher than a specified threshold.
+    classifier is higher than a given threshold.
     The resulting rectangular region is interpretable for users because it is
     expressed as a conjunction of feature predicates.
-    We demonstrate the effectiveness of the proposed method through qualitative
+    Comparing R-LIME with the existing method,
+    we demonstrate the effectiveness of the proposed method through qualitative
     and quantitative experiments using a real-world dataset.
     Finally, we discuss limitations and future work of the proposed method.
-    % 148 words
+    % 161 words
     \keywords{Interpretable machine learning \and Local surrogate model}
@@
 
-Then, model-agnostic methods are classified into
+Furthermore, model-agnostic methods are categorized into
 \emph{global} and \emph{local} methods based on their locality in input space.
@@
   \subsection{Computational Complexity}
-  % \subsubsection{Number of Queries}
+  % \subsubsection{Sample Complexity}
   Post-hoc explanation methods including LIME, Anchor, and R-LIME
-  need to query the black-box model multiple times
-  to get labels for perturbed samples, which is computationally expensive.
-  The number of queries required for LIME is $|\mathcal{Z}_p|$,
-  where $|\mathcal{Z}_p|$ is the number of perturbed samples selected by the user.
+  need to sample a perturbation vector
+  and get the output of the black-box model multiple times,
+  which is computationally expensive.
+  The number of samples required for LIME is $|\mathcal{Z}_p|$,
+  which is the number of samples designated by the user.
   On the other hand,
-  the number of queries required for Anchor and R-LIME is
-  $\mathcal{O}(B\cdot m^2+m^2\cdot\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]})$,
-  where $B$ is the beam width, $m$ is the number of features, and
-  $\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$ is the computational complexity of
-  best arm identification finding the $B$ best arms among $B\cdot m$ arms.
-  $\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$ depends on hyperparameters
-  such as beam width $B$, confidence level $1-\delta$ and tolerance $\epsilon$.
-  % \subsubsection{Updating the Linear Classifier}
-  % For Anchor, each trial is composed of sampling a perturbation vector $z$
-  % and getting output $f(z)$.
-  % But for R-LIME, a trial
-  % includes additionally updating the linear classifier $g$ by $z$ and $f(z)$.
-  % If we use support vector machine (SVM) as the linear classifier and
-  % update it by stochastic gradient descent (SGD)~\cite{robbins1951stochastic},
-  % the computational complexity of updating $g$ for each trial is $\mathcal{O}(m^2)$.
+  the expected number of samples required for Anchor and R-LIME is bounded by
+  $\mathcal{O}[m\cdot\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}]$,
+  where $\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$
+  is the expected number of samples
+  for best arm identification finding the best $B$ arms from $B\cdot m$ arms.
+  For KL-LUCB algorithm~\cite{kaufmann2013information},
+  the expected number of samples is bounded by
+  % \begin{equation}
+  %   \mathcal{O}\left[H_{\epsilon}\log\frac{H_\epsilon}{\delta}\right],
+  % \end{equation}
+  % where $H_{\epsilon}$ is sample complexity of the problem
+  % \cite{kaufmann2013information}.
+  \begin{equation}
+    \mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}=
+    \mathcal{O}\left[\frac{Bm}{\epsilon^2}\log\frac{Bm}{\epsilon^2\delta}\right].
+  \end{equation}
+
+  % \subsubsection{Complexity of Each Trial}
+  Each trial of KL-LUCB algorithm consists of sampling a perturbation vector $z$,
+  getting output $f(z)$, and updating the linear classifier $g$.
+  If we sample a perturbation vector from a multivariate normal distribution
+  using Cholesky decomposition in advance ($\mathcal{O}(2^m\cdot m^3)$),
+  we can sample $z$ in $\mathcal{O}(m^2)$.
+  If we use random forest as the black-box model,
+  the complexity of getting output is $\mathcal{O}(1)$.
+  If we use logistic regression as the linear classifier and
+  update it by stochastic gradient descent (SGD)~\cite{robbins1951stochastic},
+  the computational complexity of updating $g$ for each trial is
+  $\mathcal{O}(m)$.
+  Then the computational complexity of each trial is $\mathcal{O}(m^2)$.
+
+  % \subsubsection{Total Complexity}
+  Overall, the complexity of R-LIME is bounded by
+  \begin{equation}
+    \mathcal{O}\left[
+      2^m\cdot m^3+\frac{Bm^4}{\epsilon^2}\log\frac{Bm}{\epsilon^2\delta}
+      \right],
+  \end{equation}
+  which is very sensitive to the number of features $m$.
 \fi
@@
   \centering
-  \includegraphics[width=0.53\textwidth]{experiments/exp2/box_plot}
+  \includegraphics[width=0.5\textwidth]{experiments/exp2/box_plot}
   \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
@@
 
-\section{Challenges and Future Perspectives}
+\section{Challenges and Future Work}
  {%
@@
       \centering
-      \includegraphics[width=0.75\textwidth]{visual-rlime3}
+      \includegraphics[width=0.7\textwidth]{visual-rlime3}
       \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
@@
       \centering
-      \includegraphics[width=0.75\textwidth]{visual-rlime-imbalanced}
+      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
       \caption{R-LIME for imbalanced label distribution.
@@
 \section{Conclusion}
-We identified challenges in existing methods for local model-agnostic post-hoc
-explanations of black-box classifiers and proposed R-LIME to address them.
-We represented the rectangular region for local linear approximation as a
-conjunction of feature predicates and proposed an algorithm to
-maximize coverage under the constraint of minimum approximation accuracy.
+We argued that the interpreting the outputs of black-box models is crucial
+for their application in sensitive domains,
+and identified challenges in existing methods for local model-agnostic post-hoc
+explanations of black-box classifiers.
+To address these challenges,
+we proposed R-LIME, a method that locally approximates the decision boundary
+of a black-box classifier linearly and provides a rectangular approximation region,
+which is interpretable for users due to being expressed as a conjunction of feature predicates.
+We proposed an algorithm to
+maximize coverage of the approximation region
+as long as the accuracy of the linear approximation model exceeds a given threshold.
 Comparing the outputs of LIME and R-LIME on the real-world dataset,
 we demonstrated that R-LIME provides a clear application scope of the
-explanation and can be evaluated by users for its reliability and generality.
-However, we discussed the instability of behavior concerning imbalanced label
+explanation, can be evaluated by users for its reliability and generality,
+and achieves higher and less variable local accuracy compared to LIME\@.
+However, we discussed the instability of behavior against imbalanced label
 distributions and raised questions about the theoretical validity of using
-the KL-LUCB algorithm.
+the KL-LUCB algorithm for our problem.
 

### 2024-04-03 paper/paper.tex
ICPR 5th version

@@
 \else
+  % The title of the paper
   \title{%
     R-LIME: Rectangular Constraints and Optimization for Local Interpretable
-    Model-agnostic Explanation Methods}
+    Model-agnostic Explanation Methods
+  }
+
   % Abbreviated title for the running head
@@
     and quantitative experiments using a real-world dataset.
-    Finally, we discuss limitations and future work of the proposed method.
-    % 161 words
+    % 150 words
     \keywords{Interpretable machine learning \and Local surrogate model}
@@
   \def\hhhh{2.8}
-  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,node font=\normalsize\itshape,auto}]
+  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
     \node[nodestyle] (post-hoc) at (0,0){post-hoc};
-    \node[nodestyle] (dependent) at (-\w,-\hh){model-dependent};
+    \node[nodestyle] (dependent) at (-\w,-\hh){%
+      \begin{tabular}{c}
+        model-dependent \\
+        (DTD~\cite{montavon2017explaining}, LRP~\cite{bach2015pixel})
+      \end{tabular}
+    };
     \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
-    \node[nodestyle] (global) at (0,-\hhhh){global};
-    \node[nodestyle] (local) at (\ww,-\hhhh){\textbf{local}};
+    \node[nodestyle] (global) at (0,-\hhhh){%
+      \begin{tabular}{c}
+        global \\
+        (PDP~\cite{friedman2001greedy}, ALE~\cite{apley2020visualizing})
+      \end{tabular}
+    };
+    \node[nodestyle] (local) at (\ww,-\hhhh){%
+      \begin{tabular}{c}
+        \textbf{local} \\
+        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors})
+      \end{tabular}
+    };
     \draw(post-hoc) -- (0,-\h);
@@
 \end{figure}
-In this chapter,
+In this section,
 we overview existing research on post-hoc explanation methods,
@@
 
-First, they are categorized into \emph{model-dependent} and \emph{model-agnostic} methods
+They are broadly divided into
+\emph{model-dependent} and \emph{model-agnostic} methods
 based on their dependence on the model's structure.
@@
 \subsection{Previous Work}
-We specifically focuses on \emph{local} and \emph{model-agnostic} methods.
+We specifically focus on \emph{local} and \emph{model-agnostic} methods.
 In this section,
@@
   \subsection{Computational Complexity}
-  % \subsubsection{Sample Complexity}
   Post-hoc explanation methods including LIME, Anchor, and R-LIME
@@
   For KL-LUCB algorithm~\cite{kaufmann2013information},
-  the expected number of samples is bounded by
-  % \begin{equation}
-  %   \mathcal{O}\left[H_{\epsilon}\log\frac{H_\epsilon}{\delta}\right],
-  % \end{equation}
-  % where $H_{\epsilon}$ is sample complexity of the problem
-  % \cite{kaufmann2013information}.
   \begin{equation}
@@
   \end{equation}
-
-  % \subsubsection{Complexity of Each Trial}
-  Each trial of KL-LUCB algorithm consists of sampling a perturbation vector $z$,
-  getting output $f(z)$, and updating the linear classifier $g$.
-  If we sample a perturbation vector from a multivariate normal distribution
-  using Cholesky decomposition in advance ($\mathcal{O}(2^m\cdot m^3)$),
-  we can sample $z$ in $\mathcal{O}(m^2)$.
-  If we use random forest as the black-box model,
-  the complexity of getting output is $\mathcal{O}(1)$.
-  If we use logistic regression as the linear classifier and
-  update it by stochastic gradient descent (SGD)~\cite{robbins1951stochastic},
-  the computational complexity of updating $g$ for each trial is
-  $\mathcal{O}(m)$.
-  Then the computational complexity of each trial is $\mathcal{O}(m^2)$.
-
-  % \subsubsection{Total Complexity}
-  Overall, the complexity of R-LIME is bounded by
+  Then the total expected number of samples for Anchor and R-LIME is bounded by
   \begin{equation}
-    \mathcal{O}\left[
-      2^m\cdot m^3+\frac{Bm^4}{\epsilon^2}\log\frac{Bm}{\epsilon^2\delta}
-      \right],
+    \mathcal{O}\left[\frac{Bm^2}{\epsilon^2}\log\frac{Bm}{\epsilon^2\delta}\right].
   \end{equation}
-  which is very sensitive to the number of features $m$.
+
+  For each iteration of KL-LUCB algorithm, R-LIME needs to update
+  the linear classifier $g_i$, which is not required in Anchor.
+  But if we use logistic regression as the linear classifier,
+  the computational complexity of updating $g_i$ is $\mathcal{O}(m)$,
+  which is negligible compared to the complexity of sampling a perturbation vector
+  and getting the output of the black-box model.
 \fi
@@
 \begin{equation}
-  {\left(\mathbb{E}_{z\sim\mathcal{D}(z\mid A)}[\mathbbm{1}_{f(z)=1}]-\frac{1}{2}\right)}^2<\mu
+  {%
+    \left(
+    \mathbb{E}_{z\sim\mathcal{D}(z\mid A)}[\mathbbm{1}_{f(z)=1}]-\frac{1}{2}
+    \right)
+  }^2<\mu
 \end{equation}
@@
 with a standard deviation of 0.017.
-While the deviation was relatively small considering confidence level $1-\delta=0.95$,
-we should modify the selection algorithm to consider the varying accuracy.
+By considering the confidence level $1-\delta=0.95$,
+the deviation was relatively small.
+While there are concerns about the theoretical validity of using the KL-LUCB algorithm,
+the results suggest that the deviation is not significant in practice.
 
 \section{Conclusion}
-We argued that the interpreting the outputs of black-box models is crucial
-for their application in sensitive domains,
-and identified challenges in existing methods for local model-agnostic post-hoc
-explanations of black-box classifiers.
+Existing methods for
+local model-agnostic explanations of black-box classifiers have limitations
+that they do not explicitly indicate the application scope of the explanations.
 To address these challenges,
@@
 
-% \subsubsection{Acknowledgements}
-% Please place your acknowledgments at
-% the end of the paper, preceded by an unnumbered run-in heading (i.e.
-% 3rd-level heading).
-
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
 \ifnum\mode=0
@@
 \bibliography{myref/myref}
-%
+
 \end{document}

### 2024-04-08 paper/paper.tex
ICPR 6th version
modify details of paper

@@
     We propose a new method, R-LIME,
-    which interprets complex classifiers in an interpretable scope.
+    which interprets a complex classifier in an interpretable scope.
     R-LIME locally approximates a decision boundary of a black-box classifier
@@
     expressed as a conjunction of feature predicates.
-    Comparing R-LIME with the existing method,
-    we demonstrate the effectiveness of the proposed method through qualitative
-    and quantitative experiments using a real-world dataset.
+    We demonstrate the effectiveness of the proposed method through
+    qualitative and quantitative comparisons with the existing method
+    using a real-world dataset.
     % 150 words
@@
 \section{Introduction}
-Machine learning models, such as deep learning and random forests,
-have been widely employed in various industrial applications
+Machine learning models, such as deep neural networks and random forests,
+have been widely introduced in various industrial fields
 due to their significant improvement in accuracy in recent years.
@@
 the increasing complexity and black-box nature of these models pose challenges,
-particularly in critical decision-making scenarios like healthcare and finance,
-where the opacity of decision process becomes a major obstacle to
-implementation.
-Consequently,
+particularly in critical decision-making scenarios such as healthcare and finance,
+where the opacity of decision process becomes a major obstacle to implementation.
+In order to address this problem,
 there has been extensive research in the field of post-hoc explanations
@@
 into \emph{model-dependent} and \emph{model-agnostic} methods
-based on their dependence on the model's structure.
-Furthermore, model-agnostic methods are classified into
-\emph{global} and \emph{local} methods based on their locality in input space.
+based on their dependence on the model's structure,
+and the latter are further classified into \emph{global} and \emph{local} methods
+based on their locality in input space~\cite{samek2021explaining}.
 \begin{figure}[tbp]
@@
 In this paper,
-we focus on local model-agnostic methods.
-An example of explanations by LIME~\cite{ribeiro2016why} and
-Anchor~\cite{ribeiro2018anchors}
+we focus on \emph{local} and \emph{model-agnostic} methods.
+LIME~\cite{ribeiro2016why} and Anchor~\cite{ribeiro2018anchors}
+are representative local model-agnostic methods.
+An example of explanations by LIME and Anchor
 for a sentiment prediction model is illustrated in \cref{fig:example}.
@@
 to the output.
-The explanation by LIME (\cref{fig:example-lime}) provides suggests that
+The explanation by LIME (\cref{fig:example-lime}) suggests that
 the word ``not'' mainly contributes to the positive prediction,
@@
 which is obviously incorrect.
-Anchor represents a rectangular region
-containing the focal point,
-that maximizes the probability of the black-box classifier outputting
-the same label as the focal point.
+Anchor maximizes the coverage of a rectangular region containing the focal point
+as long as the probability of the black-box classifier outputting
+the same label as the focal point within the region exceeds a given threshold.
 While Anchor provides an effective scope of the explanation,
-the information it includes is less than LIME,
-limiting its utility~\cite{ribeiro2018anchors}.
+users can get less insight from the explanation compared to LIME\@.
 The explanation by Anchor (\cref{fig:example-anchor})
-suggests that changing words other than ``not'' and ``bad''
+suggests that replacing words other than ``not'' and ``bad''
 has little impact on the classifier's output.
@@
 we propose a new method called R-LIME (Ruled LIME),
-which interprets complex classifiers in an interpretable region.
+which provides both the contributions of each feature to the output
+and the effective scope of the explanation.
 R-LIME locally approximates a complex decision boundary linearly
 in a rectangular region and maximizes the region
-as long as the accuracy of the linear classifier is
-higher than a given threshold.
+as long as the accuracy of the linear classifier exceeds a given threshold.
 The rectangular region is interpretable for users because it is
-expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).
+expressed as a conjunction of feature predicates.
 An example of the explanation by R-LIME for a sentiment prediction model
@@
   \centering
-  \def\w{2.2}
-  \def\ww{4.4}
+  \def\w{2.5}
+  \def\ww{5.0}
   \def\h{0.7}
@@
         \textbf{local} \\
-        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors})
+        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors}, \underline{R-LIME})
       \end{tabular}
@@
 explain model's behavior in the vicinity of a specific input.
-While local methods offer explanations more simple and accurate
+While they offer explanations more simple and accurate
 than global methods,
@@
   \caption[Visual comparison of LIME, Anchor and R-LIME]{%
-    Visual comparison of LIME, Anchor and R-LIME (our proposed method).
-    The solid line represents the rectangular region containing the focal
-    point, and the dashed line represents the learned approximation model.
+    Visual comparison of LIME, Anchor and R-LIME (our method).
+    The dashed line represents the learned approximation model,
+    and the solid line represents the rectangular region containing the focal point.
   }
@@
 }\label{sec:anchor}
-Anchor represents a rectangular region containing the focal point $x$,
-expressed as a conjunction of feature predicates (a rule),
-that maximizes the probability of the black-box classifier $f$
-outputting $f(x)$ within the region.
+Anchor maximizes the coverage of a rectangular region
+containing the focal point $x$,
+expressed as a conjunction of feature predicates (a rule)
+as long as the probability of the black-box classifier $f$
+outputting $f(x)$ within the region exceeds a given threshold $\tau$
+(\cref{fig:anchor}).
 It aims to highlight important features
-contributing significantly to the output (\cref{fig:anchor}).
-For a discrete $m$-dimensional input space $\ispace$
-with a trained black-box classifier $f: \ispace \to \{0,1\}$,
-an instance $x \in \ispace$,
+contributing significantly to the output.
+For a discrete $m$-dimensional input space $\ispace$,
+a trained black-box classifier $f: \ispace \to \{0,1\}$,
+an instance $x \in \ispace$
 and a distribution $\mathcal{D}$ over the input space,
 a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
-The predicates $a_i(z)$ evaluate to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
+The predicate $a_i(z)$ evaluates to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
 The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
@@
   [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor_def_prec} \\
-  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)].
+  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)],
 \end{align}
@@
   and getting the output of the black-box model.
+  Overall, the computational complexity of R-LIME is comparable to that of Anchor.
 \fi

### 2024-04-08 experiments/exp2/lime_vs_rlime.py
change submodule name

@@ -2,7 +2,6 @@
 
 import csv
 import multiprocessing
-import sys
 from functools import partial
 
 import numpy as np
@@ -10,14 +9,10 @@ import pandas as pd  # type: ignore
 from lime import lime_tabular  # type: ignore
 from sklearn.ensemble import RandomForestClassifier  # type: ignore
 
-sys.path.append("RLIME")
-import mylime  # type: ignore
-import newlime_base  # type: ignore
-import newlime_tabular
-import newlime_utils
-from newlime_base import Arm
-from newlime_types import IntArray
-from sampler import Sampler
+from rlime import mylime, newlime_base, newlime_tabular, newlime_utils
+from rlime.newlime_base import Arm
+from rlime.newlime_types import IntArray
+from rlime.sampler import Sampler
 
 
 def main() -> None:

### 2024-04-09 experiments/exp2/lime_vs_rlime.py
modify lime_vs_rlime.py to match updating submodule exp2/rlime

@@ -6,21 +6,23 @@ from functools import partial
 
 import numpy as np
 import pandas as pd  # type: ignore
-from lime import lime_tabular  # type: ignore
+from river import preprocessing
 from sklearn.ensemble import RandomForestClassifier  # type: ignore
 
-from rlime import mylime, newlime_base, newlime_tabular, newlime_utils
-from rlime.newlime_base import Arm
-from rlime.newlime_types import IntArray
+from rlime import rlime_lime
+from rlime.arm import Arm
+from rlime.rlime import HyperParam, explain_instance
+from rlime.rlime_types import Dataset, IntArray
 from rlime.sampler import Sampler
+from rlime.utils import get_trg_sample, load_dataset
 
 
 def main() -> None:
     """Main function."""
 
     # Load the dataset.
-    dataset = newlime_utils.load_dataset(
-        "recidivism", "RLIME/datasets/", balance=True
+    dataset = load_dataset(
+        "recidivism", "rlime/examples/datasets/", balance=True
     )
 
     # Learn the black box model.
@@ -63,24 +65,26 @@ def main() -> None:
 
 
 def calc_accuracy(
-    sample: IntArray,
+    samples: IntArray,
     labels: IntArray,
     lime_weights: list[float],
-    lime_scaler,
+    lime_scaler: preprocessing.StandardScaler,
     arm: Arm,
 ) -> tuple[float, float]:
     """Calculate the precision of LIME and R-LIME.
 
     Parameters
     ----------
-    sample: newlime_utils.FloatArray
-        The samples.
-    labels: newlime_utils.IntArray
+    samples : IntArray
+        The samples to evaluate.
+    labels : IntArray
         The labels of the samples.
-    lime_weights: newlime_utils.FloatArray
+    lime_weights : list[float]
         The weights of LIME.
-    surrogate_model: newlime_tabular.SurrogateModel
-        The surrogate model of R-LIME.
+    lime_scaler : preprocessing.StandardScaler
+        The scaler of LIME.
+    arm : Arm
+        The rule of R-LIME.
 
     Returns
     -------
@@ -89,8 +93,8 @@ def calc_accuracy(
     """
 
     # Get predictions of LIME and R-LIME.
-    lime_pred = np.dot(lime_scaler.transform(sample), lime_weights) > 0
-    rlime_pred = arm.surrogate_model.predict_many(pd.DataFrame(sample))
[…]

### 2024-04-09 paper/paper.tex
modify details of paper

@@
 we can select the rule that enables explanation with high accuracy and generality.
-% The characteristics of R-LIME are listed below:
-% \begin{itemize}
-% 	\item The approximation region is optimal and interpretable.
-% 	\item The dataset is not directly accessed, and only the distribution is utilized.
-% 	\item The number of samples is dynamically determined
-% 	      based on the estimated accuracy without the need for predefining it.
-% \end{itemize}
 
@@
 greedy methods tend to converge to local optima, and to address this,
-R-LIME utilizes beam search,
+R-LIME uses beam search,
 which selects multiple candidates at each iteration.
-The pseudo code is shown in \cref{alg:greedy_search}.
+The pseudo-code is shown in \cref{alg:greedy_search}.
 
@@
 selected in the previous iteration.
-The pseudo code is shown in \cref{alg:generate_cands}.
-$T(x)$ is the set of attribute-value pairs (predicates) that are true for $x$,
+The pseudo-code is shown in \cref{alg:generate_cands}.
+$T(x)$ is the set of predicates $\{a_1,\dots,a_m\}$,
+where $a_i(z)$ evaluates to true when $z_i=x_i$ and false otherwise,
 and $T(x)\setminus A$ is the set of predicates in $T(x)$ not included in rule $A$.
@@
 Each candidate rule $A_i\in\cands$ is considered as an arm,
-and its accuracy $\Prec(A_i)$ is considered as the distribution of rewards.
+and reward of arm $a_i$ follows a Bernoulli distribution
+with $P(X=1)=\Prec(A_i)$.
 By sampling $z\sim\mathcal{D}(\cdot|A_i)$
 and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial,
-the algorithm updates $g_i$ using the sampled perturbation vector $z$
-and the pseudo-label $f(z)$ after each trial.
+the algorithm updates $g_i$ using $z$ and $f(z)$ after each trial.
 To efficiently select the rule (arm) with the highest accuracy,
 we employ the KL-LUCB algorithm \cite{kaufmann2013information}.
-The pseudo code is shown in \cref{alg:best_cands}.
+The pseudo-code is shown in \cref{alg:best_cands}.
 For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
@@
 and proceeds to the next iteration.
-The pseudo code is presented in \cref{alg:largest_valid_cand}.
+The pseudo-code is presented in \cref{alg:largest_valid_cand}.
 

### 2024-04-10 paper/paper.tex
ICPR final version

@@
 as long as the accuracy of the linear classifier exceeds a given threshold.
-The rectangular region is interpretable for users because it is
+The region is interpretable for users because it is
 expressed as a conjunction of feature predicates.
 An example of the explanation by R-LIME for a sentiment prediction model
-is illustrated in \cref{fig:example-rlime}.
+is shown in \cref{fig:example-rlime}.
 It is clear that users can apply the insights derived from the explanation
@@
   \def\ww{5.0}
-  \def\h{0.7}
-  \def\hh{1.4}
-  \def\hhh{2.1}
-  \def\hhhh{2.8}
+  \def\h{0.5}
+  \def\hh{1.3}
+  \def\hhh{1.8}
+  \def\hhhh{2.6}
   \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
@@
 
-The experiments utilized the recidivism dataset \cite{schmidt1988predicting}.
-This dataset contains information on 9,549 prisoners released from
+We used the recidivism dataset \cite{schmidt1988predicting} for our experiments.
+The dataset contains information on 9549 prisoners released from
 North Carolina prisons between July 1, 1979, and June 30, 1980.
-The dataset includes 19 items such as race, gender,
-presence of alcohol dependence, number of prior offenses and recidivism.
+The dataset includes 19 items such as race (\emph{Race}), gender (\emph{Gender}),
+presence of alcohol dependence (\emph{Alcohol}),
+number of prior offenses (\emph{Priors}),
+and presence of recidivism (\emph{Recidivism}).
 For this experiment,
 we treated the binary classification problem of predicting
-the presence or absence of recidivism (Recidivism) as the target label.
+the presence of recidivism (\emph{Recidivism}) as the target label.
 We discretized continuous features and removed missing values,
@@
 The dataset, after removing missing values,
-was split into training data (7,639 instances) and test data (955 instances).
+was split into training data (7639 instances) and test data (955 instances).
 A random forest model with 50 trees was trained using the training data.
-Subsequently, LIME and R-LIME explanations were generated
+Then, LIME and R-LIME explanations were generated
 for two instances extracted from the test data (\cref{fig:instance}).
@@
 Accuracy thresholds $\tau$ were set to $\tau=0.70,0.80,0.90$.
-
   {%
@@
 The results of the experiment are shown in \cref{fig:A,fig:B}.
-The values assigned to each attribute name represent the contribution
+The values assigned to each feature name represent the contribution
 (weights of the learned linear classifier)
@@
 normalized such that the absolute sum is 1.
-The figures also display the 5 attributes with the highest absolute contribution.
+The figures display the 5 features with the highest absolute contribution.
 
 Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) provide insights
-that attributes such as having a prior offenses (Priors),
-being served for a long time in prison (MonthsServed),
-and committing a crime against property (Crime against Property)
+that attributes such as having a prior offenses (\emph{Priors}),
+being served for a long time in prison (\emph{MonthsServed}),
+and committing a crime against property (\emph{Crime against Property})
 primarily contribute to the positive prediction
@@
 On the other hand,
-attributes like older age (Age), being married (Married),
-and being of white race (Race) contribute to the negative prediction
+attributes like older age (\emph{Age}), being married (\emph{Married}),
+and being of white race (\emph{Race}) contribute to the negative prediction
 (prediction that the prisoner will not be re-arrested).
@@
 they do not explicitly indicate the application scope of the explanations,
-leaving users unable to determine to which inmates the explanations are applicable.
+leaving users unable to determine to which prisoners the explanations are applicable.
 
 In contrast, R-LIME expresses the application scope of explanations
-as a conjunction of predicates.
+as a conjunction of feature predicates.
 For example, the explanation for instance A
 under $\tau=0.70$ (\cref{fig:A-rlime-70}) indicates that it is applicable
-only to married prisoner (Married$=$Yes).
-Furthermore, the explanations include the accuracy and coverage,
-allowing users to evaluate its reliability.
+only to married prisoner (\emph{Married} $=$\emph{Yes}).
+Furthermore, the explanations provide their accuracy and coverage,
+allowing users to evaluate reliability of the explanations.
 For example, the coverage of the explanation for instance B under $\tau=0.90$
@@
 we randomly sampled 100 instances from the test data of the recidivism dataset
-and generated explanations (with $\tau=0.70,0.80,0.90$) using LIME and R-LIME\@.
+and generated explanations using LIME and R-LIME (with $\tau=0.70,0.80,0.90$).
 We then sampled 10,000 instances within the rectangular region
@@
 R-LIME may generate less useful explanations
-when there is bias in the distribution of black-box model outputs.
-When the distribution of black-box model outputs is significantly biased
-for a given accuracy threshold $\tau$
-(when the ratio of the minority label is less than $1-\tau$),
+when the distribution of black-box classifier outputs is imbalanced.
+When the ratio of the minority label is less than $1-\tau$,
+where $\tau$ is the threshold for the accuracy of the linear classifier,
 the approximation region generated by R-LIME covers the entire input space,
@@
 the problem of selecting the rule with the highest accuracy is formulated
-as the optimal arm identification problem in multi-armed bandit theory,
-solved using the KL-LUCB algorithm \cite{kaufmann2013information}.
+as the best arm identification problem in multi-armed bandit framework,
+and solved using the KL-LUCB algorithm \cite{kaufmann2013information}.
 However, this algorithm assumes that the reward distribution remains constant,
@@
 Therefore, rewards obtained at an early stage
-might influence the estimated value and deviate from the true value.
+might influence the estimated value and
+make it deviate from the true value.
 
@@
 between the estimated accuracy and the true accuracy.
-We generated explanations for 3,200 data instances sampled from the dataset,
+We generated explanations for 3200 data instances sampled from the dataset,
 and compared the estimated accuracy with the true accuracy.
-The true accuracy was calculated based on 1,000 instances sampled
+The true accuracy was calculated based on 1000 instances sampled
 within the approximation region.
@@
 While there are concerns about the theoretical validity of using the KL-LUCB algorithm,
-the results suggest that the deviation is not significant in practice.
+these results suggest that the deviation is not significant in practice.
 
@@
 and achieves higher and less variable local accuracy compared to LIME\@.
-However, we discussed the instability of behavior against imbalanced label
+Finally, we discussed the instability of behavior against imbalanced label
 distributions and raised questions about the theoretical validity of using

### 2024-04-10 experiments/exp2/box_plot.py

@@ -31,7 +31,7 @@ def main() -> None:
         med.set_color("black")
 
     for i, tau_percent in enumerate([70, 80, 90]):
-        plt.text(1.0 + 2.5 * i, 0.3, r"$\tau=$" + f"0.{tau_percent}")
+        plt.text(1.0 + 2.5 * i, 0.33, r"$\tau=$" + f"0.{tau_percent}")
 
     plt.hlines(
         [0.7, 0.8, 0.9],

### 2024-04-10 paper/paper.tex
modify abstract of paper

@@
     and maximizes the region as long as the accuracy of the linear
-    classifier is higher than a given threshold.
+    classifier exceeds a given threshold.
     The resulting rectangular region is interpretable for users because it is
     expressed as a conjunction of feature predicates.
-    We demonstrate the effectiveness of the proposed method through
-    qualitative and quantitative comparisons with the existing method
-    using a real-world dataset.
+    Through qualitative and quantitative comparisons with the existing method
+    on a real-world dataset,
+    we demonstrate that R-LIME provides more reliable and interpretable
+    explanations than existing methods.
     % 150 words

### 2024-04-17 paper/paper.tex
ICPR really final version

@@
     However,
-    their complexity has been a major obstacle to implementation
+    their increasing complexity has been a major obstacle to implementation
     in sensitive decision-making situations.
@@
     which interprets a complex classifier in an interpretable scope.
-    R-LIME locally approximates a decision boundary of a black-box classifier
-    in a rectangular region
-    and maximizes the region as long as the accuracy of the linear
-    classifier exceeds a given threshold.
+    R-LIME locally and linearly approximates a complex decision boundary
+    of a black-box classifier in a rectangular region
+    and maximizes the region as long as the approximation accuracy
+    exceeds a given threshold.
     The resulting rectangular region is interpretable for users because it is
@@
     explanations than existing methods.
-    % 150 words
+    % 153 words
     \keywords{Interpretable machine learning \and Local surrogate model}
@@
 \section{Introduction}
-Machine learning models, such as deep neural networks and random forests,
+In recent years,
+complex machine learning models, such as deep neural networks and random forests,
 have been widely introduced in various industrial fields
-due to their significant improvement in accuracy in recent years.
+due to their significant improvement in accuracy.
 However,
-the increasing complexity and black-box nature of these models pose challenges,
+their increasing complexity and black-box nature pose challenges,
 particularly in critical decision-making scenarios such as healthcare and finance,
@@
     Example of explanations by LIME~\cite{ribeiro2016why},
-    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method).
+    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method)
     for a sentiment prediction model.
@@
 for a sentiment prediction model is illustrated in \cref{fig:example}.
-LIME approximates the complex decision boundary
-linearly around the given focal point,
+LIME linearly approximates the complex decision boundary
+around the given focal point,
 then provides the weights of the linear model as the contribution of each feature
@@
 the word ``not'' mainly contributes to the positive prediction,
-but does not explicitly indicate the effective scope.
+but does not explicitly indicate its effective scope.
 Without the scope,
@@
 For this example,
-user may apply the derived insights
+users may apply the derived insights
 to the sentence ``This book is not good.''
@@
 While Anchor provides an effective scope of the explanation,
-users can get less insight from the explanation compared to LIME\@.
+users can get less insight compared to LIME\@.
 The explanation by Anchor (\cref{fig:example-anchor})
@@
 
-To address this limitation of LIME,
+To address these limitations,
 we propose a new method called R-LIME (Ruled LIME),
@@
 and the effective scope of the explanation.
-R-LIME locally approximates a complex decision boundary linearly
+R-LIME linearly approximates a complex decision boundary
 in a rectangular region and maximizes the region
@@
 Model-dependent methods,
-such as Deep Taylor Decomposition (DTD)~\cite{montavon2017explaining}
-and Layer-wise Relevance Propagation (LRP)~\cite{bach2015pixel},
+such as deep Taylor decomposition (DTD)~\cite{montavon2017explaining}
+and layer-wise relevance propagation (LRP)~\cite{bach2015pixel},
 most of which focus on neural networks and
@@
 Global methods,
-such as Partial Dependence Plots (PDP)~\cite{friedman2001greedy}
-and Accumulated Local Effects (ALE)~\cite{apley2020visualizing},
+such as partial dependence plots (PDP)~\cite{friedman2001greedy}
+and accumulated local effects (ALE)~\cite{apley2020visualizing},
 aim to explain the model's behavior across the entire input space.
-% seeking explanations valid for any input.
 However, providing global explanations becomes challenging
@@
 In contrast, local methods,
-such as Local Interpretable Model-agnostic Explanations (LIME)
+such as local interpretable model-agnostic explanations (LIME)
 \cite{ribeiro2016why}
 and Anchor~\cite{ribeiro2018anchors},
-% SHAP~\cite{lundberg2017unified},
-% EXPLAN~\cite{rasouli2020explan},
-% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
-% and BELLA (Black box model Explanations by Local Linear Approximations)
-% \cite{radulovic2023bella},
 explain model's behavior in the vicinity of a specific input.
@@
     Visual comparison of LIME, Anchor and R-LIME (our method).
-    The dashed line represents the learned approximation model,
+    The dashed line represents the local linear approximation model,
     and the solid line represents the rectangular region containing the focal point.
@@
 (\cref{fig:lime}).
-The approximation is performed by the following two steps:
+The approximation is performed by the following steps:
 \begin{enumerate}
@@
         where $\pi_x(z)$ is a weight function designed to be larger for samples
-        closer to $x$, typically implemented using an exponential kernel.
+        closer to $x$, typically defined using an exponential kernel.
 \end{enumerate}
@@
 by showing the contribution of each feature to the output $f(x)$.
-However, due to not explicitly indicating the perturbation region,
-users cannot assess the effective scope of the explanation
+However, it does not explicitly indicate the region for generating perturbed samples,
+making it difficult for users to assess the effective scope of the explanation
 \cite{ribeiro2018anchors}.
@@
 The predicate $a_i(z)$ evaluates to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
+The reliability of the explanation is defined as the ``accuracy'' of the rule,
+and the generality of the explanation is defined as the ``coverage'' of the rule.
 The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
@@
 and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
-Anchor maximizes coverage under the constraint that
+Anchor maximizes coverage as long as
 the accuracy of the rule $A$ exceeds a given threshold $\tau$.
@@
 We propose R-LIME,
-a method that aims to address the limitations of LIME~\cite{ribeiro2016why},
+a method that aims to address the limitations of LIME~\cite{ribeiro2016why}
 and Anchor~\cite{ribeiro2018anchors}.
 Our method locally approximates the given black-box classifier $f$
-around the focal point $x$ by a linear classifier $g$ similar to LIME and BELLA,
-but samples perturbation from a rectangular region similar to Anchor
+around the focal point $x$ by a linear classifier $g$ similar to LIME,
+but generates the perturbed samples
+from a rectangular region similar to Anchor
 so that the generality of approximation is explicitly provided
 (\cref{fig:rlime}).
-The accuracy of $g$ is defined as the ``accuracy'' of the rule,
-and the generality of explanations is defined as the ``coverage'' of the rule.
 
@@
 within $A$ exceeds a given threshold $\tau$.
-The proposed method, on the other hand, learns an linear classifier $g$
+R-LIME, on the other hand, learns a linear classifier $g$
 within the rectangular region $A$ and maximizes the coverage of $A$
 under lower constraints on the accuracy of $g$.
-We modify the Anchor's definition of accuracy in \cref{eq:anchor_def_prec}
+We modify Anchor's definition of accuracy in \cref{eq:anchor_def_prec}
 as follows:
@@
   \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
-  [\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
+  [\mathbbm{1}_{f(z)=g(z)}], \label{eq:def_prec}
 \end{equation}
-where $G$ is the set of possible linear classifiers.
+where $G$ is a hypothesis space of possible linear classifiers.
 By solving the optimization problem in \cref{eq:main_problem}
-under the modified accuracy definition in \cref{eq:def_prec},
+under the modified definition of accuracy in \cref{eq:def_prec},
 we can select the rule that enables explanation with high accuracy and generality.
@@
       and predicates are added to $A$, reducing coverage.
-      The process continues until $\Prec(A)\ge\tau$,
+      The process continues until $\Prec(A)\ge\tau$ is satisfied,
       at which point the rule with the maximum coverage is output.
@@
 greedy search are often used.
-However,
-greedy methods tend to converge to local optima, and to address this,
-R-LIME uses beam search,
-which selects multiple candidates at each iteration.
+But greedy methods tend to converge to local optima,
+so we use beam search, which selects multiple candidates at each iteration.
 The pseudo-code is shown in \cref{alg:greedy_search}.
 
-\subsubsection{Generation of New Candidate Rules}
+\subsubsection{Generating New Candidate Rules}
 To generate new candidate rules,
@@
 $T(x)$ is the set of predicates $\{a_1,\dots,a_m\}$,
-where $a_i(z)$ evaluates to true when $z_i=x_i$ and false otherwise,
-and $T(x)\setminus A$ is the set of predicates in $T(x)$ not included in rule $A$.
-
-\subsubsection{Selection of Candidate Rules with Maximum Accuracy}
+where $a_i(z)$ evaluates to true when $z_i=x_i$ and false otherwise.
+$T(x)\setminus A$ is the set of predicates in $T(x)$ not included in rule $A$.
+
+\subsubsection{Searching Rules with Highest Accuracy}
 Given the set of candidate rules $\cands$,
-the algorithm selects the top $B$ candidates with the highest accuracy.
+the algorithm selects the $B$ candidate rules with the highest accuracy.
 This problem can be formulated
@@
 the algorithm updates $g_i$ using $z$ and $f(z)$ after each trial.
-To efficiently select the rule (arm) with the highest accuracy,
+To efficiently search the rule (arm) with the highest accuracy,
 we employ the KL-LUCB algorithm \cite{kaufmann2013information}.
@@
 while our method updates the classifier $g_i$ with each sampling,
-which may not satisfy this assumption.
+which may not satisfy the assumption.
 This issue is discussed further in \cref{sec:reward}.
 
-\subsubsection{Selection of the Rule with Maximum Coverage Meeting the Constraint}
-To satisfy the constraint imposed by \cref{eq:const_prec}, rule $A$ needs to fulfill the lower bound constraint:
+\subsubsection{Searching a Rule with Highest Coverage under Constraint}
+To satisfy the constraint imposed by \cref{eq:const_prec},
+a rule $A$ needs to meet the following condition:
 \begin{equation}
-  \Prec_{l}(A,\delta)>\tau
-  \label{eq:stop_condition}
+  \Prec_{l}(A,\delta)>\tau,\label{eq:stop_condition}
 \end{equation}
@@
 the $100(1-\delta)$\% confidence interval for $\Prec(A)$.
-If the received set of candidate rules, $\mathcal{A}$,
-includes a rule satisfying \cref{eq:stop_condition},
+If the set of candidate rules $\mathcal{A}$
+includes rules satisfying \cref{eq:stop_condition},
 the one with the maximum coverage among them is selected,
-and the iteration is terminated.
+then the iteration is terminated.
 If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop_condition},
@@
   the linear classifier $g_i$, which is not required in Anchor.
-  But if we use logistic regression as the linear classifier,
-  the computational complexity of updating $g_i$ is $\mathcal{O}(m)$,
-  which is negligible compared to the complexity of sampling a perturbation vector
-  and getting the output of the black-box model.
+  If we use logistic regression as the linear classifier
+  and update it by stochastic gradient descent (SGD) \cite{robbins1951stochastic},
+  the computational complexity of updating $g_i$ is $\mathcal{O}(m)$.
+  It is negligible compared to the complexity of generating a perturbed sample,
+  which is $\mathcal{O}(m^2)$ if we get a sample
+  from a multivariate normal distribution using Cholesky decomposition in advance.
   Overall, the computational complexity of R-LIME is comparable to that of Anchor.
@@
 To verify the effectiveness of the proposed method,
-We compare LIME and R-LIME using a real-world dataset.
+we compared LIME and R-LIME using a real-world dataset.
 
@@
 We used the recidivism dataset \cite{schmidt1988predicting} for our experiments.
-The dataset contains information on 9549 prisoners released from
+The dataset contains personal information on 9549 prisoners released from
 North Carolina prisons between July 1, 1979, and June 30, 1980.
@@
 resulting in 15 features.
-This problem setting can be considered as a case
-where a machine learning model is introduced to decide parole for prisoners.
-Since such decisions can have a significant impact on a person's life,
-it is crucial for users to interpret the outputs of black-box models appropriately.
-
-The dataset, after removing missing values,
-was split into training data (7639 instances) and test data (955 instances).
-A random forest model with 50 trees was trained using the training data.
+
+We splitted the dataset into training data (7639 instances) and test data (955 instances),
+and trained a random forest model with 50 trees as the black-box classifier
+using the training data.
 Then, LIME and R-LIME explanations were generated
 for two instances extracted from the test data (\cref{fig:instance}).
-For R-LIME, logistic regression was used as the linear approximation model,
-and the distribution $\mathcal{D}$ was a multivariate normal distribution
-estimated from the training data.
+For R-LIME, we used logistic regression as the linear approximation model,
+and a multivariate normal distribution estimated from the training data
+as the distribution $\mathcal{D}$.
 The beam width was set to $B=10$,
@@
 and the tolerance of the KL-LUCB algorithm to $\epsilon=0.05$.
-Accuracy thresholds $\tau$ were set to $\tau=0.70,0.80,0.90$.
+The accuracy threshold $\tau$ was set to $\tau=0.70,0.80,0.90$.
+
+This problem setting can be considered as a case
+where a complex machine learning model is introduced to decide parole for prisoners.
+Since such decisions can have a significant impact on a person's life,
+it is crucial for users to interpret the outputs of black-box models appropriately.
   {%
@@
         \caption[Two instances sampled from recidivism dataset]{%
-          Two instances sampled from recidivism dataset.
+          Two instances sampled from training data of recidivism dataset.
+          Each number in parentheses represents the integer value assigned
+          to the corresponding categorical value.
         }\label{fig:instance}
@@
 The values assigned to each feature name represent the contribution
-(weights of the learned linear classifier)
+(weight of the linear classifier)
 to the output of the black-box classifier,
@@
 Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) provide insights
-that attributes such as having a prior offenses (\emph{Priors}),
-being served for a long time in prison (\emph{MonthsServed}),
+that having a prior offenses (\emph{Priors}),
+being served for a long time in prison (\emph{Months-Served}),
 and committing a crime against property (\emph{Crime against Property})
@@
 On the other hand,
-attributes like older age (\emph{Age}), being married (\emph{Married}),
+being elderly (\emph{Age}), being married (\emph{Married}),
 and being of white race (\emph{Race}) contribute to the negative prediction
@@
 only to married prisoner (\emph{Married} $=$\emph{Yes}).
-Furthermore, the explanations provide their accuracy and coverage,
-allowing users to evaluate reliability of the explanations.
+R-LIME explanations also provide their accuracy and coverage,
+allowing users to evaluate reliability and generality of the explanations.
 For example, the coverage of the explanation for instance B under $\tau=0.90$
@@
 making it challenging to obtain a high-accuracy linear approximation.
-This allows users to discern that the application scope of this explanation is
-very narrow, limiting its utility.
+This information allows users to discern that
+the application scope of this explanation is very narrow, limiting its utility.
 
@@
 between LIME and R-LIME\@.
-Using the same settings as in \cref{sec:exp_setting},
+Under the same settings as in \cref{sec:exp_setting},
 we randomly sampled 100 instances from the test data of the recidivism dataset
@@
 The results are presented in \cref{fig:box_plot},
-showing the distribution of the accuracy of the linear approximation models
+showing the distribution of the local accuracy of the linear classifiers
 learned by LIME and R-LIME\@.
@@
 differ significantly,
-and R-LIME learns a high-accuracy linear classifier adapted to the rectangular region.
+and R-LIME learns a high-accuracy linear classifier
+adapted to the optimized rectangular region.
 Additionally, as $\tau$ increases,
@@
 when the distribution of black-box classifier outputs is imbalanced.
-When the ratio of the minority label is less than $1-\tau$,
-where $\tau$ is the threshold for the accuracy of the linear classifier,
+When the ratio of outputting the minority label is less than $1-\tau$,
+where $\tau$ is the accuracy threshold,
 the approximation region generated by R-LIME covers the entire input space,
@@
     \caption[Deviation between the estimated accuracy and the true accuracy]{%
-      Deviation between the estimated accuracy and the true accuracy.
-      Deviation was relatively small considering confidence level $1-\delta=0.95$.
+      Deviation between the estimated accuracy and the true accuracy
+      of the linear classifier learned by R-LIME.
+      The deviation $0.012\pm0.017$ was relatively small
+      considering the confidence level $1-\delta=0.95$.
     }\label{tab:reward}
@@
 While there are concerns about the theoretical validity of using the KL-LUCB algorithm,
-these results suggest that the deviation is not significant in practice.
+our results suggest that the deviation is not significant in practice.
 
@@
 Existing methods for
-local model-agnostic explanations of black-box classifiers have limitations
-that they do not explicitly indicate the application scope of the explanations.
+local model-agnostic explanations of black-box classifiers,
+such as LIME and Anchor,
+have limitations that they cannot achieve interpretability of
+both the explanation and its application scope.
 To address these challenges,
-we proposed R-LIME, a method that locally approximates the decision boundary
-of a black-box classifier linearly and provides a rectangular approximation region,
+we proposed R-LIME,
+a method that locally and linearly approximates the decision boundary
+of a black-box classifier and provides a rectangular approximation region,
 which is interpretable for users due to being expressed as a conjunction of feature predicates.

### 2024-06-25 paper.tex
build: organize directory structure and refine environment

@@
 
+\def\mode{1} % 0: Graduation thesis, 1: ICPR paper
+
+\ifnum\mode=0
+  \documentclass[11pt]{article}
+  \usepackage{luatexja}
+  \usepackage{src/style/prmlthesis}
+  \usepackage[a4paper]{geometry}
+\else
   \documentclass[runningheads]{llncs}
+\fi
 
@@
 % set the path for figures
-\graphicspath{{./data/}{./python/data/}}
+\graphicspath{{./src/}{../python/data/}{src/experiments/}}
 
@@
 % settings for cleveref
+\crefname{table}{Table}{Tables}
+\crefname{algorithm}{Algorithm}{Algorithms}
+\ifnum\mode=0
+  \crefname{figure}{Figure}{Figures}
+\else
   \crefname{figure}{Fig.}{Figs.}
-\crefname{table}{Table.}{Tables.}
+\fi
 
 % import the TeX file containing macro definitions
-\input{macro}
+\input{src/tex/macro}
 
@@
 
-% Authentic title
+\ifnum\mode=0
+  \title{%
+    R-LIME: LIME法における矩形制約と最適化
+  }
+  \etitle{%
+    R-LIME: Rectangular Constraints and Optimization for Local Interpretable
+    Model-agnostic Explanation Methods
+  }
+  \author{大原 玄嗣 (Genji Ohara)}
+  \institute{%
+    北海道大学 工学部 \\
+    情報エレクトロニクス学科 \\
+    情報理工学コース \\
+    情報認識学研究室
+  }
+  \date{2024年3月}
+  % \institute{%
+  %   Laboratory for Pattern Recognition and Machine Learning,\\
+  %   Division of Computer Science and Information Technology,\\
+  %   Department of Electronics and Information Engineering,\\
+  %   School of Engineering, Hokkaido University
+  % }
+\else
+  % The title of the paper
   \title{%
     R-LIME: Rectangular Constraints and Optimization for Local Interpretable
-  Model-agnostic Explanation Methods}
+    Model-agnostic Explanation Methods
+  }
 
@@
   % Author names and ORCID IDs
-\author{Genji Ohara\inst{1}\orcidID{0009-0000-5854-2820} \and
-  Keigo Kimura\inst{1}\orcidID{0000-0002-3614-6568} \and
-  Mineichi Kudo\inst{1}\orcidID{0000-0003-1013-3870}
+  \author{Genji Ohara\orcidID{0009-0000-5854-2820} \and
+    Keigo Kimura\orcidID{0000-0002-3614-6568} \and
+    Mineichi Kudo\orcidID{0000-0003-1013-3870}
   }
@@
     \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}
+\fi
 
@@
 
+\ifnum\mode=0
+  \pagestyle{plain}
+  \pagenumbering{roman}
+  \tableofcontents
+  \newpage
+  \listoffigures\listoftables\clearpage
+  \AddToHook{cmd/section/before}{\clearpage}
+  \pagestyle{plain}
+  \pagenumbering{arabic}
+\else
   % The abstract should briefly summarize the contents of the paper in
@@
   \begin{abstract}
-  In recent years, complex machine learning models such as deep neural networks
-  have been used in various industrial fields due to their high accuracy.
-  However, its complexity has been a major obstacle to implementation
-  in decision-making situations where transparency of the decision process is required.
+    In recent years,
+    complex machine learning models have been introduced
+    in various industrial fields due to their high accuracy.
+    However,
+    their increasing complexity has been a major obstacle to implementation
+    in sensitive decision-making situations.
     In order to address this problem,
@@
     We propose a new method, R-LIME,
-  which interprets complex classifiers in an interpretable scope.
-  R-LIME locally approximizes a complex decision boundary linearly
-  in a rectangular region
-  and maximizes the region as long as the accuracy of the linear
-  classifier is higher than a specified threshold.
+    which interprets a complex classifier in an interpretable scope.
+    R-LIME locally and linearly approximates a complex decision boundary
+    of a black-box classifier in a rectangular region
+    and maximizes the region as long as the approximation accuracy
+    exceeds a given threshold.
     The resulting rectangular region is interpretable for users because it is
     expressed as a conjunction of feature predicates.
-  We demonstrate the effectiveness of the proposed method through qualitative
-  and quantitative experiments using a real-world dataset.
-  Finally, we discuss limitations and future work of the proposed method.
-  % 148 words
+    Through qualitative and quantitative comparisons with the existing method
+    on a real-world dataset,
+    we demonstrate that R-LIME provides more reliable and interpretable
+    explanations than existing methods.
+    % 153 words
     \keywords{Interpretable machine learning \and Local surrogate model}
   \end{abstract}
+\fi
 
 \section{Introduction}
-Machine learning models, such as deep learning and random forests,
-have been widely employed in various industrial applications
-due to their significant improvement in accuracy in recent years.
+In recent years,
+complex machine learning models, such as deep neural networks and random forests,
+have been widely introduced in various industrial fields
+due to their significant improvement in accuracy.
 However,
-the increasing complexity and black-box nature of these models pose challenges,
-particularly in critical decision-making scenarios like healthcare and finance,
-where the opacity of decision rationale becomes a major obstacle to
-implementation.
-Consequently,
-there has been extensive research in the field of post hoc explanations
-for machine learning models \cite{%
-  ribeiro2016why,ribeiro2018anchors,radulovic2023bella,guidotti2018local}.
-
-Existing methods on post hoc explanations categorize into
-\emph{model-dependent} and \emph{model-agnostic} methods,
-based on their dependence on the model's structure.
-Model-dependent methods primarily focus on deep neural networks and
-explain the models' behavior using their parameters.
-While they allow a direct approach to the model,
-applying the same method to models with different structures is often challenging.
-On the other hand,
-model-agnostic methods do not rely on the models' parameters and utilize only their output.
-Although they are applicable to any model, available information is limited.
-Model-agnostic methods further classify into
-\emph{global} and \emph{local} methods based on their locality in input space.
-Global methods aim to explain the model's behavior across the entire input space,
-seeking explanations valid for any input.
-However, providing global explanations becomes challenging as the model's complexity increases.
-Local methods, in contrast, explain the model's output for a specific input
-(focal point) in the vicinity of that input.
-While local methods offer more simple and accurate explanations than global methods,
-the scope of the explanation is limited to the vicinity of the focus point.
-
-This paper specifically focuses on \emph{local} \emph{model-agnostic} methods.
-For instance, LIME (Local Interpretable Model-agnostic Explanations)
-\cite{ribeiro2016why} approximates the complex model's decision boundary
-locally using a simpler model around the given focal point.
-Although LIME enables users to interpret the local behavior of complex models,
-it does not explicitly provide the effective scope of the explanation
-\cite{ribeiro2018anchors}.
-This limitation can lead users to overgeneralize the knowledge derived from the explanation.
-Without a clear indication of the scope of the explanation,
-users might mistakenly apply the derived knowledge to instances outside this scope,
-potentially leading to a misunderstanding of the black-box model's behavior.
-
-To address this limitation of LIME,
-we propose a new method called R-LIME (Ruled LIME),
-which interprets complex classifiers in an interpretable region.
-R-LIME locally approximates a complex decision boundary linearly
-in a rectangular region and maximizes the region as long as the accuracy of the linear
-classifier is higher than a specified threshold.
-The resulting rectangular region is interpretable for users because it is
-expressed as a conjunction of feature predicates.
-
-\section{Related Work}
-\begin{figure}[t]
+their increasing complexity and black-box nature pose challenges,
+particularly in critical decision-making scenarios such as healthcare and finance,
+where the opacity of decision process becomes a major obstacle to implementation.
+In order to address this problem,
+there has been extensive research in the field of post-hoc explanations
+for machine learning models~\cite{%
+  guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.
+Existing post-hoc explanation methods are categorized
+into \emph{model-dependent} and \emph{model-agnostic} methods
+based on their dependence on the model's structure,
+and the latter are further classified into \emph{global} and \emph{local} methods
+based on their locality in input space~\cite{samek2021explaining}.
+\begin{figure}[tbp]
+  \def\scale{0.38}
   \centering
-  \vspace{0.5cm}
   \begin{subfigure}[t]{0.55\textwidth}
     \centering
-    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_a.png}
-    \caption{Instances around the focal point.}\label{fig:lime_vs_anchor_exp_a}
+    \includegraphics[scale=\scale]{example-instance}
+    \caption{Focal point.}\label{fig:example-instance}
     \vspace{0.5cm}
@@
   \begin{subfigure}[t]{0.45\textwidth}
+    \begin{subfigure}[t]{\textwidth}
       \centering
-    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_b.png}
+      \includegraphics[scale=\scale]{example-lime}
       \caption{%
-      Explanations by LIME\@.
-      They provide contributions of each feature to the output,
-      but do not explicitly indicate its scope.
-    }\label{fig:lime_vs_anchor_exp_b}
-    \vspace{0.5cm}
+        Explanation by LIME\@.
+        It provides contributions of each feature to the output,
+        but does not explicitly indicate its scope.
+      }\label{fig:example-lime}
+      \vspace{0.4cm}
     \end{subfigure}
-  \begin{subfigure}[t]{0.55\textwidth}
+    \begin{subfigure}[t]{\textwidth}
       \centering
-    \includegraphics[width=\textwidth]{lime_vs_anchor_exp_c.png}
+      \includegraphics[scale=\scale]{example-anchor}
       \caption{%
-      Explanations by Anchor.
-      They provide the effective scope of the explanation,
-      but do not provide details about the influence of each feature.
-    }\label{fig:lime_vs_anchor_exp_c}
+        Explanation by Anchor.
+        It provides the effective scope of the explanation,
+        but does not show the influence of each feature.
+      }\label{fig:example-anchor}
     \end{subfigure}
+  \end{subfigure}
+  \hspace{0.3cm}
+  \begin{subfigure}[t]{0.45\textwidth}
+    \centering
+    \ifnum\mode=0
+      \vspace{-1.79cm}
+    \else
+      \vspace{-2.24cm}
+    \fi
+    \includegraphics[scale=\scale]{example-rlime}
     \caption{%
-    Explanations by LIME and Anchor
-    for an LSTM sentiment prediction model \cite{ribeiro2018anchors}.
-  }\label{fig:lime_vs_anchor_exp}
+      Explanation by R-LIME\@.
+      It provides both contributions of each feature and
+      its effective scope.
+    }\label{fig:example-rlime}
+  \end{subfigure}
+  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
+    Example of explanations by LIME~\cite{ribeiro2016why},
+    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method)
+    for a sentiment prediction model.
+  }\label{fig:example}
 \end{figure}
-In this chapter,
-we provide an overview of existing research on local model-agnostic explanations,
+
+In this paper,
+we focus on \emph{local} and \emph{model-agnostic} methods.
+LIME~\cite{ribeiro2016why} and Anchor~\cite{ribeiro2018anchors}
+are representative local model-agnostic methods.
+An example of explanations by LIME and Anchor
+for a sentiment prediction model is illustrated in \cref{fig:example}.
+LIME linearly approximates the complex decision boundary
+around the given focal point,
+then provides the weights of the linear model as the contribution of each feature
+to the output.
+The explanation by LIME (\cref{fig:example-lime}) suggests that
+the word ``not'' mainly contributes to the positive prediction,
+but does not explicitly indicate its effective scope.
+Without the scope,
+users might mistakenly apply the knowledge derived from the explanation
+to other instances far from the focal point,
+potentially leading to misunderstanding of the black-box model's behavior
+\cite{ribeiro2018anchors}.
+For this example,
+users may apply the derived insights
+to the sentence ``This book is not good.''
+and mistakenly conclude that the word ``not''
+mainly contributes to the positive prediction for this sentence as well,
+which is obviously incorrect.
+Anchor maximizes the coverage of a rectangular region containing the focal point
+as long as the probability of the black-box classifier outputting
+the same label as the focal point within the region exceeds a given threshold.
+While Anchor provides an effective scope of the explanation,
+users can get less insight compared to LIME\@.
+The explanation by Anchor (\cref{fig:example-anchor})
+suggests that replacing words other than ``not'' and ``bad''
+has little impact on the classifier's output.
+While it clearly cannot be applied to the sentence ``This book is not good''
+because of not including the word ``bad'',
+the explanation does not provide details about the influence of each word,
+resulting in less user insight into the model's behavior compared to LIME.
+
+To address these limitations,
+we propose a new method called R-LIME (Ruled LIME),
+which provides both the contributions of each feature to the output
+and the effective scope of the explanation.
+R-LIME linearly approximates a complex decision boundary
+in a rectangular region and maximizes the region
+as long as the accuracy of the linear classifier exceeds a given threshold.
+The region is interpretable for users because it is
+expressed as a conjunction of feature predicates.
+An example of the explanation by R-LIME for a sentiment prediction model
+is shown in \cref{fig:example-rlime}.
+It is clear that users can apply the insights derived from the explanation
+only to the sentences containing the word ``not''.
+
+\section{Related Work}
+\begin{figure}[tbp]
+  \centering
+  \def\w{2.5}
+  \def\ww{5.0}
+  \def\h{0.5}
+  \def\hh{1.3}
+  \def\hhh{1.8}
+  \def\hhhh{2.6}
+  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
+    \node[nodestyle] (post-hoc) at (0,0){post-hoc};
+    \node[nodestyle] (dependent) at (-\w,-\hh){%
+      \begin{tabular}{c}
+        model-dependent \\
+        (DTD~\cite{montavon2017explaining}, LRP~\cite{bach2015pixel})
+      \end{tabular}
+    };
+    \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
+    \node[nodestyle] (global) at (0,-\hhhh){%
+      \begin{tabular}{c}
+        global \\
+        (PDP~\cite{friedman2001greedy}, ALE~\cite{apley2020visualizing})
+      \end{tabular}
+    };
+    \node[nodestyle] (local) at (\ww,-\hhhh){%
+      \begin{tabular}{c}
+        \textbf{local} \\
+        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors}, \underline{R-LIME})
+      \end{tabular}
+    };
+    \draw(post-hoc) -- (0,-\h);
+    \draw(dependent) -- (-\w,-\h) -- (\w,-\h) -- (agnostic);
+    \draw(agnostic) -- (\w,-\hhh);
+    \draw(global) -- (0,-\hhh)  -- (\ww,-\hhh) -- (local);
+  \end{tikzpicture}
+  \caption{%
+    Categorization of post-hoc explanation methods.
+    We focus on \emph{model-agnostic} and \emph{local} methods,
+    which explain model's local behavior using only its output.
+  }\label{fig:post-hoc}
+\end{figure}
+In this section,
+we overview existing research on post-hoc explanation methods,
+which explain the behavior of black-box models already trained.
+As shown in \cref{fig:post-hoc},
+post-hoc methods are classified into several categories.
+
+They are broadly divided into
+\emph{model-dependent} and \emph{model-agnostic} methods
+based on their dependence on the model's structure.
+Model-dependent methods,
+such as deep Taylor decomposition (DTD)~\cite{montavon2017explaining}
+and layer-wise relevance propagation (LRP)~\cite{bach2015pixel},
+most of which focus on neural networks and
+explain the model's behavior using its parameters~\cite{samek2021explaining}.
+While these methods provide detailed explanations
+(e.g., layer-wise explanations for neural networks),
+it is often challenging
+to apply the same method to models with different structures.
+On the other hand,
+model-agnostic methods use only the output of the model.
+Although they are applicable to any model,
+they cannot explain the reasoning process inside the model.
+
+Furthermore, model-agnostic methods are categorized into
+\emph{global} and \emph{local} methods based on their locality in input space.
+Global methods,
+such as partial dependence plots (PDP)~\cite{friedman2001greedy}
+and accumulated local effects (ALE)~\cite{apley2020visualizing},
+aim to explain the model's behavior across the entire input space.
+However, providing global explanations becomes challenging
+as the model's complexity increases.
+In contrast, local methods,
+such as local interpretable model-agnostic explanations (LIME)
+\cite{ribeiro2016why}
+and Anchor~\cite{ribeiro2018anchors},
+explain model's behavior in the vicinity of a specific input.
+While they offer explanations more simple and accurate
+than global methods,
+the scope of the explanation is limited locally.
+
+\section{Proposed Method}
+\begin{figure}[tbp]
+  \centering
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{visual-lime}
+    \caption{%
+      LIME: Locally approximates the decision boundary around the focal point.
+    }\label{fig:lime}
+  \end{subfigure}%
+  \hspace{0.03\textwidth}
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{visual-anchor}
+    \caption{%
+      Anchor: Maximizes coverage of a rectangular region
+      containing the focal point under accuracy constraints.
+    }\label{fig:anchor}
+  \end{subfigure}
+  \hspace{0.03\textwidth}
+  \begin{subfigure}[t]{0.3\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{visual-rlime3}
+    \caption{%
+      R-LIME:
+      Maximizes coverage of a rectangular region
+      under lower constraints on the accuracy of the linear classifier.
+    }\label{fig:rlime}
+  \end{subfigure}
+  \caption[Visual comparison of LIME, Anchor and R-LIME]{%
+    Visual comparison of LIME, Anchor and R-LIME (our method).
+    The dashed line represents the local linear approximation model,
+    and the solid line represents the rectangular region containing the focal point.
+  }
+\end{figure}
+
+\subsection{Previous Work}
+We specifically focus on \emph{local} and \emph{model-agnostic} methods.
+In this section,
+we briefly review existing research on local model-agnostic explanations,
 particularly focusing on studies closely related to our proposed method.
 
-\subsection{LIME (Local Interpretable Model-agnostic Explanations) \cite{ribeiro2016why}}
+\subsubsection[LIME]{%
+  LIME (Local Interpretable Model-agnostic Explanations)
+  \cite{ribeiro2016why}
+}
 LIME locally
-approximates a trained black-box classifier $f: \mathbb{R}^d \to \{0,1\}$
-around a focal point $x \in \mathbb{R}^d$
-by a linear classifier $g: \mathbb{R}^d \to \{0,1\}$
+approximates a black-box classifier $f: \mathbb{R}^m \to \{0,1\}$
+around a focal point $x \in \mathbb{R}^m$
+by a linear classifier $g: \mathbb{R}^m \to \{0,1\}$
 (\cref{fig:lime}).
-The process involves:
+The approximation is performed by the following steps:
 \begin{enumerate}
-  \item Obtaining a set of perturbed samples $\mathcal{Z}_p$ around $x$
+  \item Generating a set of perturbed samples $\mathcal{Z}_p$ around $x$
         and the set of pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
+        (i) $x$ is converted into a binary vector
+        $x'\in\{0,1\}^{m'}$,
+        (ii) perturbed samples are generated by drawing non-zero elements
+        from $x'$ uniformly at random,
+        and (iii) the perturbed samples are converted back to the original space.
   \item Learning a linear classifier $g$
@@
         where $\pi_x(z)$ is a weight function designed to be larger for samples
-        closer to $x$, typically implemented using an exponential kernel.
+        closer to $x$, typically defined using an exponential kernel.
 \end{enumerate}
-
 LIME provides valuable insights into the local behavior of the model
 by showing the contribution of each feature to the output $f(x)$.
-However, due to not explicitly indicating the perturbation region,
-users cannot assess the effective scope of the explanation
-\cite{ribeiro2018anchors}.
-An example of explanation by LIME for an LSTM sentiment prediction model
-is illustrated in \cref{fig:lime_vs_anchor_exp_b}.
-The left explanation suggests that
-the word "not" contributes to the model's positive prediction,
-which does not apply to the instance on the right.
-However, without the explicit perturbation region,
-users might mistakenly apply the left explanation to the right instance,
-potentially leading to a misunderstanding of the black-box model's behavior
+However, it does not explicitly indicate the region for generating perturbed samples,
+making it difficult for users to assess the effective scope of the explanation
 \cite{ribeiro2018anchors}.
 
-\subsection{Anchor \cite{ribeiro2018anchors}}\label{sec:anchor}
-Anchor represents a rectangular region containing the focal point $x$,
-expressed as a conjunction of feature predicates (a rule),
-that maximizes the probability of the black-box classifier $f$
-outputting $f(x)$ within the region.
+\subsubsection[Anchor]{%
+  Anchor~\cite{ribeiro2018anchors}
+}\label{sec:anchor}
+Anchor maximizes the coverage of a rectangular region
+containing the focal point $x$,
+expressed as a conjunction of feature predicates (a rule)
+as long as the probability of the black-box classifier $f$
+outputting $f(x)$ within the region exceeds a given threshold $\tau$
+(\cref{fig:anchor}).
 It aims to highlight important features
-contributing significantly to the output (\cref{fig:anchor}).
-
-For a discrete $m$-dimensional input space $\ispace$
-with a trained black-box classifier $f: \ispace \to \{0,1\}$,
-an instance $x \in \ispace$,
+contributing significantly to the output.
+For a discrete $m$-dimensional input space $\ispace$,
+a trained black-box classifier $f: \ispace \to \{0,1\}$,
+an instance $x \in \ispace$
 and a distribution $\mathcal{D}$ over the input space,
 a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
-The predicates $a_i(z)$ evaluate to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
+The predicate $a_i(z)$ evaluates to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
+The reliability of the explanation is defined as the ``accuracy'' of the rule,
+and the generality of the explanation is defined as the ``coverage'' of the rule.
 The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
@@
   [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor_def_prec} \\
-  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)].
+  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)],
 \end{align}
-
 where $\mathcal{D}(z|A)$ is the conditional distribution in the region
@@
 and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
-
-Anchor maximizes coverage under the constraint that
+Anchor maximizes coverage as long as
 the accuracy of the rule $A$ exceeds a given threshold $\tau$.
@@
 
-While Anchor provides an effective scope of the explanation,
-the information it includes is less than LIME,
-limiting its utility \cite{ribeiro2018anchors}.
-An example of Anchor explanation for an LSTM sentiment prediction model
-is depicted in \cref{fig:lime_vs_anchor_exp_c}.
-The left explanation suggests that changing words other than "not" and "bad"
-has little impact on the classifier's output.
-While it clearly does not apply to the right instance,
-the explanation does not provide details about the influence of each word,
-resulting in less user insight into the model's behavior compared to LIME
-(\cref{fig:lime_vs_anchor_exp_b}).
-
-\subsection{%
-  BELLA (Black box model Explanations by Local Linear Approximations)
-  \cite{radulovic2023bella}
-}
-BELLA addresses the non-optimization of the approximation region,
-a drawback of LIME,
-by learning a local linear classifier $g$
-using a subset $Z'$ of the dataset $Z$
-instead of perturbed samples (\cref{fig:bella}).
-The process involves:
-\begin{enumerate}
-  \item Computing the distance $d_x(z)$ for all instances $z$ in $Z$
-        with respect to the focal point $x$.
-  \item Selecting the $k$ instances with the smallest $d_x(z)$,
-        forming a subset $Z_s(k) \subseteq Z$.
-  \item Learning the local linear classifier $g$ using $Z_s(k)$
-        and calculating the similarity measure $\mathcal{R}(k)$ between $f$ and $g$
-        over $k=1,2,\dots,|Z|$.
-  \item Obtaining the optimal $k^*$ by maximizing $\mathcal{R}(k)$.
-\end{enumerate}
-
-BELLA aims to enhance the reliability of explanations
-by optimizing the approximation region for high-accuracy linear approximations.
-However, it assumes direct access to the dataset $Z$ used for training the classifier,
-making it inapplicable in scenarios where direct access to the dataset is restricted.
-Additionally,
-as BELLA presents the approximation region as a subset of the dataset,
-its interpretability is lower compared to Anchor.
-
-\section{Proposed Method}
-\begin{figure}[tb]
-  \centering
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{lime}
-    \caption{%
-      LIME: Locally approximates the decision boundary around the focal point.
-    }\label{fig:lime}
-  \end{subfigure}%
-  \hfill
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{anchor}
-    \caption{%
-      Anchor: Maximizes coverage of a rectangular region
-      containing the focal point under accuracy constraints.
-    }\label{fig:anchor}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[width=0.85\textwidth]{bella}
-    \caption{%
-      BELLA: Explores a subset of the dataset,
-      maximizing similarity between the local linear classifier
-      and the black-box classifier.
-    }\label{fig:bella}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{0.45\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{rlime3}
-    \caption{%
-      R-LIME:
-      Maximizes coverage of a rectangular region containing the focal point
-      under lower constraints on the accuracy of the linear classifier.
-    }\label{fig:rlime}
-  \end{subfigure}
-  \caption{%
-    Visual comparison of LIME, Anchor, BELLA and R-LIME (our proposed method).
-    The solid line represents the rectangular region containing the focal
-    point, and the dashed line represents the learned approximation model.
-  }
-\end{figure}
-
 \subsection{Overview}
 We propose R-LIME,
-a method that aims to address the limitations of LIME \cite{ribeiro2016why},
-Anchor \cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
+a method that aims to address the limitations of LIME~\cite{ribeiro2016why}
+and Anchor~\cite{ribeiro2018anchors}.
 Our method locally approximates the given black-box classifier $f$
-around the focal point $x$ by a linear classifier $g$ similar to LIME and BELLA,
-but samples parturbation from a rectangular region similar to Anchor
+around the focal point $x$ by a linear classifier $g$ similar to LIME,
+but generates the perturbed samples
+from a rectangular region similar to Anchor
+so that the generality of approximation is explicitly provided
 (\cref{fig:rlime}).
-The accuracy of $g$ is defined as the "accuracy" of the rule,
-and the generality of explanations is defined as the "coverage" of the rule.
 
@@
   \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
-  [\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
+  [\mathbbm{1}_{f(z)=g(z)}], \label{eq:def_prec}
 \end{equation}
-where $G$ is the set of possible linear classifiers.
+where $G$ is a hypothesis space of possible linear classifiers.
 By solving the optimization problem in \cref{eq:main_problem}
-under the modified accuracy definition in \cref{eq:def_prec},
+under the modified definition of accuracy in \cref{eq:def_prec},
 we can select the rule that enables explanation with high accuracy and generality.
-The characteristics of R-LIME are listed below:
-\begin{itemize}
-  \item The approximation region is optimal and interpretable.
-  \item The dataset is not directly accessed, and only the distribution is utilized.
-  \item The number of samples is dynamically determined
-        based on the estimated accuracy without the need for predefining it.
-\end{itemize}
 
@@
     \centering
-    \includegraphics[width=0.32\textwidth]{rlime1}
-    \includegraphics[width=0.32\textwidth]{rlime2}
-    \includegraphics[width=0.32\textwidth]{rlime3}
-    \caption{%
+    \includegraphics[width=0.32\textwidth]{visual-rlime1}
+    \includegraphics[width=0.32\textwidth]{visual-rlime2}
+    \includegraphics[width=0.32\textwidth]{visual-rlime3}
+    \caption[Overview of the R-LIME algorithm]{%
       Overview of the R-LIME algorithm.
@@
   \end{figure}
+  \def\myidt{\hspace{\algorithmicindent}}
+  \ifnum\mode=0
+    \begin{algorithm}[t]
+      \small
+      \input{src/tex/alg1}
+    \end{algorithm}
+  \else
     \begin{algorithm}[p]
-    \input{alg1}
+      \small
+      \input{src/tex/alg1}
     \end{algorithm}
+  \fi
+
+  \foreach \alg in {2,3,4}{%
       \begin{algorithm}[p]
-    \input{alg2}
-  \end{algorithm}
-  \def\myidt{\hspace{\algorithmicindent}}
-  \begin{algorithm}[p]
-    \input{alg3}
-  \end{algorithm}
-  \begin{algorithm}[p]
-    \input{alg4}
+        \small
+        \input{src/tex/alg\alg}
       \end{algorithm}
     }
-
-Our method's algorithm is mainly based on that used in Anchor.
+}
+The algorithm of R-LIME
+is mainly based on that used in Anchor\cite{ribeiro2018anchors}.
 For non-convex optimization problems like \cref{eq:main_problem},
 greedy search are often used.
-However,
-greedy methods tend to converge to local optima, and to address this,
-R-LIME utilizes beam search,
-which selects multiple candidates at each iteration.
-The pseudocode is shown in \cref{alg:greedy_search}.
+But greedy methods tend to converge to local optima,
+so we use beam search, which selects multiple candidates at each iteration.
+The pseudo-code is shown in \cref{alg:greedy_search}.
 
-\subsubsection{Generation of New Candidate Rules}
+\subsubsection{Generating New Candidate Rules}
 To generate new candidate rules,
@@
 selected in the previous iteration.
-The pseudocode is shown in \cref{alg:generate_cands}.
-$T(x)$ is the set of attribute-value pairs (predicates) that are true for $x$,
-and $T(x)\setminus A$ is the set of predicates in $T(x)$ not included in rule $A$.
+The pseudo-code is shown in \cref{alg:generate_cands}.
+$T(x)$ is the set of predicates $\{a_1,\dots,a_m\}$,
+where $a_i(z)$ evaluates to true when $z_i=x_i$ and false otherwise.
+$T(x)\setminus A$ is the set of predicates in $T(x)$ not included in rule $A$.
 
-\subsubsection{Selection of Candidate Rules with Maximum Accuracy}
-Given the set of generated candidate rules $\cands$,
-the algorithm selects the top $B$ candidates with the highest accuracy.
-This is treated as an optimal arm identification problem in the multi-armed bandit framework.
-Each candidate rule $A_i\in\cands$ is considered an arm,
-and their accuracy $\Prec(A_i)$ is treated as the distribution of rewards.
+\subsubsection{Searching Rules with Highest Accuracy}
+Given the set of candidate rules $\cands$,
+the algorithm selects the $B$ candidate rules with the highest accuracy.
+This problem can be formulated
+as best arm identification in the multi-armed bandit framework.
+Each candidate rule $A_i\in\cands$ is considered as an arm,
+and reward of arm $a_i$ follows a Bernoulli distribution
+with $P(X=1)=\Prec(A_i)$.
 By sampling $z\sim\mathcal{D}(\cdot|A_i)$
 and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial,
-the algorithm updates $g_i$ using the sampled perturbation vector $z$
-and the pseudo-label $f(z)$ after each trial.
-To efficiently select the rule (arm) with the highest accuracy,
+the algorithm updates $g_i$ using $z$ and $f(z)$ after each trial.
+To efficiently search the rule (arm) with the highest accuracy,
 we employ the KL-LUCB algorithm \cite{kaufmann2013information}.
-The pseudocode is shown in \cref{alg:best_cands}.
+The pseudo-code is shown in \cref{alg:best_cands}.
 For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
@@
 and proceeds to the next iteration.
-The pseudocode is presented in \cref{alg:largest_valid_cand}.
+The pseudo-code is presented in \cref{alg:largest_valid_cand}.
 
@@
 
+\ifnum\mode=1
+  \subsection{Computational Complexity}
+  Post-hoc explanation methods including LIME, Anchor, and R-LIME
+  need to sample a perturbation vector
+  and get the output of the black-box model multiple times,
+  which is computationally expensive.
+  The number of samples required for LIME is $|\mathcal{Z}_p|$,
+  which is the number of samples designated by the user.
+  On the other hand,
+  the expected number of samples required for Anchor and R-LIME is bounded by
+  $\mathcal{O}[m\cdot\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}]$,
+  where $\mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}$
+  is the expected number of samples
+  for best arm identification finding the best $B$ arms from $B\cdot m$ arms.
+  For KL-LUCB algorithm~\cite{kaufmann2013information},
+  \begin{equation}
+    \mathcal{O}_{\mathrm{MAB}[B\cdot m,B]}=
+    \mathcal{O}\left[\frac{Bm}{\epsilon^2}\log\frac{Bm}{\epsilon^2\delta}\right].
+  \end{equation}
+  Then the total expected number of samples for Anchor and R-LIME is bounded by
+  \begin{equation}
+    \mathcal{O}\left[\frac{Bm^2}{\epsilon^2}\log\frac{Bm}{\epsilon^2\delta}\right].
+  \end{equation}
+
+  For each iteration of KL-LUCB algorithm, R-LIME needs to update
+  the linear classifier $g_i$, which is not required in Anchor.
+  If we use logistic regression as the linear classifier
+  and update it by stochastic gradient descent (SGD) \cite{robbins1951stochastic},
+  the computational complexity of updating $g_i$ is $\mathcal{O}(m)$.
+  It is negligible compared to the complexity of generating a perturbed sample,
+  which is $\mathcal{O}(m^2)$ if we get a sample
+  from a multivariate normal distribution using Cholesky decomposition in advance.
+  Overall, the computational complexity of R-LIME is comparable to that of Anchor.
+\fi
+
 \section{Experiments}
 To verify the effectiveness of the proposed method,
-We compare LIME and R-LIME using a real-world dataset.
+we compared LIME and R-LIME using a real-world dataset.
 
@@
     \centering
-    \caption{%
+    \caption[Attributes of the recidivism dataset used in the experiments]{%
       Attributes of the recidivism dataset used in the experiments.
-      Continuous features are all discretized
+      Continuous features are all discretized,
       and only binary and ordinal features are considered.
     }\label{tab:rcdv}
+    \ifnum\mode=0
+      \small
+    \fi
     \begin{tabular}{llc}
       \toprule
-      Attribute              & Overview                              & \# of Possible Values \\
+      Attribute              & Overview                              & \# of \ifnum\mode=1 Possible \fi Values \\
       \midrule
@@
 
-The experiments utilized the recidivism dataset \cite{schmidt1988predicting}.
-This dataset contains information on 9,549 prisoners released from
+We used the recidivism dataset \cite{schmidt1988predicting} for our experiments.
+The dataset contains personal information on 9549 prisoners released from
 North Carolina prisons between July 1, 1979, and June 30, 1980.
-The dataset includes 19 items such as race, gender,
-presence of alcohol dependence, number of prior offenses, and recidivism.
+The dataset includes 19 items such as race (\emph{Race}), gender (\emph{Gender}),
+presence of alcohol dependence (\emph{Alcohol}),
+number of prior offenses (\emph{Priors}),
+and presence of recidivism (\emph{Recidivism}).
 For this experiment,
 we treated the binary classification problem of predicting
-the presence or absence of recidivism (Recidivism) as the target label.
+the presence of recidivism (\emph{Recidivism}) as the target label.
 We discretized continuous features and removed missing values,
 resulting in 15 features.
-This problem setting can be considered as a case
-where a machine learning model is introduced to decide parole for prisoners.
-Since such decisions can have a significant impact on a person's life,
-it is crucial for users to interpret the outputs of black-box models appropriately.
 
-The dataset, after removing missing values,
-was split into training data (7,639 instances) and test data (955 instances).
-A random forest model with 50 trees was trained using the training data.
-Subsequently, LIME and R-LIME explanations were generated
+We splitted the dataset into training data (7639 instances) and test data (955 instances),
+and trained a random forest model with 50 trees as the black-box classifier
+using the training data.
+Then, LIME and R-LIME explanations were generated
 for two instances extracted from the test data (\cref{fig:instance}).
-In R-LIME, logistic regression was used as the linear approximation model,
-and the distribution $\mathcal{D}$ was a multivariate normal distribution
-estimated from the training data.
+For R-LIME, we used logistic regression as the linear approximation model,
+and a multivariate normal distribution estimated from the training data
+as the distribution $\mathcal{D}$.
 The beam width was set to $B=10$,
@@
 and the tolerance of the KL-LUCB algorithm to $\epsilon=0.05$.
-Accuracy thresholds $\tau$ were set to $\tau=0.70,0.80,0.90$.
+The accuracy threshold $\tau$ was set to $\tau=0.70,0.80,0.90$.
 
+This problem setting can be considered as a case
+where a complex machine learning model is introduced to decide parole for prisoners.
+Since such decisions can have a significant impact on a person's life,
+it is crucial for users to interpret the outputs of black-box models appropriately.
   {%
 
-    \def\dir{python/exp1}
+    \def\dir{src/experiments/exp1}
     \def\Asample{0012}
@@
       \def\mylabel#1{\ifnum#1=0 \label{fig:A-instance}\else \label{fig:B-instance}\fi}
+      \ifnum\mode=0
+        \renewcommand{\arraystretch}{0.97}
+      \else
         \renewcommand{\arraystretch}{1.02}
+      \fi
       \begin{figure}[tbp]
@@
             \begin{subfigure}{\textwidth}
+              \ifnum\mode=0
+                \small
+              \fi
               \centering
@@
         \vspace{-15pt}
-        \caption{Two instances sampled from recidivism dataset.}\label{fig:instance}
+        \caption[Two instances sampled from recidivism dataset]{%
+          Two instances sampled from training data of recidivism dataset.
+          Each number in parentheses represents the integer value assigned
+          to the corresponding categorical value.
+        }\label{fig:instance}
       \end{figure}
@@
     {%
+      \ifnum\mode=0
+        \def\scale{0.32}
+        \def\imgwidth{0.45\textwidth}
+        \def\hspacebase{\hspace{-0.5em}}
+      \else
         \def\scale{0.315}
@@
         \def\hspacebase{\hspace{-1.5em}}
+      \fi
       \def\vspacebase{\vspace{0.5em}}
@@
           \hspacebase
+          \hspace{1.0em}
           \includegraphics[scale=\scale]{\dir/lime-\Asample}
@@
           \hspacebase
-          \hspace{1.0em}
+          \hspace{0.5em}
           \includegraphics[scale=\scale]{\dir/newlime-\Asample-70}
@@
           \hspacebase
+          \hspace{-0.5em}
           \includegraphics[scale=\scale]{\dir/newlime-\Asample-90}
@@
         \end{subfigure}
-        \caption{Explanation for Instance A by LIME and R-LIME.}\label{fig:A}
+        \caption[Explanation for Instance A by LIME and R-LIME]{%
+          Explanation for Instance A by LIME and R-LIME.
+        }\label{fig:A}
       \end{figure}
@@
           \hspacebase
+          \hspace{-0.7em}
           \includegraphics[scale=\scale]{\dir/lime-\Bsample}
@@
           \hspacebase
+          \hspace{0.5em}
           \includegraphics[scale=\scale]{\dir/newlime-\Bsample-70}
@@
           \hspacebase
+          \hspace{-0.8em}
           \includegraphics[scale=\scale]{\dir/newlime-\Bsample-80}
@@
           \hspacebase
-          \hspace{0em}
+          \hspace{-0.8em}
           \includegraphics[scale=\scale]{\dir/newlime-\Bsample-90}
@@
         \end{subfigure}
-        \caption{Explanation for Instance B by LIME and R-LIME}\label{fig:B}
+        \caption[Explanation for Instance B by LIME and R-LIME]{%
+          Explanation for Instance B by LIME and R-LIME.
+        }\label{fig:B}
       \end{figure}
@@
 The results of the experiment are shown in \cref{fig:A,fig:B}.
-The values assigned to each attribute name represent the contribution
-(weights of the learned linear classifier)
+The values assigned to each feature name represent the contribution
+(weight of the linear classifier)
 to the output of the black-box classifier,
 normalized such that the absolute sum is 1.
-The figures also display the 5 attributes with the highest absolute contribution.
+The figures display the 5 features with the highest absolute contribution.
 
-Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) indicate that
-attributes such as having a significant prior record (Prior) or committing a
-crime against property (Crime against Property) primarily contribute positively
-to the prediction (predicting that the prisoner will be re-arrested).
+Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) provide insights
+that having a prior offenses (\emph{Priors}),
+being served for a long time in prison (\emph{Months-Served}),
+and committing a crime against property (\emph{Crime against Property})
+primarily contribute to the positive prediction
+(prediction that the prisoner will be re-arrested).
 On the other hand,
-attributes like older age (Age), being married (Married),
-and being of white race (Race) contribute negatively to the prediction
-(predicting that the prisoner will not be re-arrested).
+being elderly (\emph{Age}), being married (\emph{Married}),
+and being of white race (\emph{Race}) contribute to the negative prediction
+(prediction that the prisoner will not be re-arrested).
 While these LIME explanations provide valuable insights into the behavior of
@@
 they do not explicitly indicate the application scope of the explanations,
-leaving users unable to determine to which inmates the explanations are applicable.
+leaving users unable to determine to which prisoners the explanations are applicable.
 
 In contrast, R-LIME expresses the application scope of explanations
-as a conjunction of predicates.
+as a conjunction of feature predicates.
 For example, the explanation for instance A
 under $\tau=0.70$ (\cref{fig:A-rlime-70}) indicates that it is applicable
-only to married prisoner (Married$=$Yes).
-Furthermore, the generated explanations include the accuracy and coverage of
-the approximation region, allowing users to evaluate how reliable the
-explanations are.
+only to married prisoner (\emph{Married} $=$\emph{Yes}).
+R-LIME explanations also provide their accuracy and coverage,
+allowing users to evaluate reliability and generality of the explanations.
 For example, the coverage of the explanation for instance B under $\tau=0.90$
-(\cref{fig:B-rlime-90}) is 0.002,
+(\cref{fig:B-rlime-90}) is 0.01\%,
 indicating that the decision boundaries around instance B are complex,
 making it challenging to obtain a high-accuracy linear approximation.
-This allows users to discern that the application scope of this explanation is
-very narrow, limiting its utility.
+This information allows users to discern that
+the application scope of this explanation is very narrow, limiting its utility.
 
@@
 between LIME and R-LIME\@.
-Using the same settings as in \cref{sec:exp_setting},
+Under the same settings as in \cref{sec:exp_setting},
 we randomly sampled 100 instances from the test data of the recidivism dataset
-and generated explanations (with $\tau=0.70,0.80,0.90$) using LIME and R-LIME\@.
+and generated explanations using LIME and R-LIME (with $\tau=0.70,0.80,0.90$).
 We then sampled 10,000 instances within the rectangular region
@@
   \centering
-  \includegraphics[width=0.55\textwidth]{python/exp2/box_plot}
+  \includegraphics[width=0.5\textwidth]{src/experiments/exp2/box_plot}
   \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
@@
 The results are presented in \cref{fig:box_plot},
-showcasing the distribution of the accuracy of the linear approximation models
+showing the distribution of the local accuracy of the linear classifiers
 learned by LIME and R-LIME\@.
-R-LIME exhibits higher accuracy compared to LIME for all values of $\tau$.
+R-LIME achieved higher accuracy compared to LIME for all values of $\tau$.
 This suggests that the linear classifiers learned by LIME and R-LIME
 differ significantly,
-and R-LIME learns a high-accuracy linear classifier adapted to the rectangular region.
+and R-LIME learns a high-accuracy linear classifier
+adapted to the optimized rectangular region.
 Additionally, as $\tau$ increases,
@@
 
-\section{Challenges and Future Perspectives}
+\section{Challenges and Future Work}
  {%
-  \def\imgwidth{0.49\textwidth}
+  \def\imgwidth{0.47\textwidth}
   \begin{figure}[t]
@@
       \centering
-      \includegraphics[width=0.78\textwidth]{newlime}
-      \caption{R-LIME for balanced data.}\label{fig:balanced}
+      \includegraphics[width=0.7\textwidth]{visual-rlime3}
+      \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
     \end{subfigure}
@@
       \centering
-      \includegraphics[width=0.8\textwidth]{newlime_for_imbalanced_data}
-      \caption{R-LIME for imbalanced data.
+      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
+      \caption{R-LIME for imbalanced label distribution.
       }\label{fig:imbalanced}
     \end{subfigure}
-    \caption{%
-      Behavior of R-LIME for balanced and imbalanced data.
+    \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
+      Behavior of R-LIME for balanced and imbalanced label distribution.
       In case of imbalanced label distribution,
@@
     }
-    \vspace{10pt}
   \end{figure}
@@
 
-\subsection{Computational Complexity}
-Most post-hoc explanation methods, including LIME, Anchor, BELLA and R-LIME,
-need to query the black-box model multiple times
-to get labels for perturbed samples, which can be computationally expensive.
-The number of queries required for LIME is $|\mathcal{Z}_p|$,
-where $|\mathcal{Z}_p|$ is the number of perturbed samples.
-
 \subsection{Behavior Regarding Imbalanced Label Distribution}
 R-LIME may generate less useful explanations
-when there is bias in the distribution of black-box model outputs.
-When the distribution of black-box model outputs is significantly biased
-for a given accuracy threshold $\tau$
-(when the ratio of the minority label is less than $1-\tau$),
+when the distribution of black-box classifier outputs is imbalanced.
+When the ratio of outputting the minority label is less than $1-\tau$,
+where $\tau$ is the accuracy threshold,
 the approximation region generated by R-LIME covers the entire input space,
@@
     \centering
-    \caption{%
-      Deviation between the estimated accuracy and the true accuracy.
-      Deviation was relatively small considering confidence level $1-\delta=0.95$.
+    \caption[Deviation between the estimated accuracy and the true accuracy]{%
+      Deviation between the estimated accuracy and the true accuracy
+      of the linear classifier learned by R-LIME.
+      The deviation $0.012\pm0.017$ was relatively small
+      considering the confidence level $1-\delta=0.95$.
     }\label{tab:reward}
-    \input{tab_exp_adv}
+    \input{src/tex/tab_exp_adv}
   \end{table}
 }
-In R-LIME,
+For R-LIME,
 the problem of selecting the rule with the highest accuracy is formulated
-as the optimal arm identification problem in multi-armed bandit theory,
-solved using the KL-LUCB algorithm \cite{kaufmann2013information}.
+as the best arm identification problem in multi-armed bandit framework,
+and solved using the KL-LUCB algorithm \cite{kaufmann2013information}.
 However, this algorithm assumes that the reward distribution remains constant,
@@
 with a standard deviation of 0.017.
-While the deviation was relatively small considering confidence level $1-\delta=0.95$,
-we should modify the selection algorithm to consider the varying accuracy.
-
-% \subsection{Evaluation through User Studies}
-% Given the nature of the field of "interpretable machine learning,"
-% where the goal is to "interpret" machine learning models,
-% it is challenging to quantitatively compare various methods.
-% While quantitative experiments were conducted in \cref{sec:exp2},
-% they mainly demonstrated that the proposed method generates
-% locally accurate explanations compared to LIME.
-% The results do not directly prove the high interpretability of the proposed method.
-% 
-% One potential method to quantitatively evaluate "interpretability" is
-% through user studies.
-% For example, \cite{ribeiro2018anchors} conducted user studies,
-% assuming that if users could predict the output of a black-box model
-% with high accuracy based on provided explanations,
-% those explanations contained valuable information about the model's behavior.
-% Similarly,
-% conducting user studies in this research would be desirable
-% to evaluate the interpretability of the proposed method.
+By considering the confidence level $1-\delta=0.95$,
+the deviation was relatively small.
+While there are concerns about the theoretical validity of using the KL-LUCB algorithm,
+our results suggest that the deviation is not significant in practice.
 
 \section{Conclusion}
-We identified challenges in existing methods for local model-agnostic post-hoc
-explanations of black-box classifiers and proposed R-LIME to address them.
-We represented the rectangular region for local linear approximation as a
-conjunction of feature predicates and proposed an algorithm to
-maximize coverage under the constraint of minimum approximation accuracy.
-Comparing the outputs of LIME and R-LIME on real-world datasets,
-we demonstrated that explanations provided by R-LIME have clearer application
-scopes and can be evaluated by users for reliability and generality.
-However, we discussed the instability of behavior concerning imbalanced label
+Existing methods for
+local model-agnostic explanations of black-box classifiers,
+such as LIME and Anchor,
+have limitations that they cannot achieve interpretability of
+both the explanation and its application scope.
+To address these challenges,
+we proposed R-LIME,
+a method that locally and linearly approximates the decision boundary
+of a black-box classifier and provides a rectangular approximation region,
+which is interpretable for users due to being expressed as a conjunction of feature predicates.
+We proposed an algorithm to
+maximize coverage of the approximation region
+as long as the accuracy of the linear approximation model exceeds a given threshold.
+Comparing the outputs of LIME and R-LIME on the real-world dataset,
+we demonstrated that R-LIME provides a clear application scope of the
+explanation, can be evaluated by users for its reliability and generality,
+and achieves higher and less variable local accuracy compared to LIME\@.
+Finally, we discussed the instability of behavior against imbalanced label
 distributions and raised questions about the theoretical validity of using
-the KL-LUCB algorithm.
+the KL-LUCB algorithm for our problem.
 
-% \subsubsection{Acknowledgements}
-% Please place your acknowledgments at
-% the end of the paper, preceded by an unnumbered run-in heading (i.e.
-% 3rd-level heading).
+\ifnum\mode=0
+  \acknowledge
+  I would like to thank Associate Professor Keigo Kimura
+  of the Laboratory for Pattern Recognition and Machine Learning,
+  Division of Computer Science and Information Technology,
+  Graduate School of Information Sci.\ and Tech., Hokkaido University.
+  He provided valuable guidance
+  from setting the research theme to outlining the research method.
+  Furthermore,
+  I appreciate the various insights shared by Professor Mineichi Kudo
+  in the same laboratory.
+  Finally, I am deeply thankful to all the members of our laboratory
+  for their helpful advice and cooperation throughout the research process.
+\fi
 
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\bibliographystyle{splncs04}
-\bibliography{MyRef/ref}
-%
+\ifnum\mode=0
+  \bibliographystyle{src/style/prml}
+\else
+  \bibliographystyle{src/style/splncs04}
+\fi
+\bibliography{src/myref/myref}
+
 \end{document}

### 2024-06-25 src/tex/alg2.tex
build: organize directory structure and refine environment

\caption{Generating new candidate rules}\label{alg:generate_cands}
\begin{algorithmic}[1]
  \Function{GenerateCands}{$\mathcal{A},x$}
  \IIf{$\mathcal{A}=\emptyset$}{\Return{$\{\mathit{true}\}$}}
    \Comment{An initial empty rule always returns $\mathit{true}$}
  \State$\cands\gets\emptyset$
  \ForAll{$A\in\mathcal{A}$}
  \ForAll{$a\in (T(x)\setminus A)$}
  \State$\cands\gets\bar{\mathcal{A}}\cup(A\wedge a)$
  \Comment{Get a new rule by adding a new predicate $a$ to $A$}
  \EndFor%
  \EndFor%
  \State\Return{$\cands$}
  \EndFunction%
\end{algorithmic}

### 2024-06-25 paper/enter_container.sh

@@ -1,6 +1,0 @@
-#!/usr/bin/bash
-
-docker compose up -d
-xhost +local:
-docker compose exec latex bash
-xhost -local:

### 2024-06-27 paper.tex
fix: remove warnings by compiler and linter

@@
 
-\def\mode{1} % 0: Graduation thesis, 1: ICPR paper
-
-\ifnum\mode=0
-  \documentclass[11pt]{article}
-  \usepackage{luatexja}
-  \usepackage{src/style/prmlthesis}
-  \usepackage[a4paper]{geometry}
-\else
 \documentclass[runningheads]{llncs}
-\fi
 
@@
 % cf. https://tex.stackexchange.com/questions/10924/underfull-hbox-in-bibliography
-\apptocmd{\sloppy}{\hbadness 10000\relax}{}{}
+\apptocmd{\sloppy}{\hbadness10000\relax}{}{}
 
 % set the path for figures
-\graphicspath{{./src/}{../python/data/}{src/experiments/}}
+\graphicspath{{./src/img}{./src/experiments/exp1}{./src/experiments/exp2}}
 
@@
 \crefname{algorithm}{Algorithm}{Algorithms}
-\ifnum\mode=0
-  \crefname{figure}{Figure}{Figures}
-\else
 \crefname{figure}{Fig.}{Figs.}
-\fi
 
@@
 
-\ifnum\mode=0
-  \title{%
-    R-LIME: LIME法における矩形制約と最適化
-  }
-  \etitle{%
-    R-LIME: Rectangular Constraints and Optimization for Local Interpretable
-    Model-agnostic Explanation Methods
-  }
-  \author{大原 玄嗣 (Genji Ohara)}
-  \institute{%
-    北海道大学 工学部 \\
-    情報エレクトロニクス学科 \\
-    情報理工学コース \\
-    情報認識学研究室
-  }
-  \date{2024年3月}
-  % \institute{%
-  %   Laboratory for Pattern Recognition and Machine Learning,\\
-  %   Division of Computer Science and Information Technology,\\
-  %   Department of Electronics and Information Engineering,\\
-  %   School of Engineering, Hokkaido University
-  % }
-\else
 % The title of the paper
 \title{%
-    R-LIME: Rectangular Constraints and Optimization for Local Interpretable
+  R-LIME\@: Rectangular Constraints and Optimization for Local Interpretable
   Model-agnostic Explanation Methods
@@
 \titlerunning{%
-    R-LIME: Rectangular Constraints and Optimization for LIME Methods
+  R-LIME\@: Rectangular Constraints and Optimization for LIME Methods
 }
@@
 % Author names and ORCID IDs
-  \author{Genji Ohara\orcidID{0009-0000-5854-2820} \and
-    Keigo Kimura\orcidID{0000-0002-3614-6568} \and
-    Mineichi Kudo\orcidID{0000-0003-1013-3870}
+\author{Genji Ohara\orcidID{0009-0000-5854-2820} \and % chktex 8
+  Keigo Kimura\orcidID{0000-0002-3614-6568} \and      % chktex 8
+  Mineichi Kudo\orcidID{0000-0003-1013-3870}          % chktex 8
 }
@@
   Hokkaido University\\
-    Sapporo 060-0814, JAPAN,\\
+  Sapporo 060--0814, JAPAN,\\
   \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}
-\fi
 
@@
 
-\ifnum\mode=0
-  \pagestyle{plain}
-  \pagenumbering{roman}
-  \tableofcontents
-  \newpage
-  \listoffigures\listoftables\clearpage
-  \AddToHook{cmd/section/before}{\clearpage}
-  \pagestyle{plain}
-  \pagenumbering{arabic}
-\else
 % The abstract should briefly summarize the contents of the paper in
@@
 \end{abstract}
-\fi
 
@@
     \centering
-    \ifnum\mode=0
-      \vspace{-1.79cm}
-    \else
     \vspace{-2.24cm}
-    \fi
     \includegraphics[scale=\scale]{example-rlime}
@@
 LIME linearly approximates the complex decision boundary
-around the given focal point,
+around the given focal point (\cref{fig:example-instance}),
 then provides the weights of the linear model as the contribution of each feature
@@
 potentially leading to misunderstanding of the black-box model's behavior
-\cite{ribeiro2018anchors}.
+~\cite{ribeiro2018anchors}.
 For this example,
 users may apply the derived insights
-to the sentence ``This book is not good.''
+to the sentence ``This book is not good.'' % chktex 38
 and mistakenly conclude that the word ``not''
@@
 the explanation does not provide details about the influence of each word,
-resulting in less user insight into the model's behavior compared to LIME.
+resulting in less user insight into the model's behavior compared to LIME\@.
 
@@
 In contrast, local methods,
-such as local interpretable model-agnostic explanations (LIME)
-\cite{ribeiro2016why}
-and Anchor~\cite{ribeiro2018anchors},
+such as local interpretable model-agnostic explanations
+(LIME)~\cite{ribeiro2016why} and Anchor~\cite{ribeiro2018anchors},
 explain model's behavior in the vicinity of a specific input.
@@
     \caption{%
-      LIME: Locally approximates the decision boundary around the focal point.
+      LIME\@: Locally approximates the decision boundary around the focal point.
     }\label{fig:lime}
@@
     \caption{%
-      R-LIME:
+      R-LIME\@:
       Maximizes coverage of a rectangular region
@@
 \subsubsection[LIME]{%
-  LIME (Local Interpretable Model-agnostic Explanations)
-  \cite{ribeiro2016why}
+  LIME (Local Interpretable Model-agnostic Explanations)~\cite{ribeiro2016why}
 }
@@
         (i) $x$ is converted into a binary vector
-        $x'\in\{0,1\}^{m'}$,
+        $x'\in{\{0,1\}}^{m'}$,
         (ii) perturbed samples are generated by drawing non-zero elements
@@
         \begin{equation}
-          \label{eq:lime_loss}
           \mathcal{L}(f,g,\pi_x)=\sum_{z\in\mathcal{Z}_p}
@@
 making it difficult for users to assess the effective scope of the explanation
-\cite{ribeiro2018anchors}.
-
-\subsubsection[Anchor]{%
-  Anchor~\cite{ribeiro2018anchors}
-}\label{sec:anchor}
+~\cite{ribeiro2018anchors}.
+
+\subsubsection[Anchor]{Anchor~\cite{ribeiro2018anchors}}
 Anchor maximizes the coverage of a rectangular region
@@
   \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
-  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor_def_prec} \\
+  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor-def-prec} \\
   \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)],
@@
 the accuracy of the rule $A$ exceeds a given threshold $\tau$.
-However, \cref{eq:anchor_def_prec} is not directly computable.
+However, \cref{eq:anchor-def-prec} is not directly computable.
 Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$,
@@
 \begin{equation}
-  \label{eq:const_prec}
+  \label{eq:const-prec}
   P(\Prec(A)\ge\tau)\ge1-\delta.
@@
 \begin{equation}
-  \label{eq:main_problem}
+  \label{eq:main-problem}
   A^*=\underset{A \text{~s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
@@
 under lower constraints on the accuracy of $g$.
-We modify Anchor's definition of accuracy in \cref{eq:anchor_def_prec}
+We modify Anchor's definition of accuracy in \cref{eq:anchor-def-prec}
 as follows:
@@
   \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
-  [\mathbbm{1}_{f(z)=g(z)}], \label{eq:def_prec}
+  [\mathbbm{1}_{f(z)=g(z)}], \label{eq:def-prec}
 \end{equation}
 where $G$ is a hypothesis space of possible linear classifiers.
-By solving the optimization problem in \cref{eq:main_problem}
-under the modified definition of accuracy in \cref{eq:def_prec},
+By solving the optimization problem in \cref{eq:main-problem}
+under the modified definition of accuracy in \cref{eq:def-prec},
 we can select the rule that enables explanation with high accuracy and generality.
 
-\subsection{Algorithm}\label{sec:alg}
+\subsection{Algorithm}
 {%
@@
   \def\myidt{\hspace{\algorithmicindent}}
-  \ifnum\mode=0
-    \begin{algorithm}[t]
-      \small
-      \input{src/tex/alg1}
-    \end{algorithm}
-  \else
   \begin{algorithm}[p]
@@
   \end{algorithm}
-  \fi
-
-  \foreach \alg in {2,3,4}{%
+
   \begin{algorithm}[p]
     \small
-        \input{src/tex/alg\alg}
+    \input{src/tex/alg2}
   \end{algorithm}
-    }
+
+  \begin{algorithm}[p]
+    \small
+    \input{src/tex/alg3}
+  \end{algorithm}
+
+  \begin{algorithm}[p]
+    \small
+    \input{src/tex/alg4}
+  \end{algorithm}
 }
@@
 is mainly based on that used in Anchor\cite{ribeiro2018anchors}.
-For non-convex optimization problems like \cref{eq:main_problem},
+For non-convex optimization problems like \cref{eq:main-problem},
 greedy search are often used.
@@
 so we use beam search, which selects multiple candidates at each iteration.
-The pseudo-code is shown in \cref{alg:greedy_search}.
+The pseudo-code is shown in \cref{alg:greedy-search}.
 
@@
 selected in the previous iteration.
-The pseudo-code is shown in \cref{alg:generate_cands}.
+The pseudo-code is shown in \cref{alg:generate-cands}.
 $T(x)$ is the set of predicates $\{a_1,\dots,a_m\}$,
@@
 To efficiently search the rule (arm) with the highest accuracy,
-we employ the KL-LUCB algorithm \cite{kaufmann2013information}.
-The pseudo-code is shown in \cref{alg:best_cands}.
+we employ the KL-LUCB algorithm~\cite{kaufmann2013information}.
+The pseudo-code is shown in \cref{alg:best-cands}.
 For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
@@
 \subsubsection{Searching a Rule with Highest Coverage under Constraint}
-To satisfy the constraint imposed by \cref{eq:const_prec},
+To satisfy the constraint imposed by \cref{eq:const-prec},
 a rule $A$ needs to meet the following condition:
 \begin{equation}
-  \Prec_{l}(A,\delta)>\tau,\label{eq:stop_condition}
+  \Prec_{l}(A,\delta)>\tau,\label{eq:stop-condition}
 \end{equation}
@@
 If the set of candidate rules $\mathcal{A}$
-includes rules satisfying \cref{eq:stop_condition},
+includes rules satisfying \cref{eq:stop-condition},
 the one with the maximum coverage among them is selected,
 then the iteration is terminated.
-If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop_condition},
+If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop-condition},
 it returns \textbf{null},
 and proceeds to the next iteration.
-The pseudo-code is presented in \cref{alg:largest_valid_cand}.
+The pseudo-code is presented in \cref{alg:largest-valid-cand}.
 
 % The algorithmic procedure outlined above approximates
-% the solution to the optimization problem in \cref{eq:main_problem}
-% under the definition of accuracy in \cref{eq:def_prec}.
-
-\ifnum\mode=1
+% the solution to the optimization problem in \cref{eq:main-problem}
+% under the definition of accuracy in \cref{eq:def-prec}.
+
 \subsection{Computational Complexity}
@@
 the linear classifier $g_i$, which is not required in Anchor.
-  If we use logistic regression as the linear classifier
-  and update it by stochastic gradient descent (SGD) \cite{robbins1951stochastic},
+If we use logistic regression as the linear classifier and update it
+by stochastic gradient descent (SGD)~\cite{robbins1951stochastic},
 the computational complexity of updating $g_i$ is $\mathcal{O}(m)$.
@@
 Overall, the computational complexity of R-LIME is comparable to that of Anchor.
-\fi
 
@@
 \subsection{Qualitative Evaluation}
-\subsubsection{Experimental Setup}\label{sec:exp_setting}
+\subsubsection{Experimental Setup}\label{sec:exp-setting}
 {%
@@
     }\label{tab:rcdv}
-    \ifnum\mode=0
-      \small
-    \fi
     \begin{tabular}{llc}
       \toprule
-      Attribute              & Overview                              & \# of \ifnum\mode=1 Possible \fi Values \\
+      Attribute              & Overview                              & \# of Possible Values \\
       \midrule
@@
 
-We used the recidivism dataset \cite{schmidt1988predicting} for our experiments.
+We used the recidivism dataset~\cite{schmidt1988predicting} for our experiments.
 The dataset contains personal information on 9549 prisoners released from
 North Carolina prisons between July 1, 1979, and June 30, 1980.
-The dataset includes 19 items such as race (\emph{Race}), gender (\emph{Gender}),
+As shown in \cref{tab:rcdv}, the dataset includes 19 items such as
+race (\emph{Race}), gender (\emph{Gender}),
 presence of alcohol dependence (\emph{Alcohol}),
@@
     \def\Bsample{0011}
-    \def\index#1{\ifnum#1=0 \Asample \else \Bsample \fi}
+    \def\index#1{\ifnum#1=0 \Asample\else\Bsample\fi}
 
@@
       \def\AB#1{\ifnum#1=0 A\else B\fi}
-      \def\mylabel#1{\ifnum#1=0 \label{fig:A-instance}\else \label{fig:B-instance}\fi}
-      \ifnum\mode=0
-        \renewcommand{\arraystretch}{0.97}
-      \else
       \renewcommand{\arraystretch}{1.02}
-      \fi
       \begin{figure}[tbp]
@@
             \begin{subfigure}{\textwidth}
-              \ifnum\mode=0
-                \small
-              \fi
               \centering
@@
                 }{}{%
-                \ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii
+                \ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii % chktex 1
                 }
@@
               \end{tabular}
-              \caption{Instance~\AB{\a}}\mylabel{\a}
+              \caption{Instance~\AB{\a}}
               \vspace{15pt}
@@
     {%
-      \ifnum\mode=0
-        \def\scale{0.32}
-        \def\imgwidth{0.45\textwidth}
-        \def\hspacebase{\hspace{-0.5em}}
-      \else
       \def\scale{0.315}
@@
       \def\hspacebase{\hspace{-1.5em}}
-      \fi
       \def\vspacebase{\vspace{0.5em}}
@@
         \begin{subfigure}[t]{\imgwidth}
-          \hspacebase
+          \hspacebase{}
           \hspace{1.0em}
-          \includegraphics[scale=\scale]{\dir/lime-\Asample}
-          \vspacebeforecaption
+          \includegraphics[scale=\scale]{lime-\Asample}
+          \vspacebeforecaption{}
           \caption{LIME}\label{fig:A-lime}
-          \vspacebase
+          \vspacebase{}
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
-          \hspacebase
+          \hspacebase{}
           \hspace{0.5em}
-          \includegraphics[scale=\scale]{\dir/newlime-\Asample-70}
-          \vspacebeforecaption
+          \includegraphics[scale=\scale]{newlime-\Asample-70}
+          \vspacebeforecaption{}
           \caption{R-LIME ($\tau=0.70$)}\label{fig:A-rlime-70}
-          \vspacebase
+          \vspacebase{}
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
-          \hspacebase
-          \includegraphics[scale=\scale]{\dir/newlime-\Asample-80}
-          \vspacebeforecaption
-          \caption{R-LIME ($\tau=0.80$)}\label{fig:A-rlime-80}
+          \hspacebase{}
+          \includegraphics[scale=\scale]{newlime-\Asample-80}
+          \vspacebeforecaption{}
+          \caption{R-LIME ($\tau=0.80$)}
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
-          \hspacebase
+          \hspacebase{}
           \hspace{-0.5em}
-          \includegraphics[scale=\scale]{\dir/newlime-\Asample-90}
-          \vspacebeforecaption
-          \caption{R-LIME ($\tau=0.90$)}\label{fig:A-rlime-90}
+          \includegraphics[scale=\scale]{newlime-\Asample-90}
+          \vspacebeforecaption{}
+          \caption{R-LIME ($\tau=0.90$)}
         \end{subfigure}
         \caption[Explanation for Instance A by LIME and R-LIME]{%
-          Explanation for Instance A by LIME and R-LIME.
+          Explanation for Instance A by LIME and R-LIME\@.
         }\label{fig:A}
@@
         \begin{subfigure}[t]{\imgwidth}
-          \hspacebase
+          \hspacebase{}
           \hspace{-0.7em}
-          \includegraphics[scale=\scale]{\dir/lime-\Bsample}
-          \vspacebeforecaption
+          \includegraphics[scale=\scale]{lime-\Bsample}
+          \vspacebeforecaption{}
           \caption{LIME}\label{fig:B-lime}
-          \vspacebase
+          \vspacebase{}
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
-          \hspacebase
+          \hspacebase{}
           \hspace{0.5em}
-          \includegraphics[scale=\scale]{\dir/newlime-\Bsample-70}
-          \vspacebeforecaption
-          \caption{R-LIME ($\tau=0.70$)}\label{fig:B-rlime-70}
-          \vspacebase
+          \includegraphics[scale=\scale]{newlime-\Bsample-70}
+          \vspacebeforecaption{}
+          \caption{R-LIME ($\tau=0.70$)}
+          \vspacebase{}
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
-          \hspacebase
+          \hspacebase{}
           \hspace{-0.8em}
-          \includegraphics[scale=\scale]{\dir/newlime-\Bsample-80}
-          \vspacebeforecaption
-          \caption{R-LIME ($\tau=0.80$)}\label{fig:B-rlime-80}
+          \includegraphics[scale=\scale]{newlime-\Bsample-80}
+          \vspacebeforecaption{}
+          \caption{R-LIME ($\tau=0.80$)}
         \end{subfigure}
         \begin{subfigure}[t]{\imgwidth}
-          \hspacebase
+          \hspacebase{}
           \hspace{-0.8em}
-          \includegraphics[scale=\scale]{\dir/newlime-\Bsample-90}
-          \vspacebeforecaption
+          \includegraphics[scale=\scale]{newlime-\Bsample-90}
+          \vspacebeforecaption{}
           \caption{R-LIME ($\tau=0.90$)}\label{fig:B-rlime-90}
@@
         \caption[Explanation for Instance B by LIME and R-LIME]{%
-          Explanation for Instance B by LIME and R-LIME.
+          Explanation for Instance B by LIME and R-LIME\@.
         }\label{fig:B}
@@
 
-\subsection{Quantitative Evaluation}\label{sec:exp2}
+\subsection{Quantitative Evaluation}
 \subsubsection{Experimental Setup}
@@
 between LIME and R-LIME\@.
-Under the same settings as in \cref{sec:exp_setting},
+Under the same settings as in \cref{sec:exp-setting},
 we randomly sampled 100 instances from the test data of the recidivism dataset
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{src/experiments/exp2/box_plot}
+  \includegraphics[width=0.5\textwidth]{box_plot}
   \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
@@
     for all values of $\tau$.
-  }\label{fig:box_plot}
+  }\label{fig:box-plot}
 \end{figure}
-The results are presented in \cref{fig:box_plot},
+The results are presented in \cref{fig:box-plot},
 showing the distribution of the local accuracy of the linear classifiers
@@
       \includegraphics[width=0.7\textwidth]{visual-rlime3}
-      \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
+      \caption{R-LIME for balanced label distribution.}
     \end{subfigure}
@@
       \caption{R-LIME for imbalanced label distribution.
-      }\label{fig:imbalanced}
+      }
     \end{subfigure}
@@
       linear approximation model always outputs the majority label.
-    }
+    }\label{fig:imbalanced}
   \end{figure}
@@
 A first possible solution to this problem is modifying the loss function.
-Using weighted logistic loss or Focal Loss \cite{lin2020focal}
+Using weighted logistic loss or Focal Loss~\cite{lin2020focal}
 as the loss function might lead to the generation of more useful explanations
@@
 to limit the label distribution bias within the approximation region.
-In addition to \cref{eq:const_prec}, adding a constraint like
+In addition to \cref{eq:const-prec}, adding a constraint like
 \begin{equation}
@@
       Deviation between the estimated accuracy and the true accuracy
-      of the linear classifier learned by R-LIME.
+      of the linear classifier learned by R-LIME\@.
       The deviation $0.012\pm0.017$ was relatively small
@@
 as the best arm identification problem in multi-armed bandit framework,
-and solved using the KL-LUCB algorithm \cite{kaufmann2013information}.
+and solved using the KL-LUCB algorithm~\cite{kaufmann2013information}.
 However, this algorithm assumes that the reward distribution remains constant,
@@
 
-\ifnum\mode=0
-  \acknowledge
-  I would like to thank Associate Professor Keigo Kimura
-  of the Laboratory for Pattern Recognition and Machine Learning,
-  Division of Computer Science and Information Technology,
-  Graduate School of Information Sci.\ and Tech., Hokkaido University.
-  He provided valuable guidance
-  from setting the research theme to outlining the research method.
-  Furthermore,
-  I appreciate the various insights shared by Professor Mineichi Kudo
-  in the same laboratory.
-  Finally, I am deeply thankful to all the members of our laboratory
-  for their helpful advice and cooperation throughout the research process.
-\fi
-
-\ifnum\mode=0
-  \bibliographystyle{src/style/prml}
-\else
 \bibliographystyle{src/style/splncs04}
-\fi
 \bibliography{src/myref/myref}

### 2024-06-27 paper.tex
feat: add reviewers' comments

@@
 
+\section*{Reviewer Response}
+\subsection*{Reviewer \#1}
+Suggestions for Rebuttal:
+\begin{enumerate}
+  \setlength{\itemsep}{15pt}
+  \item Offer guidance on how to select optimal parameters for different
+        datasets and models.
+  \item Include a discussion of other model-agnostic interpretability methods,
+        such as SHAP, to provide a more comprehensive overview.
+
+        \vspace{10pt}
+        \hspace{.02\textwidth}
+        \begin{minipage}{.92\textwidth}%
+          Thank you for your suggestion. We added an overview of other
+          model-agnostic interpretability methods to the related work section.
+        \end{minipage}
+
+  \item Add experimental comparisons with more other model-agnostic \\
+        interpretability methods to better evaluate R-LIME's effectiveness.
+\end{enumerate}
+
+\subsection*{Reviewer \#4}
+The authors should kindly explain why there is not a quantitative comparison
+between their proposed method R-LIME and Anchor. The lack of the comparison
+makes it hard to evaluate the impact of the proposed model.
+
+\subsection*{Reviewer \#5}
+\begin{itemize}
+  \setlength{\itemsep}{15pt}
+  \item It would be beneficial to move the comparison of R-LIME with Anchor
+        and LIME to the Related Work section for improved clarity and
+        organization.
+  \item The authors should consider exploring a more compatible method than the
+        KL-LUCB algorithm to achieve higher accuracy. Although the experimental
+        results suggest a minor effect, there may be potential underlying issues
+        that need to be addressed.
+  \item The title of the `Challenges and Future Work' section could be more
+        aptly replaced with `Discussion' to better reflect the content.
+\end{itemize}
+
 % typeset the header of the contribution
-\maketitle              %
+\maketitle
 

### 2024-06-30 paper.tex
add anchor explanations
feat: compare coverages between anchor and rlime

@@
 
+\usepackage[export]{adjustbox} % for valign option in \includegraphics
 \usepackage{algorithm}
@@
 \usepackage{cleveref} % for \cref
+\usepackage{color,soul} % for \hl
 \usepackage{csvsimple} % for \csvreader
@@
 % set the path for figures
-\graphicspath{{./src/img}{./src/experiments/exp1}{./src/experiments/exp2}}
+\graphicspath{{./src/img}{./src/experiments}}
 
@@
 
+{%
+  \newenvironment{mycomment}{
+    \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
+      }{\end{minipage}}
   \section*{Reviewer Response}
+  We would like to appriciate all the reviewers for their very helpful comments.
+  We added an overview of other existing methods, discussion about parameter
+  selection, and comparisons between Anchor and R-LIME\@.
+  Below are suggestions from reviewers and our response.
+
   \subsection*{Reviewer \#1}
@@
           datasets and models.
+
+          \begin{mycomment}
+            Thank you for your suggestion. We added guidance on how parameters
+            should be selected in practical use cases to \cref{sec:discussion}.
+          \end{mycomment}
+
     \item Include a discussion of other model-agnostic interpretability methods,
@@
 
-        \vspace{10pt}
-        \hspace{.02\textwidth}
-        \begin{minipage}{.92\textwidth}%
+          \begin{mycomment}
             Thank you for your suggestion. We added an overview of other
-          model-agnostic interpretability methods to the related work section.
-        \end{minipage}
+            model-agnostic interpretability methods to \cref{sec:related-work}.
+          \end{mycomment}
 
@@
           interpretability methods to better evaluate R-LIME's effectiveness.
+
+          \begin{mycomment}
+            Thank you for your suggestion. We additionally conducted qualitative
+            and quantitative comparisons between Anchor and R-LIME,
+            which demonstrated that R-LIME is more effective than Anchor.
+          \end{mycomment}
   \end{enumerate}
@@
   makes it hard to evaluate the impact of the proposed model.
+
+  \begin{mycomment}
+    Thank you for your insightful comments.
+  \end{mycomment}
 
@@
           organization.
+
+          \begin{mycomment}
+            Thank you for your suggestion.
+
+            \ldots
+          \end{mycomment}
+
     \item The authors should consider exploring a more compatible method than the
@@
           that need to be addressed.
+
+          \begin{mycomment}
+            Thank you for your valuable feedback.
+            It is true that there are theoretical issues for using the KL-LUCB
+            algorithm, although our results suggest that its practical effect
+            is negligible.
+            We leave the issues to the future work because of our limited time.
+          \end{mycomment}
+
     \item The title of the `Challenges and Future Work' section could be more
           aptly replaced with `Discussion' to better reflect the content.
+
+          \begin{mycomment}
+            Thank you for your suggestion. We renamed the section to `Discussion'.
+          \end{mycomment}
   \end{itemize}
-
-% typeset the header of the contribution
+}
+
+% Reset page number and typeset title
+\newpage
+\setcounter{page}{1}
 \maketitle
@@
 
-\section{Related Work}
+\section{Related Work}\label{sec:related-work}
 \begin{figure}[tbp]
@@
 such as local interpretable model-agnostic explanations
-(LIME)~\cite{ribeiro2016why} and Anchor~\cite{ribeiro2018anchors},
+(LIME)~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors} and
+\hl{shapley additive explanations (SHAP)}~\cite{lundberg2017unified},
 explain model's behavior in the vicinity of a specific input.
@@
 
-    \def\dir{src/experiments/exp1}
+    \def\dir{src/experiments/exp1/ver1/examples/output}
     \def\Asample{0012}
@@
       \def\scale{0.315}
-      \def\imgwidth{0.495\textwidth}
+      \def\dir{exp1/ver1/examples/output}
+      \def\imgwidth{0.3\textwidth}
       \def\hspacebase{\hspace{-1.5em}}
@@
       \def\vspacebeforecaption{\vspace{-0.4em}}
-      \begin{figure}[p]
-        \centering
-        \begin{subfigure}[t]{\imgwidth}
+
+      \newcommand{\limesubfigure}[2]{
+        \begin{subfigure}[t]{\textwidth}
+          \hspace{#2}
+          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-\index{#1}}
+          \caption{LIME}\label{fig:lime-#1}
+          \vspace{1.0em}
+        \end{subfigure}
+      }
+      \newcommand{\anchorsubfigure}[1]{
+        \foreach{\a} in {70,80,90}{
+            \begin{subfigure}[t]{\textwidth}
+              \centering
+              \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-\index{#1}-\a}
+              \caption{\hl{Anchor ($\tau=0.\a$)}}
+              \vspace{1.0em}
+            \end{subfigure}
+          }
+      }
+      \newcommand{\rlimesubfigure}[3]{
+        \begin{subfigure}[t]{\textwidth}
           \hspacebase{}
-          \hspace{1.0em}
-          \includegraphics[scale=\scale]{lime-\Asample}
+          \hspace{#3}
+          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-\index{#1}-#2}
           \vspacebeforecaption{}
-          \caption{LIME}\label{fig:A-lime}
+          \caption{R-LIME ($\tau=0.#2$)}\label{fig:rlime-#1-#2}
           \vspacebase{}
         \end{subfigure}
-        \begin{subfigure}[t]{\imgwidth}
-          \hspacebase{}
-          \hspace{0.5em}
-          \includegraphics[scale=\scale]{newlime-\Asample-70}
-          \vspacebeforecaption{}
-          \caption{R-LIME ($\tau=0.70$)}\label{fig:A-rlime-70}
-          \vspacebase{}
-        \end{subfigure}
-        \begin{subfigure}[t]{\imgwidth}
-          \hspacebase{}
-          \includegraphics[scale=\scale]{newlime-\Asample-80}
-          \vspacebeforecaption{}
-          \caption{R-LIME ($\tau=0.80$)}
-        \end{subfigure}
-        \begin{subfigure}[t]{\imgwidth}
-          \hspacebase{}
-          \hspace{-0.5em}
-          \includegraphics[scale=\scale]{newlime-\Asample-90}
-          \vspacebeforecaption{}
-          \caption{R-LIME ($\tau=0.90$)}
+      }
+      \begin{figure}[t]
+        \begin{subfigure}[t]{0.45\textwidth}
+          \centering
+          \limesubfigure{0}{-10pt}
+          \anchorsubfigure{0}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[t]{0.45\textwidth}
+          \rlimesubfigure{0}{70}{-10pt}
+
+          \vspace{12pt}
+          \rlimesubfigure{0}{90}{-22pt}
         \end{subfigure}
@@
       \end{figure}
-      \begin{figure}[p]
-        \centering
-        \begin{subfigure}[t]{\imgwidth}
-          \hspacebase{}
-          \hspace{-0.7em}
-          \includegraphics[scale=\scale]{lime-\Bsample}
-          \vspacebeforecaption{}
-          \caption{LIME}\label{fig:B-lime}
-          \vspacebase{}
-        \end{subfigure}
-        \begin{subfigure}[t]{\imgwidth}
-          \hspacebase{}
-          \hspace{0.5em}
-          \includegraphics[scale=\scale]{newlime-\Bsample-70}
-          \vspacebeforecaption{}
-          \caption{R-LIME ($\tau=0.70$)}
-          \vspacebase{}
-        \end{subfigure}
-        \begin{subfigure}[t]{\imgwidth}
-          \hspacebase{}
-          \hspace{-0.8em}
-          \includegraphics[scale=\scale]{newlime-\Bsample-80}
-          \vspacebeforecaption{}
-          \caption{R-LIME ($\tau=0.80$)}
-        \end{subfigure}
-        \begin{subfigure}[t]{\imgwidth}
-          \hspacebase{}
-          \hspace{-0.8em}
-          \includegraphics[scale=\scale]{newlime-\Bsample-90}
-          \vspacebeforecaption{}
-          \caption{R-LIME ($\tau=0.90$)}\label{fig:B-rlime-90}
+      \begin{figure}[t]
+        \begin{subfigure}[t]{0.45\textwidth}
+          \limesubfigure{1}{-30pt}
+          \anchorsubfigure{1}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[t]{0.45\textwidth}
+          \rlimesubfigure{1}{70}{-10pt}
+
+          \vspace{18pt}
+          \rlimesubfigure{1}{90}{-25pt}
         \end{subfigure}
@@
 
-Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) provide insights
+Explanations generated by LIME (\cref{fig:lime-0,fig:lime-1}) provide insights
 that having a prior offenses (\emph{Priors}),
@@
 For example, the explanation for instance A
-under $\tau=0.70$ (\cref{fig:A-rlime-70}) indicates that it is applicable
+under $\tau=0.70$ (\cref{fig:rlime-0-70}) indicates that it is applicable
 only to married prisoner (\emph{Married} $=$\emph{Yes}).
@@
 For example, the coverage of the explanation for instance B under $\tau=0.90$
-(\cref{fig:B-rlime-90}) is 0.01\%,
+(\cref{fig:rlime-1-90}) is 0.01\%,
 indicating that the decision boundaries around instance B are complex,
@@
 
-\subsection{Quantitative Evaluation}
+\begin{figure}[t]
+  \begin{subfigure}[t]{0.48\textwidth}
+    \centering
+    \includegraphics[scale=0.36,valign=t]{exp2/box_plot}
+    \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
+      Comparison of local accuracy between LIME and R-LIME\@.
+      R-LIME achieved higher and less variable accuracy compared to LIME\@.
+    }\label{fig:box-plot}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{0.48\textwidth}
+    \centering
+    \includegraphics[scale=0.35,valign=t]{exp2b/comp_cov}
+    \vspace{3pt}
+    \caption[Comparison of Coverage between Anchor and R-LIME]{%
+      \hl{%
+        Comparison of coverage between Anchor and R-LIME\@.
+        R-LIME achieved higher coverage compared to Anchor
+        for almost values of $\tau$, especially for relatively small $\tau$.
+      }
+    }\label{fig:coverage}
+  \end{subfigure}
+  \caption{Comparison of existing methods (LIME, Anchor) and R-LIME.}
+\end{figure}
+
+\subsection{Quantitative Evaluation: LIME vs. R-LIME}
+
 \subsubsection{Experimental Setup}
@@
 obtained by R-LIME and calculated the local accuracy of both methods.
+
 \subsubsection{Experimental Results}
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=0.5\textwidth]{box_plot}
-  \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
-    Comparison of local accuracy between LIME and R-LIME\@.
-    R-LIME achieved higher and less variable accuracy compared to LIME
-    for all values of $\tau$.
-  }\label{fig:box-plot}
-\end{figure}
 The results are presented in \cref{fig:box-plot},
@@
 
-\section{Challenges and Future Work}
+\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}
+\subsubsection{\hl{Experimental Setup}}
+\hl{
+  To demonstrate that R-LIME explanations are more general than Anchor,
+  we conducted a comparison of the coverage of explanations
+  between Anchor and R-LIME\@.
+  Under the same settings as in
+}\cref{sec:exp-setting},
+\hl{
+  we generated Anchor and R-LIME explanations
+  for 100 instances from the test data of the recidivism dataset,
+  under the values of $\tau=0.70,0.80,0.90$.
+}
+
+\subsubsection{\hl{Experimental Results}}
+\hl{The results are presented in} \cref{fig:coverage},
+\hl{
+  showing the coverage of the explanations by Anchor and R-LIME\@.
+  The coverage of explanations generated by R-LIME is higher compared to Anchor
+  for almost values of $\tau$, especially for relatively small $\tau$.
+  It is because of the flexibility of the linear approximation models learned by
+  R-LIME, which captures the decision boundary more precisely.
+  In contrast,
+  Anchor uses only the intervals of each feature discretized in advance,
+  which cannot capture the decision boundary flexibly and makes its scope narrow.
+}
+
+\section{\hl{Discussion}}\label{sec:discussion}
 {%

### 2024-06-30 src/experiments/exp2/box_plot.py

@@ -17,11 +17,12 @@ def main() -> None:
         accs.append(lime_acc)
         accs.append(rlime_acc)
 
+    plt.rcParams["font.size"] = 15
     bp = plt.boxplot(
         accs,
-        labels=["LIME", "R-LIME"] * 3,
+        tick_labels=["LIME", "R-LIME"] * 3,
         widths=0.7,
-        positions=[1, 2, 3.5, 4.5, 6, 7],
+        positions=[1, 2.2, 3.7, 4.9, 6.4, 7.6],
         showfliers=False,
         patch_artist=True,
     )
@@ -31,17 +32,18 @@ def main() -> None:
         med.set_color("black")
 
     for i, tau_percent in enumerate([70, 80, 90]):
-        plt.text(1.0 + 2.5 * i, 0.33, r"$\tau=$" + f"0.{tau_percent}")
+        plt.text(0.9 + 2.7 * i, 0.30, r"$\tau=$" + f"0.{tau_percent}")
 
     plt.hlines(
         [0.7, 0.8, 0.9],
-        [0, 2.5, 5],
-        [3.0, 5.5, 8],
+        [0, 2.7, 5.4],
+        [3.0, 5.7, 8.4],
         colors="black",
         linestyles="dashed",
     )
     # plt.title("Accuracy of LIME and R-LIME")
     plt.ylabel("Accuracy")
+    plt.tight_layout()
     plt.savefig("box_plot.eps")
 
 

### 2024-06-30 src/experiments/exp2/src/exp2/__init__.py

@@ -1,0 +1,2 @@
+def hello() -> str:
+    return "Hello from exp2!"

### 2024-06-30 src/experiments/exp2b/comp_cov.py

@@ -1,0 +1,110 @@
+"""Compare coverage of the explanations generated by Anchor and R-LIME."""
+
+import csv
+from pathlib import Path
+from statistics import mean, stdev
+
+import matplotlib.pyplot as plt
+
+EXAMPLES_DIR_NAME = "src/rlime-examples/examples"
+
+sample_num = 100
+
+
+def get_weights(idx: int) -> list[float] | None:
+    """Get the weights of LIME for the given sample."""
+    csv_name = EXAMPLES_DIR_NAME + f"/lime-{idx:04d}.csv"
+    try:
+        with Path(csv_name).open() as f:
+            reader = csv.reader(f)
+            return [float(x) for x in next(reader)]
+    except FileNotFoundError:
+        return None
+
+
+def get_rlime_weights(idx: int, tau: int) -> list[float] | None:
+    """Get the weights of R-LIME for the given sample."""
+    csv_name = EXAMPLES_DIR_NAME + f"/newlime-{idx:04d}-{tau:02d}.csv"
+    try:
+        with Path(csv_name).open() as f:
+            reader = csv.reader(f)
+            return [float(x) for x in next(reader)]
+    except FileNotFoundError:
+        return None
+
+
+def get_anchor_cov(idx: int, tau: int) -> float | None:
+    """Get the coverage of Anchor for the given sample."""
+    csv_name = EXAMPLES_DIR_NAME + f"/anchor-{idx:04d}-{tau:02d}.csv"
+    try:
+        with Path(csv_name).open() as f:
+            reader = csv.reader(f)
+            next(reader)  # Skip the weights.
+            return float(next(reader)[1])  # Skip the accuracy.
+    except FileNotFoundError:
+        return None
+
+
+def get_rlime_cov(idx: int, tau: int) -> float | None:
+    """Get the coverage of R-LIME for the given sample."""
+    csv_name = EXAMPLES_DIR_NAME + f"/newlime-{idx:04d}-{tau:02d}.csv"
+    try:
+        with Path(csv_name).open() as f:
+            reader = csv.reader(f)
+            next(reader)  # Skip the weights.
+            next(reader)  # Skip the rule.
+            return float(next(reader)[1])  # Skip the accuracy.
+    except FileNotFoundError:
+        return None
+
+
+def main() -> None:
+    """Compare coverages of the explanations for Anchor and R-LIME.
+
[…]

### 2024-06-30 src/experiments/exp2b/lime_vs_rlime.py

@@ -1,0 +1,168 @@
+"""Compare LIME and R-LIME on the recidivism dataset."""
+
+import csv
+import multiprocessing
+from functools import partial
+from pathlib import Path
+
+import numpy as np
+from rlime import rlime_lime
+from rlime.rlime_types import Dataset, IntArray, Rule
+from rlime.sampler import Sampler
+from rlime.utils import get_trg_sample, load_dataset
+from sklearn.ensemble import RandomForestClassifier  # type: ignore
+from sklearn.preprocessing import StandardScaler
+
+EXAMPLES_DIR_NAME = "src/rlime-examples/examples"
+
+
+def main() -> None:
+    """Main function."""
+    # Load the dataset.
+    dataset = load_dataset("recidivism", "src/datasets/", balance=True)
+
+    # Learn the black box model.
+    black_box = RandomForestClassifier(n_estimators=100, n_jobs=1)
+    black_box.fit(dataset.train, dataset.labels_train)
+
+    # Get the target instances.
+    sample_num = 100
+
+    for tau in [0.90]:
+        print(f"tau = {tau:.2f}")
+
+        result_list = multiprocessing.Manager().list()
+
+        func = partial(
+            compare_lime_and_newlime,
+            dataset=dataset,
+            black_box=black_box,
+            tau=tau,
+            result_list=result_list,
+        )
+
+        with multiprocessing.Pool() as pool:
+            pool.map(func, range(sample_num))
+
+        lime_acc, rlime_acc = zip(*result_list)
+        print("LIME")
+        print(f"  Mean: {np.mean(lime_acc):.4f}")
+        print(f"  Std : {np.std(lime_acc):.4f}")
+        print("R-LIME")
+        print(f"  Mean: {np.mean(rlime_acc):.4f}")
+        print(f"  Std : {np.std(rlime_acc):.4f}")
+
+        # Save the results to a CSV file.
+        with open(f"{int(tau*100)}.csv", "w", encoding="utf-8") as f:
+            writer = csv.writer(f)
+            writer.writerow(lime_acc)
+            writer.writerow(rlime_acc)
+
+
+def calc_accuracy(
+    samples: IntArray,
+    labels: IntArray,
+    lime_weights: list[float],
+    rlime_weights: list[float],
+    lime_scaler: StandardScaler,
+) -> tuple[float, float]:
+    """Calculate the precision of LIME and R-LIME.
+
+    Parameters
+    ----------
+    samples : IntArray
+        The samples to evaluate.
[…]

### 2024-07-04 paper.tex
ICPR 1st revised version

@@
 
+\newenvironment{mycomment}{
+  \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
+    }{\end{minipage}}
+
+\section*{Reviewer Response}
+We deeply appriciate all the reviewers who made valuable and insightful comments
+on our paper and gave us the opportunity to submit a revised version.
+We have done our best for the revision according to their comments as shown below.
+We also would like to thank in advance all the reviewers for reconsidering
+the suitability of our revised paper for the conference.
+
+\subsection*{Summary of revisions}
+We would like to appriciate all the reviewers for their clear and insightful
+comments.
+We improved our paper from the original version according to their comments.
+The major revision points are listed as follows:
+\begin{enumerate}
+  \item We added an overview of other existing methods to \cref{sec:related-work}.
+  \item We added discussion about parameter selection in \cref{sec:param}.
+  \item We conducted comparisons between Anchor and R-LIME to \cref{sec:related-work}.
+\end{enumerate}
+Please see below for a point-by-point response to each reviewer's comments.
+
+\subsection*{Responding to Reviewer \#1}
+Suggestions for Rebuttal:
+\begin{enumerate}
+  \setlength{\itemsep}{15pt}
+  \item Offer guidance on how to select optimal parameters for different
+        datasets and models.
+
+        \begin{mycomment}
+          We would appreciate for your suggestion.
+          We added \cref{sec:param} as a guidance on how parameters should be
+          selected in practice.
+        \end{mycomment}
+
+  \item Include a discussion of other model-agnostic interpretability methods,
+        such as SHAP, to provide a more comprehensive overview.
+
+        \begin{mycomment}
+          Thank you for your valuable suggestion.
+          We should add an overview of other model-agnostic interpretability
+          methods, but we only added names of some other methods to
+          \cref{sec:related-work} because of lack of space.
+        \end{mycomment}
+
+  \item Add experimental comparisons with more other model-agnostic \\
+        interpretability methods to better evaluate R-LIME's effectiveness.
+
+        \begin{mycomment}
+          We would like to appriciate your sharp observations.
+          We additionally conducted qualitative and quantitative comparisons
+          between Anchor and R-LIME,
+          which demonstrated that R-LIME generates more informative and
+          general explanations than Anchor (see \cref{sec:exp-qual,sec:exp-anchor}).
+        \end{mycomment}
+\end{enumerate}
+\subsection*{Responding to Reviewer \#4}
+The authors should kindly explain why there is not a quantitative comparison
+between their proposed method R-LIME and Anchor. The lack of the comparison
+makes it hard to evaluate the impact of the proposed model.
+
+\begin{mycomment}
+  We would appreciate for your insightful comments.
+  We additionally conducted qualitative and quantitative comparisons
+  between Anchor and R-LIME,
+  which demonstrated that R-LIME generates more informative and
+  general explanations than Anchor (see \cref{sec:exp-qual,sec:exp-anchor}).
+\end{mycomment}
+
+\subsection*{Responding to Reviewer \#5}
+\begin{itemize}
+  \setlength{\itemsep}{15pt}
+  \item It would be beneficial to move the comparison of R-LIME with Anchor
+        and LIME to the Related Work section for improved clarity and
+        organization.
+
+        \begin{mycomment}
+          We would like to appriciate for your insightful suggestion.
+          We interpreted your suggestrion to mean that we should move
+          \cref{fig:example} and its explanation to \cref{sec:related-work}.
+          We discussed about the most understandable structure of our paper.
+          And for clarity, we concluded that we should present effectiveness
+          of R-LIME compared to existing methods closely related to our method
+          in \cref{sec:introduction},
+          before we overview other existing methods in \cref{sec:related-work}.
+        \end{mycomment}
+
+  \item The authors should consider exploring a more compatible method than the
+        KL-LUCB algorithm to achieve higher accuracy. Although the experimental
+        results suggest a minor effect, there may be potential underlying issues
+        that need to be addressed.
+
+        \begin{mycomment}
+          Thank you for your valuable feedback.
+          It is true that we must address theoretical issues for using
+          KL-LUCB algorithm, although our results suggest that its practical
+          effect is negligible.
+          We focus on presenting our novel framework for local interpretability,
+          not on the detailed algorithm.
+          Thus, we leave the issues for future work because of lack of space.
+          But we deeply appreciate for your sharp observations.
+        \end{mycomment}
+
+  \item The title of the `Challenges and Future Work' section could be more
+        aptly replaced with `Discussion' to better reflect the content.
+
+        \begin{mycomment}
+          Thank you for your suggestion. We renamed the section to `Discussion'
+          for clearly reflecting the content.
+        \end{mycomment}
+\end{itemize}
+
+\newcommand{\sampleindex}[1]{\ifnum#1=0 \Asample\else\Bsample\fi}
+\def\AB#1{\ifnum#1=0 A\else B\fi}
+
+\def\paper{
+
 % The title of the paper
@@
 
-{%
-  \newenvironment{mycomment}{
-    \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
-      }{\end{minipage}}
-  \section*{Reviewer Response}
-  We would like to appriciate all the reviewers for their very helpful comments.
-  We added an overview of other existing methods, discussion about parameter
-  selection, and comparisons between Anchor and R-LIME\@.
-  Below are suggestions from reviewers and our response.
-
-  \subsection*{Reviewer \#1}
-  Suggestions for Rebuttal:
-  \begin{enumerate}
-    \setlength{\itemsep}{15pt}
-    \item Offer guidance on how to select optimal parameters for different
-          datasets and models.
-
-          \begin{mycomment}
-            Thank you for your suggestion. We added guidance on how parameters
-            should be selected in practical use cases to \cref{sec:discussion}.
-          \end{mycomment}
-
-    \item Include a discussion of other model-agnostic interpretability methods,
-          such as SHAP, to provide a more comprehensive overview.
-
-          \begin{mycomment}
-            Thank you for your suggestion. We added an overview of other
-            model-agnostic interpretability methods to \cref{sec:related-work}.
-          \end{mycomment}
-
-    \item Add experimental comparisons with more other model-agnostic \\
-          interpretability methods to better evaluate R-LIME's effectiveness.
-
-          \begin{mycomment}
-            Thank you for your suggestion. We additionally conducted qualitative
-            and quantitative comparisons between Anchor and R-LIME,
-            which demonstrated that R-LIME is more effective than Anchor.
-          \end{mycomment}
-  \end{enumerate}
-
-  \subsection*{Reviewer \#4}
-  The authors should kindly explain why there is not a quantitative comparison
-  between their proposed method R-LIME and Anchor. The lack of the comparison
-  makes it hard to evaluate the impact of the proposed model.
-
-  \begin{mycomment}
-    Thank you for your insightful comments.
-  \end{mycomment}
-
-  \subsection*{Reviewer \#5}
-  \begin{itemize}
-    \setlength{\itemsep}{15pt}
-    \item It would be beneficial to move the comparison of R-LIME with Anchor
-          and LIME to the Related Work section for improved clarity and
-          organization.
-
-          \begin{mycomment}
-            Thank you for your suggestion.
-
-            \ldots
-          \end{mycomment}
-
-    \item The authors should consider exploring a more compatible method than the
-          KL-LUCB algorithm to achieve higher accuracy. Although the experimental
-          results suggest a minor effect, there may be potential underlying issues
-          that need to be addressed.
-
-          \begin{mycomment}
-            Thank you for your valuable feedback.
-            It is true that there are theoretical issues for using the KL-LUCB
-            algorithm, although our results suggest that its practical effect
-            is negligible.
-            We leave the issues to the future work because of our limited time.
-          \end{mycomment}
-
-    \item The title of the `Challenges and Future Work' section could be more
-          aptly replaced with `Discussion' to better reflect the content.
-
-          \begin{mycomment}
-            Thank you for your suggestion. We renamed the section to `Discussion'.
-          \end{mycomment}
-  \end{itemize}
-}
-
-% Reset page number and typeset title
-\newpage
-\setcounter{page}{1}
 \maketitle
@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:introduction}
 In recent years,
@@
 there has been extensive research in the field of post-hoc explanations
-for machine learning models~\cite{%
-  guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.
+for machine learning models
+~\cite{guidotti2018local,ribeiro2016why,ribeiro2018anchors}.
 Existing post-hoc explanation methods are categorized
@@
 to apply the same method to models with different structures.
-On the other hand,
-model-agnostic methods use only the output of the model.
+In contrast,
+model-agnostic methods use only the model's output.
 Although they are applicable to any model,
@@
 In contrast, local methods,
-such as local interpretable model-agnostic explanations
+such as \hl{indivisual conditional expectation (ICE)}~\cite{goldstein2015peeking},
+local interpretable model-agnostic explanations
 (LIME)~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors} and
@@
 
-\subsection{Qualitative Evaluation}
+\subsection{Qualitative Evaluation}\label{sec:exp-qual}
 \subsubsection{Experimental Setup}\label{sec:exp-setting}
@@
     \def\Bsample{0011}
-    \def\index#1{\ifnum#1=0 \Asample\else\Bsample\fi}
 
     {%
-      \def\AB#1{\ifnum#1=0 A\else B\fi}
       \renewcommand{\arraystretch}{1.02}
@@
                 \csvreader[no head, late after line= \\]{%
-                  \dir/\index{\a}.csv
+                  \dir/\sampleindex{\a}.csv
                 }{}{%
@@
     }
-    {%
-      \def\scale{0.315}
-      \def\dir{exp1/ver1/examples/output}
-      \def\imgwidth{0.3\textwidth}
-      \def\hspacebase{\hspace{-1.5em}}
-      \def\vspacebase{\vspace{0.5em}}
-      \def\vspacebeforecaption{\vspace{-0.4em}}
-
-      \newcommand{\limesubfigure}[2]{
-        \begin{subfigure}[t]{\textwidth}
-          \hspace{#2}
-          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-\index{#1}}
-          \caption{LIME}\label{fig:lime-#1}
-          \vspace{1.0em}
-        \end{subfigure}
-      }
-      \newcommand{\anchorsubfigure}[1]{
-        \foreach{\a} in {70,80,90}{
-            \begin{subfigure}[t]{\textwidth}
-              \centering
-              \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-\index{#1}-\a}
-              \caption{\hl{Anchor ($\tau=0.\a$)}}
-              \vspace{1.0em}
-            \end{subfigure}
-          }
-      }
-      \newcommand{\rlimesubfigure}[3]{
-        \begin{subfigure}[t]{\textwidth}
-          \hspacebase{}
-          \hspace{#3}
-          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-\index{#1}-#2}
-          \vspacebeforecaption{}
-          \caption{R-LIME ($\tau=0.#2$)}\label{fig:rlime-#1-#2}
-          \vspacebase{}
-        \end{subfigure}
-      }
-      \begin{figure}[t]
-        \begin{subfigure}[t]{0.45\textwidth}
-          \centering
-          \limesubfigure{0}{-10pt}
-          \anchorsubfigure{0}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[t]{0.45\textwidth}
-          \rlimesubfigure{0}{70}{-10pt}
-
-          \vspace{12pt}
-          \rlimesubfigure{0}{90}{-22pt}
-        \end{subfigure}
-        \caption[Explanation for Instance A by LIME and R-LIME]{%
-          Explanation for Instance A by LIME and R-LIME\@.
-        }\label{fig:A}
-      \end{figure}
-      \begin{figure}[t]
-        \begin{subfigure}[t]{0.45\textwidth}
-          \limesubfigure{1}{-30pt}
-          \anchorsubfigure{1}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[t]{0.45\textwidth}
-          \rlimesubfigure{1}{70}{-10pt}
-
-          \vspace{18pt}
-          \rlimesubfigure{1}{90}{-25pt}
-        \end{subfigure}
-        \caption[Explanation for Instance B by LIME and R-LIME]{%
-          Explanation for Instance B by LIME and R-LIME\@.
-        }\label{fig:B}
-      \end{figure}
-    }
-  }
+  }
+
+\input{src/fig-examples}
 \subsubsection{Experimental Results}
@@
 
+\hl{
+  Anchor provides conditions for the model's output to be fixed with high
+  probability.
+  For example,
+  the explanation for instance A under $\tau=0.70$
+} (\cref{fig:anchor-0-70})
+\hl{
+  means that the model will predict with 75.66 \% probability
+  that the prisoner will commit no more crimes
+  when a prisoner is older than 33 and has one prior offense.
+  Although it clearly provides the explanation's application scope,
+  it does not provide details about how these conditions affect the model's output.
+}
+
 In contrast, R-LIME expresses the application scope of explanations
@@
 
+\vspace{-1pt}
 \subsection{Quantitative Evaluation: LIME vs. R-LIME}
@@
 
+\vspace{-5pt}
 \subsubsection{Experimental Results}
@@
 
-\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}
+\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}\label{sec:exp-anchor}
 \subsubsection{\hl{Experimental Setup}}
@@
 
-\section{\hl{Discussion}}\label{sec:discussion}
+\section{\hl{Discussion}}
  {%
@@
 our results suggest that the deviation is not significant in practice.
+
+\subsection{\hl{Parameter Selection}}\label{sec:param}
+
+\hl{
+  R-LIME requires some hyperparameters to be selected by users,
+  such as the threshold of accuracy $\tau$, beam width $B$, tolerance $\epsilon$
+  and confidence level $\delta$.
+  $B$ should be large and $\epsilon$ and $\delta$ should be small for
+  accurate results, as long as the computational cost is acceptable.
+  $\tau$ should be carefully selected by users, sometimes interactively,
+  considering the tradeoff between
+  the accuracy and generality of the explanation.
+}
 
@@
 
+\newpage
 \bibliographystyle{src/style/splncs04}
 \bibliography{src/myref/myref}
+}
+
+% Reset page number and typeset title
+\newpage
+\setcounter{page}{1}
+\paper{}
+\renewcommand{\hl}[1]{#1}
+% \newpage
+% \setcounter{page}{1}
+% \paper{}
 

### 2024-07-04 src/fig-examples.tex
ICPR 1st revised version

\def\scale{0.315}
\def\dir{exp1/ver1/examples/output}
\def\imgwidth{0.3\textwidth}
\def\hspacebase{\hspace{-1.5em}}
\def\vspacebase{\vspace{0.5em}}
\def\vspacebeforecaption{\vspace{-0.4em}}

\newcommand{\limesubfigure}[2]{
	\begin{subfigure}[t]{\textwidth}
		\hspace{#2}
		\includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-\sampleindex{#1}}
		\caption{LIME}\label{fig:lime-#1}
		\vspace{1.0em}
	\end{subfigure}
}
\newcommand{\anchorsubfigure}[1]{
	\foreach{\a} in {70,80,90}{
			\begin{subfigure}[t]{\textwidth}
				\centering
				\includegraphics[scale=0.33]{exp1/ver2/examples/anchor-\sampleindex{#1}-\a}
				\caption{\hl{Anchor ($\tau=0.\a$)}}
				\vspace{1.0em}
			\end{subfigure}
		}
}
\newcommand{\rlimesubfigure}[3]{
}
\begin{figure}[t]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\begin{subfigure}[t]{\textwidth}
			\hspace{-10pt}
			\includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0012}
			\caption{LIME}\label{fig:lime-0}
			\vspace{1.0em}
		\end{subfigure}

		\vspace{10pt}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-70}  % chktex 8
			\caption{\hl{Anchor ($\tau=0.70$)}}\label{fig:anchor-0-70}
			\vspace{1.0em}
		\end{subfigure}

		\vspace{10pt}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-90}  % chktex 8
			\caption{\hl{Anchor ($\tau=0.90$)}}\label{fig:anchor-0-90}
			\vspace{1.0em}
		\end{subfigure}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{0.45\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\hspacebase{}
			\hspace{-5pt}
			\includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-70}  % chktex 8
			\vspacebeforecaption{}
			\caption{R-LIME ($\tau=0.70$)}\label{fig:rlime-0-70}
			\vspacebase{}
		\end{subfigure}
		\begin{subfigure}[t]{\textwidth}
			\hspacebase{}
			\hspace{-17pt}
			\includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-90}  % chktex 8
			\vspacebeforecaption{}
			\caption{R-LIME ($\tau=0.90$)}
			\vspacebase{}
		\end{subfigure}
	\end{subfigure}
	\caption[Explanation for Instance A by LIME and R-LIME]{%
		Explanation for Instance A by LIME and R-LIME\@.
	}\label{fig:A}
\end{figure}
\begin{figure}[t]
	\begin{subfigure}[t]{0.45\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\hspace{-26.5pt}
			\includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0011}
			\caption{LIME}\label{fig:lime-1}
			\vspace{1.0em}
		\end{subfigure}

		\vspace{10pt}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-70}  % chktex 8
			\caption{\hl{Anchor ($\tau=0.70$)}}\label{fig:anchor-1-70}
			\vspace{1.0em}
		\end{subfigure}

		\vspace{10pt}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-90}  % chktex 8
			\caption{\hl{Anchor ($\tau=0.90$)}}\label{fig:anchor-1-90}
			\vspace{1.0em}
		\end{subfigure}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{0.45\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\hspacebase{}
			\hspace{-5pt}
			\includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-70}  % chktex 8
			\vspacebeforecaption{}
			\caption{R-LIME ($\tau=0.90$)}
			\vspacebase{}
		\end{subfigure}
		\begin{subfigure}[t]{\textwidth}
			\hspacebase{}
			\hspace{-20pt}
			\includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-90}  % chktex 8
			\vspacebeforecaption{}
			\caption{R-LIME ($\tau=0.90$)}\label{fig:rlime-1-90}
			\vspacebase{}
		\end{subfigure}
	\end{subfigure}
	\caption[Explanation for Instance B by LIME and R-LIME]{%
		Explanation for Instance B by LIME and R-LIME\@.
	}\label{fig:B}
\end{figure}

### 2024-07-04 src/experiments/exp2b/box_plot.py

@@ -1,0 +1,61 @@
+"""Module providing a function creating a box plot of the data in a file."""
+
+import csv
+
+import matplotlib.pyplot as plt
+
+
+def main() -> None:
+    """Main function of the module."""
+
+    plt.figure()
+
+    accs = []
+    for tau_percent in [70, 80, 90]:
+        file_name = f"{tau_percent}.csv"
+        lime_acc, rlime_acc = read_data(file_name)
+        accs.append(lime_acc)
+        accs.append(rlime_acc)
+
+    plt.rcParams["font.size"] = 15
+    bp = plt.boxplot(
+        accs,
+        tick_labels=["LIME", "R-LIME"] * 3,
+        widths=0.7,
+        positions=[1, 2.2, 3.7, 4.9, 6.4, 7.6],
+        showfliers=False,
+        patch_artist=True,
+    )
+    colors = ["#377eb8", "#4daf4a"] * 3
+    for patch, med, color in zip(bp["boxes"], bp["medians"], colors):
+        patch.set_facecolor(color)
+        med.set_color("black")
+
+    for i, tau_percent in enumerate([70, 80, 90]):
+        plt.text(0.9 + 2.7 * i, 0.30, r"$\tau=$" + f"0.{tau_percent}")
+
+    plt.hlines(
+        [0.7, 0.8, 0.9],
+        [0, 2.7, 5.4],
+        [3.0, 5.7, 8.4],
+        colors="black",
+        linestyles="dashed",
+    )
+    # plt.title("Accuracy of LIME and R-LIME")
+    plt.ylabel("Accuracy")
+    plt.tight_layout()
+    plt.savefig("box_plot.eps")
+
+
+def read_data(filename: str) -> tuple[list[float], list[float]]:
+    """Reads data from a file and returns it as a list of lists."""
+    data = []
+    with open(filename, newline="", encoding="utf-8") as file:
+        reader = csv.reader(file, delimiter=",")
+        for row in reader:
+            data.append([float(x) for x in row])
+    return data[0], data[1]
+
+
+if __name__ == "__main__":
+    main()

### 2024-07-04 src/experiments/exp2b/comp_cov.py

@@ -7,8 +7,7 @@ from statistics import mean, stdev
 import matplotlib.pyplot as plt
 
 EXAMPLES_DIR_NAME = "src/rlime-examples/examples"
-
-sample_num = 100
+SAMPLE_NUM = 703
 
 
 def get_weights(idx: int) -> list[float] | None:
@@ -69,9 +68,9 @@ def main() -> None:
 
     tau_list = [65, 70, 75, 80, 85, 90]
     for tau in tau_list:
-        anchor_covs = [get_anchor_cov(idx, tau) for idx in range(sample_num)]
+        anchor_covs = [get_anchor_cov(idx, tau) for idx in range(SAMPLE_NUM)]
         anchor_covs = [x for x in anchor_covs if x is not None]
-        rlime_covs = [get_rlime_cov(idx, tau) for idx in range(sample_num)]
+        rlime_covs = [get_rlime_cov(idx, tau) for idx in range(SAMPLE_NUM)]
         rlime_covs = [x for x in rlime_covs if x is not None]
 
         print("----")

### 2024-07-04 src/experiments/exp2b/lime_vs_rlime.py

@@ -1,8 +1,6 @@
 """Compare LIME and R-LIME on the recidivism dataset."""
 
 import csv
-import multiprocessing
-from functools import partial
 from pathlib import Path
 
 import numpy as np
@@ -31,18 +29,22 @@ def main() -> None:
     for tau in [0.90]:
         print(f"tau = {tau:.2f}")
 
-        result_list = multiprocessing.Manager().list()
+        # result_list = multiprocessing.Manager().list()
 
-        func = partial(
-            compare_lime_and_newlime,
-            dataset=dataset,
-            black_box=black_box,
-            tau=tau,
-            result_list=result_list,
-        )
+        # func = partial(
+        #     compare_lime_and_newlime,
+        #     dataset=dataset,
+        #     black_box=black_box,
+        #     tau=tau,
+        #     result_list=result_list,
+        # )
 
-        with multiprocessing.Pool() as pool:
-            pool.map(func, range(sample_num))
+        # with multiprocessing.Pool() as pool:
+        #     pool.map(func, range(sample_num))
+
+        result_list: list[tuple[float, float]] = []
+        for idx in range(sample_num):
+            compare_lime_and_newlime(idx, dataset, black_box, tau, result_list)
 
         lime_acc, rlime_acc = zip(*result_list)
         print("LIME")
@@ -65,6 +67,7 @@ def calc_accuracy(
     lime_weights: list[float],
     rlime_weights: list[float],
     lime_scaler: StandardScaler,
+    rlime_scaler: StandardScaler,
 ) -> tuple[float, float]:
     """Calculate the precision of LIME and R-LIME.
 
@@ -86,9 +89,6 @@ def calc_accuracy(
     tuple[float, float]
         The precision of LIME and R-LIME.
     """
-    rlime_scaler = StandardScaler()
-    rlime_scaler.fit(samples)
-
     # Get predictions of LIME and R-LIME.
     lime_pred = np.dot(lime_scaler.transform(samples), lime_weights) > 0
     rlime_pred = np.dot(rlime_scaler.transform(samples), rlime_weights) > 0
@@ -132,6 +132,9 @@ def compare_lime_and_newlime(
 
     lime_weights, scaler = rlime_lime.explain(trg, sampler, 5000)
 
+    scale_samples, _ = sampler.sample(10000, ())
+    rlime_scaler = StandardScaler().fit(scale_samples)
+
     def get_rlime_weights() -> tuple[list[float], Rule] | None:
         try:
             csv_name = (
[…]

### 2024-07-09 paper.tex
modify details on paper

@@
   \item We added discussion about parameter selection in \cref{sec:param}.
-  \item We conducted comparisons between Anchor and R-LIME to \cref{sec:related-work}.
+  \item We conducted qualitative and quantitative comparisons
+        between Anchor and R-LIME in \cref{sec:exp-qual,sec:exp-anchor}.
 \end{enumerate}
@@
 
-\input{src/fig-examples}
+  {%
+    \def\scale{0.315}
+    \def\dir{exp1/ver1/examples/output}
+    \def\imgwidth{0.3\textwidth}
+    \def\hspacebase{\hspace{-1.5em}}
+    \def\vspacebase{\vspace{0.5em}}
+    \def\vspacebeforecaption{\vspace{-0.4em}}
+    \begin{figure}[t]
+      \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \begin{subfigure}[t]{\textwidth}
+          \hspace{-10pt}
+          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0012}
+          \caption{LIME}\label{fig:lime-0}
+          \vspace{1.0em}
+        \end{subfigure}
+
+        \vspace{10pt}
+        \begin{subfigure}[t]{\textwidth}
+          \centering
+          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-70}  % chktex 8
+          \caption{\hl{Anchor ($\tau=0.70$)}}\label{fig:anchor-0-70}
+          \vspace{1.0em}
+        \end{subfigure}
+
+        \vspace{10pt}
+        \begin{subfigure}[t]{\textwidth}
+          \centering
+          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-90}  % chktex 8
+          \caption{\hl{Anchor ($\tau=0.90$)}}
+          \vspace{1.0em}
+        \end{subfigure}
+      \end{subfigure}
+      \hfill
+      \begin{subfigure}[t]{0.45\textwidth}
+        \begin{subfigure}[t]{\textwidth}
+          \hspacebase{}
+          \hspace{-5pt}
+          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-70}  % chktex 8
+          \vspacebeforecaption{}
+          \caption{R-LIME ($\tau=0.70$)}\label{fig:rlime-0-70}
+          \vspacebase{}
+        \end{subfigure}
+        \begin{subfigure}[t]{\textwidth}
+          \hspacebase{}
+          \hspace{-17pt}
+          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-90}  % chktex 8
+          \vspacebeforecaption{}
+          \caption{R-LIME ($\tau=0.90$)}
+          \vspacebase{}
+        \end{subfigure}
+      \end{subfigure}
+      \caption[Explanation for Instance A by LIME and R-LIME]{%
+        Explanation for Instance A by LIME and R-LIME\@.
+      }\label{fig:A}
+    \end{figure}
+    \begin{figure}[t]
+      \begin{subfigure}[t]{0.45\textwidth}
+        \begin{subfigure}[t]{\textwidth}
+          \hspace{-26.5pt}
+          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0011}
+          \caption{LIME}\label{fig:lime-1}
+          \vspace{1.0em}
+        \end{subfigure}
+
+        \vspace{10pt}
+        \begin{subfigure}[t]{\textwidth}
+          \centering
+          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-70}  % chktex 8
+          \caption{\hl{Anchor ($\tau=0.70$)}}
+          \vspace{1.0em}
+        \end{subfigure}
+
+        \vspace{10pt}
+        \begin{subfigure}[t]{\textwidth}
+          \centering
+          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-90}  % chktex 8
+          \caption{\hl{Anchor ($\tau=0.90$)}}
+          \vspace{1.0em}
+        \end{subfigure}
+      \end{subfigure}
+      \hfill
+      \begin{subfigure}[t]{0.45\textwidth}
+        \begin{subfigure}[t]{\textwidth}
+          \hspacebase{}
+          \hspace{-5pt}
+          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-70}  % chktex 8
+          \vspacebeforecaption{}
+          \caption{R-LIME ($\tau=0.90$)}
+          \vspacebase{}
+        \end{subfigure}
+        \begin{subfigure}[t]{\textwidth}
+          \hspacebase{}
+          \hspace{-20pt}
+          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-90}  % chktex 8
+          \vspacebeforecaption{}
+          \caption{R-LIME ($\tau=0.90$)}\label{fig:rlime-1-90}
+          \vspacebase{}
+        \end{subfigure}
+      \end{subfigure}
+      \caption[Explanation for Instance B by LIME and R-LIME]{%
+        Explanation for Instance B by LIME and R-LIME\@.
+      }\label{fig:B}
+    \end{figure}
+  }
+
 \subsubsection{Experimental Results}
@@
 
-\vspace{-5pt}
 \subsubsection{Experimental Results}
@@
   for 100 instances from the test data of the recidivism dataset,
-  under the values of $\tau=0.70,0.80,0.90$.
+  under the values of $\tau=0.65,0.70,0.75,0.80,0.85,0.90$.
 }

### 2024-07-10 paper.tex
ICPR final revised version

@@
 
+% TODO REBUTTAL: Please enter paper ID
+\def\paperID{735} % *** Enter the paper ID here
+
 \begin{document}
-
-\newenvironment{mycomment}{
-  \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
-    }{\end{minipage}}
-
-\section*{Reviewer Response}
-We deeply appriciate all the reviewers who made valuable and insightful comments
+\begin{center}
+  % smaller title font only for rebuttal
+  % additional two empty lines at the end of the title
+  \vspace*{-22pt}
+  \begin{tabular}[t]{c}{
+      \large\bf
+      Paper ID \paperID{}
+    }
+  \end{tabular}
+  \par
+  % additional small space at the end of the author name
+  % additional empty line at the end of the title block
+\end{center}
+We deeply appriciate all the reviewers who made sharp and valuable comments
 on our paper and gave us the opportunity to submit a revised version.
@@
 
-\subsection*{Summary of revisions}
+\section*{Summary of revisions}
 We would like to appriciate all the reviewers for their clear and insightful
@@
 \begin{enumerate}
-  \item We added an overview of other existing methods to \cref{sec:related-work}.
+  \item We added an overview of other existing methods in \cref{sec:related-work}.
   \item We added discussion about parameter selection in \cref{sec:param}.
@@
 
-\subsection*{Responding to Reviewer \#1}
+\newenvironment{mycomment}{
+  \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
+    }{\end{minipage}}
+
+\section*{Responding to Reviewer \#1}
 Suggestions for Rebuttal:
@@
           methods, but we only added names of some other methods to
-          \cref{sec:related-work} because of lack of space.
+          \cref{sec:related-work}, because of lack of space.
         \end{mycomment}
@@
 \end{enumerate}
-\subsection*{Responding to Reviewer \#4}
+\section*{Responding to Reviewer \#4}
 The authors should kindly explain why there is not a quantitative comparison
@@
 
-\subsection*{Responding to Reviewer \#5}
+\section*{Responding to Reviewer \#5}
 \begin{itemize}
@@
 To efficiently search the rule (arm) with the highest accuracy,
-we employ the KL-LUCB algorithm~\cite{kaufmann2013information}.
+we employ KL-LUCB algorithm~\cite{kaufmann2013information}.
 The pseudo-code is shown in \cref{alg:best-cands}.
-For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
+For tolerance $\epsilon\in[0,1]$, KL-LUCB algorithm guarantees below:
 \begin{equation}
@@
 However,
-the KL-LUCB algorithm assumes that the reward distribution for each arm
+KL-LUCB algorithm assumes that the reward distribution for each arm
 remains unchanged,
@@
 
-\subsection{Computational Complexity}
+\subsection{Computational Complexity}\label{subsec:complexity}
 Post-hoc explanation methods including LIME, Anchor, and R-LIME
@@
 \section{Experiments}
-To verify the effectiveness of the proposed method,
-we compared LIME and R-LIME using a real-world dataset.
-
+To verify the effectiveness of our method,
+we compared LIME, \hl{Anchor} and R-LIME using a real-world dataset.
+\hl{Our code for R-LIME is available on GitHub}\footnote{\url{https://github.com/g-ohara/rlime}}.
+
+\newpage
 \subsection{Qualitative Evaluation}\label{sec:exp-qual}
@@
 using the training data.
-Then, LIME and R-LIME explanations were generated
+Then, we generate LIME, \hl{Anchor} and R-LIME explanations
 for two instances extracted from the test data (\cref{fig:instance}).
@@
 as the distribution $\mathcal{D}$.
-The beam width was set to $B=10$,
+\hl{For both Anchor and R-LIME,} the beam width was set to $B=10$,
 the confidence coefficient to $1-\delta=0.95$,
-and the tolerance of the KL-LUCB algorithm to $\epsilon=0.05$.
-The accuracy threshold $\tau$ was set to $\tau=0.70,0.80,0.90$.
+and the tolerance of KL-LUCB algorithm to $\epsilon=0.05$.
+The accuracy threshold $\tau$ was set to $\tau=0.70,0.90$.
 
@@
 Since such decisions can have a significant impact on a person's life,
-it is crucial for users to interpret the outputs of black-box models appropriately.
+it is crucial for users to appropriately interpret the outputs of black-box models.
   {%
@@
 
-\hl{
+\hl{%
   Anchor provides conditions for the model's output to be fixed with high
@@
 } (\cref{fig:anchor-0-70})
-\hl{
+\hl{%
   means that the model will predict with 75.66 \% probability
@@
 
-In contrast, R-LIME expresses the application scope of explanations
-as a conjunction of feature predicates.
+In contrast to LIME and Anchor,
+R-LIME provides both contribution of each feature to the output and
+the application scope of the explanation.
 For example, the explanation for instance A
@@
 \subsubsection{\hl{Experimental Setup}}
-\hl{
+\hl{%
   To demonstrate that R-LIME explanations are more general than Anchor,
@@
 }\cref{sec:exp-setting},
-\hl{
+\hl{%
   we generated Anchor and R-LIME explanations
@@
 \hl{The results are presented in} \cref{fig:coverage},
-\hl{
+\hl{%
   showing the coverage of the explanations by Anchor and R-LIME\@.
@@
 
-\subsection{Behavior Regarding Imbalanced Label Distribution}
+\subsection{Behavior for Imbalanced Label Distribution}
 R-LIME may generate less useful explanations
@@
 as the best arm identification problem in multi-armed bandit framework,
-and solved using the KL-LUCB algorithm~\cite{kaufmann2013information}.
+and solved using KL-LUCB algorithm~\cite{kaufmann2013information}.
 However, this algorithm assumes that the reward distribution remains constant,
@@
 the deviation was relatively small.
-While there are concerns about the theoretical validity of using the KL-LUCB algorithm,
+While there are concerns about the theoretical validity of using KL-LUCB algorithm,
 our results suggest that the deviation is not significant in practice.
@@
 
-\hl{
-  R-LIME requires some hyperparameters to be selected by users,
+\hl{In} \cref{subsec:complexity},
+\hl{%
+  we discussed about the computational complexity of R-LIME,
+  which depends on some hyperparameters.
+  R-LIME requires the hyperparameters to be selected by users,
   such as the threshold of accuracy $\tau$, beam width $B$, tolerance $\epsilon$
@@
   accurate results, as long as the computational cost is acceptable.
-  $\tau$ should be carefully selected by users, sometimes interactively,
-  considering the tradeoff between
-  the accuracy and generality of the explanation.
+  On the other hand, $\tau$ should be carefully selected by users,
+  sometimes interactively, considering the tradeoff between
+  the accuracy and generality of generated explanation.
 }
@@
 as long as the accuracy of the linear approximation model exceeds a given threshold.
-Comparing the outputs of LIME and R-LIME on the real-world dataset,
-we demonstrated that R-LIME provides a clear application scope of the
-explanation, can be evaluated by users for its reliability and generality,
-and achieves higher and less variable local accuracy compared to LIME\@.
-Finally, we discussed the instability of behavior against imbalanced label
-distributions and raised questions about the theoretical validity of using
-the KL-LUCB algorithm for our problem.
+Comparing R-LIME with existing methods on the real-world dataset,
+we demonstrated that R-LIME achieves interpretability of both the explanation
+and its application scope,
+and provides explanations more accurate than LIME and more general than Anchor.
+Finally,
+we discussed the instability of behavior against imbalanced label distributions,
+raised questions about the theoretical validity of using KL-LUCB algorithm,
+and hyperparameter tuning in practice.
 
@@
 \renewcommand{\hl}[1]{#1}
-% \newpage
-% \setcounter{page}{1}
-% \paper{}
+\newpage
+\setcounter{page}{1}
+\paper{}
 

### 2024-07-10 paper.tex
ICPR really final revised version

@@
 \end{center}
-We deeply appriciate all the reviewers who made sharp and valuable comments
+We deeply appreciate all the reviewers who made sharp and valuable comments
 on our paper and gave us the opportunity to submit a revised version.
 We have done our best for the revision according to their comments as shown below.
-We also would like to thank in advance all the reviewers for reconsidering
-the suitability of our revised paper for the conference.
+We also thank in advance all the reviewers for reconsidering
+our revised paper's suitability for the conference.
 
 \section*{Summary of revisions}
-We would like to appriciate all the reviewers for their clear and insightful
+We appreciate all the reviewers for their clear and insightful
 comments.
-We improved our paper from the original version according to their comments.
+We have improved our paper based on their comments.
 The major revision points are listed as follows:
-\begin{enumerate}
-  \item We added an overview of other existing methods in \cref{sec:related-work}.
+\begin{itemize}
+  \item We mentioned the names of other existing methods in \cref{sec:related-work}.
   \item We added discussion about parameter selection in \cref{sec:param}.
@@
         between Anchor and R-LIME in \cref{sec:exp-qual,sec:exp-anchor}.
-\end{enumerate}
+  \item We renamed the section `Challenges and Future Work' to `Discussion'.
+\end{itemize}
 Please see below for a point-by-point response to each reviewer's comments.
@@
         \begin{mycomment}
-          We would appreciate for your suggestion.
-          We added \cref{sec:param} as a guidance on how parameters should be
-          selected in practice.
+          We appreciate your suggestion.
+          We added \cref{sec:param} to provide guidance on
+          how parameters should be selected in practice.
         \end{mycomment}
@@
           Thank you for your valuable suggestion.
-          We should add an overview of other model-agnostic interpretability
-          methods, but we only added names of some other methods to
-          \cref{sec:related-work}, because of lack of space.
+          Although we acknowledge the importance of including an overview of
+          other model-agnostic interpretability methods,
+          due to space constraints, we only mentioned the names of some
+          other methods in \cref{sec:related-work}.
         \end{mycomment}
@@
         \begin{mycomment}
-          We would like to appriciate your sharp observations.
+          We appreciate your sharp observations.
           We additionally conducted qualitative and quantitative comparisons
@@
 \begin{mycomment}
-  We would appreciate for your insightful comments.
+  We appreciate your insightful comments.
   We additionally conducted qualitative and quantitative comparisons
@@
         \begin{mycomment}
-          We would like to appriciate for your insightful suggestion.
-          We interpreted your suggestrion to mean that we should move
+          We appreciate your insightful suggestion.
+          We interpreted your suggestion to mean that we should move
           \cref{fig:example} and its explanation to \cref{sec:related-work}.
-          We discussed about the most understandable structure of our paper.
-          And for clarity, we concluded that we should present effectiveness
-          of R-LIME compared to existing methods closely related to our method
-          in \cref{sec:introduction},
+          After discussing the most understandable structure of our paper,
+          we concluded that we should present effectiveness of R-LIME
+          compared to closely related methods in \cref{sec:introduction},
           before we overview other existing methods in \cref{sec:related-work}.
@@
           Thank you for your valuable feedback.
-          It is true that we must address theoretical issues for using
-          KL-LUCB algorithm, although our results suggest that its practical
-          effect is negligible.
-          We focus on presenting our novel framework for local interpretability,
-          not on the detailed algorithm.
-          Thus, we leave the issues for future work because of lack of space.
-          But we deeply appreciate for your sharp observations.
+          While our results suggest that the practical effect of using
+          the KL-LUCB algorithm is negligible,
+          we acknowledge the need to address its theoretical issues.
+          Our focus is on presenting our novel framework for local
+          interpretability, not the detailed algorithm.
+          Thus, we leave the issues for future work due to space constraints.
+          However, we deeply appreciate your sharp observations.
         \end{mycomment}
@@
           Thank you for your suggestion. We renamed the section to `Discussion'
-          for clearly reflecting the content.
+          to clearly reflect the content.
         \end{mycomment}
@@
   In recent years,
-  complex machine learning models have been introduced
+  complex machine learning models have been widely introduced
   in various industrial fields due to their high accuracy.
   However,
-  their increasing complexity has been a major obstacle to implementation
+  their increasing complexity has been a major obstacle to their implementation
   in sensitive decision-making situations.
@@
   both the explanation and its scope.
-  We propose a new method, R-LIME,
-  which interprets a complex classifier in an interpretable scope.
-  R-LIME locally and linearly approximates a complex decision boundary
-  of a black-box classifier in a rectangular region
+  We propose R-LIME, a novel method that interprets complex classifiers
+  within an interpretable scope.
+  R-LIME locally and linearly approximates the complex decision boundary
+  of a black-box classifier within a rectangular region
   and maximizes the region as long as the approximation accuracy
@@
   expressed as a conjunction of feature predicates.
-  Through qualitative and quantitative comparisons with the existing method
-  on a real-world dataset,
+  Through qualitative and quantitative comparisons on a real-world dataset,
   we demonstrate that R-LIME provides more reliable and interpretable
@@
 have been widely introduced in various industrial fields
-due to their significant improvement in accuracy.
+due to their significant improvements in accuracy.
 However,
@@
 particularly in critical decision-making scenarios such as healthcare and finance,
-where the opacity of decision process becomes a major obstacle to implementation.
+where the lack of transparency becomes a major obstacle to implementation.
 In order to address this problem,
-there has been extensive research in the field of post-hoc explanations
-for machine learning models
+extensive research has focused on post-hoc explanations for complex models
 ~\cite{guidotti2018local,ribeiro2016why,ribeiro2018anchors}.
-Existing post-hoc explanation methods are categorized
+Post-hoc explanation methods are categorized
 into \emph{model-dependent} and \emph{model-agnostic} methods
 based on their dependence on the model's structure,
-and the latter are further classified into \emph{global} and \emph{local} methods
-based on their locality in input space~\cite{samek2021explaining}.
+with the latter further classified into \emph{global} and \emph{local} methods
+based on the locality in the input space~\cite{samek2021explaining}.
 \begin{figure}[tbp]
@@
 To address these limitations,
-we propose a new method called R-LIME (Ruled LIME),
+we propose R-LIME (Ruled LIME),
 which provides both the contributions of each feature to the output
@@
 and layer-wise relevance propagation (LRP)~\cite{bach2015pixel},
-most of which focus on neural networks and
+primarily focus on neural networks and
 explain the model's behavior using its parameters~\cite{samek2021explaining}.
@@
 Although they are applicable to any model,
-they cannot explain the reasoning process inside the model.
-
-Furthermore, model-agnostic methods are categorized into
-\emph{global} and \emph{local} methods based on their locality in input space.
+they cannot explain the internal reasoning processes of the model.
+
+Model-agnostic methods are further categorized into
+\emph{global} and \emph{local} methods based on their locality in the input space.
 Global methods,
@@
 In contrast, local methods,
-such as \hl{indivisual conditional expectation (ICE)}~\cite{goldstein2015peeking},
+such as \hl{individual conditional expectation (ICE)}~\cite{goldstein2015peeking},
 local interpretable model-agnostic explanations
@@
 \hl{shapley additive explanations (SHAP)}~\cite{lundberg2017unified},
-explain model's behavior in the vicinity of a specific input.
-While they offer explanations more simple and accurate
-than global methods,
+explain the model's behavior in the vicinity of a specific input.
+While they offer explanations simpler and more accurate than global methods,
 the scope of the explanation is limited locally.
@@
 We specifically focus on \emph{local} and \emph{model-agnostic} methods.
-In this section,
-we briefly review existing research on local model-agnostic explanations,
+This section briefly reviews existing research on local model-agnostic explanations,
 particularly focusing on studies closely related to our proposed method.
@@
 around a focal point $x \in \mathbb{R}^m$
-by a linear classifier $g: \mathbb{R}^m \to \{0,1\}$
+using a linear classifier $g: \mathbb{R}^m \to \{0,1\}$
 (\cref{fig:lime}).
-The approximation is performed by the following steps:
+The approximation process involves the following steps:
 \begin{enumerate}
-  \item Generating a set of perturbed samples $\mathcal{Z}_p$ around $x$
-        and the set of pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
-        (i) $x$ is converted into a binary vector
-        $x'\in{\{0,1\}}^{m'}$,
-        (ii) perturbed samples are generated by drawing non-zero elements
-        from $x'$ uniformly at random,
-        and (iii) the perturbed samples are converted back to the original space.
-  \item Learning a linear classifier $g$
+  \item Generate a set of perturbed samples $\mathcal{Z}_p$ around $x$
+        and their pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
+        (i) Convert $x$ into a binary vector $x'\in{\{0,1\}}^{m'}$,
+        (ii) generate perturbed samples by randomly drawing non-zero elements
+        from $x'$,
+        and (iii) convert the perturbed samples back to the original space.
+  \item Train a linear classifier $g$
         using $\mathcal{Z}_p$ and $f(\mathcal{Z}_p)$
@@
         \end{equation}
-        where $\pi_x(z)$ is a weight function designed to be larger for samples
-        closer to $x$, typically defined using an exponential kernel.
+        where $\pi_x(z)$ is a weight function that assigns larger weights
+        for samples closer to $x$, typically defined using an exponential kernel.
 \end{enumerate}
 LIME provides valuable insights into the local behavior of the model
-by showing the contribution of each feature to the output $f(x)$.
-However, it does not explicitly indicate the region for generating perturbed samples,
+by showing each feature's contribution to the output $f(x)$.
+However, it does not explicitly define the region for generating perturbed samples,
 making it difficult for users to assess the effective scope of the explanation
@@
 We propose R-LIME,
-a method that aims to address the limitations of LIME~\cite{ribeiro2016why}
+a novel method designed to address the limitations of LIME~\cite{ribeiro2016why}
 and Anchor~\cite{ribeiro2018anchors}.
-Our method locally approximates the given black-box classifier $f$
-around the focal point $x$ by a linear classifier $g$ similar to LIME,
-but generates the perturbed samples
-from a rectangular region similar to Anchor
-so that the generality of approximation is explicitly provided
-(\cref{fig:rlime}).
+Similar to LIME,
+it locally approximates the black-box classifier $f$
+around the focal point $x$ using a linear classifier $g$,
+and similar to Anchor,
+it generates the perturbed samples for approximation
+from a rectangular region (\cref{fig:rlime}).
 
@@
 }
-The algorithm of R-LIME
-is mainly based on that used in Anchor\cite{ribeiro2018anchors}.
+The R-LIME algorithm
+is mainly based on the method used in Anchor\cite{ribeiro2018anchors}.
 For non-convex optimization problems like \cref{eq:main-problem},
 greedy search are often used.
-But greedy methods tend to converge to local optima,
-so we use beam search, which selects multiple candidates at each iteration.
+But greedy methods often converge to local optima,
+so we use beam search, which selects multiple candidates at each iteration
+to improve the search robustness.
 The pseudo-code is shown in \cref{alg:greedy-search}.
@@
 To efficiently search the rule (arm) with the highest accuracy,
-we employ KL-LUCB algorithm~\cite{kaufmann2013information}.
+we employ the KL-LUCB algorithm~\cite{kaufmann2013information}.
 The pseudo-code is shown in \cref{alg:best-cands}.
-For tolerance $\epsilon\in[0,1]$, KL-LUCB algorithm guarantees below:
+For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
 \begin{equation}
@@
 However,
-KL-LUCB algorithm assumes that the reward distribution for each arm
+the KL-LUCB algorithm assumes that the reward distribution for each arm
 remains unchanged,
@@
 \subsection{Computational Complexity}\label{subsec:complexity}
-Post-hoc explanation methods including LIME, Anchor, and R-LIME
+Post-hoc explanation methods including LIME, Anchor and R-LIME
 need to sample a perturbation vector
@@
 for best arm identification finding the best $B$ arms from $B\cdot m$ arms.
-For KL-LUCB algorithm~\cite{kaufmann2013information},
+For the KL-LUCB algorithm~\cite{kaufmann2013information},
 \begin{equation}
@@
 
-For each iteration of KL-LUCB algorithm, R-LIME needs to update
+For each iteration of the KL-LUCB algorithm, R-LIME needs to update
 the linear classifier $g_i$, which is not required in Anchor.
@@
 To verify the effectiveness of our method,
-we compared LIME, \hl{Anchor} and R-LIME using a real-world dataset.
+we conducted qualitative and quantitative comparisons of R-LIME
+with LIME and Anchor, using a real-world dataset.
 \hl{Our code for R-LIME is available on GitHub}\footnote{\url{https://github.com/g-ohara/rlime}}.
@@
 The dataset contains personal information on 9549 prisoners released from
-North Carolina prisons between July 1, 1979, and June 30, 1980.
+North Carolina prisons between July 1, 1979 and June 30, 1980.
 As shown in \cref{tab:rcdv}, the dataset includes 19 items such as
@@
 using the training data.
-Then, we generate LIME, \hl{Anchor} and R-LIME explanations
+Then, we generate LIME, Anchor and R-LIME explanations
 for two instances extracted from the test data (\cref{fig:instance}).
@@
 as the distribution $\mathcal{D}$.
-\hl{For both Anchor and R-LIME,} the beam width was set to $B=10$,
+For both Anchor and R-LIME, the beam width was set to $B=10$,
 the confidence coefficient to $1-\delta=0.95$,
-and the tolerance of KL-LUCB algorithm to $\epsilon=0.05$.
+and the tolerance of the KL-LUCB algorithm to $\epsilon=0.05$.
 The accuracy threshold $\tau$ was set to $\tau=0.70,0.90$.
@@
   we generated Anchor and R-LIME explanations
-  for 100 instances from the test data of the recidivism dataset,
+  for 704 instances from the test data of the recidivism dataset,
   under the values of $\tau=0.65,0.70,0.75,0.80,0.85,0.90$.
@@
 as the best arm identification problem in multi-armed bandit framework,
-and solved using KL-LUCB algorithm~\cite{kaufmann2013information}.
+and solved using the KL-LUCB algorithm~\cite{kaufmann2013information}.
 However, this algorithm assumes that the reward distribution remains constant,
@@
 the deviation was relatively small.
-While there are concerns about the theoretical validity of using KL-LUCB algorithm,
+While there are concerns about the theoretical validity of using the KL-LUCB algorithm,
 our results suggest that the deviation is not significant in practice.
@@
 Finally,
-we discussed the instability of behavior against imbalanced label distributions,
-raised questions about the theoretical validity of using KL-LUCB algorithm,
+we discussed the instability of behavior with imbalanced label distributions,
+raised questions about the theoretical validity of using the KL-LUCB algorithm,
 and hyperparameter tuning in practice.

### 2024-08-15 paper.tex
feat: remove all submodules for camera-ready

@@
 \usepackage{array} % for m column type
-\usepackage{bbm} % for \mathbbm
+% \usepackage{bbm} % for \mathbbm
+\usepackage{dsfont}
+\newcommand{\mathbbm}[1]{\mathds{#1}}
 \usepackage{booktabs} % for \toprule, \midrule, \bottomrule
 \usepackage{cleveref} % for \cref
-\usepackage{color,soul} % for \hl
 \usepackage{csvsimple} % for \csvreader
@@
 \begin{document}
-\begin{center}
-  % smaller title font only for rebuttal
-  % additional two empty lines at the end of the title
-  \vspace*{-22pt}
-  \begin{tabular}[t]{c}{
-      \large\bf
-      Paper ID \paperID{}
-    }
-  \end{tabular}
-  \par
-  % additional small space at the end of the author name
-  % additional empty line at the end of the title block
-\end{center}
-We deeply appreciate all the reviewers who made sharp and valuable comments
-on our paper and gave us the opportunity to submit a revised version.
-We have done our best for the revision according to their comments as shown below.
-We also thank in advance all the reviewers for reconsidering
-our revised paper's suitability for the conference.
-
-\section*{Summary of revisions}
-We appreciate all the reviewers for their clear and insightful
-comments.
-We have improved our paper based on their comments.
-The major revision points are listed as follows:
-\begin{itemize}
-  \item We mentioned the names of other existing methods in \cref{sec:related-work}.
-  \item We added discussion about parameter selection in \cref{sec:param}.
-  \item We conducted qualitative and quantitative comparisons
-        between Anchor and R-LIME in \cref{sec:exp-qual,sec:exp-anchor}.
-  \item We renamed the section `Challenges and Future Work' to `Discussion'.
-\end{itemize}
-Please see below for a point-by-point response to each reviewer's comments.
-
-\newenvironment{mycomment}{
-  \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
-    }{\end{minipage}}
-
-\section*{Responding to Reviewer \#1}
-Suggestions for Rebuttal:
-\begin{enumerate}
-  \setlength{\itemsep}{15pt}
-  \item Offer guidance on how to select optimal parameters for different
-        datasets and models.
-
-        \begin{mycomment}
-          We appreciate your suggestion.
-          We added \cref{sec:param} to provide guidance on
-          how parameters should be selected in practice.
-        \end{mycomment}
-
-  \item Include a discussion of other model-agnostic interpretability methods,
-        such as SHAP, to provide a more comprehensive overview.
-
-        \begin{mycomment}
-          Thank you for your valuable suggestion.
-          Although we acknowledge the importance of including an overview of
-          other model-agnostic interpretability methods,
-          due to space constraints, we only mentioned the names of some
-          other methods in \cref{sec:related-work}.
-        \end{mycomment}
-
-  \item Add experimental comparisons with more other model-agnostic \\
-        interpretability methods to better evaluate R-LIME's effectiveness.
-
-        \begin{mycomment}
-          We appreciate your sharp observations.
-          We additionally conducted qualitative and quantitative comparisons
-          between Anchor and R-LIME,
-          which demonstrated that R-LIME generates more informative and
-          general explanations than Anchor (see \cref{sec:exp-qual,sec:exp-anchor}).
-        \end{mycomment}
-\end{enumerate}
-\section*{Responding to Reviewer \#4}
-The authors should kindly explain why there is not a quantitative comparison
-between their proposed method R-LIME and Anchor. The lack of the comparison
-makes it hard to evaluate the impact of the proposed model.
-
-\begin{mycomment}
-  We appreciate your insightful comments.
-  We additionally conducted qualitative and quantitative comparisons
-  between Anchor and R-LIME,
-  which demonstrated that R-LIME generates more informative and
-  general explanations than Anchor (see \cref{sec:exp-qual,sec:exp-anchor}).
-\end{mycomment}
-
-\section*{Responding to Reviewer \#5}
-\begin{itemize}
-  \setlength{\itemsep}{15pt}
-  \item It would be beneficial to move the comparison of R-LIME with Anchor
-        and LIME to the Related Work section for improved clarity and
-        organization.
-
-        \begin{mycomment}
-          We appreciate your insightful suggestion.
-          We interpreted your suggestion to mean that we should move
-          \cref{fig:example} and its explanation to \cref{sec:related-work}.
-          After discussing the most understandable structure of our paper,
-          we concluded that we should present effectiveness of R-LIME
-          compared to closely related methods in \cref{sec:introduction},
-          before we overview other existing methods in \cref{sec:related-work}.
-        \end{mycomment}
-
-  \item The authors should consider exploring a more compatible method than the
-        KL-LUCB algorithm to achieve higher accuracy. Although the experimental
-        results suggest a minor effect, there may be potential underlying issues
-        that need to be addressed.
-
-        \begin{mycomment}
-          Thank you for your valuable feedback.
-          While our results suggest that the practical effect of using
-          the KL-LUCB algorithm is negligible,
-          we acknowledge the need to address its theoretical issues.
-          Our focus is on presenting our novel framework for local
-          interpretability, not the detailed algorithm.
-          Thus, we leave the issues for future work due to space constraints.
-          However, we deeply appreciate your sharp observations.
-        \end{mycomment}
-
-  \item The title of the `Challenges and Future Work' section could be more
-        aptly replaced with `Discussion' to better reflect the content.
-
-        \begin{mycomment}
-          Thank you for your suggestion. We renamed the section to `Discussion'
-          to clearly reflect the content.
-        \end{mycomment}
-\end{itemize}
-
 \newcommand{\sampleindex}[1]{\ifnum#1=0 \Asample\else\Bsample\fi}
 \def\AB#1{\ifnum#1=0 A\else B\fi}
-
-\def\paper{
 
@@
 
-\section{Introduction}\label{sec:introduction}
+\section{Introduction}
 In recent years,
@@
 
-\section{Related Work}\label{sec:related-work}
+\section{Related Work}
 \begin{figure}[tbp]
@@
 In contrast, local methods,
-such as \hl{individual conditional expectation (ICE)}~\cite{goldstein2015peeking},
+such as individual conditional expectation (ICE)~\cite{goldstein2015peeking},
 local interpretable model-agnostic explanations
 (LIME)~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors} and
-\hl{shapley additive explanations (SHAP)}~\cite{lundberg2017unified},
+shapley additive explanations (SHAP)~\cite{lundberg2017unified},
 explain the model's behavior in the vicinity of a specific input.
@@
 with LIME and Anchor, using a real-world dataset.
-\hl{Our code for R-LIME is available on GitHub}\footnote{\url{https://github.com/g-ohara/rlime}}.
+Our code for R-LIME is available on GitHub\footnote{\url{https://github.com/g-ohara/rlime}}.
 
 \newpage
-\subsection{Qualitative Evaluation}\label{sec:exp-qual}
+\subsection{Qualitative Evaluation}
 \subsubsection{Experimental Setup}\label{sec:exp-setting}
@@
 
-    \def\dir{src/experiments/exp1/ver1/examples/output}
+    \def\dir{src/experiments/exp1/}
     \def\Asample{0012}
@@
     \def\scale{0.315}
-    \def\dir{exp1/ver1/examples/output}
+    \def\dir{exp1/}
     \def\imgwidth{0.3\textwidth}
@@
           \hspace{-10pt}
-          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0012}
+          \includegraphics[scale=\scale]{exp1/lime-0012}
           \caption{LIME}\label{fig:lime-0}
@@
           \centering
-          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-70}  % chktex 8
-          \caption{\hl{Anchor ($\tau=0.70$)}}\label{fig:anchor-0-70}
+          \includegraphics[scale=0.33]{exp1/anchor-0012-70}  % chktex 8
+          \caption{Anchor ($\tau=0.70$)}\label{fig:anchor-0-70}
           \vspace{1.0em}
@@
           \centering
-          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-90}  % chktex 8
-          \caption{\hl{Anchor ($\tau=0.90$)}}
+          \includegraphics[scale=0.33]{exp1/anchor-0012-90}  % chktex 8
+          \caption{Anchor ($\tau=0.90$)}
           \vspace{1.0em}
@@
           \hspace{-5pt}
-          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-70}  % chktex 8
+          \includegraphics[scale=\scale]{exp1/rlime-0012-70}  % chktex 8
           \vspacebeforecaption{}
@@
           \hspace{-17pt}
-          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-90}  % chktex 8
+          \includegraphics[scale=\scale]{exp1/rlime-0012-90}  % chktex 8
           \vspacebeforecaption{}
@@
           \hspace{-26.5pt}
-          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0011}
+          \includegraphics[scale=\scale]{exp1/lime-0011}
           \caption{LIME}\label{fig:lime-1}
@@
           \centering
-          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-70}  % chktex 8
-          \caption{\hl{Anchor ($\tau=0.70$)}}
+          \includegraphics[scale=0.33]{exp1/anchor-0011-70}  % chktex 8
+          \caption{Anchor ($\tau=0.70$)}
           \vspace{1.0em}
@@
           \centering
-          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-90}  % chktex 8
-          \caption{\hl{Anchor ($\tau=0.90$)}}
+          \includegraphics[scale=0.33]{exp1/anchor-0011-90}  % chktex 8
+          \caption{Anchor ($\tau=0.90$)}
           \vspace{1.0em}
@@
           \hspace{-5pt}
-          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-70}  % chktex 8
+          \includegraphics[scale=\scale]{exp1/rlime-0011-70}  % chktex 8
           \vspacebeforecaption{}
@@
           \hspace{-20pt}
-          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-90}  % chktex 8
+          \includegraphics[scale=\scale]{exp1/rlime-0011-90}  % chktex 8
           \vspacebeforecaption{}
@@
 
-\hl{%
 Anchor provides conditions for the model's output to be fixed with high
@@
 the explanation for instance A under $\tau=0.70$
-} (\cref{fig:anchor-0-70})
-\hl{%
+(\cref{fig:anchor-0-70})
 means that the model will predict with 75.66 \% probability
@@
 it does not provide details about how these conditions affect the model's output.
-}
 
@@
     \centering
-    \includegraphics[scale=0.35,valign=t]{exp2b/comp_cov}
+    \includegraphics[scale=0.35,valign=t]{exp2/comp_cov}
     \vspace{3pt}
     \caption[Comparison of Coverage between Anchor and R-LIME]{%
-      \hl{%
       Comparison of coverage between Anchor and R-LIME\@.
@@
       for almost values of $\tau$, especially for relatively small $\tau$.
-      }
     }\label{fig:coverage}
@@
 
-\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}\label{sec:exp-anchor}
-\subsubsection{\hl{Experimental Setup}}
-\hl{%
+\subsection{Quantitative Evaluation: Anchor vs. R-LIME}
+\subsubsection{Experimental Setup}
 To demonstrate that R-LIME explanations are more general than Anchor,
@@
 Under the same settings as in
-}\cref{sec:exp-setting},
-\hl{%
+\cref{sec:exp-setting},
 we generated Anchor and R-LIME explanations
@@
 under the values of $\tau=0.65,0.70,0.75,0.80,0.85,0.90$.
-}
-
-\subsubsection{\hl{Experimental Results}}
-\hl{The results are presented in} \cref{fig:coverage},
-\hl{%
+
+\subsubsection{Experimental Results}
+The results are presented in \cref{fig:coverage},
 showing the coverage of the explanations by Anchor and R-LIME\@.
@@
 which cannot capture the decision boundary flexibly and makes its scope narrow.
-}
-
-\section{\hl{Discussion}}
+
+\section{Discussion}
  {%
@@
 
-\subsection{\hl{Parameter Selection}}\label{sec:param}
-
-\hl{In} \cref{subsec:complexity},
-\hl{%
+\subsection{Parameter Selection}
+
+In \cref{subsec:complexity},
 we discussed about the computational complexity of R-LIME,
@@
 the accuracy and generality of generated explanation.
-}
 
@@
 \bibliographystyle{src/style/splncs04}
-\bibliography{src/myref/myref}
-}
-
-% Reset page number and typeset title
-\newpage
-\setcounter{page}{1}
-\paper{}
-\renewcommand{\hl}[1]{#1}
-\newpage
-\setcounter{page}{1}
-\paper{}
+\bibliography{src/ref}
 

### 2024-08-15 src/experiments/exp2/box_plot.py

@@ -1,61 +1,0 @@
-"""Module providing a function creating a box plot of the data in a file."""
-
-import csv
-
-import matplotlib.pyplot as plt
-
-
-def main() -> None:
-    """Main function of the module."""
-
-    plt.figure()
-
-    accs = []
-    for tau_percent in [70, 80, 90]:
-        file_name = f"{tau_percent}.csv"
-        lime_acc, rlime_acc = read_data(file_name)
-        accs.append(lime_acc)
-        accs.append(rlime_acc)
-
-    plt.rcParams["font.size"] = 15
-    bp = plt.boxplot(
-        accs,
-        tick_labels=["LIME", "R-LIME"] * 3,
-        widths=0.7,
-        positions=[1, 2.2, 3.7, 4.9, 6.4, 7.6],
-        showfliers=False,
-        patch_artist=True,
-    )
-    colors = ["#377eb8", "#4daf4a"] * 3
-    for patch, med, color in zip(bp["boxes"], bp["medians"], colors):
-        patch.set_facecolor(color)
-        med.set_color("black")
-
-    for i, tau_percent in enumerate([70, 80, 90]):
-        plt.text(0.9 + 2.7 * i, 0.30, r"$\tau=$" + f"0.{tau_percent}")
-
-    plt.hlines(
-        [0.7, 0.8, 0.9],
-        [0, 2.7, 5.4],
-        [3.0, 5.7, 8.4],
-        colors="black",
-        linestyles="dashed",
-    )
-    # plt.title("Accuracy of LIME and R-LIME")
-    plt.ylabel("Accuracy")
-    plt.tight_layout()
-    plt.savefig("box_plot.eps")
-
-
-def read_data(filename: str) -> tuple[list[float], list[float]]:
-    """Reads data from a file and returns it as a list of lists."""
-    data = []
-    with open(filename, newline="", encoding="utf-8") as file:
-        reader = csv.reader(file, delimiter=",")
-        for row in reader:
-            data.append([float(x) for x in row])
-    return data[0], data[1]
-
-
-if __name__ == "__main__":
-    main()

### 2024-08-15 src/experiments/exp2/lime_vs_rlime.py

@@ -1,174 +1,0 @@
-"""Compare LIME and R-LIME on the recidivism dataset."""
-
-import csv
-import multiprocessing
-from functools import partial
-
-import numpy as np
-import pandas as pd  # type: ignore
-from river import preprocessing
-from sklearn.ensemble import RandomForestClassifier  # type: ignore
-
-from rlime import rlime_lime
-from rlime.arm import Arm
-from rlime.rlime import HyperParam, explain_instance
-from rlime.rlime_types import Dataset, IntArray
-from rlime.sampler import Sampler
-from rlime.utils import get_trg_sample, load_dataset
-
-
-def main() -> None:
-    """Main function."""
-
-    # Load the dataset.
-    dataset = load_dataset(
-        "recidivism", "rlime/examples/datasets/", balance=True
-    )
-
-    # Learn the black box model.
-    black_box = RandomForestClassifier(n_estimators=100, n_jobs=1)
-    black_box.fit(dataset.train, dataset.labels_train)
-
-    # Get the target instances.
-    sample_num = 100
-
-    for tau in [0.70, 0.80, 0.90]:
-
-        print(f"tau = {tau:.2f}")
-
-        result_list = multiprocessing.Manager().list()
-
-        func = partial(
-            compare_lime_and_newlime,
-            dataset=dataset,
-            black_box=black_box,
-            tau=tau,
-            result_list=result_list,
-        )
-
-        with multiprocessing.Pool() as pool:
-            pool.map(func, range(sample_num))
-
-        lime_acc, rlime_acc = zip(*result_list)
-        print("LIME")
-        print(f"  Mean: {np.mean(lime_acc):.4f}")
-        print(f"  Std : {np.std(lime_acc):.4f}")
-        print("R-LIME")
-        print(f"  Mean: {np.mean(rlime_acc):.4f}")
-        print(f"  Std : {np.std(rlime_acc):.4f}")
-
-        # Save the results to a CSV file.
-        with open(f"{int(tau*100)}.csv", "w", encoding="utf-8") as f:
-            writer = csv.writer(f)
-            writer.writerow(lime_acc)
-            writer.writerow(rlime_acc)
-
-
-def calc_accuracy(
-    samples: IntArray,
-    labels: IntArray,
-    lime_weights: list[float],
-    lime_scaler: preprocessing.StandardScaler,
-    arm: Arm,
-) -> tuple[float, float]:
-    """Calculate the precision of LIME and R-LIME.
-
-    Parameters
-    ----------
[…]

### 2024-08-15 src/experiments/exp2/src/exp2/__init__.py

@@ -1,2 +1,0 @@
-def hello() -> str:
-    return "Hello from exp2!"

### 2024-08-15 src/experiments/exp2b/comp_cov.py

@@ -1,109 +1,0 @@
-"""Compare coverage of the explanations generated by Anchor and R-LIME."""
-
-import csv
-from pathlib import Path
-from statistics import mean, stdev
-
-import matplotlib.pyplot as plt
-
-EXAMPLES_DIR_NAME = "src/rlime-examples/examples"
-SAMPLE_NUM = 703
-
-
-def get_weights(idx: int) -> list[float] | None:
-    """Get the weights of LIME for the given sample."""
-    csv_name = EXAMPLES_DIR_NAME + f"/lime-{idx:04d}.csv"
-    try:
-        with Path(csv_name).open() as f:
-            reader = csv.reader(f)
-            return [float(x) for x in next(reader)]
-    except FileNotFoundError:
-        return None
-
-
-def get_rlime_weights(idx: int, tau: int) -> list[float] | None:
-    """Get the weights of R-LIME for the given sample."""
-    csv_name = EXAMPLES_DIR_NAME + f"/newlime-{idx:04d}-{tau:02d}.csv"
-    try:
-        with Path(csv_name).open() as f:
-            reader = csv.reader(f)
-            return [float(x) for x in next(reader)]
-    except FileNotFoundError:
-        return None
-
-
-def get_anchor_cov(idx: int, tau: int) -> float | None:
-    """Get the coverage of Anchor for the given sample."""
-    csv_name = EXAMPLES_DIR_NAME + f"/anchor-{idx:04d}-{tau:02d}.csv"
-    try:
-        with Path(csv_name).open() as f:
-            reader = csv.reader(f)
-            next(reader)  # Skip the weights.
-            return float(next(reader)[1])  # Skip the accuracy.
-    except FileNotFoundError:
-        return None
-
-
-def get_rlime_cov(idx: int, tau: int) -> float | None:
-    """Get the coverage of R-LIME for the given sample."""
-    csv_name = EXAMPLES_DIR_NAME + f"/newlime-{idx:04d}-{tau:02d}.csv"
-    try:
-        with Path(csv_name).open() as f:
-            reader = csv.reader(f)
-            next(reader)  # Skip the weights.
-            next(reader)  # Skip the rule.
-            return float(next(reader)[1])  # Skip the accuracy.
-    except FileNotFoundError:
-        return None
-
-
-def main() -> None:
[…]

### 2024-08-15 src/experiments/exp2b/lime_vs_rlime.py

@@ -1,173 +1,0 @@
-"""Compare LIME and R-LIME on the recidivism dataset."""
-
-import csv
-from pathlib import Path
-
-import numpy as np
-from rlime import rlime_lime
-from rlime.rlime_types import Dataset, IntArray, Rule
-from rlime.sampler import Sampler
-from rlime.utils import get_trg_sample, load_dataset
-from sklearn.ensemble import RandomForestClassifier  # type: ignore
-from sklearn.preprocessing import StandardScaler
-
-EXAMPLES_DIR_NAME = "src/rlime-examples/examples"
-
-
-def main() -> None:
-    """Main function."""
-    # Load the dataset.
-    dataset = load_dataset("recidivism", "src/datasets/", balance=True)
-
-    # Learn the black box model.
-    black_box = RandomForestClassifier(n_estimators=100, n_jobs=1)
-    black_box.fit(dataset.train, dataset.labels_train)
-
-    # Get the target instances.
-    sample_num = 100
-
-    for tau in [0.90]:
-        print(f"tau = {tau:.2f}")
-
-        # result_list = multiprocessing.Manager().list()
-
-        # func = partial(
-        #     compare_lime_and_newlime,
-        #     dataset=dataset,
-        #     black_box=black_box,
-        #     tau=tau,
-        #     result_list=result_list,
-        # )
-
-        # with multiprocessing.Pool() as pool:
-        #     pool.map(func, range(sample_num))
-
-        result_list: list[tuple[float, float]] = []
-        for idx in range(sample_num):
-            compare_lime_and_newlime(idx, dataset, black_box, tau, result_list)
-
-        lime_acc, rlime_acc = zip(*result_list)
-        print("LIME")
-        print(f"  Mean: {np.mean(lime_acc):.4f}")
-        print(f"  Std : {np.std(lime_acc):.4f}")
-        print("R-LIME")
-        print(f"  Mean: {np.mean(rlime_acc):.4f}")
-        print(f"  Std : {np.std(rlime_acc):.4f}")
-
-        # Save the results to a CSV file.
-        with open(f"{int(tau*100)}.csv", "w", encoding="utf-8") as f:
-            writer = csv.writer(f)
-            writer.writerow(lime_acc)
-            writer.writerow(rlime_acc)
-
-
-def calc_accuracy(
-    samples: IntArray,
-    labels: IntArray,
-    lime_weights: list[float],
-    rlime_weights: list[float],
-    lime_scaler: StandardScaler,
[…]

### 2024-08-15 src/experiments/exp_adv/complexity.py

@@ -1,56 +1,0 @@
-"""Calculate the complexity of queries for the black-box classifiers
-in R-LIME."""
-
-import sys
-from typing import Any
-
-from sklearn.ensemble import RandomForestClassifier
-
-sys.path.append("RLIME")
-
-from RLIME import newlime_base, newlime_tabular, newlime_utils
-from RLIME.newlime_types import IntArray
-
-
-class BlackBoxClassifier(RandomForestClassifier):  # type: ignore
-    """A black-box classifier for R-LIME."""
-
-    def __init__(self, *args: str, **kwargs: int) -> None:
-        """Initialize the black-box classifier."""
-
-        super().__init__(*args, **kwargs)
-        self.predict_count = 0
-
-    def predict(self, X: IntArray) -> Any:
-        """Predict the labels of the input instances."""
-
-        self.predict_count += X.shape[0]
-        print(f"Predict count: {self.predict_count}")
-        return super().predict(X)
-
-
-def main() -> None:
-    """Main function."""
-
-    # Load the dataset.
-    dataset = newlime_utils.load_dataset(
-        "recidivism", "datasets/", balance=True
-    )
-
-    # Learn the black box model.
-    black_box = BlackBoxClassifier(n_estimators=100, n_jobs=1)
-    black_box.fit(dataset.train, dataset.labels_train)
-
-    idx = 0
-    trg, _, _ = newlime_utils.get_trg_sample(idx, dataset)
-    hyper_param = newlime_base.HyperParam()
-    result = newlime_tabular.explain_instance(
-        trg, dataset, black_box, hyper_param
-    )
-
-    if result is None:
-        print("No explanation found.")
-        return
-    names, arm = result
-    print(f"Names: {names}")
-    print(f"ARM: {arm}")

### 2024-08-15 src/experiments/exp_adv/imbalanced.py

@@ -1,142 +1,0 @@
-"""This module generates the experiment data for the paper."""
-
-import random
-import sys
-
-import numpy as np
-import pandas as pd
-from river import compose
-from sklearn.ensemble import RandomForestClassifier
-from tqdm import tqdm
-
-from prelearning import get_covered_samples, surrogate_precision
-
-sys.path.append("NewLIME")
-# pylint: disable=import-error,wrong-import-position
-import newlime_tabular  # pyright: ignore[reportMissingImports] # noqa: E402
-import newlime_utils  # pyright: ignore[reportMissingImports] # noqa: E402
-
-
-def main() -> None:
-    """Main function."""
-
-    # Load the dataset.
-    balanced = newlime_utils.load_dataset(
-        "recidivism", "NewLIME/anchor-experiments/datasets/", balance=True
-    )
-    imbalanced = newlime_utils.get_imbalanced_dataset(balanced, 0.10)
-
-    # Set the hyper-parameters for NewLIME.
-    hyper_param = newlime_tabular.HyperParam(
-        delta=0.05,
-        epsilon=0.05,
-        epsilon_stop=0.05,
-        beam_size=10,
-        batch_size=1000,
-        desired_confidence=0.70,
-        coverage_samples_num=10000,
-        max_rule_length=None,
-    )
-
-    for dataset in [imbalanced, balanced]:
-        # Learn the black box model.
-        black_box = RandomForestClassifier(n_estimators=100, n_jobs=5)
-        black_box.fit(dataset.train, dataset.labels_train)
-
-        # Print the number of labels in the dataset.
-        print_labels_count(dataset, black_box)
-
-        # Print the precision, recall, and coverage of the surrogate model
-        # returned by NewLIME under the rule.
-        idx_list = random.sample(range(len(dataset.test)), 10)
-        trgs = dataset.test[idx_list]
-        explainer = newlime_tabular.NewLimeTabularExplainer(
-            dataset.class_names,
-            dataset.feature_names,
-            dataset.train,
-            dataset.categorical_names,
-        )
-        sum_vals = [0.0, 0.0, 0.0]
-        names = ["Precision", "Recall", "Coverage"]
-        for trg in tqdm(trgs):
-            vals = get_prec_and_recall(
-                explainer, hyper_param, black_box, dataset, trg
-            )
-            sum_vals = [sum_val + val for sum_val, val in zip(sum_vals, vals)]
-
[…]

### 2024-08-15 src/experiments/exp_adv/prelearning.py

@@ -1,210 +1,0 @@
-"""This module generates the experiment data for the paper. The data is used to
-measure the gap between the precision returned by NewLIME and the true
-precision under the rule. The gap is calculated by the following formula:
-
-        gap = returned_precision - true_precision
-
-The gap is calculated for each target sample. The mean and the standard
-deviation of the gaps are calculated for all the target samples. The mean and
-the standard deviation are used to evaluate the performance of NewLIME. The
-smaller the mean and the standard deviation are, the better the performance of
-NewLIME is.
-"""
-
-import multiprocessing
-import sys
-from typing import Any
-
-import numpy as np
-import pandas as pd
-from river import compose
-from sklearn.ensemble import RandomForestClassifier
-from tqdm import tqdm
-
-sys.path.append("../NewLIME")
-
-
-# pylint: disable=import-error,wrong-import-position
-import newlime_tabular  # pyright: ignore[reportMissingImports] # noqa: E402
-import newlime_utils  # pyright: ignore[reportMissingImports] # noqa: E402
-
-
-def main() -> None:
-    """Main function."""
-
-    # Set the hyperparameters.
-    hyper_param = newlime_tabular.HyperParam(
-        tau=0.80,
-        delta=0.05,
-        epsilon=0.05,
-        epsilon_stop=0.05,
-        beam_size=10,
-        batch_size=1000,
-        init_sample_num=0,
-        coverage_samples_num=1000,
-        max_rule_length=None,
-    )
-
-    # Set the number of processes.
-    process_num = 16
-
-    # Set the number of target samples for each process.
-    samples_num = 200
-
-    # Load the dataset.
-    dataset = newlime_utils.load_dataset(
-        "recidivism", "../NewLIME/anchor-experiments/datasets/", balance=True
-    )
-
-    # Learn the black box model.
-    black_box = RandomForestClassifier(n_estimators=100, n_jobs=5)
-    black_box.fit(dataset.train, dataset.labels_train)
-
-    processes = []
-    result_list = multiprocessing.Manager().list()
-
-    # Measure the gap between the precision returned by NewLIME and the true
-    # precision. Caluculating the gap is time-consuming, so we use multiple
-    # processes to accelerate the calculation.
-    for i in range(process_num):
-        np.random.seed(i)
-        process = multiprocessing.Process(
-            target=measure_gap,
-            args=(samples_num, dataset, black_box, hyper_param, result_list),
-        )
-        process.start()
[…]

### 2025-03-08 main.tex
fix(action): rename main file

--- 2024-08-15 paper.tex
@@
 % Command '\usepackage{amsmath}' results in the following warning:
+% ------------------------------
 % Package amsmath Warning: Unable to redefine math accent \vec.
+% ------------------------------
+% cf. https://tex.stackexchange.com/questions/102507/how-to-fix-this-amsmath-warning-about-redefining-vec
 \RequirePackage{amsmath} % for environments such as align
@@
 \documentclass[runningheads]{llncs}
-
-% If possible, figure files should be included in EPS format.
-
-% If you use the hyperref package, please uncomment the following two lines
-% to display URLs in blue roman font according to Springer's eBook style:
-%\usepackage{color}
-%\renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 \usepackage{array} % for m column type
-% \usepackage{bbm} % for \mathbbm
-\usepackage{dsfont}
-\newcommand{\mathbbm}[1]{\mathds{#1}}
 \usepackage{booktabs} % for \toprule, \midrule, \bottomrule
+
 \usepackage{cleveref} % for \cref
 \usepackage{csvsimple} % for \csvreader
+\usepackage{dsfont} % for \mathds
 \usepackage[T1]{fontenc} % for T1 font encoding
@@
 
-% set the path for figures
-\graphicspath{{./src/img}{./src/experiments}}
-
 % set the label format for subcaption
@@
 \input{src/tex/macro}
-
-% TODO REBUTTAL: Please enter paper ID
-\def\paperID{735} % *** Enter the paper ID here
 
@@
   Sapporo 060--0814, JAPAN,\\
-  \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}
+  \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}
+}
 
@@
     \centering
-    \includegraphics[scale=\scale]{example-instance}
+    \includegraphics[scale=\scale]{src/img/example-instance}
     \caption{Focal point.}\label{fig:example-instance}
@@
       \centering
-      \includegraphics[scale=\scale]{example-lime}
+      \includegraphics[scale=\scale]{src/img/example-lime}
       \caption{%
@@
       \centering
-      \includegraphics[scale=\scale]{example-anchor}
+      \includegraphics[scale=\scale]{src/img/example-anchor}
       \caption{%
@@
     \vspace{-2.24cm}
-    \includegraphics[scale=\scale]{example-rlime}
+    \includegraphics[scale=\scale]{src/img/example-rlime}
     \caption{%
@@
     \centering
-    \includegraphics[width=\textwidth]{visual-lime}
+    \includegraphics[width=\textwidth]{src/img/visual-lime}
     \caption{%
@@
     \centering
-    \includegraphics[width=\textwidth]{visual-anchor}
+    \includegraphics[width=\textwidth]{src/img/visual-anchor}
     \caption{%
@@
     \centering
-    \includegraphics[width=\textwidth]{visual-rlime3}
+    \includegraphics[width=\textwidth]{src/img/visual-rlime3}
     \caption{%
@@
   \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
-  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor-def-prec} \\
+  [\mathds{1}_{f(z)=f(x)}], \label{eq:anchor-def-prec} \\
   \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)],
@@
   \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
-  [\mathbbm{1}_{f(z)=g(z)}], \label{eq:def-prec}
+  [\mathds{1}_{f(z)=g(z)}], \label{eq:def-prec}
 \end{equation}
@@
     \centering
-    \includegraphics[width=0.32\textwidth]{visual-rlime1}
-    \includegraphics[width=0.32\textwidth]{visual-rlime2}
-    \includegraphics[width=0.32\textwidth]{visual-rlime3}
+    \includegraphics[width=0.32\textwidth]{src/img/visual-rlime1}
+    \includegraphics[width=0.32\textwidth]{src/img/visual-rlime2}
+    \includegraphics[width=0.32\textwidth]{src/img/visual-rlime3}
     \caption[Overview of the R-LIME algorithm]{%
@@
 By sampling $z\sim\mathcal{D}(\cdot|A_i)$
-and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial,
+and obtaining the reward $\mathds{1}_{f(z)=g_i(z)}$ for each trial,
 the algorithm updates $g_i$ using $z$ and $f(z)$ after each trial.
@@
           \hspace{-10pt}
-          \includegraphics[scale=\scale]{exp1/lime-0012}
+          \includegraphics[scale=\scale]{src/experiments/exp1/lime-0012}
           \caption{LIME}\label{fig:lime-0}
@@
           \centering
-          \includegraphics[scale=0.33]{exp1/anchor-0012-70}  % chktex 8
+          \includegraphics[scale=0.33]{src/experiments/exp1/anchor-0012-70}  % chktex 8
           \caption{Anchor ($\tau=0.70$)}\label{fig:anchor-0-70}
@@
           \centering
-          \includegraphics[scale=0.33]{exp1/anchor-0012-90}  % chktex 8
+          \includegraphics[scale=0.33]{src/experiments/exp1/anchor-0012-90}  % chktex 8
           \caption{Anchor ($\tau=0.90$)}
@@
           \hspace{-5pt}
-          \includegraphics[scale=\scale]{exp1/rlime-0012-70}  % chktex 8
+          \includegraphics[scale=\scale]{src/experiments/exp1/rlime-0012-70}  % chktex 8
           \vspacebeforecaption{}
@@
           \hspace{-17pt}
-          \includegraphics[scale=\scale]{exp1/rlime-0012-90}  % chktex 8
+          \includegraphics[scale=\scale]{src/experiments/exp1/rlime-0012-90}  % chktex 8
           \vspacebeforecaption{}
@@
           \hspace{-26.5pt}
-          \includegraphics[scale=\scale]{exp1/lime-0011}
+          \includegraphics[scale=\scale]{src/experiments/exp1/lime-0011}
           \caption{LIME}\label{fig:lime-1}
@@
           \centering
-          \includegraphics[scale=0.33]{exp1/anchor-0011-70}  % chktex 8
+          \includegraphics[scale=0.33]{src/experiments/exp1/anchor-0011-70}  % chktex 8
           \caption{Anchor ($\tau=0.70$)}
@@
           \centering
-          \includegraphics[scale=0.33]{exp1/anchor-0011-90}  % chktex 8
+          \includegraphics[scale=0.33]{src/experiments/exp1/anchor-0011-90}  % chktex 8
           \caption{Anchor ($\tau=0.90$)}
@@
           \hspace{-5pt}
-          \includegraphics[scale=\scale]{exp1/rlime-0011-70}  % chktex 8
+          \includegraphics[scale=\scale]{src/experiments/exp1/rlime-0011-70}  % chktex 8
           \vspacebeforecaption{}
@@
           \hspace{-20pt}
-          \includegraphics[scale=\scale]{exp1/rlime-0011-90}  % chktex 8
+          \includegraphics[scale=\scale]{src/experiments/exp1/rlime-0011-90}  % chktex 8
           \vspacebeforecaption{}
@@
     \centering
-    \includegraphics[scale=0.36,valign=t]{exp2/box_plot}
+    \includegraphics[scale=0.36,valign=t]{src/experiments/exp2/box_plot}
     \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
@@
     \centering
-    \includegraphics[scale=0.35,valign=t]{exp2/comp_cov}
+    \includegraphics[scale=0.35,valign=t]{src/experiments/exp2/comp_cov}
     \vspace{3pt}
@@
       \centering
-      \includegraphics[width=0.7\textwidth]{visual-rlime3}
+      \includegraphics[width=0.7\textwidth]{src/img/visual-rlime3}
       \caption{R-LIME for balanced label distribution.}
@@
       \centering
-      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
+      \includegraphics[width=0.7\textwidth]{src/img/visual-rlime-imbalanced}
       \caption{R-LIME for imbalanced label distribution.
@@
     \left(
-    \mathbb{E}_{z\sim\mathcal{D}(z\mid A)}[\mathbbm{1}_{f(z)=1}]-\frac{1}{2}
+    \mathbb{E}_{z\sim\mathcal{D}(z\mid A)}[\mathds{1}_{f(z)=1}]-\frac{1}{2}
     \right)
